### 2015-09-28 smoothed.tex
smoothed.tex is added.

\documentclass{article}

\usepackage{textcomp}
\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\usepackage{cite}
\usepackage{float}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{simplemargins}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{url}

\usepackage{etoolbox}
\usepackage{lipsum}

\setallmargins{1in}
\onehalfspacing

\linespread{1.8} % line space

\patchcmd{\thebibliography}{\section*}{\section*}{}{}

% don't need the following. simply use defaults
%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
%\setlength{\parskip}{3pt plus 2pt}
%\setlength{\parindent}{20pt}
%\setlength{\oddsidemargin}{0.5cm}
%\setlength{\evensidemargin}{0.5cm}
%\setlength{\marginparsep}{0.75cm}
%\setlength{\marginparwidth}{2.5cm}
%\setlength{\marginparpush}{1.0cm}
%\setlength{\textwidth}{150mm}

\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
%\author{

%\begin{center}
%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave. Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave. Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\

%\end{center}

% }

\begin{document}
%\thispagestyle{empty}
\maketitle

\newpage

\begin{center}
\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave. Memphis TN 38152 \\ Phone (901) 678-2007\\
\vspace{10 mm}
 \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
\vspace{10 mm}
\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
\vspace{10 mm}
\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\

\end{center}

\newpage

\begin{abstract}
In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs. We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity. In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells. We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes. We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them. We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude. For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3. To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively. Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.  We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran. The horizontal peak ground acceleration is selected as the ground motion parameter. The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions. The seismic hazard map for northern Iran is presented. The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region. The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
\end{abstract}

\smallskip
\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran

\section{Introduction}

Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life. These earthquakes are categorized in various tectonic seismic zones. Different tectonic seismic regions have been defined for Iran in different studies.  Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification. Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}. \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran. Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
\noindent
In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur. Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
\noindent
In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D. The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes. In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}. Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively. These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
\noindent
In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years. At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D. (western segments), 1665 A.D. (eastern segments), and 1830 A.D. (central segments) \cite{Berberian1999}. Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}. Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}. \\
\noindent
Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran. Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models. According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour. Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively. In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran. The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years. In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}. \citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}. They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.  Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures. In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\

In this study we used smoothed seismicity \citep{Frankel1995}. We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh. We computed seismic parameters and catalog completeness in these regions. Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part. We used \citet{Karimiparidari2013} seismicity parameters in these regions.  We consider the MW5 earthquake as a threshold magnitude  for structural damage. In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.

\begin{figure} [H]
\centering
\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
\caption{ a) Map of Iran and surrounding countries. The study area is presented in gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}. }

\label{fig:Iran}
\end{figure}

\noindent
Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region. Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran. Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions. In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity. We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran. This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}. \\
\noindent
Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States. The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis. This method is simpler for hazards calculation and is based solely on recorded seismicity history. In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information. Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty. \citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation. At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.  Surprisingly, they recorded velocity of $0\  mm/yr$. \\
\noindent
The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity. Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California. They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns. \citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia. They defined 4 different models with different correlation distances, including a model based of the total released seismic energy. They gained an acceptable PGA in comparison with other seismic hazard approaches. \citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity. Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones. This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}. We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region. Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.

\section{Seismic regions and seismicity rate}
With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones. Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$). A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}. \citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog. The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities. 
In the present study, historical data are integrated with instrumental data. For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.

\subsection{Alborz Mountain Range (Alborz)}
Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. Here a series of historical earthquakes occurred within a time period of more than 1100 years. Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region. At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression. An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.

\subsection{Azerbaijan}
There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7). However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them. Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.

\subsection{Kopeh Dagh}
The main Kopeh-Dagh fault system has experienced some historic earthquakes. Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran. This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km. 
Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.

\section{Magnitude Conversion}

In this study we use two sets of data, i.e., historical and instrumental seismic catalogs. We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude. Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran. The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type. In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.

\begin{figure} [H]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
\label{fig:historical}
\end{figure}

\section{Declustering}

It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process. Therefore, in order to accomplish this, we declustered the earthquake catalog. In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}. Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.

\begin{figure} [H]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
\label{fig:instrumental}
\end{figure}

\section{Completeness tests}
For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor. To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.   Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.

\begin{figure} [H]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
\label{fig:comptest}
\end{figure}

We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report. Table 1 presents the completeness of catalog of each region for different moment magnitudes.

\begin{table}[h]
\centering
\caption{Completeness threshold of three tectonic seismic regions.}
\begin{tabular}{cccc}
 ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
3-4         & 2004       & 2004   & 2005       \\ \hline
4-5         & 1960       & 1960   & 1960       \\ \hline
5-6         & 1900       & 1900   & 1900       \\ \hline
6-7         & 1844       & 1809   & 1810         \\ \hline
7 $< $    &  85          & -400    & 10         \\ \hline
\end{tabular}
\end{table}

\section{ Gutenberg-Richter Parameters}
For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}. The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package. For smoothed seismicity areas, $b-value$ is assumed constant. The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
\noindent
\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog. In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters. We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code. The updated values are displayed in Table 2. \\
\noindent
Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively. The completeness of each region can be seen easily from the scatter plot of completeness test.

\begin{table}[h]
\centering
\caption{Seismicity parameters for three tectonic seismic regions.}
    \begin{tabular}{ccccc}
    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
    \end{tabular}

\end{table}

\section{Methodology for Hazard calculation}

To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}. In this model, seismic events are spatially gridded to cells. We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ . Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past. \\
\noindent
According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage. In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure. In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
\noindent
According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km). This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$. Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ). The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c. For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}

\begin{equation}
\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
\end{equation}

\noindent
where,  $\tilde{n}_i$  is normalized to preserve the total number of events. $\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell. The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
\noindent
For a grid of sites and by using $\tilde{n}_i$ from Eq. (1), the annual probability of exceeding specified ground motions is calculated. For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site. Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:

\begin{equation}
\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
\end{equation}

\noindent
where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$. Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation. The $b-value$ is considered uniform throughout most of the area. $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$. This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}

\section{Attenuation relationship}
The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard. \citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran. After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59. Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude. Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively. Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.  \citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.    \\

\noindent

The attenuation relationship is:

\begin{equation}
ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
\end{equation}

where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.

\section{Hazard Calculation}

The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity. These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
\noindent
Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.  In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}. Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
\noindent
We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude. We assume magnitude increment as $\Delta_M = 0.1$. In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells. \\
\noindent
Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes. \citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$. \citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy. \citet{Foteva2006} used 10 and 15 km in a different model. Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location. In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}. Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events. Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651. Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively. The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.

\begin{figure} [H]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
\label{fig:10percent}
\end{figure}

\begin{figure} [H]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
\label{fig:2percent}
\end{figure}

\section{Discussion}

Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps. The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years. The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger. Figure 5 presents the map of PGA for 10\% exceedance in 50 years. The highest and the lowest contour values are 0.44g and 0.12g, respectively. The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively. (We disregarded the values in the Caspian Sea and also close to the study region's borders). Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province. Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province. Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}). Many seismic hazard analysis studies have been done in the region based on different methods. Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.

\begin{table}[h]
\centering
\caption{Comparison of PGA, from different studies for selected cities in Northern Iran. (V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}

\hline

	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\ 
	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline

\end{tabular}

\end{table}

According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones. According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones. However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.

\section{Conclusion}

The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs. Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity. According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.  We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data. The results of this paper can be addressed in three main conclusions. First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance. Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity. Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future. As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage). Studying the sensitivity rate of these parameters could develop a more trustworthy result. Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.

\section{Acknowledgements}

 We express our appreciation to Art Frankel, PhD, of the U.S. Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package. We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters. We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog. We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.

\newpage

%\section*{References}

{
\renewcommand{\bibname}{}
\bibliographystyle{ascelike}
\bibliography{PSHA}
}

\end{document}

### 2015-09-28 buildpdf.sh
buildpdf.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+
+pdflatex $1.tex
+bibtex   $1.aux
+pdflatex $1.tex
+pdflatex $1.tex
+
+open -a Adobe\ Acrobat\ Pro.app ${1}.pdf
+
+rm ${1}.fff ${1}.log ${1}.aux ${1}.ttt ${1}.bbl ${1}.lof ${1}.blg ${1}.spl ${1}.out
+
+clear

### 2015-09-28 buildpdf.sh
add a runnig command to the buildpdf.sh

@@ -1,5 +1,6 @@
 #!/bin/bash
 
+# run : ./buildpdf.sh smooth
 
 pdflatex $1.tex
 bibtex   $1.aux

### 2015-09-28 Acknowledgements.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
 \section{Acknowledgements}
@@
 We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 Conclusion.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
 \section{Conclusion}
@@
 Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 Discussion.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
 \section{Discussion}
@@
 However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 GR_param.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
 \section{ Gutenberg-Richter Parameters}
@@
 \end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 Hazard_calculation.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
 \section{Hazard Calculation}
@@
 \end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 MH_calculation.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
 \section{Methodology for Hazard calculation}
@@
 This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 abstract.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
 In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
@@
 The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 attenuation_relationship.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
 \section{Attenuation relationship}
@@
 where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 completness_test.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
 \section{Completeness tests}
@@
 \end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 declustering.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
 \section{Declustering}
@@
 \end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 introduction.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
 \section{Introduction}
-
 Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
@@
 The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 magnitude_conversion.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
 \section{Magnitude Conversion}
@@
 \end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2015-09-28 main.tex
seperate the tex files.

--- 2015-09-28 smoothed.tex
@@
 
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
 \usepackage{xcolor}
@@
 \title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
 
 \begin{document}
-%\thispagestyle{empty}
+
 \maketitle
@@
 \begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
+\input{abstract}
 \end{abstract}
@@
 
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
+\input{content}
 
 \newpage
-
-%\section*{References}
 

### 2015-09-28 buildpdf.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-# run : ./buildpdf.sh smooth
+# run : ./buildpdf.sh main
 
 pdflatex $1.tex
 bibtex   $1.aux

### 2015-10-23 Acknowledgements.tex
Many of Ricardo's comments were addressed.

@@
 Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
+We are also very thankful to Andrzej Kijko, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
+We wish to thank Mehdi Zare, International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
 We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.

### 2015-10-23 Discussion.tex
Many of Ricardo's comments were addressed.

@@
 \caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
+(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012} , Ak2011: \citet{Akbari2011} ) }
 \begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}

### 2015-10-23 MH_calculation.tex
Many of Ricardo's comments were addressed.

@@
 Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
+Category 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
 \\
 \noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
+According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
 In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
+In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation.
+\\
 \noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
+\noindent
+In order to calculate the annual rate ($\lambda$) of exceeding ground motion (u) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
+We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
+number of events bigger than $M_{ref}$) values to incremental (i.e.
+number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values.
+Using Gaussian function we smooth the number of events in each cell.
+The smoothed value $\tilde{n}_i$ is obtained from
 
@@
 \noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
+Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
+Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to
 
@@
 \end{equation}
-
 \noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
+where $k$ and $l$ are denoted as index of distance and magnitude bin.
 $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.

### 2015-10-23 abstract.tex
Many of Ricardo's comments were addressed.

@@
 In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
+We evaluate seismic hazard over whole three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) and part of two tectonic seismic zones (Zagros and Central-East Iran) using smoothed historical seismicity.
 In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.

### 2015-10-23 completness_test.tex
Many of Ricardo's comments were addressed.

@@
 For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
+In order to determine the catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
 Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
 A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
+Fig.~\ref{fig:comptest} (a,b,c) show the plot of earthquake magnitude with time.
+Fig.~\ref{fig:comptest}(d-o) present the cumulative number of earthquake with magnitude, in defined ranges.
+We define a completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
+These times which presents the completeness of the catalog of each region for different moment magnitude are represented at Table 1.
+We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
 
@@
 \end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
 

### 2015-10-23 introduction.tex
Many of Ricardo's comments were addressed.

@@
 We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
+We also consider seismicity of part of Central-East Iran and Zagros regions.
 We computed seismic parameters and catalog completeness in these regions.
@@
 We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
+We consider the $Mw5$ earthquake as a threshold magnitude  for structural damage.
+In order to consider damage to the historical masonry building we also considered $Mw4.5$ as a threshold for structural damage to these kind of building.
 
@@
 The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
+In the present study, historical data are integrated with instrumental data. We use the tectonic seismic division to categorized the data according to the seismic tectonic regions. 
 \subsection{Alborz Mountain Range (Alborz)}
@@
 Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
+At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
+The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
 The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
@@
 The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
+Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879.
+Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.
 
@@
 Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
+This was the strongest earthquake to strike this region since at least 1455.
 The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.

### 2016-01-11 abstract.tex
Rewriting the paper in the springer format.

@@
 For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
+To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5.
 Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
+We also consider the combination of regions as a uniform region.
 We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
@@
 The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
+\textcolor{red}{The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
+The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.}

### 2016-01-11 introduction.tex
Rewriting the paper in the springer format.

@@
 Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
 Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
 \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
+Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).\\
  Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
+Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.
 \\
 \noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
+In the last three decades, different seismic hazard analysis studies \citep[e.g.,][]{Tavakoli1999,Ghodrati2003} substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
 \citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
@@
 
-In this study we used smoothed seismicity \citep{Frankel1995}.
+In this study we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
 We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
@@
 Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the $Mw5$ earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered $Mw4.5$ as a threshold for structural damage to these kind of building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
+We consider the $Mw \  5$ earthquake as a threshold magnitude  for structural damage.
+In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $Mw \  4.5$ as a threshold for structural damage to these kind of building.
 
@@
 Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
+In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
 We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
@@
 The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
 We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
 Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data. We use the tectonic seismic division to categorized the data according to the seismic tectonic regions. 
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.

### 2016-01-11 analysis_parameters.tex
adding new section files, journal of seismology format's file.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
 \newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
+\section{Analysis Parameters}
+\subsection{Magnitude Interval}
 
 In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
+We use the historical catalog which is converted into moment magnitude and reported by \citep{Karimiparidari2013}.
 Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
@@
 
-\section{Declustering}
+\subsection{Minimum Magnitude}
+\subsection{Attenuation Relationship}
+The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
+\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
+After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
+Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
+Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
+Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
+\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
+\\
 
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
+\noindent
 
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
+The attenuation relationship is:
 
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
+\begin{equation}
+ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
+\end{equation}
 
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
+where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
 
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
+\subsection{b-value}
 
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
 For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
@@
 
-\section{Methodology for Hazard calculation}
+\subsection{Catalogue Completness}
+For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
+In order to determine the catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
+Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
+A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
+Fig.~\ref{fig:comptest} (a,b,c) show the plot of earthquake magnitude with time.
+Fig.~\ref{fig:comptest}(d-o) present the cumulative number of earthquake with magnitude, in defined ranges.
+We define a completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
+These times which presents the completeness of the catalog of each region for different moment magnitude are represented at Table 1.
+We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
 
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
-
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
+\begin{figure*} [!ht]
 \centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
+\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
+\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
+\label{fig:comptest}
+\end{figure*}
 
@@
 \centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
+\caption{Completeness threshold of three tectonic seismic regions.}
+\begin{tabular}{cccc}
+ ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
+3-4         & 2004       & 2004   & 2005       \\ \hline
+4-5         & 1960       & 1960   & 1960       \\ \hline
+5-6         & 1900       & 1900   & 1900       \\ \hline
+6-7         & 1844       & 1809   & 1810         \\ \hline
+7 $< $    &  85          & -400    & 10         \\ \hline
 \end{tabular}
-
 \end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}

### 2016-01-11 hazard_analysis_results.tex
adding new section files, journal of seismology format's file.

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
 \newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
+\section{Hazard Analysis Results}
 
@@
 
-\begin{figure} [H]
+\begin{figure*} [!ht]
 \centering
@@
 \label{fig:10percent}
-\end{figure}
+\end{figure*}
 
-\begin{figure} [H]
+\begin{figure*} [!ht]
 \centering
@@
 \label{fig:2percent}
-\end{figure}
+\end{figure*}
 
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}
+\subsection{Uniform Region}
+\subsection{3 Regions}
+\subsection{5 Regions}
+\subsection{Hazard Curve}

### 2016-01-11 springer_main.tex
adding new section files, journal of seismology format's file.

\RequirePackage{fix-cm}

%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[natbib,smallextended]{svjour3}       % onecolumn (second format)

\documentclass[natbib,twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage[a4paper]{geometry}
\usepackage{xcolor}
%\usepackage[margin=1in]{geometry}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
 \usepackage{aps-bibstyle}  % use this style if you upload to .tex file only a part of Bibtex created bbl.
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
 \journalname{Journal of Seismology}
%
% Definitions for the journal names
\newcommand{\aap}{{Astron. Astrophys.}}
\newcommand{\apj}{{Astrophys. J.}}
\newcommand{\grl}{{Geophys. Res. Lett.}}
\newcommand{\solphys}{{Solar Phys.}}
%
\begin{document}

\title{ Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}

\author{Naeem Khoshnevis         \and
             Shima Azizzadehroodpish \and
             Chris H Cramer \and
             Ricardo Taborda}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Naeem Khoshnevis \at
               University of Memphis \\
               Center for Earthquake Research and Information \\
               3890 Central Ave. Memphis TN 38152 \\
              Tel.: +1(901) 678-2007\\
               \email{nkhshnvs@memphis.edu}        
           \and
           Shima Azizzadehroodpish \at
                            University of Memphis \\
               Center for Earthquake Research and Information \\
               Department of Civil Engineering \\
             \email{szzzdhrd@memphis.edu}        
\and
Chris H Cramer \at
                            University of Memphis \\
               Center for Earthquake Research and Information \\
               \email{ccramer@memphis.edu}    
\and
Ricardo Taborda \at
                            University of Memphis \\
               Center for Earthquake Research and Information \\
               \email{rtbrdros@memphis.edu}   
}

\date{Received: date / Accepted: date}

\maketitle

\begin{abstract}
\input{abstract}
\keywords{Seismic hazard \and Spatially smoothed seismicity \and Northern Iran}

\end{abstract}

\input{content}

\newpage
\bibliographystyle{aps-nameyear}      % American Physical Society (APS) style, author-year citations
\bibliography{PSHA}                           % name your BibTeX data base
\nocite{*}

\end{document}

### 2016-01-11 analysis_parameters.tex
Region of interest and Seismic hazard are completed.

@@
 \subsection{Magnitude Interval}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog which is converted into moment magnitude and reported by \citep{Karimiparidari2013}.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
 \subsection{Minimum Magnitude}
@@
 
-\begin{table}[h]
+\begin{table*}[!ht]
 \centering
@@
 
-\end{table}
+\end{table*}
 

### 2016-01-11 seismic_hazard.tex
adding new section files, journal of seismology format's file.
Region of interest and Seismic hazard are completed.

--- 2015-10-23 MH_calculation.tex
@@
-\section{Methodology for Hazard calculation}
+\section{Seismic Hazard}
 
+\subsection{Background}
+
+Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
+Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
+According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
+Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
+In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
+The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
+In this study we use background seismicity to calculate the seismic hazard.Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
+They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
+\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
+They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
+They gained an acceptable PGA in comparison with other seismic hazard approaches.
+\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
+Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
+This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
+
+\subsection{Analysis Method}
+\subsubsection{smoothed seismicity method}
 To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
@@
 Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
+Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_ w5$ .
+Category 5+ and others ($M6+$ and $M7+$) assume that future $M_w 4.5$ events will occur near where they have occurred in the past.
 \\
@@
 According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation.
+In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
 \\
@@
 \noindent
-In order to calculate the annual rate ($\lambda$) of exceeding ground motion (u) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
+In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
 We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
@@
 This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
+
+\subsubsection{ingredients}

### 2016-01-17 analysis_parameters.tex
Chapter 4 is completed.

@@
-\newpage
 \section{Analysis Parameters}
-\subsection{Magnitude Interval}
-\subsection{Minimum Magnitude}
+%\subsection{Magnitude Interval}
+%\subsection{Minimum Magnitude}
 \subsection{Attenuation Relationship}
@@
 Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
+\citet{Kalkan2004} ).
+We also presented the results for  $\pm$ standard deviation.
 \\
@@
 \begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
+\begin{split}
+ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
+b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
+\end{split}
 \end{equation}
@@
 For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
+The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.\\
 \noindent
 \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
+Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively.
+For the north Iran uniform model we used 4.5 as a completeness magnitude.
 In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
 We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
+The updated values are displayed in Table \ref{tab:b_value}.
 \noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
 
@@
     \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
+    ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
+    Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
+    Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
+    Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
+    Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
+    Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
+    Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
     \end{tabular}
-
+ \label{tab:b_value} 
 \end{table*}
 
-\subsection{Catalogue Completness}
+\subsection{Catalog Completness}
 For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-In order to determine the catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-Fig.~\ref{fig:comptest} (a,b,c) show the plot of earthquake magnitude with time.
-Fig.~\ref{fig:comptest}(d-o) present the cumulative number of earthquake with magnitude, in defined ranges.
-We define a completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
-These times which presents the completeness of the catalog of each region for different moment magnitude are represented at Table 1.
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
+\citet{Frankel1995} plotted the cumulative number of events against time for different regions.
+He assumes that from the point that the line become linear, the catalog is complete.
+Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP \citep{Wiemer2001}, \citet{Zare2014} reported the catalog completeness for the study regions.
+World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
+Up to 1961 these data formed the early instrumental period.
+In 1961 the Worldwide Standardized Seismograph Network (WWSSN) was stablished.
+The record of these seismographs considerably improved the seismic catalogs in different part of the world \citep{Shearer2009}.
+Fig.~\ref{fig:completness_scatter} shows the magnitude distribution of events with respect to the time of occurrence of the events.
 
@@
 \centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
+\includegraphics[scale=0.6]{figures/pdf/completness_scatter.pdf} 
+\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c)Central, d)Kopeh Dagh, e)Zagros}
+\label{fig:completness_scatter}
 \end{figure*}
 
-\begin{table}[h]
+ According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions.
+We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
+In order to be able to compare the results with \citet{Zare2014} we merge the data of Azerbaijan and Alborz seismic regions.
+Fig.~\ref{fig:completness_compare_zare_2014_Az_Al} shows the completeness of catalog for earthquakes with different magnitude range in Azerbaijan-Alborz region.
+According to this figure, midrange magnitudes ($ 4 < Mw < 6 $) fairly obey the network developments in 1900 and 1961.
+The completeness thresholds for each magnitude range which are reported by \citet{Zare2014} are shown by dashed green line.
+In this study we follow the \citet{Frankel1995} approach to determine the completeness of each region.
+Even though the approach used by \citet{Frankel1995} will lead to the conservative results, we make sure that we don't use a period of time without knowing the complete number of events.
+Determining the completeness of the catalog is very sensitive to the data.
+Converting earthquake magnitudes from different scales to moment magnitude obviously has some error.
+Having broader range of magnitude will help to minimize these sort of error.
+In this study we consider the magnitude intervals for completeness study as $Mw = 1$.
+
+\begin{figure*} [!ht]
 \centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
+\includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
+\caption{Cumulative number of earthquakes with respect to the time.
+Magnitude range is represented in a box at the top left corner.
+Solid black lines represent the starting of early instrumental (1900) and instrumental (1961) period.
+Green dashed lines represents the completeness threshold reported by \citet{Zare2014}.
+Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
+\label{fig:completness_compare_zare_2014_Az_Al}
+\end{figure*}
+
+\noindent
+Fig.~\ref{fig:comp_test_all_mag} illustrates the completeness of data for each magnitude threshold in five different regions.
+A uniform rise of cumulative number of earthquake in each magnitude range, defines the threshold for catalog completeness.
+We define a completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
+We assume the catalog for earthquakes with magnitude greater than  7 ($M_w > 7$) is complete from the first historical earthquake report.
+Determining the completeness of the catalog for $ 6 < Mw \leq 7 $ needs precise observation of the catalog.
+In Azerbaijan tectonic seismic region after 1045  $Mw = 6.2$ earthquake the catalog seems complete up to 1318.
+However, between 1318 and 1581 (263 years) only one earthquake with magnitude $Mw > 6$ is reported (1440,  $Mw = 6.2$ ).
+Considering the activity of the Azerbaijan region, in this study we assume that the catalog is complete for earthquake with magnitude $ 6 < Mw \leq 7 $ after 1581.
+Similar situation happened at the period of 1715 - 1833.
+It worth to mention that , the time period is shorter than before (118 years), meanwhile in this period of time two earthquakes with magnitude $Mw>7$ occurred in the Azerbaijan region (1721 $Mw=7.7$, 1780 $Mw=7.6$).
+The catalog may or may not be completed after 1045, however in this study we consider 1581 as a completeness threshold for magnitude  $ 6 < Mw \leq 7 $.
+Considering completeness of the catalog for Azerbaijan region from 1581 will result in conservative PGA for the region in compare with the model with threshold of 1045.
+We picked the completeness threshold for other regions and other magnitude ranges according as a year that the cumulative number of earthquakes increment uniformly.
+Table ~\ref{tab:completeness} shows the summary of values used in this study.
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.28]{figures/pdf/comp_test_all_mag.pdf} 
+\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Kopek Dagh, g-h)Kopeh Dagh, i-j)Zagros}
+\label{fig:comp_test_all_mag}
+\end{figure*}
+
+\begin{table*}[!ht]
+\centering
+\caption{Completeness threshold of tectonic seismic regions.}
+\begin{tabular}{ccccccccc}
+ ~           & Azerbaijan & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
+3-4         & 1961          & 2005   & 2005             & 2005            & 2005    & 2005          \\ \hline
+4-5         & 1961          & 1961   & 1950             & 1961            & 1961    & 1961          \\ \hline
+5-6         & 1900          & 1900   & 1900             & 1854            & 1900    & 1900           \\ \hline
+6-7         & 1581          & 1664   & 1673             & 1837            & 1853    & 1778           \\ \hline
+7 $< $    & 1042          & -401    & 9                   & 762              & 1439    & -401            \\ 
 \end{tabular}
-\end{table}
+\label{tab:completeness}
+\end{table*}

### 2016-01-17 hazard_analysis_results.tex
Chapter 4 is completed.

@@
-\newpage
 \section{Hazard Analysis Results}
@@
 Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
+%Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
 The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
+
+\subsection{Hazard Curve}
+We calculated the probability of exceedance of the ground motion from different ground motion levels, separately for each of 5 regions.
+We add the probability of all regions in order to have the effect of seismicity from all tectonic seismic regions.
+The results are presented as annual rate of exceedance.
+Fig.~\ref{fig:hazardcurve} represents the hazard curve of different model for some of important northern cities in Iran.
 
@@
 \centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
+\includegraphics[scale=0.4]{figures/pdf/HazardCurve.pdf} 
+\caption{Seismic Hazard Curve of Northern Cities in Iran}
+\label{fig:hazardcurve}
+\end{figure*}
+
+\subsection{5 Regions}
+We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance. 
+Fig.~\ref{fig:pga_10_mean} and Fig.~\ref{fig:pga_2_mean} show the results for 10\% and 2\% probability of exceedance in 50 years, respectively.
+These results are according to the mean value of the attenuation relationship.
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.3]{figures/pdf/pga_10_mean.pdf} 
+\caption{Peak ground acceleration for 10\% probability of exceedance in 50 years.}
+\label{fig:pga_10_mean}
 \end{figure*}
@@
 \centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
+\includegraphics[scale=0.3]{figures/pdf/pga_2_mean.pdf} 
+\caption{Peak ground acceleration for 2\% probability of exceedance in 50 years.}
+\label{fig:pga_2_mean}
 \end{figure*}
@@
 \subsection{Uniform Region}
-\subsection{3 Regions}
-\subsection{5 Regions}
-\subsection{Hazard Curve}
+Fig.~\ref{fig:pga_10_mean_uniform} and Fig.~\ref{fig:pga_2_mean_uniform} show the results for 10\% and 2\% probability of exceedance in 50 years for the uniform model, respectively.
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.3]{figures/pdf/pga_10_mean_uniform.pdf} 
+\caption{Peak ground acceleration for 10\% probability of exceedance in 50 years (uniform model).}
+\label{fig:pga_10_mean_uniform}
+\end{figure*}
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.3]{figures/pdf/pga_2_mean_uniform.pdf} 
+\caption{Peak ground acceleration for 2\% probability of exceedance in 50 years (uniform model).}
+\label{fig:pga_2_mean_uniform}
+\end{figure*}
+
+%\subsection{3 Regions}

### 2016-01-19 hazard_analysis_results.tex
Section 5 added.

@@
 In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
+Therefore, our study region includes parts of central Iran and the Zagros tectonic seismic regions.\\
 \noindent
@@
 Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
+Regarding the important parameters in determining the location of earhtquake (e.g.
+velocity model, station distribution, number and quality of seismic phases),\citet{Mirzaei1997} believes the uncertainties of the most reliable epicenters are probably at least 10 km.
+In developing of seismic hazard zoning map for Iran,\citet{Zare2012} considered the epicentral uncertainty as 30 km.
+Even though the uncertainties are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
+Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 13561.
 Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-%Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
 

### 2016-01-31 Conclusion.tex
Many of Ricardo's comments were addressed.
Conclusion added.

@@
 \section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
+The result of a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs is provided.
+Seismic hazard is evaluated over entire three regions (Azerbaijan, Alboz, Kopeh-Dagh) as well as part of Central and Zagros tectonic seismic regions using the smoothed background seismicity.
+In order to determine the seismic hazard in North Iran, different studies have been done.
+These studies are based on defining faults as a seismic source model.
+Using faults as a seismic source model could result in accurate values in case the faults are precisely determined.
+There are considerable uncertainties on fault characteristic, specially on fault length.
+Instead of using faults as a seismic source, we consider each earthquake event as a point source in the model.
+We reduce the uncertainty in earthquake location by smoothing the number of earthquake in adjacent cells.
+We defined models based on considering the whole North Iran as a uniform seismic tectonic regions and 5 different seismic tectonic regions.
+The differences in catalog completeness, b value, and maximum magnitude of earthquake in these two models resulted in different results.
+This indicate the idea that dividing regions into subregions is necessary in order to be able to get accurate results.
+The result are also sensitive to the minimum magnitude.
+The structures built according to engineering code are supposed to withstand the earthquake with magnitude 5 at the reasonable distance.
+However, closer $M_w > 4.5$ for those structures and also older masonry structures could cause structural damage.
+A combination of two models $(M_w > 4.5, M_w>5)$ in each city based on number of engineering and old masonry structures will provide more accurate results.
+The results are provided for mean peak horizontal acceleration in bedrock.
+The ground acceleration in soil deposits and inside basin will be bigger than the provided values.
+This model reduce the epistemic uncertainty regarding the recognizing faults and earthquake location.
+Combination of this model with a study based on using faults will increase the values for existing non-active seismic fault regions.

### 2016-01-31 abstract.tex
Conclusion added.

@@
 In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over whole three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) and part of two tectonic seismic zones (Zagros and Central-East Iran) using smoothed historical seismicity.
+We evaluate seismic hazard over whole three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) and part of two tectonic seismic zones (Zagros and Central-East Iran) using smoothed seismicity.
 In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
@@
 The seismic hazard map for northern Iran is presented.
-\textcolor{red}{The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.}

### 2016-01-31 analysis_parameters.tex
working on discussion and conclusion part. Adding annual rate of earthquake figure.
Conclusion added.

@@
 \noindent
-
 The attenuation relationship is:
@@
 The updated values are displayed in Table \ref{tab:b_value}.
+Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.4]{figures/pdf/annual_rate_m.pdf} 
+\caption{Annual occurrence rate of the earthquake. a) Azerbaijan, b) Alborz, c) KopehDagh, d)Central, e)Zagros f) North Iran}
+\label{fig:annual_m}
+\end{figure*}
+
 \noindent
@@
 \includegraphics[scale=0.6]{figures/pdf/completness_scatter.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c)Central, d)Kopeh Dagh, e)Zagros}
+\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c)Central, d)Kopeh-Dagh, e)Zagros}
 \label{fig:completness_scatter}
@@
 
- According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions.
+ According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions' catalog.
 We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
@@
 A uniform rise of cumulative number of earthquake in each magnitude range, defines the threshold for catalog completeness.
-We define a completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
+We define the completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
 We assume the catalog for earthquakes with magnitude greater than  7 ($M_w > 7$) is complete from the first historical earthquake report.
@@
 Similar situation happened at the period of 1715 - 1833.
-It worth to mention that , the time period is shorter than before (118 years), meanwhile in this period of time two earthquakes with magnitude $Mw>7$ occurred in the Azerbaijan region (1721 $Mw=7.7$, 1780 $Mw=7.6$).
+It worth to mention that in this case, the time period is shorter than before (118 years), meanwhile in this period of time two earthquakes with magnitude $Mw>7$ occurred in the Azerbaijan region (1721 $Mw=7.7$, 1780 $Mw=7.6$).
 The catalog may or may not be completed after 1045, however in this study we consider 1581 as a completeness threshold for magnitude  $ 6 < Mw \leq 7 $.

### 2016-01-31 introduction.tex
Conclusion added.

@@
 In the last three decades, different seismic hazard analysis studies \citep[e.g.,][]{Tavakoli1999,Ghodrati2003} substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
+\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the HAZUS method \citep{FEMA2003}.
 They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
@@
 In this study we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
+We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopeh Dagh.
 We also consider seismicity of part of Central-East Iran and Zagros regions.

### 2016-02-23 springer_main.tex
Chapter 4 is completed.
working on discussion and conclusion part. Adding annual rate of earthquake figure.
added correct bst file

@@
 
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[natbib,smallextended]{svjour3}       % onecolumn (second format)
+% Document Settings
+\documentclass[natbib,twocolumn]{svjour3}
 
-\documentclass[natbib,twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
+% Flushing
+\smartqed
+
+% Packages
 \usepackage{graphicx}
-\usepackage[a4paper]{geometry}
 \usepackage{xcolor}
-%\usepackage[margin=1in]{geometry}
+\usepackage{amsmath}
+\usepackage{multirow}
+\usepackage{marvosym}
 
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
 \usepackage{aps-bibstyle}  % use this style if you upload to .tex file only a part of Bibtex created bbl.
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
+
+% Journal Name
 \journalname{Journal of Seismology}
-%
-% Definitions for the journal names
-\newcommand{\aap}{{Astron. Astrophys.}}
-\newcommand{\apj}{{Astrophys. J.}}
-\newcommand{\grl}{{Geophys. Res. Lett.}}
-\newcommand{\solphys}{{Solar Phys.}}
-%
+
+% START: The Document
 \begin{document}
 
-\title{ Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
+% Long Title
+\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity}
 
-\author{Naeem Khoshnevis         \and
-             Shima Azizzadehroodpish \and
-             Chris H Cramer \and
-             Ricardo Taborda}
+% Running Title
+\titlerunning{Seismic Hazard of Northern Iran}
 
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Naeem Khoshnevis \at
-               University of Memphis \\
-               Center for Earthquake Research and Information \\
-               3890 Central Ave. Memphis TN 38152 \\
-              Tel.: +1(901) 678-2007\\
-               \email{nkhshnvs@memphis.edu}        
-           \and
-           Shima Azizzadehroodpish \at
-                            University of Memphis \\
-               Center for Earthquake Research and Information \\
-               Department of Civil Engineering \\
-             \email{szzzdhrd@memphis.edu}        
-\and
-Chris H Cramer \at
-                            University of Memphis \\
-               Center for Earthquake Research and Information \\
-               \email{ccramer@memphis.edu}    
-\and
-Ricardo Taborda \at
-                            University of Memphis \\
-               Center for Earthquake Research and Information \\
-               \email{rtbrdros@memphis.edu}   
+% Authors
+\author{%
+	N.~Khoshnevis \and
+	S.~Azizzadeh-Roodpish \and
+	R.~Taborda \and
+	C.~H.~Cramer
 }
 
-\date{Received: date / Accepted: date}
+% Affiliations
+\institute{%
+	N.~Khoshnevis \and C.~H.~Cramer \at
+	Center for Earthquake Research and Information,
+	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
+	\and
+	S.~Azizzadeh-Roodpish \and R.~Taborda (\Letter)\at
+	Department of Civil Engineering, and
+	Center for Earthquake Research and Information,
+	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
+	\email{ricardo.taborda@memphis.edu}  
+}
 
+% Date
+% \date{Received: date / Accepted: date}
+
+% Title Production
 \maketitle
 
+% Abstract
 \begin{abstract}
 	\input{abstract}
-\keywords{Seismic hazard \and Spatially smoothed seismicity \and Northern Iran}
-
+	\keywords{%
+		Seismic hazard \and 
+		Spatially smoothed seismicity 
+		\and Northern Iran
+	}
 \end{abstract}
 
+% Article Content
 \input{content}
 
-\newpage
-\bibliographystyle{aps-nameyear}      % American Physical Society (APS) style, author-year citations
-\bibliography{PSHA}                           % name your BibTeX data base
-\nocite{*}
+% Bibliography
+\bibliographystyle{spbasic}
+\bibliography{PSHA}
+% \nocite{*}
 
+% END: The Document
 \end{document}

### 2016-02-23 main.tex
start to restructure the paper.
finished first clean-up of main file

@@
-\documentclass{article}
+\RequirePackage{fix-cm}
 
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
+% Document Settings
+\documentclass[natbib,twocolumn]{svjour3}
+
+% Flushing
+\smartqed
+
+% Packages
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage{amsmath}
 \usepackage{multirow}
-\usepackage{url}
+\usepackage{marvosym}
 
-\usepackage{etoolbox}
-\usepackage{lipsum}
+% Journal Name
+\journalname{Journal of Seismology}
 
-\setallmargins{1in}
-\onehalfspacing
+% START: The Document
+\begin{document}
 
-\linespread{1.8} % line space
+% Long Title
+\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity}
 
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
+% Running Title
+\titlerunning{Seismic Hazard of Northern Iran}
 
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
+% Authors
+\author{%
+	N.~Khoshnevis \and
+	S.~Azizzadeh-Roodpish \and
+	R.~Taborda \and
+	C.~H.~Cramer
 }
 
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
+% Affiliations
+\institute{%
+	N.~Khoshnevis \and C.~H.~Cramer \at
+	Center for Earthquake Research and Information,
+	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
+	\and
+	S.~Azizzadeh-Roodpish \and R.~Taborda (\Letter)\at
+	Department of Civil Engineering, and
+	Center for Earthquake Research and Information,
+	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
+	\email{ricardo.taborda@memphis.edu}  
+}
 
-\begin{document}
+% Date
+% \date{Received: date / Accepted: date}
 
+% Title Production
 \maketitle
 
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
+% Abstract
 \begin{abstract}
 	\input{abstract}
+	\keywords{%
+		Seismic hazard \and 
+		Spatially smoothed seismicity 
+		\and Northern Iran
+	}
 \end{abstract}
 
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
+% Article Content
 \input{content}
 
-\newpage
+% Bibliography
+\bibliographystyle{spbasic}
+\bibliography{PSHA}
+% \nocite{*}
 
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
+% END: The Document
 \end{document}

### 2016-02-26 abstract.tex
working on the abstract...

@@
+% 
+This article presents a seismic hazard assessment for northern Iran, using a smoothed seismicity approach in combination with an updated seismic catalog and a recently introduced ground motion prediction equation.
+In the assessment, we evaluate the hazard considering the contribution of the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh.
+For completeness, we also consider the partial contribution of the two remaining seismic zones of Zagros and the central and eastern
+
+% Ricardo is working on this...
+
+,  and
+
+recently introduced
+
+ We conduct an assessment of seismic hazard for northern Iran using
+
 In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.

### 2016-02-26 abstract.tex
completed first revision of abstract

--- 2016-01-31 abstract.tex
@@
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
+% 
+This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a recently introduced ground motion prediction equation.
+We evaluate the hazard considering over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, and for completeness, we also consider the partial contribution of the two remaining seismic zones, that is, Zagros to the south-west, and the central and eastern Iranian seismic zone.
+Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree in both the latitude and longitude directions.
+After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events with magnitude greater than 3 within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
+Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
+Seismicity parameters are calculated and smoothed for each region separately, and for comparison purposes, we also consider the combination of all the seismic zones as a uniform region.
+Seismic hazard curves are first obtained for two distinct models defined on two structural risk scenarios based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, and then combined into a single one to account for the proportion of reinforced and unreinforced structures.
+The results are presented in terms of expected peak ground acceleration curves and hazard maps and considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, and compared to equivalent estimations available in the literature at selected locations.
+Despite some localized differences \textcolor{red}{[???]}, we find our results to be in good agreement with previous results.
+Therefore, we find the method used here is appropriate to estimate seismic hazard for northern Iran.
+We conclude with an analysis of the results and its implications for the region, and highlight...
+or offer some additional thoughts about...
+\textcolor{red}{[Naeem: what would you say is the main conclusion or major finidng?]}.
+
+% Naeem's original abstract
+
+% In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
 We evaluate seismic hazard over whole three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) and part of two tectonic seismic zones (Zagros and Central-East Iran) using smoothed seismicity.

### 2016-02-26 abstract.tex
polished abstract

@@
 This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a recently introduced ground motion prediction equation.
-We evaluate the hazard considering over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, and for completeness, we also consider the partial contribution of the two remaining seismic zones, that is, Zagros to the south-west, and the central and eastern Iranian seismic zone.
+We evaluate the hazard over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan to the northwest, the Alborz Mountain Range in the northern-central region of Iran, and Kopeh-Dagh to the northeast.
+For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zone.
 Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree in both the latitude and longitude directions.
@@
 or offer some additional thoughts about...
-\textcolor{red}{[Naeem: what would you say is the main conclusion or major finidng?]}.
+\textcolor{red}{[Naeem: what would you say is the main conclusion or major finding?]}.
 

### 2016-02-26 abstract.tex
Put comments on Abstract.

@@
 % 
-This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a recently introduced ground motion prediction equation.
-We evaluate the hazard over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan to the northwest, the Alborz Mountain Range in the northern-central region of Iran, and Kopeh-Dagh to the northeast.
+This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a recently introduced ground motion prediction equation \textcolor{red}{ (The attenuation relationship \citep{Kalkan2004} has been introduced in 2004 (Not recently).
+In 2014, \citet{Zafarani2014} evaluated many different attenuation relationship based on recently recorded data.
+They found \citet{Kalkan2004} has the best fit with data for PGA.)}.
+We evaluate the hazard over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan to the northwest \textcolor{red}{(I'm not sure "Azerbaijan to the northwest" is correct.
+Because the whole area is Azerbaijan.)}, the Alborz Mountain Range in the northern-central region of Iran, and Kopeh-Dagh to the northeast \textcolor{red}{(Please see the comment on Azerbaijan)}.
 For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zone.
 Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree in both the latitude and longitude directions.
-After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events with magnitude greater than 3 within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
+After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events with magnitude greater than 3 \textcolor{red}{(We used earthquake with magnitude 3 and greater only after 2000, before that data are greater than 4.)} within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
 Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
@@
 The results are presented in terms of expected peak ground acceleration curves and hazard maps and considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, and compared to equivalent estimations available in the literature at selected locations.
-Despite some localized differences \textcolor{red}{[???]}, we find our results to be in good agreement with previous results.
+Despite some localized differences \textcolor{red}{[???]}, we find our results to be in good agreement with previous results \textcolor{red}{(We may need to write the conclusion from other point of view.
+The method, attenuation relationship, and  even data (some sort of) are different from other studies.
+So we expect to see different results.
+Not only we expect but at some point we should see some differences because of the method.
+There are some places that we don't have any recorded earthquake or they are not  as much to increase the hazard.
+In this study for those places we get lower hazard, but in studies based on recognizing faults as a source, they ends up with higher hazard.
+I think we can say that even though the other studies are good, but they are not complete and we need to use this method alongside them.)}.
 Therefore, we find the method used here is appropriate to estimate seismic hazard for northern Iran.

### 2016-02-26 introduction.tex
working on introduction...

@@
 \section{Introduction}
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
+
+% Naeem's original Introduction
+
+% Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
 The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
@@
 \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).\\
+Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
 Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
 Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.
-\\
-\noindent
-In the last three decades, different seismic hazard analysis studies \citep[e.g.,][]{Tavakoli1999,Ghodrati2003} substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
+
+% In the last three decades, different seismic hazard analysis studies \citep[e.g.,][]{Tavakoli1999,Ghodrati2003} substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
 \citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the HAZUS method \citep{FEMA2003}.
@@
 
-In this study we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
+% In this study we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
 We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopeh Dagh.
@@
 
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
+% Recently, northern Iran has been studied in detail from different seismological points of view.
 \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
@@
 This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
+
+% Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
 The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
@@
 Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
+
+% The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
 We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.

### 2016-02-27 abstract.tex
making progress with the introduction

--- 2016-02-26 abstract.tex
@@
 % 
-This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a recently introduced ground motion prediction equation.
-We evaluate the hazard considering over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, and for completeness, we also consider the partial contribution of the two remaining seismic zones, that is, Zagros to the south-west, and the central and eastern Iranian seismic zone.
-Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree in both the latitude and longitude directions.
-After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events with magnitude greater than 3 within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
+This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data.
+We evaluate the hazard over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh.
+For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zones.
+Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both the latitude and longitude directions.
+After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
 Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
 Seismicity parameters are calculated and smoothed for each region separately, and for comparison purposes, we also consider the combination of all the seismic zones as a uniform region.
-Seismic hazard curves are first obtained for two distinct models defined on two structural risk scenarios based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, and then combined into a single one to account for the proportion of reinforced and unreinforced structures.
-The results are presented in terms of expected peak ground acceleration curves and hazard maps and considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, and compared to equivalent estimations available in the literature at selected locations.
-Despite some localized differences \textcolor{red}{[???]}, we find our results to be in good agreement with previous results.
-Therefore, we find the method used here is appropriate to estimate seismic hazard for northern Iran.
-We conclude with an analysis of the results and its implications for the region, and highlight...
-or offer some additional thoughts about...
-\textcolor{red}{[Naeem: what would you say is the main conclusion or major finidng?]}.
+Seismic hazard curves obtained for two distinct models defined according to two structural risk scenarios.
+These scenarios are based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 for unreinforced and informal construction, and greater than 5.0 for modern structures following design regulations.
+We also present results for a combined scenario based on the proportion of reinforced and unreinforced structures.
+The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the difference observed due to the intrinsic differences in the methods employed here in light of results obtained by other previous studies.
+In conclusion, we find our results to be helpful in understanding seismic hazard for norther Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain a more robust estimates at specific areas of interest.
+
+% -------------------------
+
+% Naeem's comment about differences with previous studies...
+
+% We may need to write the conclusion from other point of view.
+The method, attenuation relationship, and even data (some sort of) are different from other studies.
+So we expect to see different results.
+Not only we expect but at some point we should see some differences because of the method.
+There are some places that we don't have any recorded earthquake or they are not  as much to increase the hazard.
+In this study for those places we get lower hazard, but in studies based on recognizing faults as a source, they ends up with higher hazard.
+I think we can say that even though the other studies are good, but they are not complete and we need to use this method alongside them.
+
+% Naeem's comment about GMPE...
+
+% The attenuation relationship \citep{Kalkan2004} has been introduced in 2004 (Not recently).
+In 2014, \citet{Zafarani2014} evaluated many different attenuation relationship based on recently recorded data.
+They found \citet{Kalkan2004} has the best fit with data for PGA.
+
+% Naeem's info about magnitude selection...
+
+% We used earthquake with magnitude 3 and greater only after 2000, before that data are greater than 4.
+
+% -------------------------
 

### 2016-02-27 introduction.tex
making progress with the introduction

@@
 \section{Introduction}
+
+This article presents a new seismic hazard assessment for northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to be the most reliable attenuation relationship to predict peak ground response in the region.
+The Iranian plateau is located on the Himalayan-Alpine seismic belt.
+It is confined between the convergent movements of the Arabian and Eurasian plates, and laterally trapped between the Arabian and eastern Asia-Minor to the west, and the Indian and Eurasian plates to the east.
+This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges \citep[e.g.,][]{Berberian_1981_Chap}.
+It also defines the seismic activity of the region, one with a long history of large magnitude ($M>7$) earthquakes dating back to the eight century, which has repeatedly damage Iran's infrastructure and taken the lives of thousands.
+
+According to this tectonic setting and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, and up to twenty to twenty-three seismotectonic provinces in the more elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
+Contemporary, well-accepted studies divide Iran into five major tectonic regions: Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran \citep[e.g.,][]{Mirzaei1998}.
+More recently, in a study aimed to develop a uniform earthquake catalog for Iran, \citet{Karimiparidari2013} further divided the Azerbaijan-Alborz region into two separate seismic zones: Azerbaijan and the Alborz Mountain Range, hereafter referred to simply as Alborz.
+We adopt the latter definition of six seismic basic seismic zones and focus our attention on those most relevant to the northern part of the country, that is, Azerbaijan, Alborz and Kopeh-Dagh.
+
+Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}].
+These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}}.
+While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk in high and therefore more complete and accurate assessments of seismic hazard are necessary.
+
+We are particularly interested in the assessment of seismic hazard in northern Iran.
+This region has a significant population density with respect to the rest of the country, and includes some of its most populated cities: Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht.
+These cities alone house about 31.5 million people.
+They represent nearly 40 percent of the total population of Iran and a good portion of its economic activity.
+In this study we ...
+
+In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
 

### 2016-02-27 introduction.tex
making progress with the introduction

@@
 Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}].
-These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}}.
-While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk in high and therefore more complete and accurate assessments of seismic hazard are necessary.
+These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
+While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk is high and therefore more complete and accurate assessments of seismic hazard are necessary.
 

### 2016-02-28 introduction.tex
working on introduction

@@
 These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk is high and therefore more complete and accurate assessments of seismic hazard are necessary.
+While improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest high levels of seismic and therefore more complete and accurate assessments of seismic hazard, that incorporate the latest available data and alternative methods, are necessary.
 
-We are particularly interested in the assessment of seismic hazard in northern Iran.
-This region has a significant population density with respect to the rest of the country, and includes some of its most populated cities: Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht.
-These cities alone house about 31.5 million people.
-They represent nearly 40 percent of the total population of Iran and a good portion of its economic activity.
-In this study we ...
+In this article, we are particularly interested in the assessment of the seismic hazard of northern Iran.
+This region houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht; and has suffered the devastating effects of earthquakes in the past (e.g., \textcolor{red}{two references}).
+Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Ghodrati2011, Abdollahzadeh2014a, Boostan2015} \textcolor{red}{[Are these good references?
+we need them to be about northern Iran.
+Any other?]}.
+In general, these studies highlight the significant seismic hazard of the region, and...
+\textcolor{red}{[need punch line conclusions here]}.
+However useful, most previous studies focus on particular locations (e.g., Tehran) or are based on the categorization of seismogenic faults, which are often subjectively interpreted and limited to the availability data.
+Here, we use the smoothed seismicity method introduced by \citep{Frankel1995}.
+This approach to map seismic hazard has been used with success in other regions (\textcolor{red}{[two references needed here]}).
+Its major feature is the treatment of recorded and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
+While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to reduce the uncertainty associated with fault mapping and
 
+The method is solely based on cataloged
+
+features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
+This method is simpler for hazards calculation and is based solely on recorded seismicity history.
+In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
+
+% To assess the seismic hazard for this region, we use the smoothed seismicity method introduced by \citep{Frankel1995}.
+In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh; but for completeness, we also consider the partial contribution of the areas of Zagros and the central-east seismic zones within our domain of interest (see Figure \ref{fig:Iran}).
+
+% Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
+The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
+This method is simpler for hazards calculation and is based solely on recorded seismicity history.
+In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
+Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
+\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
+At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
+Surprisingly, they recorded velocity of $0\  mm/yr$.
+
+An important aspect of seismic hazard is the proper definition of attenuation parameters.
+In a recent effort, \citet{Zafarani2014} reviewed multiple available ground motion prediction equations available in the literature and concluded that the most appropriate attenuation relationship to be used in northern Iran, int he Alborz and Kopeh-Dagh regions, was
+
+% \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
+The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
+
+\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
+The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
+Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
+
+which may cause significant damage to northern Iran.
+Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
+In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
+We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
+This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
+
+has a significant population density
+
+with respect to the rest of the country, and includes some of its most populated cities: . Not accounting for rural areas,
+
+these cities house about 31.5 million people, which represents nearly 40 percent of the total population of Iran.
+
+Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh.
+For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zones.
+
+we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
+We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopeh Dagh.
+We also consider seismicity of part of Central-East Iran and Zagros regions.
+We computed seismic parameters and catalog completeness in these regions.
+Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
+We consider the $Mw \  5$ earthquake as a threshold magnitude  for structural damage.
+In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $Mw \  4.5$ as a threshold for structural damage to these kind of building.
+
+% Naeem's original Introduction
+
+% in which many destructive earthquakes have been reported.
+
+% continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
 In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
+
+% In this study we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
+We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopeh Dagh.
+We also consider seismicity of part of Central-East Iran and Zagros regions.
+We computed seismic parameters and catalog completeness in these regions.
+Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
+We consider the $Mw \  5$ earthquake as a threshold magnitude  for structural damage.
+In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $Mw \  4.5$ as a threshold for structural damage to these kind of building.
+
+% Recently, northern Iran has been studied in detail from different seismological points of view.
+\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
+The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
+Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
+Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
+In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
+We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
+This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
+
+% Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
+The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
+This method is simpler for hazards calculation and is based solely on recorded seismicity history.
+In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
+Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
+\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
+At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
+Surprisingly, they recorded velocity of $0\  mm/yr$.
+
+% The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
+We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
+Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
 

### 2016-02-29 introduction.tex
finished first revision of introduction - now close to final

--- 2016-02-27 introduction.tex
@@
 These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-While such improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest that seismic risk is high and therefore more complete and accurate assessments of seismic hazard are necessary.
+While improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest high levels of seismic and therefore more complete and accurate assessments of seismic hazard, that incorporate the latest available data and alternative methods, are necessary.
 
-We are particularly interested in the assessment of seismic hazard in northern Iran.
-This region has a significant population density with respect to the rest of the country, and includes some of its most populated cities: Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht.
-These cities alone house about 31.5 million people.
-They represent nearly 40 percent of the total population of Iran and a good portion of its economic activity.
-In this study we ...
+In this article, we are particularly interested in the assessment of the seismic hazard of northern Iran.
+This region houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht; and has suffered the devastating effects of earthquakes in the past (e.g., \textcolor{red}{two references}).
+Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Ghodrati2011, Abdollahzadeh2014a, Boostan2015} \textcolor{red}{[Are these good references?
+we need them to be about northern Iran.
+Any other?]}.
+In general, these studies highlight the significant seismic hazard of the region, and...
+\textcolor{red}{[need punch line conclusions here]}.
 
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
+However useful, most previous studies focus on particular locations or are based on specific categorization of seismogenic faults, which are often subjectively interpreted and limited to the availability data.
+Here, we use the smoothed seismicity method introduced by \citet{Frankel1995}.
+This approach has been used with success in other regions (\textcolor{red}{[two references needed here]}).
+Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
+While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to reduce the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
+In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh; but for completeness, we also consider the partial contribution of the areas of Zagros and the central-east seismic zones within our domain of interest (see Figure \ref{fig:Iran}).
+In addition, for comparison purposes, we obtain results for the the combination of all seismic zones as a uniform region.
+
+In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the approach followed to estimate seismic hazard for the region.
+Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region \citep{Zafarani2014, Kalkan2004}, and the estimation of the Gutenberg-Richter seismicity parameters, which are necessary for the smoothed seismicity method.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+We consider two hazard models based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ 4.5 and 5.0 for unreinforced and reinforced structures, respectively; and later combine these results into a single analysis based on the composition of the structural building inventory of the country.
+We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.
+
+% *********************************************************************************************************************
+% *********************************************************************************************************************
+
+% Pieces of text in original introduction that could or should be used later
+% --------------------------------------------------------------------------
+
+% \citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the HAZUS method \citep{FEMA2003}.
+They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
+
+% Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
+The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
+This method is simpler for hazards calculation and is based solely on recorded seismicity history.
+In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
+\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
+At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
+Surprisingly, they recorded velocity of $0\  mm/yr$.
+
+% An important aspect of seismic hazard is the proper definition of attenuation parameters.
+In a recent effort, \citet{Zafarani2014} reviewed multiple ground motion prediction equations available in the literature and concluded that the most appropriate attenuation relationship to be used in northern Iran was \citet{Kallan2004}
+
+% \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
+The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
+Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
+
+% In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
+We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
+This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
+
+% Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
+In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
+We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
+This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
+
+% We computed seismic parameters and catalog completeness in these regions.
+Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
+In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $M_w$ 4.5 as a threshold for structural damage.
+
+% The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
+Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
+
+% *********************************************************************************************************************
+% *********************************************************************************************************************
 
 % Naeem's original Introduction
+% -----------------------------
 

### 2016-02-29 abstract.tex
finished first revision of introduction - now close to final
fixed region vs zone in abstract

@@
 Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
-Seismicity parameters are calculated and smoothed for each region separately, and for comparison purposes, we also consider the combination of all the seismic zones as a uniform region.
+Seismicity parameters are calculated and smoothed for each seismic zone separately, and for comparison purposes, we also consider the combination of all the seismic zones as a single seismotectonic region.
 Seismic hazard curves obtained for two distinct models defined according to two structural risk scenarios.
@@
 
-% -------------------------
+% *********************************************************************************************************************
+% *********************************************************************************************************************
 
@@
 
-% -------------------------
+% *********************************************************************************************************************
+% *********************************************************************************************************************
 
 % Naeem's original abstract
+% -------------------------
 

### 2016-02-29 abstract.tex
fixed region vs zone in abstract

@@
 We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the difference observed due to the intrinsic differences in the methods employed here in light of results obtained by other previous studies.
-In conclusion, we find our results to be helpful in understanding seismic hazard for norther Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain a more robust estimates at specific areas of interest.
+In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain a more robust estimates at specific areas of interest.
 

### 2016-03-03 abstract.tex
almost final introduction. i also polished the abstract

--- 2016-02-29 abstract.tex
@@
 % 
-This article presents a seismic hazard assessment for northern Iran where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data.
-We evaluate the hazard over a geographical region including the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh.
-For completeness, we also consider the partial contribution of the two remaining seismic zones to the south, that is, Zagros to the southwest, and the south-central and southeastern Iranian seismic zones.
-Following the concepts of smoothed seismicity, events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both the latitude and longitude directions.
+This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data.
+We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh.
+For completeness, we also consider the partial contribution of the seismic zones of Zagros to the southwest, and the south-central and southeastern Iranian seismic zones.
+In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude.
 After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
-Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
-Seismicity parameters are calculated and smoothed for each seismic zone separately, and for comparison purposes, we also consider the combination of all the seismic zones as a single seismotectonic region.
-Seismic hazard curves obtained for two distinct models defined according to two structural risk scenarios.
-These scenarios are based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 for unreinforced and informal construction, and greater than 5.0 for modern structures following design regulations.
-We also present results for a combined scenario based on the proportion of reinforced and unreinforced structures.
+Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region.
+Seismic hazard curves are obtained for two distinct models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0 for unreinforced and reinforced structures, respectively.
+We also obtain results for a combined scenario of these two models.
 The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the difference observed due to the intrinsic differences in the methods employed here in light of results obtained by other previous studies.
-In conclusion, we find our results to be helpful in understanding seismic hazard for norther Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain a more robust estimates at specific areas of interest.
+We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the differences observed.
+In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.
 
@@
 % *********************************************************************************************************************
+
+% Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
+
+% greater than 4.5 for unreinforced and informal construction buildings, and greater than 5.0 for modern structures following design regulations
 

### 2016-03-03 introduction.tex
almost final introduction. i also polished the abstract

@@
 This article presents a new seismic hazard assessment for northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to be the most reliable attenuation relationship to predict peak ground response in the region.
+
 The Iranian plateau is located on the Himalayan-Alpine seismic belt.
-It is confined between the convergent movements of the Arabian and Eurasian plates, and laterally trapped between the Arabian and eastern Asia-Minor to the west, and the Indian and Eurasian plates to the east.
-This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges \citep[e.g.,][]{Berberian_1981_Chap}.
-It also defines the seismic activity of the region, one with a long history of large magnitude ($M>7$) earthquakes dating back to the eight century, which has repeatedly damage Iran's infrastructure and taken the lives of thousands.
+It is confined between the convergent movements of the Arabian and Eurasian plates, and laterally trapped between the Arabian and eastern Asia-Minor to the west, and the Indian and Eurasian plates to the east \citep{Berberian_1981_Chap}.
+This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges.
+It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eight century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
 
@@
 
-Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999} [\textcolor{red}{Add at least two more references here}].
+Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE}.
 These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-While improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest high levels of seismic and therefore more complete and accurate assessments of seismic hazard, that incorporate the latest available data and alternative methods, are necessary.
+While improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest high levels of seismic risk.
+Therefore, more complete and accurate assessments of seismic hazard---incorporating the latest available data and alternative methods---are necessary.
 
-In this article, we are particularly interested in the assessment of the seismic hazard of northern Iran.
-This region houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht; and has suffered the devastating effects of earthquakes in the past (e.g., \textcolor{red}{two references}).
-Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Ghodrati2011, Abdollahzadeh2014a, Boostan2015} \textcolor{red}{[Are these good references?
-we need them to be about northern Iran.
-Any other?]}.
+Northern Iran houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht.
+This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.
+Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
 In general, these studies highlight the significant seismic hazard of the region, and...
@@
 Here, we use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This approach has been used with success in other regions (\textcolor{red}{[two references needed here]}).
+This approach has been used with success in other regions \citep[e.g.][]{Boyd2008, Kalkan2009, Moschetti2014}.
 Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.

### 2016-03-04 abstract.tex
additional fixes as agreed

@@
 This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data.
-We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh.
-For completeness, we also consider the partial contribution of the seismic zones of Zagros to the southwest, and the south-central and southeastern Iranian seismic zones.
+We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh; and for completeness, we also consider the contribution of parts of other neighboring seismic zones that fall within our region of interest.
+% For completeness, we also consider the partial contribution of the seismic zones of Zagros to the southwest, and the south-central and southeastern Iranian seismic zones. 
 In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude.
@@
 Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region.
-Seismic hazard curves are obtained for two distinct models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0 for unreinforced and reinforced structures, respectively.
-We also obtain results for a combined scenario of these two models.
+Seismic hazard curves are obtained for two
+% distinct 
+models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, depending on the type of construction, 
+ % for unreinforced and reinforced structures, respectively. We 
+and also obtain results for a combined scenario using these two models.
 The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.

### 2016-03-04 introduction.tex
additional fixes as agreed

@@
 
-Northern Iran houses nearly 40 percent (31.5 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, and Rasht.
+Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, Rasht, and Ardabil.
 This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.
 Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
-In general, these studies highlight the significant seismic hazard of the region, and...
-\textcolor{red}{[need punch line conclusions here]}.
+Among other things, these studies have highlighted the prevailing differences between different studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.
 
@@
 Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We consider two hazard models based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ 4.5 and 5.0 for unreinforced and reinforced structures, respectively; and later combine these results into a single analysis based on the composition of the structural building inventory of the country.
+We consider two hazard models based on the assumption that damage occurs above an earthquake magnitude $M_w$ 4.5 for informal construction buildings, and above $M_w$ 5.0 for structures built in accordance to code regulations.
+The results of these two models are then combined
+% and 5.0 for unreinforced and reinforced structures, respectively; We later combine these results 
+into a single analysis based on the composition of the structural building inventory of the country.
 We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.

### 2016-03-04 GMT_sctipts/historical_earthquake/Figure3.sh
GMT scripts for plotting instrumental, historical, and Seismotectonic zones added.

@@ -1,0 +1,78 @@
+#!/bin/bash
+# Set stuff up
+# World Topography
+# By : Naeem Khoshnevis
+
+
+ 
+
+LONMIN=43.5
+LONMAX=61.5
+LATMIN=34
+LATMAX=40
+REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
+PROJ=-JM18
+MOREPS=-K
+CONTINUEPS="-K -O"
+ENDPS=-O
+DATASET=11
+DATAGRID=-I30c
+LINE=-W1
+
+grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
+CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
+TOPOILLUM=220
+
+#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
+grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
+
+grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
+
+pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
+
+
+awk '{print $2,$3,$1,($4^3.2)/1000}' historical.txt|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
+psscale -D3.5i/4.2i/6i/0.15ih -Ba100:"Earthquake Time": -Ccolors.cpt -K -O >>  $0.ps
+#awk '{print $9,$10}' usgs_data.txt|psxy -Sc0.3 -G51/255/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
+#awk '{print $9,$10}' IIEES_data.txt|psxy -Sc0.2 -G250/51/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
+
+
+# magnitude scale
+
+
+cat << EOF | awk '{print $2,$3,$1,($4^3.2)/1000}'|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
+900 60 38     5
+900 60 38.5   6
+900 60 38.9   7
[…]

### 2016-03-08 figures/gmt/regional-map.sh
fixing files

@@ -1,0 +1,75 @@
+
+clear
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT_LABEL               = 12
+
+# gmt gmtset MAP_FRAME_PEN            = 0.75p,black
+# gmt gmtset MAP_FRAME_WIDTH          = 0.75p
+# gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+# gmt gmtset MAP_GRID_PEN_PRIMARY     = 0.75p
+# gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+# gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
+# gmt gmtset MAP_LABEL_OFFSET         = 8p
+# gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=regional-map
+PSNAME=${OUTNAME}.ps
+
+LONMIN=36
+LONMAX=72
+LATMIN=22
+LATMAX=42
+
+REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
+
+# ------------------------------------------------------------------------------
+
+gmt pscoast -R${REGION} -JM -Slightblue -G255/211/155 -Dh -W0.25p -B4 -N1/0.25p --FORMAT_GEO_MAP=dddF -V -P -K > ${PSNAME}
+
+# Region of Interest
+# ------------------------------------------------------------------------------
+
+gmt psxy -W0.5 -R -JM -V -O >> ${PSNAME} << END
+43.5	34
+43.5	40
+61.5    40
+61.5    34
+43.5	34
+END
+
+# Creating PDF
+# ------------------------------------------------------------------------------
+
+gmt ps2raster ${PSNAME} -Tf -Au0.1c
+
+# Opening PDF
+# ------------------------------------------------------------------------------
+
+open -a Adobe\ Acrobat\ Pro.app ${OUTNAME}.pdf
+
+
+
+# PROJ=-JM16
+# MOREPS=-K
+# CONTINUEPS="-K -O"
+# ENDPS=-O
+# DATASET=9
+# DATAGRID=-I30c
+# LINE=-W1
+
[…]

### 2016-03-08 figures/gmt/regional-map.sh
update

@@ -28,14 +28,18 @@ LATMAX=42
 
 REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
 
+PROJ=M5i
+
 # ------------------------------------------------------------------------------
 
-gmt pscoast -R${REGION} -JM -Slightblue -G255/211/155 -Dh -W0.25p -B4 -N1/0.25p --FORMAT_GEO_MAP=dddF -V -P -K > ${PSNAME}
+gmt pscoast -R${REGION} -J${PROJ} -Slightblue -G255/211/155 -Dh -W0.25p -B4 -N1/0.25p -Ba4f2g2 -V -P -K > ${PSNAME}
+
+ # --FORMAT_GEO_MAP=dddF
 
 # Region of Interest
 # ------------------------------------------------------------------------------
 
-gmt psxy -W0.5 -R -JM -V -O >> ${PSNAME} << END
+gmt psxy -W0.5 -R -J${PROJ} -V -O >> ${PSNAME} << END
 43.5	34
 43.5	40
 61.5    40

### 2016-03-09 figures/gmt/regional-map.sh
updates

@@ -6,14 +6,14 @@ clear
 
 gmt gmtset FONT_LABEL               = 12
 
-# gmt gmtset MAP_FRAME_PEN            = 0.75p,black
-# gmt gmtset MAP_FRAME_WIDTH          = 0.75p
-# gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
-# gmt gmtset MAP_GRID_PEN_PRIMARY     = 0.75p
-# gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
-# gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
-# gmt gmtset MAP_LABEL_OFFSET         = 8p
-# gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
+gmt gmtset MAP_FRAME_PEN            = 0.75p,black
+gmt gmtset MAP_FRAME_WIDTH          = 0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
+gmt gmtset MAP_LABEL_OFFSET         = 8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
 
 # Set script constants
 # ------------------------------------------------------------------------------
@@ -28,18 +28,17 @@ LATMAX=42
 
 REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
 
-PROJ=M5i
-
 # ------------------------------------------------------------------------------
 
-gmt pscoast -R${REGION} -J${PROJ} -Slightblue -G255/211/155 -Dh -W0.25p -B4 -N1/0.25p -Ba4f2g2 -V -P -K > ${PSNAME}
+gmp psmap 
+gmt pscoast -R${REGION} -JX5id/3id -BWNes+a4f2 -Slightblue -G255/211/155 -Dh -W0.25p -N1/0.25p -V -P -K > ${PSNAME}
 
- # --FORMAT_GEO_MAP=dddF
+# --FORMAT_GEO_MAP=dddF
 
 # Region of Interest
 # ------------------------------------------------------------------------------
 
-gmt psxy -W0.5 -R -J${PROJ} -V -O >> ${PSNAME} << END
[…]

### 2016-03-09 introduction.tex
finished figure 1

@@
 
-Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, Rasht, and Ardabil.
+Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil.
 This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.

### 2016-03-09 figures/draft-gmt/Seismotectonic/Figure_1_a.sh

@@ -1,53 +1,0 @@
-#!/bin/bash
-# Set stuff up
-# World Topography
-# By : Naeem Khoshnevis
- 
-
-LONMIN=25
-LONMAX=80
-LATMIN=20
-LATMAX=45
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM16
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=9
-DATAGRID=-I30c
-LINE=-W1
-
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
-
-grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V  # in this case Dataset = 9
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
-
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N2   -K  -Y1 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1 -B10f5/10f5  -Lf45/23/23/1000 -K -O -W2 >> $0.ps
-
-
-
-
-
-cat << EOF13 |psxy  -Sc0.05  -W1 -R$REGION $PROJ -K -O  >> $0.ps
-
-43.5	34
-43.5	40
-61.5    40
-61.5    34
-44.228  39.4
-48.971  31.136
-60.173  36.429
-61.435  25.075
-
-EOF13
-
-
-
-
-
-
-

### 2016-03-09 figures/draft-gmt/Seismotectonic/Figure_1_b.sh

@@ -1,207 +1,0 @@
-#!/bin/bash
-# Set stuff up
-# World Topography
-# By : Naeem Khoshnevis
-
-
- 
-
-LONMIN=43.5
-LONMAX=61.5
-LATMIN=34
-LATMAX=40
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM18
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=11
-DATAGRID=-I30c
-LINE=-W1
-
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
-
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
-grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N1 -V
-
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N2   -K  -Y8 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1 -B4f2/4f2  -Lf58/34.8/58.5s/200 -K -O -W2 >> $0.ps
-
-
-
-cat << EOF |pstext -R$REGION $PROJ  -K -O  >> $0.ps
-#  47.5 38.1 12  -60 1 c Ardabil
-#  43   36.0 20  00 1 c Iraq
-#  52   35.5 12  00 3 r Tehran
-  52   33.5 20  00 1 c Iran 
-#  42.5 39.5 20  00 1 c Turkey
-#  47.6 40.3 16  45 1 c Azerbaijan
-#  51.4   39   16  00 7 c Caspian Sea
- 
-EOF
-
-
-
-#G
-cat << EOF13 |psxy   -W8 -R$REGION $PROJ -K -O  >> $0.ps
-47.344753	40.72171
-49.599926	39.52165
-49.26277	38.11627
-51.85228	36.86008
-54.88121	38.01132
-53.19502	39.433327
-53.29621	39.878605
-55.519176	39.318867
-61.2336	36.95889
-61.145393	34.578835
-59.67538	35.37419
-58.63931	35.737476
-56.517025	36.478027
-54.994373	35.992893
[…]

### 2016-03-09 figures/gmt/regional-map.sh

@@ -1,19 +1,23 @@
 
 clear
 
+rm gmt.conf gmt.history
+
 # Set GMT constants
 # ------------------------------------------------------------------------------
 
-gmt gmtset FONT_LABEL               = 12
+gmt gmtset FONT_LABEL               10
 
-gmt gmtset MAP_FRAME_PEN            = 0.75p,black
-gmt gmtset MAP_FRAME_WIDTH          = 0.75p
-gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
-gmt gmtset MAP_GRID_PEN_PRIMARY     = 0.75p
-gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
-gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
-gmt gmtset MAP_LABEL_OFFSET         = 8p
-gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
 
 # Set script constants
 # ------------------------------------------------------------------------------
@@ -21,24 +25,30 @@ gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
 OUTNAME=regional-map
 PSNAME=${OUTNAME}.ps
 
-LONMIN=36
-LONMAX=72
-LATMIN=22
-LATMAX=42
-
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-
+# The large Map
 # ------------------------------------------------------------------------------
 
-gmp psmap 
[…]

### 2016-03-10 region-of-interest.tex
updates

\begin{figure*}[!ht] 
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-01}
	\caption{Region of interest and Iranian seismic zones. At the top, the map of Iran and surrounding countries with shaded relief in the background and the Iranian seismic zones \citep[after][]{Karimiparidari2013} and region of interest in the foreground. The dashed box indicates the complete region of interest and the thicker line box indicates the effective area for which seismic hazard is estimated. The effective region of interest is shown in greater detail at the bottom. Details include the location of the major urban centers and seismic faults in northern Iran.}
	\label{fig:iran}
\end{figure*}

\section{Region of Interest}

Seismic activity in the Iranian plateau is dominated by the tectonic contacts between the Arabian, Eurasian, and Indian plates, which confine the region laterally between the Indian and Eurasian plates, and the Arabian and eastern Asia-Minor plates to the east and west, respectively. This setting gives rise to the Zagros, Alborz, and east Iranian mountain ranges, and defines the geology of the region. Based on these conditions, Iranian seismicity is typically divided into various seismic zones, varying from as few as four to as many as twenty-three \citep[e.g.,][]{Stocklin1968, Berberian1976, Tavakoli1999}. Here, we adopt the model proposed by \citet{Karimiparidari2013}, which consists of six seismic zones: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East, and Makram (Fig.~\ref{fig:iran}).

Within this context, we define our region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}. These limits correspond to the effective region of interest for which we will present results ins subsequent sections. Our calculations, however, included data from a slightly larger region with a 0.5\textdegree{}-perimeter as indicated in the figure. This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the region of interest. The effective region has an area of 1,703 km $\times$ 667 km, and as shown in Fig.~\ref{fig:iran}, it encloses the northern part of Iran with the complete seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, and portions of the Zagros and Central-East seismic zones.

At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the effects of the north Tabriz fault (NTF) system. This system is a complex northwest-trending structure with right-lateral, strike-slip faulting mechanisms \citep{Berberian1999}. The NTF has ruptured in multiple occasions in the last few centuries of which there are historical accounts.

% There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.

% The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879. Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}. Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively. These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\

% *********************************************************************************************************************
% *********************************************************************************************************************

% Naeem's original Text
% ---------------------

% With respect to different seismicity rates of the regions \citep{Nemati2015}, as well as the completeness of the seismic catalog \citep{Zare2014} , the study region is divided into three tectonic seismic zones. Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$). Part of Central Iran and Zagros regions are inside of the study region. We also calculated the seismicity parameters in these regions. Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.

% \begin{figure*}[!ht] 
% \centering
% \includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
% \caption{ a) Map of Iran and surrounding countries. The study area is presented in gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}. }

% \label{fig:Iran}
% \end{figure*}

% \subsection{Tectonic Regions and Seismic Faults}

% \subsubsection{Alborz Mountain Range (Alborz)}
% Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. Here a series of historical earthquakes occurred within a time period of more than 1100 years. Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region. At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
% The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
% The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression. An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}. Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}. Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}. \\

% \subsubsection{Azerbaijan}
% There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
% The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879. Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}. Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively. These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\

% \subsubsection{Kopeh Dagh}
% The main Kopeh-Dagh fault system has experienced some historic earthquakes. Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran. This was the strongest earthquake to strike this region since at least 1455.
% The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km. 
% Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
% The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
% Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\

% \subsection{Historical  and Instrumental Seismicity}
% Uniform earthquake catalog is the most important factor in seismic hazard analysis of a region.  Different studies have been conducted in order to prepare a uniform catalog for Iranian Earthquake. Historical event interpretation and different magnitude conversion relationships are some of the factors which make all these catalogs different. Among different sources \citet{Ambraseys2005}, \citet{Berberian1994}, and \citet{moinfar1994} are some of the main sources for Iranian earthquake catalog. These catalogs contain historical and instrumental earthquakes that have been reported in literature and national and international networks. According to \citet{Ambraseys2005}, there are some scattered indication of earthquake effects  back to third millinuim BC. However, adequate documentary coverage of individual events begins from seventh century A.D. \citet{Mirzaei1997} provided a comprehensive list of studies that have been done in compilation a uniform catalog for Iranian earthquakes in order to prepare a uniform catalog of earthquake (all earthquakes are converted to surface wave magnitude Ms) for seismic hazard assessment in Iran. The catalog is covering the period of 4th century B.C. through 1994. The instrumental data is achievable from three national agencies including IIEES, International Institute of Earthquake Engineering and Seismology; IRSC, The Iranian seismological center, University of Tehran; and BHRC, Building and Housing Research Center (Iran Strong Motion Network) (For more information about these networks see \citet{Karimiparidari2013}).
% Many most of attenuation relationship use  moment magnitude $M_w$ as an input for the equation \citep{Douglas2011}. Moment magnitude is not suffering from saturation and has physical meaning \citep{Kanamori1977}. Due to mentioned reasons Mw has become a most appropriate magnitude scale in recent studies. 
%  \citet{Karimiparidari2013}compiled a uniform earthquake catalog for Iran and adjacent areas, using international and national databanks until April 2010.  They developed relationships between moment magnitude and other magnitude based on orthogonal regression.  They removed the dependent events (aftershocks and foreshocks) using the procedure by \citet{Gardner1974}. The catalog of events with magnitude equal and above Mw 5.5 is provided. 
% \citet{Shahvar2013} presented a unified and homogeneous catalog for the Iranian plateau $(M_w >= 4)$, created by merging data from two local catalogs and seven international agencies for 1900-2011 period. They used orthogonal regression method \citep{Castellaro2006} to derive magnitude conversion relation. By removing foreshocks and aftershocks according to the procedure detailed in Uhrhammer(1986), they also provided declustered version of the catalog.

% The recent unified catalog for Middle East region is published as a part of Global Earth Model (GEM) and the Earthquake Model of the Middle East (EMME) project by \citet{Zare2014}. They used all historical (pre-1900), early and modern instrumental events up to 2006. The catalog contains data from Alborz-Azerbaijan, Afghanistan-Pakistan, Saudi Arabia, Caucasus, Central Iran, Kopeh-Dagh, Makran, Zagros, and part of Turkey. The magnitude of all events are converted to Mw through relationships which is derived at previous studies or newly derived at the study relationships. They declustered data through different methods including \citet{Gardner1974}, Uhrhammer(1986), \citet{Reasenberg1985}, and Gruenthal. \citet{Zare2014} provided the catalog completeness for different magnitude range using  the cumulative frequency-magnitude distribution of  \citet{Gutenberg1944} and \citet{richter1958}, and frequency magnitude distributaion of ZMAP \citep{Wiemer2001} software. The methods confirms the results of each other.

% In this study we consider earthquakes with Mw equal and greater than 3. Earthquakes with magnitude 3 are not considered as a structural threat, however, the epicenter of earthquakes with magnitude $M_w 3$ are a  susceptible location for future bigger earthquakes.  According to our preliminary data processing based on IIEES data, Iranian catalog for earthquake with magnitude greater and equal 3, is complete from 2005. In order to make sure about the completeness of the catalog, we use IIEES data from 2000. We used the EMME project data provided by \citet{Zare2014} up to 2000. Fig.~\ref{fig:historical} represents the historical data (pre 1900) in the study region.

% \subsubsection{Magnitude Conversion}

% The catalog of recorded earthquake from 2000-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale. We converted the $M_L$, $M_s$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}. There also some of data which is recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010}, developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_s$ scales to the $M_w$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the Md to Mw. Although they defined the equation based on $M_w>=4.5$, we extrapolate the equation for lower magnitude. We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate "a" value  in Gutenberge-Richter equation.

% \begin{figure*}[!ht]

% \centering
% \includegraphics[scale=0.4]{figures/pdf/Figure2.pdf} 
% \caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
% \label{fig:historical}
% \end{figure*}

% \subsubsection{Declustering}

% It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process. Therefore, in order to accomplish this, we declustered the earthquake catalog. In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}. For north Iran (lon: 42-62.5, lat: 33-41), from 7478 earthquake event we removed 605 Foreshocks and 2917 aftershocks.
% Whole data that we used for seismicity parameters of Zagros and Central Iran tectonic seismic regions are not included in these numbers. Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.

% \begin{figure*}[!ht]

% \centering
% \includegraphics[scale=0.25]{figures/pdf/Figure3.pdf} 
% \caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
% \label{fig:instrumental}
% \end{figure*}

% \subsection{Divisions}

% As we discussed earlier (see the Introduction section), classifying the tectonic seismic regions has been a controversial debate. In this study we consider two seismic tectonic models. First model is according to \citet{Mirzaei1998} and \citet{Karimiparidari2013} classification, which includes Azerbaijan, Alborz, Kopek Dagh, and part of Central Iran, and Zagros, the second model is a uniform model for the whole north Iran.

### 2016-03-10 region-of-interest.tex
updates to section 2

@@
 This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
-The effective region has an area of 1,703 km $\times$ 667 km, and as shown in Fig.~\ref{fig:iran}, it encloses the northern part of Iran with the complete seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, and portions of the Zagros and Central-East seismic zones.
+The effective region has an area of 1,703 km $\times$ 667 km, and as shown in Fig.~\ref{fig:iran}, it encloses the northern part of Iran with most of the Azerbaijan seismic zone, the complete zones of Alborz and Kopeh-Dagh, and the northernmost portions of the Zagros and Central-East seismic zones.
 
-At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the effects of the north Tabriz fault (NTF) system.
-This system is a complex northwest-trending structure with right-lateral, strike-slip faulting mechanisms \citep{Berberian1999}.
-The NTF has ruptured in multiple occasions in the last few centuries of which there are historical accounts.
+At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the north Tabriz fault (NTF) system.
+This system is a complex northwest-trending structure with a predominant right-lateral, str\-ike-slip faulting mechanism \citep{Berberian1999}.
+Historical accounts document the occurrence of earthquakes in this area as far back as to the 9th century, with events in the years 858 ($M$ 6.0), 1042 ($M$ 7.3), 1273 ($M$ 6.5), and 1304 ($M$ 6.7) \citep{Berberian1999}.
+In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.3 1721 Shelbi earthquake in the southeastern section, the $M$ 7.4 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
+According to \citet{Jones1834}, the Shelbi and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively; and the latter presented vertical separations of about 2 to 4 m.
+Other notable events include the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes.
+More recently, the NTF system produced the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage to the region and took the lives of more than 1500 people \citep{USGS_ardabil,USGS_tabriz}.
 
-% There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
+Transitioning from the Azerbaijan to the Alborz seismic zone, the next fault system runs along the Rocks of the Talesh mountains, to the northwest of the Alborz Mountains.
+Faults in this area have ruptured recently, including an $M_s$ 6.0 low-angle thrust earthquake in 1978 \citep{Berberian1999} and the $M_w$ 7.4 1990 Manjil-Rudbar earthquake, which caused numerous deaths and significant damage to the region in the south Caspian depression \citep{USGS_manjil}.
+At the central area of the Alborz seismic zone, near Tehran, the region is characterized by active reverse faults in the North Tehran Thrust (NTT) system.
+These faults are parallel to the northwest-trending structural gain of the Alborz Mountains belt, and include the south-dipping partially blind faults of Davudieh, Shian, and Bagh-E Feyz.
+According to \citet{Ambraseys2005}, both Tehran and the ancient city of Rey have been devastated in multiple occasions due to severe earthquakes in this area.
+Historical accounts document the occurrence of multiple $M>7$ earthquakes in 743, 958, 1177, 1655, and 1830.
+The 1830 earthquake, in particular, ruptured the central segments of the NTT, adjacent to the Mosha fault.
 
-% The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
+To the east, the Kopeh-Dagh fault system is the predominant faulting system in the seismic zone of the same name.
+This system consists of several partly overlapping segments parallel to a NW--SE oriented structure of step-overs characterized by short south-dipping thrust faults striking E--W \citep{Berberian2001}, which exhibits active tectonic displacements along more than 500 km \citep{Trifonov1978}.
+This system is responsible for the $M_s$ 7.2 earthquake that stroke Ashgabat, the capital city of Turkmenistan and destroyed more than 30 villages in Iran in 1948.
+Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 B.C., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
 

### 2016-03-11 region-of-interest.tex
updates

@@
 Within this context, we define our region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}.
-These limits correspond to the effective region of interest for which we will present results ins subsequent sections.
+These limits correspond to the effective region of interest for which we will present results in subsequent sections.
 Our calculations, however, included data from a slightly larger region with a 0.5\textdegree{}-perimeter as indicated in the figure.
@@
 Historical accounts document the occurrence of earthquakes in this area as far back as to the 9th century, with events in the years 858 ($M$ 6.0), 1042 ($M$ 7.3), 1273 ($M$ 6.5), and 1304 ($M$ 6.7) \citep{Berberian1999}.
-In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.3 1721 Shelbi earthquake in the southeastern section, the $M$ 7.4 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
-According to \citet{Jones1834}, the Shelbi and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively; and the latter presented vertical separations of about 2 to 4 m.
+In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.3 1721 Shebli earthquake in the southeastern section, the $M$ 7.4 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
+According to \citet{Jones1834}, the Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively; and the latter presented vertical separations of about 2 to 4 m.
 Other notable events include the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes.
@@
 These faults are parallel to the northwest-trending structural gain of the Alborz Mountains belt, and include the south-dipping partially blind faults of Davudieh, Shian, and Bagh-E Feyz.
-According to \citet{Ambraseys2005}, both Tehran and the ancient city of Rey have been devastated in multiple occasions due to severe earthquakes in this area.
-Historical accounts document the occurrence of multiple $M>7$ earthquakes in 743, 958, 1177, 1655, and 1830.
+According to \citet{Ambraseys2005}, Tehran---or the ancient city of Rey---has been devastated in multiple occasions due to severe earthquakes in this area.
+Historical accounts document the occurrence of multiple $M>7$ earthquakes in 743, 958, 1177, 1665, and 1830.
 The 1830 earthquake, in particular, ruptured the central segments of the NTT, adjacent to the Mosha fault.
@@
 This system is responsible for the $M_s$ 7.2 earthquake that stroke Ashgabat, the capital city of Turkmenistan and destroyed more than 30 villages in Iran in 1948.
-Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 B.C., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
+Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
 

### 2016-03-13 region-of-interest.tex
figures 2 and 3 and other fixes

@@
-\begin{figure*}[!ht] 
+\begin{figure*}[ht!] 
 	\centering
@@
 	\label{fig:iran}
+\end{figure*}
+
+\begin{figure*}[ht!] 
+	\centering
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-02}
+	\caption{Notable earthquakes in the region of interest and within three major seismic zones in northern Iran.
+Epicentral locations are indicated with stars.
+The labels next to each star or linked with a line to avoid congestion show the magnitude and year of the earthquake.}
+	\label{fig:selected}
 \end{figure*}
@@
 
-At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the north Tabriz fault (NTF) system.
+At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault (NTF) system.
 This system is a complex northwest-trending structure with a predominant right-lateral, str\-ike-slip faulting mechanism \citep{Berberian1999}.
-Historical accounts document the occurrence of earthquakes in this area as far back as to the 9th century, with events in the years 858 ($M$ 6.0), 1042 ($M$ 7.3), 1273 ($M$ 6.5), and 1304 ($M$ 6.7) \citep{Berberian1999}.
-In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.3 1721 Shebli earthquake in the southeastern section, the $M$ 7.4 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
+Historical accounts document the occurrence of earthquakes in this area as far back as to the 9th century, with events in the years 858 ($M$ 6.0), 1042 ($M$ 7.3), and 1304 ($M$ 6.7) \citep{Berberian1999}.
+In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.7 1721 Tabriz earthquake in the southeastern section, the $M$ 7.6 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
 According to \citet{Jones1834}, the Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively; and the latter presented vertical separations of about 2 to 4 m.
 Other notable events include the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes.
-More recently, the NTF system produced the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage to the region and took the lives of more than 1500 people \citep{USGS_ardabil,USGS_tabriz}.
+More recently, the same region was stroke by the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage and took the lives of more than 1500 people \citep{USGS_ardabil, USGS_tabriz}.
 
 Transitioning from the Azerbaijan to the Alborz seismic zone, the next fault system runs along the Rocks of the Talesh mountains, to the northwest of the Alborz Mountains.
-Faults in this area have ruptured recently, including an $M_s$ 6.0 low-angle thrust earthquake in 1978 \citep{Berberian1999} and the $M_w$ 7.4 1990 Manjil-Rudbar earthquake, which caused numerous deaths and significant damage to the region in the south Caspian depression \citep{USGS_manjil}.
+Faults in this area have ruptured recently \citep{Berberian1999}.
+% , including an $M_s$ 6.0 low-angle thrust earthquake in 1978 \citep{Berberian1999} and 
+The $M_w$ 7.4 1990 Manjil-Rudbar earthquake, for instance, caused numerous deaths and significant damage to the region in the south Caspian depression \citep{USGS_manjil}.
 At the central area of the Alborz seismic zone, near Tehran, the region is characterized by active reverse faults in the North Tehran Thrust (NTT) system.
@@
 This system consists of several partly overlapping segments parallel to a NW--SE oriented structure of step-overs characterized by short south-dipping thrust faults striking E--W \citep{Berberian2001}, which exhibits active tectonic displacements along more than 500 km \citep{Trifonov1978}.
-This system is responsible for the $M_s$ 7.2 earthquake that stroke Ashgabat, the capital city of Turkmenistan and destroyed more than 30 villages in Iran in 1948.
-Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
+This system is responsible for the $M_w$ 7.3 earthquake that stroke Ashgabat, the capital city of Turkmenistan and destroyed more than 30 villages in Iran in 1948.
+Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at the boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
+These and other notable earthquakes in the seismic zones of Azerbaijan and Alborz are shown in Fig.~\ref{fig:selected}.
 

### 2016-03-13 figures/gmt/regional-map.sh

@@ -108,6 +108,9 @@ END
 
 gmt ps2raster ${PSNAME} -Tf -Au0.25c
 rm ${PSNAME}
+rm mytopo.grad
+rm mytopo.hist
+rm mytopo.norm
 
 # Opening PDF
 # ------------------------------------------------------------------------------
@@ -115,21 +118,3 @@ rm ${PSNAME}
 open -a Adobe\ Acrobat\ Pro.app ${OUTNAME}.pdf
 
 
-# PROJ=-JM16
-# MOREPS=-K
-# CONTINUEPS="-K -O"
-# ENDPS=-O
-# DATASET=9
-# DATAGRID=-I30c
-# LINE=-W1
-
-# grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-# CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-# TOPOILLUM=220
-
-# grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V  # in this case Dataset = 9
-# #grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
-
-# grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N2   -K  -Y1 -X8  >  $0.ps
-
-# pscoast -R$REGION $PROJ -N1 -B10f5/10f5  -Lf45/23/23/1000 -K -O -W2 >> $0.ps

### 2016-03-13 figures/gmt/seismicity.sh

@@ -1,0 +1,99 @@
+
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=seismicity
+PSNAME=${OUTNAME}.ps
+
+# Top Map - Notable
+# ------------------------------------------------------------------------------
+
+gmt grdgradient mytopo.grd -A300 -Gmytopo.grad -Nt
+gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+# Top Map - Historical
+# ------------------------------------------------------------------------------
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWnes -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+
+# gmt psbasemap -R -J -BWnes -Ba2f1 -Y-3.5i -V -P -O -K >> ${PSNAME}
+gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+gmt makecpt -Chot -T0/1800/100 -Z -V > historical.cpt
+awk '{print $2,$3,$1,($4^3.2)/1000}' historical.txt > data.txt
[…]

### 2016-03-13 figures/gmt/selectedquakes.sh

@@ -1,0 +1,94 @@
+
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=selectedquakes
+PSNAME=${OUTNAME}.ps
+
+# Top Map - Notable
+# ------------------------------------------------------------------------------
+
+gmt grdgradient mytopo.grd -A300 -Gmytopo.grad -Nt
+gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWneS -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+gmt psxy -Sa8p -W0.35p,black -Gyellow -R -J -B -V -O -K >> ${PSNAME} << END
+46.3	38.1
+46.3	38.1
+45.5	38.5
+46.7	37.9
+46.0	38.2
+45.6	38.3
[…]

### 2016-03-13 figures/draft-gmt/Instrumental/Instrumental.sh
cleaning up studd no longer needed

@@ -1,53 +1,0 @@
-#!/bin/bash
-# Set stuff up
-# World Topography
-# By : Naeem Khoshnevis
-
-
- 
-
-LONMIN=43.5
-LONMAX=61.5
-LATMIN=34
-LATMAX=40
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM18
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=11
-DATAGRID=-I30c
-LINE=-W1
-
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
-
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
-grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
-
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
-
-
-awk '{print $1,$2,($3^3.2)/1000}' instrumental.txt|psxy -Sc -G196/19/19 -W2  -R$REGION $PROJ -K -O >> $0.ps
-
-cat << EOF |awk '{print $1,$2,($3^3.2)/1000}' |psxy -Sc -G196/19/19 -W2  -R$REGION $PROJ -K -O >> $0.ps
-
-61 37.7   3
-61 38.0   4
-61 38.2   5
-61 38.6   6
-61 39.0   7
-61 39.7   8
-
- 
- 
-EOF
-
-
-
-
-
-

### 2016-03-13 figures/draft-gmt/historical_earthquake/Figure3.sh

@@ -1,78 +1,0 @@
-#!/bin/bash
-# Set stuff up
-# World Topography
-# By : Naeem Khoshnevis
-
-
- 
-
-LONMIN=43.5
-LONMAX=61.5
-LATMIN=34
-LATMAX=40
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM18
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=11
-DATAGRID=-I30c
-LINE=-W1
-
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
-
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
-grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
-
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
-
-
-awk '{print $2,$3,$1,($4^3.2)/1000}' historical.txt|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
-psscale -D3.5i/4.2i/6i/0.15ih -Ba100:"Earthquake Time": -Ccolors.cpt -K -O >>  $0.ps
-#awk '{print $9,$10}' usgs_data.txt|psxy -Sc0.3 -G51/255/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
-#awk '{print $9,$10}' IIEES_data.txt|psxy -Sc0.2 -G250/51/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
-
-
-# magnitude scale
-
-
-cat << EOF | awk '{print $2,$3,$1,($4^3.2)/1000}'|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
-900 60 38     5
-900 60 38.5   6
-900 60 38.9   7
-900 60 39.6   8
[…]

### 2016-03-13 figures/draft-gmt/historical_earthquake/Mag_7.sh

@@ -1,77 +1,0 @@
-#!/bin/bash
-# Set stuff up
-# World Topography
-# By : Naeem Khoshnevis
-
-
- 
-
-LONMIN=43.5
-LONMAX=61.5
-LATMIN=34
-LATMAX=40
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM18
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=11
-DATAGRID=-I30c
-LINE=-W1
-
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
-
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
-grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
-
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
-
-
-awk '{print $2,$3,$1,($4^4)/6000}' historical_7.txt|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
-psscale -D3.5i/4.2i/6i/0.15ih -Ba100:"Earthquake Time": -Ccolors.cpt -K -O >>  $0.ps
-#awk '{print $9,$10}' usgs_data.txt|psxy -Sc0.3 -G51/255/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
-#awk '{print $9,$10}' IIEES_data.txt|psxy -Sc0.2 -G250/51/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
-
-
-# magnitude scale
-
-
-cat << EOF | awk '{print $2,$3,$1,($4^4)/6000}'|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
-
-900 60 39     7
-900 60 39.5     8
-
- 
-EOF
-
-
-
[…]

### 2016-03-13 figures/draft-gmt/historical_earthquake/PSHA_plots.sh

@@ -1,67 +1,0 @@
-#!/bin/bash
-# Set stuff up
-# World Topography
-# By : Naeem Khoshnevis
-
-
- 
-
-LONMIN=42
-LONMAX=62
-LATMIN=34
-LATMAX=41
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM18
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=11
-DATAGRID=-I30c
-LINE=-W1
-
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
-
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
-grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
-
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
-
-
-awk '{print $2,$3,$1,($4*$4)/150}' historical.txt|psxy -Sc -G51/51/255 -W1 -Ccolors.cpt -R$REGION $PROJ -K -O >> $0.ps
-psscale -D3.5i/4.2i/8i/0.15ih -Ba100:"Earthquake Time": -Ccolors.cpt -K -O >>  $0.ps
-#awk '{print $9,$10}' usgs_data.txt|psxy -Sc0.3 -G51/255/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
-#awk '{print $9,$10}' IIEES_data.txt|psxy -Sc0.2 -G250/51/51 -W1 -R$REGION $PROJ -K -O >> $0.ps
-
-#awk '{print $9,$10}' complete_catalog_az_declustered.txt|psxy -Sc0.2 -G51/51/150  -W1 -R$REGION $PROJ -K -O >> $0.ps
-
-
-
-cat << EOF |pstext -R$REGION $PROJ  -K -O  >> $0.ps
-#  47.5 38.1 12  -60 1 c Ardabil
[…]

### 2016-03-13 seismic-catalog.tex
updates to seismic catalog section

--- 2016-03-11 region-of-interest.tex
@@
-\begin{figure*}[!ht] 
+\begin{figure*}[ht!] 
 	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-01}
-	\caption{Region of interest and Iranian seismic zones.
-At the top, the map of Iran and surrounding countries with shaded relief in the background and the Iranian seismic zones \citep[after][]{Karimiparidari2013} and region of interest in the foreground.
-The dashed box indicates the complete region of interest and the thicker line box indicates the effective area for which seismic hazard is estimated.
-The effective region of interest is shown in greater detail at the bottom.
-Details include the location of the major urban centers and seismic faults in northern Iran.}
-	\label{fig:iran}
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
+	\caption{Seismic catalog.
+(a) Historical seismicity prior to 1900.
+(b) Instrumental seismicity.
+Size of symbols is proportional to the magnitude of the events.
+In the case of the historical seismicity catalog, the color fill indicates the year of the event.}
+	\label{fig:selected}
 \end{figure*}
 
-\section{Region of Interest}
+\section{Seismic Catalog}
 
-Seismic activity in the Iranian plateau is dominated by the tectonic contacts between the Arabian, Eurasian, and Indian plates, which confine the region laterally between the Indian and Eurasian plates, and the Arabian and eastern Asia-Minor plates to the east and west, respectively.
-This setting gives rise to the Zagros, Alborz, and east Iranian mountain ranges, and defines the geology of the region.
-Based on these conditions, Iranian seismicity is typically divided into various seismic zones, varying from as few as four to as many as twenty-three \citep[e.g.,][]{Stocklin1968, Berberian1976, Tavakoli1999}.
-Here, we adopt the model proposed by \citet{Karimiparidari2013}, which consists of six seismic zones: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East, and Makram (Fig.~\ref{fig:iran}).
+A fundamental step in regional seismic hazard analysis is the compilation of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
+Instrumental data are easily accessible through agencies such as the International Institute of Earthquake Engineering and Seismology (IIEES), the Iranian Seismological Center (IRSC) at the University of Tehran, or the Iranian Strong Motion Network operated by the Building and Housing Research Center (BHRC).
+Historical data, on the other hand, lends itself to subjective interpretation.
+Notable previous efforts to compose uniform earthquake catalogs for Iran include but are not limited to \citet{moinfar1994}, \citet{Berberian1994}, and \citet{Ambraseys2005}.
+These studies, however, differ from each other in their use of magnitude scales or magnitude conversion rules, and the extent to which they accept historical accounts as valid data.
+According to \citet{Ambraseys2005}, for instance, there is evidence of earthquakes that goes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret.
+\citet{Mirzaei1997} compiled a catalog with historical events dating back to the 4th century B.C.~and instrumental earthquakes through 1994 in which a comprehensive list of studies was considered and magnitudes uniformly converted to surface wave magnitude ($M_s$).
 
-Within this context, we define our region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}.
-These limits correspond to the effective region of interest for which we will present results in subsequent sections.
-Our calculations, however, included data from a slightly larger region with a 0.5\textdegree{}-perimeter as indicated in the figure.
-This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
-The effective region has an area of 1,703 km $\times$ 667 km, and as shown in Fig.~\ref{fig:iran}, it encloses the northern part of Iran with most of the Azerbaijan seismic zone, the complete zones of Alborz and Kopeh-Dagh, and the northernmost portions of the Zagros and Central-East seismic zones.
+Most ground motion prediction equations used today for seismic hazard assessments, however, use moment magnitude ($M_w$) instead, as it is well-known that this magnitude scale does not suffer from saturation issues as other scales, and provides a meaningful relationship with the physics of the rupture.
+Recent catalogs such as that by \citet{Karimiparidari2013}, \citet{Shahvar2013}, and \citet{Zare2014} are all compiled using magnitudes converted to $M_w$.
+\citet{Karimiparidari2013}, for instance, compiled a catalog for Iran and adjacent areas using international and national datasets including events up until April, 2010 with $M_w > 5$.
+They developed relationships between moment magnitude and other magnitude scales and removed dependent events (foreshocks and aftershocks) using the procedure by \citet{Gardner1974}.
+\citet{Shahvar2013} built a catalog for the Iranian plateau for events with $M_w \geq 4$ merging data from two local and seven international datasets for the 1900--2011 period.
+They used the orthogonal regression method by \citet{Castellaro2006} to derive magnitude conversions and removed foreshocks and aftershocks according to the procedure by \textcolor{red}{Uhrhammer (1986)}.
+In addition, \citet{Shahvar2013} provided a declustered version of the catalog.
 
-At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the north Tabriz fault (NTF) system.
-This system is a complex northwest-trending structure with a predominant right-lateral, str\-ike-slip faulting mechanism \citep{Berberian1999}.
-Historical accounts document the occurrence of earthquakes in this area as far back as to the 9th century, with events in the years 858 ($M$ 6.0), 1042 ($M$ 7.3), 1273 ($M$ 6.5), and 1304 ($M$ 6.7) \citep{Berberian1999}.
-In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.3 1721 Shebli earthquake in the southeastern section, the $M$ 7.4 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
-According to \citet{Jones1834}, the Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively; and the latter presented vertical separations of about 2 to 4 m.
-Other notable events include the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes.
-More recently, the NTF system produced the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage to the region and took the lives of more than 1500 people \citep{USGS_ardabil,USGS_tabriz}.
+In turn, the catalog by \citet{Zare2014} uses both historical data prior to 1900 and instrumental data up until 2006, and includes events from Afghanistan-Pakis\-tan, Saudi Arabia, the Caucasus, and parts of Turkey in addition to the Alborz-Azerbaijan, Zagros, Central Iran, Kopeh-Dagh and Makran seismic zones.
+All events in this catalog are converted to $M_w$ using relationships from previous studies \textcolor{red}{(e.g., pending ref.)}; and data were declustered using various methods including \citet{Gardner1974}, \citet{Reasenberg1985}, \textcolor{red}{Uhrhammer (1986), and Gruenthal (????) [is this level of detail really necessary?]}.
+In addition, \citet{Zare2014} provided the catalog completeness for different magnitude ranges using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and \citet{richter1958}, and the frequency magnitude distribution obtained using ZMAP \citep{Wiemer2001}, and found the methods to yield consistent results.
+This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
 
-Transitioning from the Azerbaijan to the Alborz seismic zone, the next fault system runs along the Rocks of the Talesh mountains, to the northwest of the Alborz Mountains.
-Faults in this area have ruptured recently, including an $M_s$ 6.0 low-angle thrust earthquake in 1978 \citep{Berberian1999} and the $M_w$ 7.4 1990 Manjil-Rudbar earthquake, which caused numerous deaths and significant damage to the region in the south Caspian depression \citep{USGS_manjil}.
-At the central area of the Alborz seismic zone, near Tehran, the region is characterized by active reverse faults in the North Tehran Thrust (NTT) system.
-These faults are parallel to the northwest-trending structural gain of the Alborz Mountains belt, and include the south-dipping partially blind faults of Davudieh, Shian, and Bagh-E Feyz.
-According to \citet{Ambraseys2005}, Tehran---or the ancient city of Rey---has been devastated in multiple occasions due to severe earthquakes in this area.
-Historical accounts document the occurrence of multiple $M>7$ earthquakes in 743, 958, 1177, 1665, and 1830.
-The 1830 earthquake, in particular, ruptured the central segments of the NTT, adjacent to the Mosha fault.
+In this study we consider earthquakes with $M_w \geq 3$...
 
-To the east, the Kopeh-Dagh fault system is the predominant faulting system in the seismic zone of the same name.
-This system consists of several partly overlapping segments parallel to a NW--SE oriented structure of step-overs characterized by short south-dipping thrust faults striking E--W \citep{Berberian2001}, which exhibits active tectonic displacements along more than 500 km \citep{Trifonov1978}.
-This system is responsible for the $M_s$ 7.2 earthquake that stroke Ashgabat, the capital city of Turkmenistan and destroyed more than 30 villages in Iran in 1948.
-Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
+ % Earthquakes with magnitude 3 are not considered as a structural threat, however, the epicenter of earthquakes with magnitude $M_w 3$ are a  susceptible location for future bigger earthquakes.
+According to our preliminary data processing based on IIEES data, Iranian catalog for earthquake with magnitude greater and equal 3, is complete from 2005.
+In order to make sure about the completeness of the catalog, we use IIEES data from 2000.
+We used the EMME project data provided by \citet{Zare2014} up to 2000.
+Fig.~\ref{fig:historical} represents the historical data (pre 1900) in the study region.
+
+% In this study we consider earthquakes with Mw equal and greater than 3.
+Earthquakes with magnitude 3 are not considered as a structural threat, however, the epicenter of earthquakes with magnitude $M_w 3$ are a  susceptible location for future bigger earthquakes.
+According to our preliminary data processing based on IIEES data, Iranian catalog for earthquake with magnitude greater and equal 3, is complete from 2005.
+In order to make sure about the completeness of the catalog, we use IIEES data from 2000.
+We used the EMME project data provided by \citet{Zare2014} up to 2000.
+Fig.~\ref{fig:historical} represents the historical data (pre 1900) in the study region.
+
+% \subsubsection{Magnitude Conversion}
+
+% The catalog of recorded earthquake from 2000-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale.
+We converted the $M_L$, $M_s$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}.
+There also some of data which is recorded in $M_D$ (Duration magnitude).
+These data are reported by International Seismological Centre (ISC).
+\citet{Deniz2010}, developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_s$ scales to the $M_w$ scales using orthogonal regression procedure.
+They used data of earthquake that occurred in Turkey from different data centers including ISC.
+In this study we use the conversion equation of \citet{Deniz2010} to convert the Md to Mw.
+Although they defined the equation based on $M_w>=4.5$, we extrapolate the equation for lower magnitude.
+We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate "a" value  in Gutenberge-Richter equation.
+
+% \subsubsection{Declustering}
+
+% It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
+Therefore, in order to accomplish this, we declustered the earthquake catalog.
+In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
+For north Iran (lon: 42-62.5, lat: 33-41), from 7478 earthquake event we removed 605 Foreshocks and 2917 aftershocks.
+% Whole data that we used for seismicity parameters of Zagros and Central Iran tectonic seismic regions are not included in these numbers.
+Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
 
@@
 
-% With respect to different seismicity rates of the regions \citep{Nemati2015}, as well as the completeness of the seismic catalog \citep{Zare2014} , the study region is divided into three tectonic seismic zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-Part of Central Iran and Zagros regions are inside of the study region.
-We also calculated the seismicity parameters in these regions.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
+% \subsection{Historical  and Instrumental Seismicity}
 
-% \begin{figure*}[!ht] 
-% \centering
-% \includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-% \caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-% \label{fig:Iran}
-% \end{figure*}
-
-% \subsection{Tectonic Regions and Seismic Faults}
-
-% \subsubsection{Alborz Mountain Range (Alborz)}
-% Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
-% The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-% The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-
-% \subsubsection{Azerbaijan}
-% There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-% The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-
-% \subsubsection{Kopeh Dagh}
-% The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455.
-% The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-% Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-% The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-% Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-
-% \subsection{Historical  and Instrumental Seismicity}
 % Uniform earthquake catalog is the most important factor in seismic hazard analysis of a region.
@@
 The instrumental data is achievable from three national agencies including IIEES, International Institute of Earthquake Engineering and Seismology; IRSC, The Iranian seismological center, University of Tehran; and BHRC, Building and Housing Research Center (Iran Strong Motion Network) (For more information about these networks see \citet{Karimiparidari2013}).
+
 % Many most of attenuation relationship use  moment magnitude $M_w$ as an input for the equation \citep{Douglas2011}.
@@
 Due to mentioned reasons Mw has become a most appropriate magnitude scale in recent studies.
+
 %  \citet{Karimiparidari2013}compiled a uniform earthquake catalog for Iran and adjacent areas, using international and national databanks until April 2010.

### 2016-03-14 introduction.tex
updates and finished seismic catalog section

@@
 While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to reduce the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
-In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh; but for completeness, we also consider the partial contribution of the areas of Zagros and the central-east seismic zones within our domain of interest (see Figure \ref{fig:Iran}).
+In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh; but for completeness, we also consider the partial contribution of the areas of Zagros and the central-east seismic zones within our domain of interest (see Fig.~\ref{fig:iran}).
 In addition, for comparison purposes, we obtain results for the the combination of all seismic zones as a uniform region.
@@
 We consider two hazard models based on the assumption that damage occurs above an earthquake magnitude $M_w$ 4.5 for informal construction buildings, and above $M_w$ 5.0 for structures built in accordance to code regulations.
-The results of these two models are then combined
-% and 5.0 for unreinforced and reinforced structures, respectively; We later combine these results 
-into a single analysis based on the composition of the structural building inventory of the country.
+The results of these two models are then combined into a single analysis based on the composition of the structural building inventory of the country.
 We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.

### 2016-03-14 seismic-catalog.tex
updates and finished seismic catalog section

@@
-\begin{figure*}[ht!] 
+\begin{figure*}[t] 
 	\centering
 	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
-	\caption{Seismic catalog.
-(a) Historical seismicity prior to 1900.
-(b) Instrumental seismicity.
+	\caption{Location of events considered in the compiled seismic catalog.
+(a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}.
+(b) Instrumental seismicity up until December 2015 for $M_w \geq 3$ (IIEES) and $M_w \geq 4$ \citep[after][]{Zare2014}.
 Size of symbols is proportional to the magnitude of the events.
-In the case of the historical seismicity catalog, the color fill indicates the year of the event.}
-	\label{fig:selected}
+In the case of the historical seismicity catalog, the color fill indicates the year of the event.
+The borderlines of the seismic zones shown in Fig.~\ref{fig:regional} are shown in the background in white, along with the light gray shaded relief.}
+	\label{fig:catalog}
 \end{figure*}
@@
 
-In this study we consider earthquakes with $M_w \geq 3$...
+In this study we adopt the catalog compiled by \citet{Zare2014} for both historical and instrumental earthquakes.
+This catalog includes events of magnitude $M_w \geq 4$ from 550 A.d.~to December 1999.
+We complemented it with events $M \geq 3$ occurred between January 2000 and December 2015 obtained from the IIEES database.
+Our analysis of this dataset indicated that the catalog satisfies completeness from 2005 onward.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
+% The result of our compilation is shown in Fig.~\ref{fig:catalog}, which includes maps for historical and instrumental seismicity. 
+% The following sections provide additional details about magnitude conversion and de\-clustering of the events in our combined catalog.
 
- % Earthquakes with magnitude 3 are not considered as a structural threat, however, the epicenter of earthquakes with magnitude $M_w 3$ are a  susceptible location for future bigger earthquakes.
-According to our preliminary data processing based on IIEES data, Iranian catalog for earthquake with magnitude greater and equal 3, is complete from 2005.
-In order to make sure about the completeness of the catalog, we use IIEES data from 2000.
-We used the EMME project data provided by \citet{Zare2014} up to 2000.
-Fig.~\ref{fig:historical} represents the historical data (pre 1900) in the study region.
+The portion of the catalog obtained from IIEES for $M \geq 3$ earthquakes between 2000 and 2015 contained event reports that use different magnitude scales.
+We converted all events with magnitudes in $M_L$, $M_s$, and $mb$ scales to $M_w$ using the same conversion relationships used by \citet{Zare2014}, which allowed us to preserve compatibility with the historical and instrumental seismicity catalog adopted from the same work of \citet{Zare2014}.
+In addition, the dataset from IIEES also contained events reported with duration magnitude ($M_D$), as reported by the International Seismological Centre (ISC).
+In these cases we used the empirical relationship developed by \citet{Deniz2010} to convert $M_D$ to $M_w$.
+Although this relationship was derived based on a dataset for $M_w>=4.5$ events, we extrapolate the equation for lower magnitude and found that results to adjust well with the general trend, which should provide for good estimates of the $a$-value in the Gutenberg-Richter equation.
 
-% In this study we consider earthquakes with Mw equal and greater than 3.
-Earthquakes with magnitude 3 are not considered as a structural threat, however, the epicenter of earthquakes with magnitude $M_w 3$ are a  susceptible location for future bigger earthquakes.
-According to our preliminary data processing based on IIEES data, Iranian catalog for earthquake with magnitude greater and equal 3, is complete from 2005.
-In order to make sure about the completeness of the catalog, we use IIEES data from 2000.
-We used the EMME project data provided by \citet{Zare2014} up to 2000.
-Fig.~\ref{fig:historical} represents the historical data (pre 1900) in the study region.
-
-% \subsubsection{Magnitude Conversion}
-
-% The catalog of recorded earthquake from 2000-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale.
-We converted the $M_L$, $M_s$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}.
-There also some of data which is recorded in $M_D$ (Duration magnitude).
-These data are reported by International Seismological Centre (ISC).
-\citet{Deniz2010}, developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_s$ scales to the $M_w$ scales using orthogonal regression procedure.
-They used data of earthquake that occurred in Turkey from different data centers including ISC.
-In this study we use the conversion equation of \citet{Deniz2010} to convert the Md to Mw.
-Although they defined the equation based on $M_w>=4.5$, we extrapolate the equation for lower magnitude.
-We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate "a" value  in Gutenberge-Richter equation.
-
-% \subsubsection{Declustering}
-
-% It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-For north Iran (lon: 42-62.5, lat: 33-41), from 7478 earthquake event we removed 605 Foreshocks and 2917 aftershocks.
-% Whole data that we used for seismicity parameters of Zagros and Central Iran tectonic seismic regions are not included in these numbers.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
+Last but not least important, we declustered the catalog prior to using it in the assessment of seismic hazard for the region of interest.
+This entailed the removal of foreshocks and aftershocks from the catalog to adjust the dataset to include only those events in agreement with a Poissonian model, which is a well-accepted model for seismic sources.
+Out of the original 7,478 earthquakes in the assembled catalog for the seismic regions of Azerbaijan, Alborz and Kopeh-Dagh, we removed 605 foreshocks and 2,917 aftershocks.
+The resulting final set of events in the catalog compiled for this study is shown in Fig.~\ref{fig:catalog}, which includes maps for both historical and instrumental seismicity.
 

### 2016-03-14 figures/gmt/selectedfaults.sh
Fault line script added.

@@ -1,0 +1,3238 @@
+
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=selectedquakes
+PSNAME=${OUTNAME}.ps
+
+# Top Map - Notable
+# ------------------------------------------------------------------------------
+
+gmt grdgradient mytopo.grd -A300 -Gmytopo.grad -Nt
+gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWneS -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+#Garmsar Fault
+gmt psxy  -W0.35p,black  -R -J -B -V -O -K >> ${PSNAME} << END
+51.863075	35.202847
+51.893387	35.209576
+51.91615	35.213024
+51.942707	35.21652
+51.96547	35.219967
+52.01144	35.198116
+52.030754	35.179165
+52.053814	35.163452
+52.08808	35.16064
+52.129898	35.161106
[…]

### 2016-03-14 figures/gmt/selectedfaults.sh
Add Temp_fault.ai file.

@@ -22,7 +22,7 @@ gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
 # Set script constants
 # ------------------------------------------------------------------------------
 
-OUTNAME=selectedquakes
+OUTNAME=selectedfaults
 PSNAME=${OUTNAME}.ps
 
 # Top Map - Notable

### 2016-05-12 analysis_parameters.tex
revise the seismic hazard section and also polish the figure 4 and 5.

@@
 \section{Analysis Parameters}
-%\subsection{Magnitude Interval}
-%\subsection{Minimum Magnitude}
 \subsection{Attenuation Relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
+
+The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis.
 \citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
@@
 Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ).
-We also presented the results for  $\pm$ standard deviation.
+The epistemic uncertainty in attenuation relationship is being considered through using the logic tree approach.
+Having close mean value and similar logic tree weights, logic tree approach will have a minor effect in considering the epistemic uncertainty.
+In this study instead of using  different GMPEs we use the best model of attenuation relationship for PGA \citep{Zafarani2014} as well $\pm$ standard deviation.
 \\
@@
 
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
 \subsection{b-value}
 
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
+For each of the three seismic regions, Gutenberg-Richter parameters and maximum magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
 The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
@@
 Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively.
-For the north Iran uniform model we used 4.5 as a completeness magnitude.
+For the uniform model we used 4.5 as a completeness magnitude.
 In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
+We also used the seismicity parameters of \citet{Karimiparidari2013} as the priory information in HA3 code.
 The updated values are displayed in Table \ref{tab:b_value}.
@@
 \centering
-\includegraphics[scale=0.4]{figures/pdf/annual_rate_m.pdf} 
-\caption{Annual occurrence rate of the earthquake. a) Azerbaijan, b) Alborz, c) KopehDagh, d)Central, e)Zagros f) North Iran}
+\includegraphics[scale=0.3]{figures/pdf/figure-04} 
+\caption{The annual probability of exceeding the specified magnitude in different seismic tectonic region (a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros).
+The margin display the positive and negative standard deviation.}
 \label{fig:annual_m}
@@
 He assumes that from the point that the line become linear, the catalog is complete.
-Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP \citep{Wiemer2001}, \citet{Zare2014} reported the catalog completeness for the study regions.
+This approach is similar to the MAXC method of ZMAP software \citep{Wiemer2001}, where the completeness treshold is the maximum value of the first derivative of the frequency-magnitude curve.
+Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP, \citet{Zare2014} reported the catalog completeness for the study regions.
 World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
@@
 \centering
-\includegraphics[scale=0.6]{figures/pdf/completness_scatter.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c)Central, d)Kopeh-Dagh, e)Zagros}
+\includegraphics[scale=0.5]{figures/pdf/figure-05.pdf} 
+\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros}
 \label{fig:completness_scatter}
@@
 The catalog may or may not be completed after 1045, however in this study we consider 1581 as a completeness threshold for magnitude  $ 6 < Mw \leq 7 $.
-Considering completeness of the catalog for Azerbaijan region from 1581 will result in conservative PGA for the region in compare with the model with threshold of 1045.
+Considering completeness of the catalog for Azerbaijan region from 1581 will result in conservative PGA for the region in comparison with the model with threshold of 1045.
 We picked the completeness threshold for other regions and other magnitude ranges according as a year that the cumulative number of earthquakes increment uniformly.
@@
 \end{table*}
+
+%% ---------------------------------------------
+%% ---------------------------------------------
+%
+%% My (Naeem) original text.
+%
+%
+%\section{Analysis Parameters}
+%%\subsection{Magnitude Interval}
+%%\subsection{Minimum Magnitude}
+%\subsection{Attenuation Relationship}
+%The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
+\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
+After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
+Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
+Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
+Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
+\citet{Kalkan2004} ).
+We also presented the results for  $\pm$ standard deviation.
+\\
+%
+%\noindent
+%The attenuation relationship is:
+%
+%\begin{equation}
+%\begin{split}
+%ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
+%b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
+%\end{split}
+%\end{equation}
+%
+%where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
+%
+%\subsection{b-value}
+%
+%For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
+The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
+For smoothed seismicity areas, $b-value$ is assumed constant.
+The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.\\
+%\noindent
+%\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
+Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively.
+For the north Iran uniform model we used 4.5 as a completeness magnitude.
+In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
+We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
+The updated values are displayed in Table \ref{tab:b_value}.
+Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.
+%
+%\begin{figure*} [!ht]
+%\centering
+%\includegraphics[scale=0.4]{figures/pdf/annual_rate_m.pdf} 
+%\caption{Annual occurrence rate of the earthquake. a) Azerbaijan, b) Alborz, c) KopehDagh, d)Central, e)Zagros f) North Iran}
+%\label{fig:annual_m}
+%\end{figure*}
+%
+%
+%
+%
+%\noindent
+%
+%
+%\begin{table*}[!ht]
+%\centering
+%\caption{Seismicity parameters for three tectonic seismic regions.}
+%    \begin{tabular}{ccccc}
+%    ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
+%    Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
+%    Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
+%    Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
+%    Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
+%    Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
+%    Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
+%    \end{tabular}
+% \label{tab:b_value} 
+%\end{table*}
+%
+%
+%\subsection{Catalog Completness}
+%For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
+\citet{Frankel1995} plotted the cumulative number of events against time for different regions.
+He assumes that from the point that the line become linear, the catalog is complete.
+Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP \citep{Wiemer2001}, \citet{Zare2014} reported the catalog completeness for the study regions.
+World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
+Up to 1961 these data formed the early instrumental period.
+In 1961 the Worldwide Standardized Seismograph Network (WWSSN) was stablished.
+The record of these seismographs considerably improved the seismic catalogs in different part of the world \citep{Shearer2009}.
+Fig.~\ref{fig:completness_scatter} shows the magnitude distribution of events with respect to the time of occurrence of the events.
+%
+%\begin{figure*} [!ht]
+%\centering
+%\includegraphics[scale=0.6]{figures/pdf/completness_scatter.pdf} 
+%\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c)Central, d)Kopeh-Dagh, e)Zagros}
+%\label{fig:completness_scatter}
+%\end{figure*}
+%
+% According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions' catalog.
+We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
+In order to be able to compare the results with \citet{Zare2014} we merge the data of Azerbaijan and Alborz seismic regions.
+Fig.~\ref{fig:completness_compare_zare_2014_Az_Al} shows the completeness of catalog for earthquakes with different magnitude range in Azerbaijan-Alborz region.
+According to this figure, midrange magnitudes ($ 4 < Mw < 6 $) fairly obey the network developments in 1900 and 1961.
+The completeness thresholds for each magnitude range which are reported by \citet{Zare2014} are shown by dashed green line.
+In this study we follow the \citet{Frankel1995} approach to determine the completeness of each region.
+Even though the approach used by \citet{Frankel1995} will lead to the conservative results, we make sure that we don't use a period of time without knowing the complete number of events.
+Determining the completeness of the catalog is very sensitive to the data.
+Converting earthquake magnitudes from different scales to moment magnitude obviously has some error.
+Having broader range of magnitude will help to minimize these sort of error.
+In this study we consider the magnitude intervals for completeness study as $Mw = 1$.
+%
+%\begin{figure*} [!ht]
+%\centering
+%\includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
+%\caption{Cumulative number of earthquakes with respect to the time.
+Magnitude range is represented in a box at the top left corner.
+Solid black lines represent the starting of early instrumental (1900) and instrumental (1961) period.
+Green dashed lines represents the completeness threshold reported by \citet{Zare2014}.
+Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
+%\label{fig:completness_compare_zare_2014_Az_Al}
+%\end{figure*}
+%
+%\noindent
+%Fig.~\ref{fig:comp_test_all_mag} illustrates the completeness of data for each magnitude threshold in five different regions.
+A uniform rise of cumulative number of earthquake in each magnitude range, defines the threshold for catalog completeness.
+We define the completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
+We assume the catalog for earthquakes with magnitude greater than  7 ($M_w > 7$) is complete from the first historical earthquake report.
+Determining the completeness of the catalog for $ 6 < Mw \leq 7 $ needs precise observation of the catalog.
+In Azerbaijan tectonic seismic region after 1045  $Mw = 6.2$ earthquake the catalog seems complete up to 1318.
+However, between 1318 and 1581 (263 years) only one earthquake with magnitude $Mw > 6$ is reported (1440,  $Mw = 6.2$ ).
+Considering the activity of the Azerbaijan region, in this study we assume that the catalog is complete for earthquake with magnitude $ 6 < Mw \leq 7 $ after 1581.
+Similar situation happened at the period of 1715 - 1833.
+It worth to mention that in this case, the time period is shorter than before (118 years), meanwhile in this period of time two earthquakes with magnitude $Mw>7$ occurred in the Azerbaijan region (1721 $Mw=7.7$, 1780 $Mw=7.6$).
+The catalog may or may not be completed after 1045, however in this study we consider 1581 as a completeness threshold for magnitude  $ 6 < Mw \leq 7 $.
+Considering completeness of the catalog for Azerbaijan region from 1581 will result in conservative PGA for the region in compare with the model with threshold of 1045.
+We picked the completeness threshold for other regions and other magnitude ranges according as a year that the cumulative number of earthquakes increment uniformly.
+Table ~\ref{tab:completeness} shows the summary of values used in this study.
+%
+%
+%
+%\begin{figure*} [!ht]
+%\centering
+%\includegraphics[scale=0.28]{figures/pdf/comp_test_all_mag.pdf} 
+%\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Kopek Dagh, g-h)Kopeh Dagh, i-j)Zagros}
+%\label{fig:comp_test_all_mag}
+%\end{figure*}
+%
+%
+%
+%\begin{table*}[!ht]
+%\centering
+%\caption{Completeness threshold of tectonic seismic regions.}
+%\begin{tabular}{ccccccccc}
+% ~           & Azerbaijan & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
+%3-4         & 1961          & 2005   & 2005             & 2005            & 2005    & 2005          \\ \hline
+%4-5         & 1961          & 1961   & 1950             & 1961            & 1961    & 1961          \\ \hline
+%5-6         & 1900          & 1900   & 1900             & 1854            & 1900    & 1900           \\ \hline
+%6-7         & 1581          & 1664   & 1673             & 1837            & 1853    & 1778           \\ \hline
+%7 $< $    & 1042          & -401    & 9                   & 762              & 1439    & -401            \\ 
+%\end{tabular}
+%\label{tab:completeness}
+%\end{table*}

### 2016-05-12 seismic_hazard.tex
Section 5 added.
revise the seismic hazard section and also polish the figure 4 and 5.

@@
 
-\subsection{Background}
-
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
+Occurrence of devastating historical earthquake and also essential needs for constructing new buildings and infrastructures inspired researchers to study the seismic hazard of northern Iran from different points of view.
+Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years corresponding to 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
+According to their study, North Tabriz fault zone and north of Tehran fault zone have the highest acceleration.
 Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
@@
 The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In this study we use background seismicity to calculate the seismic hazard.Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
+In this study we use background seismicity to estimate the seismic hazard in northern Iran.
+Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
 They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
@@
 \subsubsection{smoothed seismicity method}
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
+We use spatially smoothed seismic hazard analysis \citep{Frankel1995} to estimate the seismic hazard.
 In this model, seismic events are spatially gridded to cells.
@@
 Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_ w5$ .
-Category 5+ and others ($M6+$ and $M7+$) assume that future $M_w 4.5$ events will occur near where they have occurred in the past.
+Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$ .
+Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
 \\
 \noindent
-According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
+According to Building and Housing Research Center  \citep{BHRC2014}, $M_w 5$ is considered as a threshold magnitude for onsetting the structural damage.
+In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
 \\
 \noindent
-\noindent
+
 In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
@@
 \begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
+\begin{split}
+\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} \\
+p(u>u_0 | D_k ,M_l),
+\end{split}
 \end{equation}
+
 \noindent
@@
 $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
+This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}.
+
+% -----------------------------------------------------------------------
+% -----------------------------------------------------------------------
+
+%%% My (Naeem) original text
+
+%\subsection{Background}
+%
+%Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
+Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
+According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
+Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
+In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
+The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
+%In this study we use background seismicity to calculate the seismic hazard.Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
+They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
+\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
+They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
+They gained an acceptable PGA in comparison with other seismic hazard approaches.
+\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
+Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
+This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
+%
+%\subsection{Analysis Method}
+%\subsubsection{smoothed seismicity method}
+%To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
+In this model, seismic events are spatially gridded to cells.
+We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
+According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
+Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
+Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_ w5$ .
+Category 5+ and others ($M6+$ and $M7+$) assume that future $M_w 4.5$ events will occur near where they have occurred in the past.
+\\
+%\noindent
+%According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
+In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
+\\
+%\noindent
+%\noindent
+%In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
+We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
+number of events bigger than $M_{ref}$) values to incremental (i.e.
+number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values.
+Using Gaussian function we smooth the number of events in each cell.
+The smoothed value $\tilde{n}_i$ is obtained from
+%
+%\begin{equation}
+%\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
+%\end{equation}
+%
+%\noindent
+%where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
+$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
+The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
+%\noindent
+%Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
+%Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to 
+%
+%\begin{equation}
+%\begin{split}
+%\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} \\
+%p(u>u_0 | D_k ,M_l),
+%\end{split}
+%\end{equation}
+
+%\noindent
+%where $k$ and $l$ are denoted as index of distance and magnitude bin.
+$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
 This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\subsubsection{ingredients}

### 2016-05-12 hazard_analysis_results.tex
first general revision.

@@
 \noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central Iran and the Zagros tectonic seismic regions.\\
+As mentioned earlier we broader the study region by 0.5\textdegree{}-perimeter to avoid the unexpected effect of outer border seismicity as well as avoiding the artifcial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
+Also it provides more uniform surrounding of the study area\citep{Lapajne1997}.
 \noindent
@@
 Even though the uncertainties are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 13561.
+Regarding the study domain and the 0.1 grid size, the total number of source as grid points is 13561.
 Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
@@
 
-\subsection{5 Regions}
+\subsection{Peak Ground Acceleration}
 We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance. 
@@
 
-\subsection{Uniform Region}
 Fig.~\ref{fig:pga_10_mean_uniform} and Fig.~\ref{fig:pga_2_mean_uniform} show the results for 10\% and 2\% probability of exceedance in 50 years for the uniform model, respectively.
@@
 \end{figure*}
-
-%\subsection{3 Regions}

### 2016-05-26 Hazard_calculation.tex
New paper summary added.

@@
 \noindent
+As discussed before the border of the study region 
 Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.

### 2016-05-26 GMT_sctipts/smoothed_pga/pga_data_plots.m
GMT script to plot the pga values + data added.

@@ -1,0 +1,175 @@
+clc
+clear all
+close all 
+
+
+load ('pga_10_50_mean_m_45.txt');
+load ('pga_10_50_mean_m_45_uniform.txt');
+load ('pga_10_50_mean_m_5.txt');
+load ('pga_10_50_mean_m_5_uniform.txt');
+load ('pga_10_50_minus_m_45.txt');
+load ('pga_10_50_minus_m_45_uniform.txt');
+load ('pga_10_50_minus_m_5.txt');
+load ('pga_10_50_minus_m_5_uniform.txt');
+load ('pga_10_50_plus_m_45.txt');
+load ('pga_10_50_plus_m_45_uniform.txt');
+load ('pga_10_50_plus_m_5.txt');
+load ('pga_10_50_plus_m_5_uniform.txt');
+load ('pga_2_50_mean_m_45.txt');
+load ('pga_2_50_mean_m_45_uniform.txt');
+load ('pga_2_50_mean_m_5.txt');
+load ('pga_2_50_mean_m_5_uniform.txt');
+load ('pga_2_50_minus_m_45.txt');
+load ('pga_2_50_minus_m_45_uniform.txt');
+load ('pga_2_50_minus_m_5.txt');
+load ('pga_2_50_minus_m_5_uniform.txt');
+load ('pga_2_50_plus_m_45.txt');
+load ('pga_2_50_plus_m_45_uniform.txt');
+load ('pga_2_50_plus_m_5.txt');
+load ('pga_2_50_plus_m_5_uniform.txt');
+
+
+% NW differ slightly in 2% & 10% 
+figure;
+scatter3(pga_2_50_mean_m_5_uniform(:,1),pga_2_50_mean_m_5_uniform(:,2),pga_2_50_mean_m_5_uniform(:,3),40,pga_2_50_mean_m_5_uniform(:,3),'filled')
+title ('pga-2-50-mean-m-5-uniform')
+
+
+figure;
+scatter3(pga_10_50_mean_m_5_uniform(:,1),pga_10_50_mean_m_5_uniform(:,2),pga_10_50_mean_m_5_uniform(:,3),40,pga_10_50_mean_m_5_uniform(:,3),'filled')
+title ('pga-10-50-mean-m-5-uniform')
+
+% 
+% %%%%%%%%%%%%%%%%%%%
+
+figure;
[…]

### 2016-05-26 GMT_sctipts/smoothed_pga/smoothed_pga.sh

@@ -1,0 +1,38 @@
+#!/bin/sh
+# Makes smoothed seismicity map from EQ catalog
+
+filename=`echo $1`
+
+gmt4 gmtset HEADER_FONT = 4
+gmt4 gmtset HEADER_FONT_SIZE = 20
+gmt4 gmtset GRID_CROSS_SIZE_PRIMARY = 1
+gmt4 gmtset LABEL_FONT = 4
+gmt4 gmtset LABEL_FONT_SIZE = 20
+
+
+
+gmt4 psxy -R43.5/61.5/34/40 -Jm1.2c -Ba1f0.2/a1f0.2WSNE -W5t5_5:0 -K  -H  -Y5  sqrt.d >pgamap.ps
+gmt4 blockmean $filename.txt -R -I.01>tempmean
+gmt4 surface tempmean -R -I.01 -Gtempmap.grd -T0.3
+gmt4 grdimage tempmap.grd -R -Jm1.2c -Ccont1.cpt -K -O >>pgamap.ps
+gmt4 grdcontour tempmap.grd -Jm1.2c -R -O -K -C0.1 -A0.1 >> pgamap.ps
+gmt4 pscoast -R -Jm1.2c -B2g2/2g2:."Northern Iran seismic zone 10% in 50y PGA Hazard Map": -Dh -W1 -K -O -Na >>pgamap.ps
+gmt4 psscale -Ccont1.cpt -D14.0/3.5/6.0/0.3 -O -B:g: -X9 >>pgamap.ps
+
+#ps2pdf pgamap.ps pgaMapO1.pdf
+
+#ps2raster pgamap.ps -TG -Au -FpgaMapO1-png
+
+ps2pdf pgamap.ps $filename.pdf
+
+
+#gv pgamap.ps &
+
+# uncomment to have png surface
+#psxy -R43.5/61.5/34/40 -Jm1.2c -Ba1f0.2/a1f0.2WSNE -W5t5_5:0 -K  -H  -Y5  sqrt.d >pgamap.ps
+#psbasemap -R -Jm1.2c -Bwesn  -K  -Y5 >pgamap.ps
+#blockmean pga_2_50.txt -R -I.01>tempmean
+#surface tempmean -R -I.01 -Gtempmap.grd -T0.3
+#grdimage tempmap.grd -R -Jm1.2c -Ccont1.cpt -K  -O >>pgamap.ps
[…]

### 2016-06-02 abstract.tex
modified figure 2 and improved references up to catalog section

@@
 We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh; and for completeness, we also consider the contribution of parts of other neighboring seismic zones that fall within our region of interest.
-% For completeness, we also consider the partial contribution of the seismic zones of Zagros to the southwest, and the south-central and southeastern Iranian seismic zones. 
-In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources by in themselves, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude.
+In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude.
 After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
 Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region.
-Seismic hazard curves are obtained for two
-% distinct 
-models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, depending on the type of construction, 
- % for unreinforced and reinforced structures, respectively. We 
-and also obtain results for a combined scenario using these two models.
+Seismic hazard curves are obtained for two models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, depending on the type of construction.
+We
+also obtain results for a combined scenario using these two models.
 The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
@@
 In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.
-
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
-% Smoothing was done using a Gaussian filter in incremental intervals of magnitude.
-
-% greater than 4.5 for unreinforced and informal construction buildings, and greater than 5.0 for modern structures following design regulations
-
-% Naeem's comment about differences with previous studies...
-
-% We may need to write the conclusion from other point of view.
-The method, attenuation relationship, and even data (some sort of) are different from other studies.
-So we expect to see different results.
-Not only we expect but at some point we should see some differences because of the method.
-There are some places that we don't have any recorded earthquake or they are not  as much to increase the hazard.
-In this study for those places we get lower hazard, but in studies based on recognizing faults as a source, they ends up with higher hazard.
-I think we can say that even though the other studies are good, but they are not complete and we need to use this method alongside them.
-
-% Naeem's comment about GMPE...
-
-% The attenuation relationship \citep{Kalkan2004} has been introduced in 2004 (Not recently).
-In 2014, \citet{Zafarani2014} evaluated many different attenuation relationship based on recently recorded data.
-They found \citet{Kalkan2004} has the best fit with data for PGA.
-
-% Naeem's info about magnitude selection...
-
-% We used earthquake with magnitude 3 and greater only after 2000, before that data are greater than 4.
-
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
-% Naeem's original abstract
-% -------------------------
-
-% In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over whole three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) and part of two tectonic seismic zones (Zagros and Central-East Iran) using smoothed seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We also consider the combination of regions as a uniform region.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.

### 2016-06-02 introduction.tex
modified figure 2 and improved references up to catalog section

@@
 
-This article presents a new seismic hazard assessment for northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to be the most reliable attenuation relationship to predict peak ground response in the region.
+This article presents a new seismic hazard assessment for the northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to be the most reliable attenuation relationship to predict peak ground response in the region.
 
@@
 According to this tectonic setting and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, and up to twenty to twenty-three seismotectonic provinces in the more elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
-Contemporary, well-accepted studies divide Iran into five major tectonic regions: Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran \citep[e.g.,][]{Mirzaei1998}.
+Contemporary, well-accepted models divide Iran into five major tectonic regions: Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran \citep[e.g.,][]{Mirzaei1998}.
 More recently, in a study aimed to develop a uniform earthquake catalog for Iran, \citet{Karimiparidari2013} further divided the Azerbaijan-Alborz region into two separate seismic zones: Azerbaijan and the Alborz Mountain Range, hereafter referred to simply as Alborz.
-We adopt the latter definition of six seismic basic seismic zones and focus our attention on those most relevant to the northern part of the country, that is, Azerbaijan, Alborz and Kopeh-Dagh.
+We adopt the latter definition of six seismic seismic zones and focus our attention on those most relevant to the northern part of the country, Azerbaijan, Alborz and Kopeh-Dagh.
 
-Over the last three decades there have been multiple efforts to better estimate the seismic hazard and assess seismic risk in Iran \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE}.
-These studies have been, in part, intended to help improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-While improvements in design practice are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran, other indicators suggest high levels of seismic risk.
-Therefore, more complete and accurate assessments of seismic hazard---incorporating the latest available data and alternative methods---are necessary.
+Over the last three decades there have been multiple efforts to better estimate the seismic parameters and hazard, and improve the assessment of seismic risk in Iran \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE, Khodaverdian_2016_BSSA}.
+The most recent of these studies \citep{Khodaverdian_2016_BSSA} focuses in the estimation of spatially-variable seismic parameters for the whole country using a similar approach to the one we used here.
+We, however, focus our attention in the northern three seismic zones of the country assuming regionally-based seismic parameters.
+Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
+Such improvements are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran.
+However, other indicators suggest persistent high levels of seismic risk.
+Therefore, more complete and accurate assessments of seismic hazard---incorporating the latest available data and alternative methods---are still deemed necessary.
 
 Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil.
-This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.
-Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
-Among other things, these studies have highlighted the prevailing differences between different studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.
+This region has suffered devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.
+Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
+Among other things, these studies have highlighted the prevailing differences between studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.
 
-However useful, most previous studies focus on particular locations or are based on specific categorization of seismogenic faults, which are often subjectively interpreted and limited to the availability data.
-Here, we use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This approach has been used with success in other regions \citep[e.g.][]{Boyd2008, Kalkan2009, Moschetti2014}.
+Most previous studies focus on particular locations or are based on specific categorization of seismogenic faults, which are often subjectively interpreted and limited to data availability.
+We use the smoothed seismicity method introduced by \citet{Frankel1995}.
+This approach has been used with success in other regions \citep[e.g.][]{Boyd2008, Kalkan2009, Moschetti2014}, including Iran \citep{Khodaverdian_2016_BSSA}.
 Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
@@
 
-In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the approach followed to estimate seismic hazard for the region.
-Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region \citep{Zafarani2014, Kalkan2004}, and the estimation of the Gutenberg-Richter seismicity parameters, which are necessary for the smoothed seismicity method.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We consider two hazard models based on the assumption that damage occurs above an earthquake magnitude $M_w$ 4.5 for informal construction buildings, and above $M_w$ 5.0 for structures built in accordance to code regulations.
-The results of these two models are then combined into a single analysis based on the composition of the structural building inventory of the country.
+In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the adopted approach.
+Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region \citep{Zafarani2014, Kalkan2004}, and the estimation of the Gutenberg-Richter seismicity parameters.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, considering different magnitude thresholds.
 We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.

### 2016-06-02 region-of-interest.tex
updates and finished seismic catalog section
modified figure 2 and improved references up to catalog section

@@
-\begin{figure*}[ht!] 
+\begin{figure*}[t] 
 	\centering
@@
 
-\begin{figure*}[ht!] 
+\begin{figure*}[t] 
 	\centering
 	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-02}
-	\caption{Notable earthquakes in the region of interest and within three major seismic zones in northern Iran.
+	\caption{(a) Main fault line and fault systems, and (b) notable earthquakes in the region of interest.
+White lines delimit the three major seismic zones in northern Iran.
 Epicentral locations are indicated with stars.
@@
 
-Seismic activity in the Iranian plateau is dominated by the tectonic contacts between the Arabian, Eurasian, and Indian plates, which confine the region laterally between the Indian and Eurasian plates, and the Arabian and eastern Asia-Minor plates to the east and west, respectively.
-This setting gives rise to the Zagros, Alborz, and east Iranian mountain ranges, and defines the geology of the region.
-Based on these conditions, Iranian seismicity is typically divided into various seismic zones, varying from as few as four to as many as twenty-three \citep[e.g.,][]{Stocklin1968, Berberian1976, Tavakoli1999}.
-Here, we adopt the model proposed by \citet{Karimiparidari2013}, which consists of six seismic zones: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East, and Makram (Fig.~\ref{fig:iran}).
-
-Within this context, we define our region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}.
+We define our region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}.
 These limits correspond to the effective region of interest for which we will present results in subsequent sections.
@@
 This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
-The effective region has an area of 1,703 km $\times$ 667 km, and as shown in Fig.~\ref{fig:iran}, it encloses the northern part of Iran with most of the Azerbaijan seismic zone, the complete zones of Alborz and Kopeh-Dagh, and the northernmost portions of the Zagros and Central-East seismic zones.
+The effective region has an area of 1,703 km $\times$ 667 km.
+It encloses the northern part of Iran with most of the Azerbaijan seismic zone, the complete zones of Alborz and Kopeh-Dagh, and the northernmost portions of the Zagros and Central-East seismic zones.
 
 At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault (NTF) system.
-This system is a complex northwest-trending structure with a predominant right-lateral, str\-ike-slip faulting mechanism \citep{Berberian1999}.
+This system, shown in Fig.~\ref{fig:selected}a, is a complex northwest-trending structure with a predominant right-lateral, strike-slip faulting mechanism \citep{Berberian1999}.
 Historical accounts document the occurrence of earthquakes in this area as far back as to the 9th century, with events in the years 858 ($M$ 6.0), 1042 ($M$ 7.3), and 1304 ($M$ 6.7) \citep{Berberian1999}.
 In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.7 1721 Tabriz earthquake in the southeastern section, the $M$ 7.6 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
-According to \citet{Jones1834}, the Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively; and the latter presented vertical separations of about 2 to 4 m.
-Other notable events include the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes.
-More recently, the same region was stroke by the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage and took the lives of more than 1500 people \citep{USGS_ardabil, USGS_tabriz}.
+According to \citet{Jones1834}, the Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively, and the latter presented vertical separations of about 2 to 4 m.
+The locations of these and other notable events, including the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes, are shown in Fig.~\ref{fig:selected}b.
+More recently, the same region was stroke by the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage and took the lives of more than 1500 people.
 
 Transitioning from the Azerbaijan to the Alborz seismic zone, the next fault system runs along the Rocks of the Talesh mountains, to the northwest of the Alborz Mountains.
-Faults in this area have ruptured recently \citep{Berberian1999}.
-% , including an $M_s$ 6.0 low-angle thrust earthquake in 1978 \citep{Berberian1999} and 
-The $M_w$ 7.4 1990 Manjil-Rudbar earthquake, for instance, caused numerous deaths and significant damage to the region in the south Caspian depression \citep{USGS_manjil}.
-At the central area of the Alborz seismic zone, near Tehran, the region is characterized by active reverse faults in the North Tehran Thrust (NTT) system.
+Faults in this area have also ruptured recently \citep{Berberian1999}.
+The $M_w$ 7.4 1990 Manjil-Rudbar earthquake, for instance, caused numerous deaths and significant damage to the region in the south Caspian depression.
+At the central area of the Alborz seismic zone, near Tehran, the region is characterized by active reverse faults in the North Tehran Thrust (NTT) system (see Fig.~\ref{fig:selected}a for reference).
 These faults are parallel to the northwest-trending structural gain of the Alborz Mountains belt, and include the south-dipping partially blind faults of Davudieh, Shian, and Bagh-E Feyz.
@@
 
-To the east, the Kopeh-Dagh fault system is the predominant faulting system in the seismic zone of the same name.
-This system consists of several partly overlapping segments parallel to a NW--SE oriented structure of step-overs characterized by short south-dipping thrust faults striking E--W \citep{Berberian2001}, which exhibits active tectonic displacements along more than 500 km \citep{Trifonov1978}.
-This system is responsible for the $M_w$ 7.3 earthquake that stroke Ashgabat, the capital city of Turkmenistan and destroyed more than 30 villages in Iran in 1948.
-Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at the boundary between the Neyshabur and Binalud reverse faults between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D., roughly 30 kilometers from the border of Iran \citep{Berberian2001}.
-These and other notable earthquakes in the seismic zones of Azerbaijan and Alborz are shown in Fig.~\ref{fig:selected}.
+To the east, the Main Kopeh-Dagh Fault is the predominant faulting system in the seismic zone with the same name.
+This system consists of several partly overlapping segments parallel to a NW--SE oriented structure of step-overs, which exhibits active tectonic displacements along a distance of more than 500 km \citep{Trifonov1978}.
+The system is also characterized by short south-dipping thrust faults striking E--W \citep{Berberian2001}.
+The Main Kopeh-Dagh Fault is responsible for the $M_w$ 7.3 1948 earthquake (Fig.~\ref{fig:selected}b).
+This event stroke Ashgabat, the capital city of Turkmenistan, and destroyed more than 30 villages in Iran.
+Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at the boundary between the Neyshabur and Binalud reverse faults (Fig.~\ref{fig:selected}a) between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001}.
+
+% *********************************************************************************************************************
+% *********************************************************************************************************************
+
+% Seismic activity in the Iranian plateau is dominated by the tectonic contacts between the Arabian, Eurasian, and Indian plates, which confine the region laterally between the Indian and Eurasian plates, and the Arabian and eastern Asia-Minor plates to the east and west, respectively.
+This setting gives rise to the Zagros, Alborz, and east Iranian mountain ranges, and defines the geology of the region.
+Based on these conditions, Iranian seismicity is typically divided into various seismic zones, varying from as few as four to as many as twenty-three \citep[e.g.,][]{Stocklin1968, Berberian1976, Tavakoli1999}.
+Here, we adopt the model proposed by \citet{Karimiparidari2013}, which consists of six seismic zones: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East, and Makram (Fig.~\ref{fig:iran}).
+
+% Within this context, w
 

### 2016-06-02 seismic-catalog.tex
modified figure 2 and improved references up to catalog section

@@
 These studies, however, differ from each other in their use of magnitude scales or magnitude conversion rules, and the extent to which they accept historical accounts as valid data.
-According to \citet{Ambraseys2005}, for instance, there is evidence of earthquakes that goes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret.
+
+According to \citet{Ambraseys2005}, there is evidence of earthquakes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret.
 \citet{Mirzaei1997} compiled a catalog with historical events dating back to the 4th century B.C.~and instrumental earthquakes through 1994 in which a comprehensive list of studies was considered and magnitudes uniformly converted to surface wave magnitude ($M_s$).
+Most ground motion prediction equations employed today in seismic hazard, however, use moment magnitude ($M_w$) instead.
 
-Most ground motion prediction equations used today for seismic hazard assessments, however, use moment magnitude ($M_w$) instead, as it is well-known that this magnitude scale does not suffer from saturation issues as other scales, and provides a meaningful relationship with the physics of the rupture.
 Recent catalogs such as that by \citet{Karimiparidari2013}, \citet{Shahvar2013}, and \citet{Zare2014} are all compiled using magnitudes converted to $M_w$.
 \citet{Karimiparidari2013}, for instance, compiled a catalog for Iran and adjacent areas using international and national datasets including events up until April, 2010 with $M_w > 5$.
-They developed relationships between moment magnitude and other magnitude scales and removed dependent events (foreshocks and aftershocks) using the procedure by \citet{Gardner1974}.
+They developed relationships between moment magnitude and other magnitude scales and removed foreshocks and aftershocks using the procedure by \citet{Gardner1974}.
 \citet{Shahvar2013} built a catalog for the Iranian plateau for events with $M_w \geq 4$ merging data from two local and seven international datasets for the 1900--2011 period.
-They used the orthogonal regression method by \citet{Castellaro2006} to derive magnitude conversions and removed foreshocks and aftershocks according to the procedure by \textcolor{red}{Uhrhammer (1986)}.
+They used the orthogonal regression method by \citet{Castellaro2006} to derive magnitude conversions and removed foreshocks and aftershocks according to the procedure by \citet{Uhrhammer_1986_EN}.
 In addition, \citet{Shahvar2013} provided a declustered version of the catalog.
 
-In turn, the catalog by \citet{Zare2014} uses both historical data prior to 1900 and instrumental data up until 2006, and includes events from Afghanistan-Pakis\-tan, Saudi Arabia, the Caucasus, and parts of Turkey in addition to the Alborz-Azerbaijan, Zagros, Central Iran, Kopeh-Dagh and Makran seismic zones.
-All events in this catalog are converted to $M_w$ using relationships from previous studies \textcolor{red}{(e.g., pending ref.)}; and data were declustered using various methods including \citet{Gardner1974}, \citet{Reasenberg1985}, \textcolor{red}{Uhrhammer (1986), and Gruenthal (????) [is this level of detail really necessary?]}.
-In addition, \citet{Zare2014} provided the catalog completeness for different magnitude ranges using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and \citet{richter1958}, and the frequency magnitude distribution obtained using ZMAP \citep{Wiemer2001}, and found the methods to yield consistent results.
+In turn, the catalog by \citet{Zare2014} uses both historical data prior to 1900 and instrumental data up until 2006, including events from Afghanistan, Pakis\-tan, Saudi Arabia, the Caucasus and parts of Turkey, in addition to the Alborz-Azerbaijan, Zagros, central Iran, Kopeh-Dagh and Makran seismic zones.
+All events in this catalog are converted to $M_w$ using relationships derived by the authors and by \citet{Escordilis_2006_JS}; and declustered using various methods \citep{Gardner1974, Reasenberg1985, Uhrhammer_1986_EN}.
+In addition, \citet{Zare2014} provided the catalog completeness for different magnitude ranges using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and \citet{richter1958}, and the frequency magnitude distribution obtained using ZMAP \citep{Wiemer2001}, and found these methods to yield consistent results.
 This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
@@
 While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
+
 % The result of our compilation is shown in Fig.~\ref{fig:catalog}, which includes maps for historical and instrumental seismicity. 

### 2016-06-02 seismic_hazard.tex
modified figure 2 and improved references up to catalog section

@@
 Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
+This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2003, Kalkan2009, Moschetti2014, Boyd2008}.
 

### 2016-06-03 catalog.tex
started methodology section

--- 2016-06-02 seismic-catalog.tex
@@
 In the case of the historical seismicity catalog, the color fill indicates the year of the event.
-The borderlines of the seismic zones shown in Fig.~\ref{fig:regional} are shown in the background in white, along with the light gray shaded relief.}
+The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief.}
 	\label{fig:catalog}
@@
 A fundamental step in regional seismic hazard analysis is the compilation of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
-Instrumental data are easily accessible through agencies such as the International Institute of Earthquake Engineering and Seismology (IIEES), the Iranian Seismological Center (IRSC) at the University of Tehran, or the Iranian Strong Motion Network operated by the Building and Housing Research Center (BHRC).
+Nowadays, instrumental datasets are easily accessible through international, regional, and local agencies.
 Historical data, on the other hand, lends itself to subjective interpretation.
-Notable previous efforts to compose uniform earthquake catalogs for Iran include but are not limited to \citet{moinfar1994}, \citet{Berberian1994}, and \citet{Ambraseys2005}.
+Notable previous efforts to compose uniform earthquake catalogs for Iran include but are not limited to \citet{Ambraseys_1982_Book}, \citet{moinfar1994}, and \citet{Berberian_1995_Tech}.
 These studies, however, differ from each other in their use of magnitude scales or magnitude conversion rules, and the extent to which they accept historical accounts as valid data.
 
-According to \citet{Ambraseys2005}, there is evidence of earthquakes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret.
+According to \citet{Ambraseys_1982_Book}, there is evidence of earthquakes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret.
 \citet{Mirzaei1997} compiled a catalog with historical events dating back to the 4th century B.C.~and instrumental earthquakes through 1994 in which a comprehensive list of studies was considered and magnitudes uniformly converted to surface wave magnitude ($M_s$).
@@
 Recent catalogs such as that by \citet{Karimiparidari2013}, \citet{Shahvar2013}, and \citet{Zare2014} are all compiled using magnitudes converted to $M_w$.
-\citet{Karimiparidari2013}, for instance, compiled a catalog for Iran and adjacent areas using international and national datasets including events up until April, 2010 with $M_w > 5$.
+\citet{Karimiparidari2013}, for instance, compiled a catalog for Iran and adjacent areas using international and national datasets including events up until April, 2010, with $M_w > 5$.
 They developed relationships between moment magnitude and other magnitude scales and removed foreshocks and aftershocks using the procedure by \citet{Gardner1974}.
@@
 
-In turn, the catalog by \citet{Zare2014} uses both historical data prior to 1900 and instrumental data up until 2006, including events from Afghanistan, Pakis\-tan, Saudi Arabia, the Caucasus and parts of Turkey, in addition to the Alborz-Azerbaijan, Zagros, central Iran, Kopeh-Dagh and Makran seismic zones.
-All events in this catalog are converted to $M_w$ using relationships derived by the authors and by \citet{Escordilis_2006_JS}; and declustered using various methods \citep{Gardner1974, Reasenberg1985, Uhrhammer_1986_EN}.
-In addition, \citet{Zare2014} provided the catalog completeness for different magnitude ranges using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and \citet{richter1958}, and the frequency magnitude distribution obtained using ZMAP \citep{Wiemer2001}, and found these methods to yield consistent results.
+In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and complement it for our particular region of interest.
 This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
+It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity.
+Instrumental datasets included information from international, regional, and local agencies and networks, such as the U.S.~Geological Survey's National Earthquake Information Center (NEIC), the International Seismological Center (ISC) bulletins, the International Institute of Earthquake Engineering and Seismology (IIEES), the Iranian Seismological Center (IRSC) at the University of Tehran, and the Iranian Strong Motion Network operated by the Building and Housing Research Center (BHRC), among others.
+Historical data included the datasets prepared over the years by \citet{Ambraseys_1982_Book}, \citet{Ambraseys_2005_Book}, and \citet{Ambraseys_2009_Book}.
 
-In this study we adopt the catalog compiled by \citet{Zare2014} for both historical and instrumental earthquakes.
+For the particular case of our region of interest, the catalog prepared by \citet{Zare2014} included events $M_w \geq 4$ between 550 B.C.~and 2006.
+We took information from the catalog up to December 1999, and complemented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
+By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar for events $M_w \geq 4$ catalog but only included data up until 2011, which excluded the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.
+
+In terms of magnitude scale, the events in \citet{Zare2014} were converted from $M_L$, $M_s$ and $m_b$ scales to $M_w$ using relationships derived by the authors and by \citet{Escordilis_2006_JS}.
+For consistency, we used the same conversion relationships for the portion of the catalog obtained from IIEES for $M \geq 3$ earthquakes between 2000 and 2015.
+The dataset from IIEES also contained events reported by ISC on a duration magnitude ($M_D$) scale.
+In these cases we used the empirical relationship introduced by \citet{Deniz2010} to convert $M_D$ to $M_w$.
+Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results to adjust well with the general trend.
+
+Selection and declustering was also done in consistence with the original catalog, using the methods by \citet{Gardner1974}, \citet{Reasenberg1985} and \citet{Uhrhammer_1986_EN}.
+We obtained the declustered version of \citet{Zare2014}, selected 7,478 earthquakes within our region of interest, and removed 605 foreshocks and 2,917 aftershocks, leaving only those events in agreement with a Poissonian model.
+The same procedure was used for the added events between 2000 and 2015.
+These steps altogether allowed us to preserve compatibility with the original catalog while also including the most recent events.
+The final set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.
+
+% *********************************************************************************************************************
+% *********************************************************************************************************************
+
+% ***** In addition, \citet{Zare2014} provided the catalog completeness for different magnitude ranges using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and \citet{richter1958}, and the frequency magnitude distribution obtained using ZMAP \citep{Wiemer2001}, and found these methods to yield consistent results.
+
+% **** Our analysis of this dataset indicated that the catalog satisfies completeness from 2005 onward.
+
+% *********************************************************************************************************************
+% *********************************************************************************************************************
+
+% \citet{Zare2014} uses both historical data prior to 1900 and instrumental data up until 2006, including events from Afghanistan, Pakis\-tan, Saudi Arabia, the Caucasus and parts of Turkey, in addition to the Alborz-Azerbaijan, Zagros, central Iran, Kopeh-Dagh and Makran seismic zones.
+
+% All events in this catalog are converted to $M_w$ using relationships derived by the authors and by \citet{Escordilis_2006_JS}; and declustered using various methods \citep{Gardner1974, Reasenberg1985, Uhrhammer_1986_EN}.
+
+% This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
+
+% In this study we adopt the catalog compiled by \citet{Zare2014} for both historical and instrumental earthquakes.
 This catalog includes events of magnitude $M_w \geq 4$ from 550 A.d.~to December 1999.
-We complemented it with events $M \geq 3$ occurred between January 2000 and December 2015 obtained from the IIEES database.
-Our analysis of this dataset indicated that the catalog satisfies completeness from 2005 onward.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
+
+% We complemented it with events $M \geq 3$ occurred between January 2000 and December 2015 obtained from the IIEES database.
 
@@
 
-The portion of the catalog obtained from IIEES for $M \geq 3$ earthquakes between 2000 and 2015 contained event reports that use different magnitude scales.
+% The portion of the catalog obtained from IIEES for $M \geq 3$ earthquakes between 2000 and 2015 contained event reports that use different magnitude scales.
 We converted all events with magnitudes in $M_L$, $M_s$, and $mb$ scales to $M_w$ using the same conversion relationships used by \citet{Zare2014}, which allowed us to preserve compatibility with the historical and instrumental seismicity catalog adopted from the same work of \citet{Zare2014}.
-In addition, the dataset from IIEES also contained events reported with duration magnitude ($M_D$), as reported by the International Seismological Centre (ISC).
-In these cases we used the empirical relationship developed by \citet{Deniz2010} to convert $M_D$ to $M_w$.
-Although this relationship was derived based on a dataset for $M_w>=4.5$ events, we extrapolate the equation for lower magnitude and found that results to adjust well with the general trend, which should provide for good estimates of the $a$-value in the Gutenberg-Richter equation.
 
-Last but not least important, we declustered the catalog prior to using it in the assessment of seismic hazard for the region of interest.
+% Last but not least important, we declustered the catalog prior to using it in the assessment of seismic hazard for the region of interest.
 This entailed the removal of foreshocks and aftershocks from the catalog to adjust the dataset to include only those events in agreement with a Poissonian model, which is a well-accepted model for seismic sources.

### 2016-06-03 hazard.tex
started methodology section

\section{Approach to Seismic Hazard}

There have been multiple efforts to estimate seismic hazard for Iran. A brief report on the most recent review of seismic hazard studies used for composing the hazard zoning map of Iran, as included in the current version of the Iranian seismic code \citep{BHRC2014}, can be found in \citet{Moinfar_2012_WCEE}. Other previous efforts include, for instance, the work by \citet{Tavakoli1999}, who presented iso-acceleration contour lines and seismic hazard zonation for Iran based on known major fault-lines and area-source models; and the results obtained by \citet{Ghodrati2003}, who presented a refined hazard assessment for the metropolitan area of Tehran using a logic tree approach to combine results from three attenuation relationships.

More recently, \citet{Khodaverdian_2016_BSSA} used a smoothed seismicity approach to estimate spatially variable seismicity parameters $a$ and $b$ \citep{Gutenberg1944} and compose seismic hazard maps for the whole country. Here, we also use a smoothed seismicity approach, but place our emphasis on northern Iran and use spatially variable $a$-values but seismic zone-specific $b$-values. The smoothed seismicity approach addres\-ses the aleatoric uncertainty of future earthquake locations by using the contribution of the background regional seismicity in combination with a smoothing (Gaussian) function. The smoothing takes place over spatial grid-cells which contribute to and borrow information from neighboring cells about earthquake occurrence, and thus eliminates the need for specific source locations. This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.

In particular, we use the smoothed seismicity method introduced by \citet{Frankel1995}. In this approach, the region of interest is divided into regular-size grid cells. Then, the number of events within each cell of magnitude greater than a given reference value $M_{\mathrm{ref}}$ are counted.

seismic events grouped within spatially gridded cells

%We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$ . Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.

% *********************************************************************************************************************
% *********************************************************************************************************************

% Occurrence of devastating historical earthquake and also essential needs for constructing new buildings and infrastructures inspired researchers to study the seismic hazard of northern Iran from different points of view. Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years corresponding to 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models. According to their study, North Tabriz fault zone and north of Tehran fault zone have the highest acceleration. Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively. In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran. The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years. 
% In this study we use background seismicity to estimate the seismic hazard in northern Iran. Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California. They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns. \citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia. They defined 4 different models with different correlation distances, including a model based of the total released seismic energy. They gained an acceptable PGA in comparison with other seismic hazard approaches. \citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity. Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones. This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2003, Kalkan2009, Moschetti2014, Boyd2008}.

% *********************************************************************************************************************
% *********************************************************************************************************************

% \subsection{Analysis Method}

% \subsubsection{smoothed seismicity method}

% We use spatially smoothed seismic hazard analysis \citep{Frankel1995} to estimate the seismic hazard. In this model, seismic events are spatially gridded to cells. We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$ . Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past. \\
% \noindent
% According to Building and Housing Research Center  \citep{BHRC2014}, $M_w 5$ is considered as a threshold magnitude for onsetting the structural damage. In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation. \\
% \noindent

% In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell. We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e. number of events bigger than $M_{ref}$) values to incremental (i.e. number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values. Using Gaussian function we smooth the number of events in each cell. The smoothed value $\tilde{n}_i$ is obtained from

% \begin{equation}
% \tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
% \end{equation}

% \noindent
% where,  $\tilde{n}_i$  is normalized to preserve the total number of events. $\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell. The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
% \noindent
% Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
% Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to

% \begin{equation}
% \begin{split}
% \lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} \\
% p(u>u_0 | D_k ,M_l),
% \end{split}
% \end{equation}

% \noindent
% where $k$ and $l$ are denoted as index of distance and magnitude bin. $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$. This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}.

% -----------------------------------------------------------------------
% -----------------------------------------------------------------------

%%% My (Naeem) original text

%\subsection{Background}
%
%Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran. Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models. According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour. Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively. In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran. The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years. 
%In this study we use background seismicity to calculate the seismic hazard.Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California. They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns. \citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia. They defined 4 different models with different correlation distances, including a model based of the total released seismic energy. They gained an acceptable PGA in comparison with other seismic hazard approaches. \citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity. Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones. This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
%
%\subsection{Analysis Method}
%\subsubsection{smoothed seismicity method}
%To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}. In this model, seismic events are spatially gridded to cells. We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_ w5$ . Category 5+ and others ($M6+$ and $M7+$) assume that future $M_w 4.5$ events will occur near where they have occurred in the past. \\
%\noindent
%According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage. In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation. \\
%\noindent
%\noindent
%In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell. We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e. number of events bigger than $M_{ref}$) values to incremental (i.e. number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values. Using Gaussian function we smooth the number of events in each cell. The smoothed value $\tilde{n}_i$ is obtained from
%
%\begin{equation}
%\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
%\end{equation}
%
%\noindent
%where,  $\tilde{n}_i$  is normalized to preserve the total number of events. $\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell. The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
%\noindent
%Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
%Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to 
%
%\begin{equation}
%\begin{split}
%\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} \\
%p(u>u_0 | D_k ,M_l),
%\end{split}
%\end{equation}

%\noindent
%where $k$ and $l$ are denoted as index of distance and magnitude bin. $P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$. This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}

### 2016-06-05 catalog.tex
completed hazard section

@@
 
-A fundamental step in regional seismic hazard analysis is the compilation of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
+\subsection{Composition}
+
+A fundamental step in regional seismic hazard analysis is the composition of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
 Nowadays, instrumental datasets are easily accessible through international, regional, and local agencies.
@@
 The final set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.
+
+\subsection{Completeness}
+
+\textcolor{red}{We will bring the completeness section here.}
 

### 2016-06-05 hazard.tex
completed hazard section

@@
 
-There have been multiple efforts to estimate seismic hazard for Iran.
-A brief report on the most recent review of seismic hazard studies used for composing the hazard zoning map of Iran, as included in the current version of the Iranian seismic code \citep{BHRC2014}, can be found in \citet{Moinfar_2012_WCEE}.
-Other previous efforts include, for instance, the work by \citet{Tavakoli1999}, who presented iso-acceleration contour lines and seismic hazard zonation for Iran based on known major fault-lines and area-source models; and the results obtained by \citet{Ghodrati2003}, who presented a refined hazard assessment for the metropolitan area of Tehran using a logic tree approach to combine results from three attenuation relationships.
+There have been multiple assessments of seismic hazard for Iran.
+A brief report on the most recent review done to define the hazard zoning map of Iran included in the Iranian seismic code \citep{BHRC2014} can be found in \citet{Moinfar_2012_WCEE}.
+Other previous efforts include, for instance, the work of \citet{Tavakoli1999}, who presented iso-acceleration contour lines and seismic hazard zonation for Iran based on known major fault-lines and area-source models; the results obtained by \citet{Ghodrati2003}, who presented a refined hazard assessment for the metropolitan area of Tehran using a logic tree approach to combine results from three attenuation relationships; and the recent study by \citet{Khodaverdian_2016_BSSA}, who used a smoothed seismicity approach to estimate spatially variable seismicity parameters for the whole country.
 
-More recently, \citet{Khodaverdian_2016_BSSA} used a smoothed seismicity approach to estimate spatially variable seismicity parameters $a$ and $b$ \citep{Gutenberg1944} and compose seismic hazard maps for the whole country.
-Here, we also use a smoothed seismicity approach, but place our emphasis on northern Iran and use spatially variable $a$-values but seismic zone-specific $b$-values.
-The smoothed seismicity approach addres\-ses the aleatoric uncertainty of future earthquake locations by using the contribution of the background regional seismicity in combination with a smoothing (Gaussian) function.
-The smoothing takes place over spatial grid-cells which contribute to and borrow information from neighboring cells about earthquake occurrence, and thus eliminates the need for specific source locations.
+Once a seismic catalog has been defined, the second most important step is precisely the definition of the seismicity parameters $a$ and $b$ used in the Gutenberg-Richter recurrence relation 
+% 
+\begin{equation}
+	\log_{10} N = a - b M \, ,
+\end{equation}
+% 
+\noindent
+where $N$ is the number of earthquakes with magnitude greater than or equal to $M$, $a$ accounts for the number of earthquakes that occur within a given region, and $b$ is a measure of the occurrence of earthquakes relative to magnitude \citep{Gutenberg1944}.
+These parameters can be assumed constant or variable depending on the approach used.
+
+In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}.
 This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.
+In it, the $b$-value is usually assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes.
+The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells.
+The parameter $a$ is determined based on the number of events $n_i$ within each cell $i$ of magnitude greater than a reference value $M_{\mathrm{ref}}$, and discretized in different magnitude ranges (or bins).
+The number of earthquakes within each cell is then smoothed spatially taking into account the values of neighboring cells using a Gaussian function.
+In essence, the smoothed seismicity approach addresses the aleatoric uncertainty of future earthquake locations by using a weighted contribution of the background regional seismicity, and thus eliminates the need for knowledge about specific fault locations.
 
-In particular, we use the smoothed seismicity method introduced by \citet{Frankel1995}.
-In this approach, the region of interest is divided into regular-size grid cells.
-Then, the number of events within each cell of magnitude greater than a given reference value $M_{\mathrm{ref}}$ are counted.
+In this study we discretize the region of interest into a regular grid with cells of size 0.1\textdegree{} $\times$ 0.1\textdegree{} (in longitude and latitude).
+The parameter $a$ for each cell is obtained based on the information in the seismic catalog described in the previous section.
+Following \citet{Frankel1995}, $n_i$ is smoothed using the normalized Gaussian function
+% 
+\begin{equation}
+	\tilde{n_i} = \frac
+		{ \sum_{j} n_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
+		{ \sum_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
+	\, ,
+	\label{eq:nnorm}
+\end{equation}
+% 
+where $\tilde{n}_i$ is the smoothed, normalized number of events in cell $i$, $\Delta_{ij}$ is the distance between the $i$-th and $j$-th cells, and $c$ is the correlation distance.
+We use a correlation distance of 30 km.
+The summations in (\ref{eq:nnorm}) are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
+It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
+We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having complemented the earthquake catalog for events above this threshold.
 
-seismic events grouped within spatially gridded cells
+In turn, we consider the $b$-values to be constant within each seismic zone as delimited in Fig.~\ref{fig:iran}.
+Details about the calculation of the $b$-value for each zone are provided below.
+By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within super-grid cells of size 1\textdegree{} $\times$ 1\textdegree{} and $a$-values within the usual grid cells of size 0.1\textdegree{} $\times$ 0.1\textdegree{}.
+While this approach is novel in the sense that it also grids $b$-values, these super-cells may easily cross over zones of different seismogenic characteristics, and thus may not be faithful to the nature of earthquakes within any given zone.
+Admittedly, these are subjective decisions and any reasonable choice may be valid and within the margins of the associated epistemic uncertainty.
 
-%We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$ .
-Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
+Last, the annual rate $\lambda$ of exceeding a reference ground motion $u_o$ is defined by
+% 
+\begin{align}
+	\lambda & \left( u > u_o \right) = \nonumber \\
+		& \sum_{k} \sum_{l} 10^{ {}^{ \left[ \log \left( \frac{ N_{k} }{ T } \right) - b \left( M_l - M_{\mathrm{ref}} \right) \right] } }
+		P \left( u > u_o | D_k , M_l \right)
+		\, .
+	\label{eq:exceed}
+\end{align}
+% 
+Here, the values of $\tilde{n}_i$ have been previously binned by their distance from the site of interest, $N_k$ is the total of $\tilde{n}_i$ values for cells within a certain bin distance, $T$ is the time in years used to determine $N_k$, and $k$ and $l$ are the indexes of the distance and magnitude bins, respectively.
+$P ( u > u_o | D_k , M_l )$ is the probability of $u$ exceeding $u_o$ given an earthquake of magnitude $M_l$ at a distance $D_k$ \citep{Frankel1995}.
+
+It is clear from (\ref{eq:exceed}) that the hazard calculations depends also on the choice of an attenuation relationship to obtain predict the level of ground motion at a site ($u$) for any given earthquake.
+In the following two sections we describe how we obtained the $b$-values for the different seismic zones influencing the hazard in northern Iran and our choice of a suitable attenuation relationship (ground motion prediction equation).
 
 % *********************************************************************************************************************
+% PENDING TO USE
+% *********************************************************************************************************************
+
+% We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
+
+% Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$.
+
+% Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
+
+% According to Building and Housing Research Center \citep{BHRC2014}, $M_w 5$ is considered as a threshold magnitude for onsetting the structural damage.
+
+% In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it,
+
+% in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
+
+% *********************************************************************************************************************
+% ALREADY USED
 % *********************************************************************************************************************
@@
 
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
 % \subsection{Analysis Method}
@@
 % We use spatially smoothed seismic hazard analysis \citep{Frankel1995} to estimate the seismic hazard. 
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$ .
-Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
-\\
-% \noindent
+% In this model, seismic events are spatially gridded to cells. 
+% We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. 
+% % According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. 
+% % Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. 
+% Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$. 
+% Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
 % According to Building and Housing Research Center \citep{BHRC2014}, $M_w 5$ is considered as a threshold magnitude for onsetting the structural damage. 
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
-\\
-% \noindent
-
+% In the smoothed seismicity method, the model uses each event location as a point source, 
+% hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, 
+% in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
 % In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
-We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
+% We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
 number of events bigger than $M_{ref}$) values to incremental (i.e.
 number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values.
-Using Gaussian function we smooth the number of events in each cell.
-The smoothed value $\tilde{n}_i$ is obtained from
+
+% Using Gaussian function we smooth the number of events in each cell. The smoothed value $\tilde{n}_i$ is obtained from
 
@@
 $\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-% \noindent
+The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.
+
 % Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
+
 % Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to
@@
 
-% -----------------------------------------------------------------------
-% -----------------------------------------------------------------------
+% *********************************************************************************************************************
+% OLD STUFF
+% *********************************************************************************************************************
 

### 2016-06-05 catalog.tex
re-organized titles and files

--- 2016-06-03 catalog.tex
@@
-\begin{figure*}[t] 
-	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
-	\caption{Location of events considered in the compiled seismic catalog.
-(a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}.
-(b) Instrumental seismicity up until December 2015 for $M_w \geq 3$ (IIEES) and $M_w \geq 4$ \citep[after][]{Zare2014}.
-Size of symbols is proportional to the magnitude of the events.
-In the case of the historical seismicity catalog, the color fill indicates the year of the event.
-The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief.}
-	\label{fig:catalog}
-\end{figure*}
-
 \section{Seismic Catalog}
 
-A fundamental step in regional seismic hazard analysis is the compilation of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
-Nowadays, instrumental datasets are easily accessible through international, regional, and local agencies.
-Historical data, on the other hand, lends itself to subjective interpretation.
-Notable previous efforts to compose uniform earthquake catalogs for Iran include but are not limited to \citet{Ambraseys_1982_Book}, \citet{moinfar1994}, and \citet{Berberian_1995_Tech}.
-These studies, however, differ from each other in their use of magnitude scales or magnitude conversion rules, and the extent to which they accept historical accounts as valid data.
+\input{composition}
 
-According to \citet{Ambraseys_1982_Book}, there is evidence of earthquakes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret.
-\citet{Mirzaei1997} compiled a catalog with historical events dating back to the 4th century B.C.~and instrumental earthquakes through 1994 in which a comprehensive list of studies was considered and magnitudes uniformly converted to surface wave magnitude ($M_s$).
-Most ground motion prediction equations employed today in seismic hazard, however, use moment magnitude ($M_w$) instead.
-
-Recent catalogs such as that by \citet{Karimiparidari2013}, \citet{Shahvar2013}, and \citet{Zare2014} are all compiled using magnitudes converted to $M_w$.
-\citet{Karimiparidari2013}, for instance, compiled a catalog for Iran and adjacent areas using international and national datasets including events up until April, 2010, with $M_w > 5$.
-They developed relationships between moment magnitude and other magnitude scales and removed foreshocks and aftershocks using the procedure by \citet{Gardner1974}.
-\citet{Shahvar2013} built a catalog for the Iranian plateau for events with $M_w \geq 4$ merging data from two local and seven international datasets for the 1900--2011 period.
-They used the orthogonal regression method by \citet{Castellaro2006} to derive magnitude conversions and removed foreshocks and aftershocks according to the procedure by \citet{Uhrhammer_1986_EN}.
-In addition, \citet{Shahvar2013} provided a declustered version of the catalog.
-
-In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and complement it for our particular region of interest.
-This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
-It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity.
-Instrumental datasets included information from international, regional, and local agencies and networks, such as the U.S.~Geological Survey's National Earthquake Information Center (NEIC), the International Seismological Center (ISC) bulletins, the International Institute of Earthquake Engineering and Seismology (IIEES), the Iranian Seismological Center (IRSC) at the University of Tehran, and the Iranian Strong Motion Network operated by the Building and Housing Research Center (BHRC), among others.
-Historical data included the datasets prepared over the years by \citet{Ambraseys_1982_Book}, \citet{Ambraseys_2005_Book}, and \citet{Ambraseys_2009_Book}.
-
-For the particular case of our region of interest, the catalog prepared by \citet{Zare2014} included events $M_w \geq 4$ between 550 B.C.~and 2006.
-We took information from the catalog up to December 1999, and complemented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
-By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar for events $M_w \geq 4$ catalog but only included data up until 2011, which excluded the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.
-
-In terms of magnitude scale, the events in \citet{Zare2014} were converted from $M_L$, $M_s$ and $m_b$ scales to $M_w$ using relationships derived by the authors and by \citet{Escordilis_2006_JS}.
-For consistency, we used the same conversion relationships for the portion of the catalog obtained from IIEES for $M \geq 3$ earthquakes between 2000 and 2015.
-The dataset from IIEES also contained events reported by ISC on a duration magnitude ($M_D$) scale.
-In these cases we used the empirical relationship introduced by \citet{Deniz2010} to convert $M_D$ to $M_w$.
-Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results to adjust well with the general trend.
-
-Selection and declustering was also done in consistence with the original catalog, using the methods by \citet{Gardner1974}, \citet{Reasenberg1985} and \citet{Uhrhammer_1986_EN}.
-We obtained the declustered version of \citet{Zare2014}, selected 7,478 earthquakes within our region of interest, and removed 605 foreshocks and 2,917 aftershocks, leaving only those events in agreement with a Poissonian model.
-The same procedure was used for the added events between 2000 and 2015.
-These steps altogether allowed us to preserve compatibility with the original catalog while also including the most recent events.
-The final set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.
+\input{completeness}
 

### 2016-06-05 completeness.tex
re-organized titles and files

\subsection{Completeness}

\textcolor{red}{We will bring the completeness section here.}

### 2016-06-05 composition.tex
re-organized titles and files

\begin{figure*}[t] 
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
	\caption{Location of events considered in the compiled seismic catalog. (a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}. (b) Instrumental seismicity up until December 2015 for $M_w \geq 3$ (IIEES) and $M_w \geq 4$ \citep[after][]{Zare2014}. Size of symbols is proportional to the magnitude of the events. In the case of the historical seismicity catalog, the color fill indicates the year of the event. The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief.}
	\label{fig:catalog}
\end{figure*}

\subsection{Composition}

A fundamental step in regional seismic hazard analysis is the composition of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes. Nowadays, instrumental datasets are easily accessible through international, regional, and local agencies. Historical data, on the other hand, lends itself to subjective interpretation. Notable previous efforts to compose uniform earthquake catalogs for Iran include but are not limited to \citet{Ambraseys_1982_Book}, \citet{moinfar1994}, and \citet{Berberian_1995_Tech}. These studies, however, differ from each other in their use of magnitude scales or magnitude conversion rules, and the extent to which they accept historical accounts as valid data.

According to \citet{Ambraseys_1982_Book}, there is evidence of earthquakes as far back as the third millennium B.C., yet some of those accounts are difficult to interpret. \citet{Mirzaei1997} compiled a catalog with historical events dating back to the 4th century B.C.~and instrumental earthquakes through 1994 in which a comprehensive list of studies was considered and magnitudes uniformly converted to surface wave magnitude ($M_s$). Most ground motion prediction equations employed today in seismic hazard, however, use moment magnitude ($M_w$) instead.

Recent catalogs such as that by \citet{Karimiparidari2013}, \citet{Shahvar2013}, and \citet{Zare2014} are all compiled using magnitudes converted to $M_w$. \citet{Karimiparidari2013}, for instance, compiled a catalog for Iran and adjacent areas using international and national datasets including events up until April, 2010, with $M_w > 5$. They developed relationships between moment magnitude and other magnitude scales and removed foreshocks and aftershocks using the procedure by \citet{Gardner1974}. \citet{Shahvar2013} built a catalog for the Iranian plateau for events with $M_w \geq 4$ merging data from two local and seven international datasets for the 1900--2011 period. They used the orthogonal regression method by \citet{Castellaro2006} to derive magnitude conversions and removed foreshocks and aftershocks according to the procedure by \citet{Uhrhammer_1986_EN}. In addition, \citet{Shahvar2013} provided a declustered version of the catalog.

In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and complement it for our particular region of interest. This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project. It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity. Instrumental datasets included information from international, regional, and local agencies and networks, such as the U.S.~Geological Survey's National Earthquake Information Center (NEIC), the International Seismological Center (ISC) bulletins, the International Institute of Earthquake Engineering and Seismology (IIEES), the Iranian Seismological Center (IRSC) at the University of Tehran, and the Iranian Strong Motion Network operated by the Building and Housing Research Center (BHRC), among others. Historical data included the datasets prepared over the years by \citet{Ambraseys_1982_Book}, \citet{Ambraseys_2005_Book}, and \citet{Ambraseys_2009_Book}.

For the particular case of our region of interest, the catalog prepared by \citet{Zare2014} included events $M_w \geq 4$ between 550 B.C.~and 2006. We took information from the catalog up to December 1999, and complemented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015. While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes. By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar for events $M_w \geq 4$ catalog but only included data up until 2011, which excluded the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.

In terms of magnitude scale, the events in \citet{Zare2014} were converted from $M_L$, $M_s$ and $m_b$ scales to $M_w$ using relationships derived by the authors and by \citet{Escordilis_2006_JS}. For consistency, we used the same conversion relationships for the portion of the catalog obtained from IIEES for $M \geq 3$ earthquakes between 2000 and 2015. The dataset from IIEES also contained events reported by ISC on a duration magnitude ($M_D$) scale. In these cases we used the empirical relationship introduced by \citet{Deniz2010} to convert $M_D$ to $M_w$. Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results to adjust well with the general trend.

Selection and declustering was also done in consistence with the original catalog, using the methods by \citet{Gardner1974}, \citet{Reasenberg1985} and \citet{Uhrhammer_1986_EN}. We obtained the declustered version of \citet{Zare2014}, selected 7,478 earthquakes within our region of interest, and removed 605 foreshocks and 2,917 aftershocks, leaving only those events in agreement with a Poissonian model. The same procedure was used for the added events between 2000 and 2015. These steps altogether allowed us to preserve compatibility with the original catalog while also including the most recent events. The final set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.

### 2016-06-06 composition.tex
fixed comments by Naeem

@@
 
-Selection and declustering was also done in consistence with the original catalog, using the methods by \citet{Gardner1974}, \citet{Reasenberg1985} and \citet{Uhrhammer_1986_EN}.
-We obtained the declustered version of \citet{Zare2014}, selected 7,478 earthquakes within our region of interest, and removed 605 foreshocks and 2,917 aftershocks, leaving only those events in agreement with a Poissonian model.
-The same procedure was used for the added events between 2000 and 2015.
-These steps altogether allowed us to preserve compatibility with the original catalog while also including the most recent events.
-The final set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.
+Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}.
+In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events prior to 2000, complemented with all $M>3$ events from 2000 to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
+The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.

### 2016-06-06 hazard.tex
re-organized titles and files
fixed comments by Naeem

@@
-\section{Approach to Seismic Hazard}
+\section{Seismic Hazard Approach}
 
@@
 This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.
-In it, the $b$-value is usually assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes.
+In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes.
 The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells.
@@
 Details about the calculation of the $b$-value for each zone are provided below.
-By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within super-grid cells of size 1\textdegree{} $\times$ 1\textdegree{} and $a$-values within the usual grid cells of size 0.1\textdegree{} $\times$ 0.1\textdegree{}.
-While this approach is novel in the sense that it also grids $b$-values, these super-cells may easily cross over zones of different seismogenic characteristics, and thus may not be faithful to the nature of earthquakes within any given zone.
-Admittedly, these are subjective decisions and any reasonable choice may be valid and within the margins of the associated epistemic uncertainty.
+By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within large grid-cells of size 1\textdegree{} $\times$ 1\textdegree{} based on the average seismicity within a 200-km radius from each cell.
+While gridding $b$-values and considering the influence of neighboring large-size cells allows to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may pollute the computation of $b$-values.
+Admittedly, these are subjective decisions and any reasonable choice can be considered valid or within the margins of the associated epistemic uncertainty.
 

### 2016-06-06 analysis_parameters.tex
first general revision.
finished attenuation relationship section

@@
 \section{Analysis Parameters}
-\subsection{Attenuation Relationship}
 
-The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis.
+% \subsection{Attenuation Relationship}
+
+% The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis.
 \citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
@@
 
-\noindent
-The attenuation relationship is:
+% \noindent
+% The attenuation relationship is:
 
-\begin{equation}
-\begin{split}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
-b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{split}
-\end{equation}
+% \begin{equation}
+% \begin{split}
+% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
+% b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
+% \end{split}
+% \end{equation}
 
@@
 \subsection{Catalog Completness}
+
 For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
@@
 \centering
-\includegraphics[scale=0.28]{figures/pdf/comp_test_all_mag.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Kopek Dagh, g-h)Kopeh Dagh, i-j)Zagros}
+\includegraphics[scale=0.28]{figures/pdf/figure-07.pdf} 
+\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Central, g-h)Kopeh Dagh, i-j)Zagros}
 \label{fig:comp_test_all_mag}

### 2016-06-06 attenuation.tex
finished attenuation relationship section

\section{Attenuation Relationship}

The last piece in our hazard analysis process is the choice of an adequate attenuation relationship, or ground motion prediction equation (GMPE). This is a highly influential factor because it controls the spatial extent to which the local occurrence of earthquakes can influence regional hazard.

Recently, \citet{Zafarani2014} investigated the predictive capabilities of a set of nine local, regional, and next generation attenuation (NGA) GMPEs to determine their applicability for northern Iran. They evaluated GMPE predictions against data from 32 earthquakes of magnitudes $M_w$ ranging between 4.7 and 7.4. This included comparisons of PGA and response spectral accelerations (SA) computed from time-series recorded on 163 stations located at epicentral distances of up to 200 km. The evaluation was done using the likelihood (LH) and log-likelihood (LLH) methods of \citet{Scherbaum_2004_BSSA, Scherbaum_2009_BSSA}. The combined evaluation for PGA, and SA for seven periods (T) between 0.1 and 2.0 s, yielded that the best overall predictions were those of the GMPEs introduced by \citet{Ghasemi_2009_JS}, \citet{Abrahamson_2008_ES}, and \citet{Chiou2008}. For the specific case of PGA ($T=0$ s), however, the best results were those obtained with the GMPEs introduced by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}.

Since our hazard analysis here focuses on PGA values, we concentrated our attention in the last set of GMPEs. In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other. Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the approached of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis lead to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively. These results meant that neither of them had a substantial advantage over the others.

Based on this, we selected the GMPE proposed by \citet{Kalkan2004} for our analysis. This equation is of the form
% 
\begin{align}
	\ln \left( Y \right) =
		& \hspace{1ex} b_1 + b_2(M_w - 6) + b_3 \left( M_w - 6 \right)^{2} \nonumber \\ 
		& + b_5 \ln \left( r \right) + b_V \ln \left( V_S / V_A \right)
	\, ,
\end{align}
% 
where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, $V_S$ is the shear wave velocity of the site of interest, and the distance $r$ is given by
% 
\begin{equation}
	r= \sqrt{ r^2_{\mathit{cl}} + h^2 }
	\, .
\end{equation}
% 
where $r_{\mathit{cl}}$ is the horizontal distance to the site of interest and $h$ is a reference fictitious depth, both given in km. According to \citet{Kalkan2004}, in the case of $Y$ representing PGA, the coefficients $b_1$, $b_2$, $b_3$, $b_5$ and $b_V$ are
% 
\begin{equation}
\begin{array}{lcrlcr} 
	b_1 &=&  0.393   \,,&\hspace{2em}   b_2 &=& 0.576\,,   \\
	b_3 &=& -0.107   \,,&\hspace{2em}   b_5 &=& -0.899\,,  \\
	b_V &=& -0.200   \,; 
	\nonumber
\end{array}
\end{equation}
% 
and $V_A$, $V_S$ and $h$ are
% 
\begin{equation}
\begin{array}{lcrl} 
	V_A &=& 1,112 & \mathrm{m/s}	\\
	V_S &=&   700 & \mathrm{m/s}	\\
	h   &=&  6.91 & \mathrm{km}\,,
	\nonumber
\end{array}
\end{equation}
% 
respectively. The value of $V_S$ is assumed to represent average surface rock sites.

% *********************************************************************************************************************
% OLD
% *********************************************************************************************************************

% The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis. \citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran. After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59. Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude. Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively. The epistemic uncertainty in attenuation relationship is being considered through using the logic tree approach. Having close mean value and similar logic tree weights, logic tree approach will have a minor effect in considering the epistemic uncertainty. In this study instead of using  different GMPEs we use the best model of attenuation relationship for PGA \citep{Zafarani2014} as well $\pm$ standard deviation. \\

% \noindent
% The attenuation relationship is:

% \begin{equation}
% \begin{split}
% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
% b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
% \end{split}
% \end{equation}

% *********************************************************************************************************************
% OLDER
% *********************************************************************************************************************

% \section{Attenuation relationship}

% The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard. \citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran. After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59. Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude. Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively. Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.  \citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.    \\

% \noindent

% The attenuation relationship is:

% \begin{equation}
% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
% \end{equation}

% where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.

### 2016-06-06 composition.tex
finished attenuation relationship section

@@
 Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}.
-In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events prior to 2000, complemented with all $M>3$ events from 2000 to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
+In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with all $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
 The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.

### 2016-06-06 introduction.tex
finished attenuation relationship section

@@
 We use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This approach has been used with success in other regions \citep[e.g.][]{Boyd2008, Kalkan2009, Moschetti2014}, including Iran \citep{Khodaverdian_2016_BSSA}.
+This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
 Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
@@
 In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the adopted approach.
-Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region \citep{Zafarani2014, Kalkan2004}, and the estimation of the Gutenberg-Richter seismicity parameters.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, considering different magnitude thresholds.
+Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, considering different magnitude thresholds.
 We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.

### 2016-06-06 analysis_parameters.tex
working on parameters section

@@
 
-\begin{figure*} [!ht]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/figure-04} 
-\caption{The annual probability of exceeding the specified magnitude in different seismic tectonic region (a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros).
+% \begin{figure*} [!ht]
+% \centering
+% \includegraphics[scale=0.3]{figures/pdf/figure-04} 
+% \caption{The annual probability of exceeding the specified magnitude in different seismic tectonic region (a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros).
 The margin display the positive and negative standard deviation.}
-\label{fig:annual_m}
-\end{figure*}
+% \label{fig:annual_m}
+% \end{figure*}
 
-\noindent
+% \noindent
 
-\begin{table*}[!ht]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
-    Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
-    Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
-    Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
-    Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
-    Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
-    \end{tabular}
- \label{tab:b_value} 
-\end{table*}
+% \begin{table*}[!ht]
+% \centering
+% \caption{Seismicity parameters for three tectonic seismic regions.}
+%     \begin{tabular}{ccccc}
+%     ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
+%     Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
+%     Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
+%     Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
+%     Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
+%     Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
+%     Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
+%     \end{tabular}
+%  \label{tab:b_value} 
+% \end{table*}
 

### 2016-06-06 b-value.tex
working on parameters section

--- 2016-06-06 analysis_parameters.tex
@@
-\section{Analysis Parameters}
-
-% \subsection{Attenuation Relationship}
-
-% The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-The epistemic uncertainty in attenuation relationship is being considered through using the logic tree approach.
-Having close mean value and similar logic tree weights, logic tree approach will have a minor effect in considering the epistemic uncertainty.
-In this study instead of using  different GMPEs we use the best model of attenuation relationship for PGA \citep{Zafarani2014} as well $\pm$ standard deviation.
-\\
-
-% \noindent
-% The attenuation relationship is:
-
-% \begin{equation}
-% \begin{split}
-% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
-% b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-% \end{split}
-% \end{equation}
-
-\subsection{b-value}
+\section{Seismicity Parameters}
 
@@
 For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.\\
-\noindent
+The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.
+
 \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
@@
 
-% \begin{figure*} [!ht]
-% \centering
-% \includegraphics[scale=0.3]{figures/pdf/figure-04} 
-% \caption{The annual probability of exceeding the specified magnitude in different seismic tectonic region (a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros).
-The margin display the positive and negative standard deviation.}
-% \label{fig:annual_m}
-% \end{figure*}
-
-% \noindent
-
-% \begin{table*}[!ht]
-% \centering
-% \caption{Seismicity parameters for three tectonic seismic regions.}
-%     \begin{tabular}{ccccc}
-%     ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
-%     Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
-%     Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
-%     Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
-%     Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
-%     Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
-%     Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
-%     \end{tabular}
-%  \label{tab:b_value} 
-% \end{table*}
-
-\subsection{Catalog Completness}
-
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-\citet{Frankel1995} plotted the cumulative number of events against time for different regions.
-He assumes that from the point that the line become linear, the catalog is complete.
-This approach is similar to the MAXC method of ZMAP software \citep{Wiemer2001}, where the completeness treshold is the maximum value of the first derivative of the frequency-magnitude curve.
-Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP, \citet{Zare2014} reported the catalog completeness for the study regions.
-World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
-Up to 1961 these data formed the early instrumental period.
-In 1961 the Worldwide Standardized Seismograph Network (WWSSN) was stablished.
-The record of these seismographs considerably improved the seismic catalogs in different part of the world \citep{Shearer2009}.
-Fig.~\ref{fig:completness_scatter} shows the magnitude distribution of events with respect to the time of occurrence of the events.
-
-\begin{figure*} [!ht]
+\begin{figure*}[t]
     \centering
-\includegraphics[scale=0.5]{figures/pdf/figure-05.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros}
-\label{fig:completness_scatter}
+    \includegraphics[width=\textwidth]{figures/pdf/figure-04} 
+    \caption{Annual probability of exceedance as a function of earthquake magnitude for seismic tectonic regions of (a) Alborz, (b) Azerbaijan, (c) Central Iran, (d) Kopeh Dagh, (e) Uniform (f) Zagros.
+The shaded range indicates the models' $\pm 1$ standard deviation.}
+    \label{fig:annual_m}
 \end{figure*}
 
- According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions' catalog.
-We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
-In order to be able to compare the results with \citet{Zare2014} we merge the data of Azerbaijan and Alborz seismic regions.
-Fig.~\ref{fig:completness_compare_zare_2014_Az_Al} shows the completeness of catalog for earthquakes with different magnitude range in Azerbaijan-Alborz region.
-According to this figure, midrange magnitudes ($ 4 < Mw < 6 $) fairly obey the network developments in 1900 and 1961.
-The completeness thresholds for each magnitude range which are reported by \citet{Zare2014} are shown by dashed green line.
-In this study we follow the \citet{Frankel1995} approach to determine the completeness of each region.
-Even though the approach used by \citet{Frankel1995} will lead to the conservative results, we make sure that we don't use a period of time without knowing the complete number of events.
-Determining the completeness of the catalog is very sensitive to the data.
-Converting earthquake magnitudes from different scales to moment magnitude obviously has some error.
-Having broader range of magnitude will help to minimize these sort of error.
-In this study we consider the magnitude intervals for completeness study as $Mw = 1$.
-
-\begin{figure*} [!ht]
+\begin{table*}[t]
     \centering
-\includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
-\caption{Cumulative number of earthquakes with respect to the time.
-Magnitude range is represented in a box at the top left corner.
-Solid black lines represent the starting of early instrumental (1900) and instrumental (1961) period.
-Green dashed lines represents the completeness threshold reported by \citet{Zare2014}.
-Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
-\label{fig:completness_compare_zare_2014_Az_Al}
-\end{figure*}
-
-\noindent
-Fig.~\ref{fig:comp_test_all_mag} illustrates the completeness of data for each magnitude threshold in five different regions.
-A uniform rise of cumulative number of earthquake in each magnitude range, defines the threshold for catalog completeness.
-We define the completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
-We assume the catalog for earthquakes with magnitude greater than  7 ($M_w > 7$) is complete from the first historical earthquake report.
-Determining the completeness of the catalog for $ 6 < Mw \leq 7 $ needs precise observation of the catalog.
-In Azerbaijan tectonic seismic region after 1045  $Mw = 6.2$ earthquake the catalog seems complete up to 1318.
-However, between 1318 and 1581 (263 years) only one earthquake with magnitude $Mw > 6$ is reported (1440,  $Mw = 6.2$ ).
-Considering the activity of the Azerbaijan region, in this study we assume that the catalog is complete for earthquake with magnitude $ 6 < Mw \leq 7 $ after 1581.
-Similar situation happened at the period of 1715 - 1833.
-It worth to mention that in this case, the time period is shorter than before (118 years), meanwhile in this period of time two earthquakes with magnitude $Mw>7$ occurred in the Azerbaijan region (1721 $Mw=7.7$, 1780 $Mw=7.6$).
-The catalog may or may not be completed after 1045, however in this study we consider 1581 as a completeness threshold for magnitude  $ 6 < Mw \leq 7 $.
-Considering completeness of the catalog for Azerbaijan region from 1581 will result in conservative PGA for the region in comparison with the model with threshold of 1045.
-We picked the completeness threshold for other regions and other magnitude ranges according as a year that the cumulative number of earthquakes increment uniformly.
-Table ~\ref{tab:completeness} shows the summary of values used in this study.
-
-\begin{figure*} [!ht]
-\centering
-\includegraphics[scale=0.28]{figures/pdf/figure-07.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Central, g-h)Kopeh Dagh, i-j)Zagros}
-\label{fig:comp_test_all_mag}
-\end{figure*}
-
-\begin{table*}[!ht]
-\centering
-\caption{Completeness threshold of tectonic seismic regions.}
-\begin{tabular}{ccccccccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
-3-4         & 1961          & 2005   & 2005             & 2005            & 2005    & 2005          \\ \hline
-4-5         & 1961          & 1961   & 1950             & 1961            & 1961    & 1961          \\ \hline
-5-6         & 1900          & 1900   & 1900             & 1854            & 1900    & 1900           \\ \hline
-6-7         & 1581          & 1664   & 1673             & 1837            & 1853    & 1778           \\ \hline
-7 $< $    & 1042          & -401    & 9                   & 762              & 1439    & -401            \\ 
+    \caption{Seismicity parameters for the tectonic seismic regions influencing seismic hazard in northern Iran.}
+    \begin{tabular}{ccccc}
+        \hline                                                                              \\[-1.6ex]
+                        & $b$-value         & Computed $M_{\max}$   & Observed $M_{\max}$   \\[0.6ex]
+        \hline                                                                              \\[-1.6ex]
+        Azerbaijan      & 1.10 $\pm$ 0.03   & 7.93 $\pm$ 0.34       & 7.7                   \\
+        Alborz          & 1.03 $\pm$ 0.03   & 7.85 $\pm$ 0.66       & 7.8                   \\
+        Kopeh Dagh      & 0.89 $\pm$ 0.04   & 7.78 $\pm$ 0.31       & 7.6                   \\
+        Zagros          & 0.99 $\pm$ 0.02   & 7.47 $\pm$ 0.26       & 7.4                   \\
+        Central-East    & 0.95 $\pm$ 0.04   & 7.84 $\pm$ 0.34       & 7.6                   \\
+        Uniform Model   & 0.90 $\pm$ 0.02   & 7.87 $\pm$ 0.26       & 7.8                   \\[0.5ex]
+        \hline 
     \end{tabular}
-\label{tab:completeness}
+    \label{tab:b_value} 
 \end{table*}
-
-%% ---------------------------------------------
-%% ---------------------------------------------
-%
-%% My (Naeem) original text.
-%
-%
-%\section{Analysis Parameters}
-%%\subsection{Magnitude Interval}
-%%\subsection{Minimum Magnitude}
-%\subsection{Attenuation Relationship}
-%The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ).
-We also presented the results for  $\pm$ standard deviation.
-\\
-%
-%\noindent
-%The attenuation relationship is:
-%
-%\begin{equation}
-%\begin{split}
-%ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
-%b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-%\end{split}
-%\end{equation}
-%
-%where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-%
-%\subsection{b-value}
-%
-%For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.\\
-%\noindent
-%\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively.
-For the north Iran uniform model we used 4.5 as a completeness magnitude.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table \ref{tab:b_value}.
-Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.
-%
-%\begin{figure*} [!ht]
-%\centering
-%\includegraphics[scale=0.4]{figures/pdf/annual_rate_m.pdf} 
-%\caption{Annual occurrence rate of the earthquake. a) Azerbaijan, b) Alborz, c) KopehDagh, d)Central, e)Zagros f) North Iran}
-%\label{fig:annual_m}
-%\end{figure*}
-%
-%
-%
-%
-%\noindent
-%
-%
-%\begin{table*}[!ht]
-%\centering
-%\caption{Seismicity parameters for three tectonic seismic regions.}
-%    \begin{tabular}{ccccc}
-%    ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
-%    Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
-%    Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
-%    Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
-%    Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
-%    Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
-%    Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
-%    \end{tabular}
-% \label{tab:b_value} 
-%\end{table*}
-%
-%
-%\subsection{Catalog Completness}
-%For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-\citet{Frankel1995} plotted the cumulative number of events against time for different regions.
-He assumes that from the point that the line become linear, the catalog is complete.
-Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP \citep{Wiemer2001}, \citet{Zare2014} reported the catalog completeness for the study regions.
-World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
-Up to 1961 these data formed the early instrumental period.
-In 1961 the Worldwide Standardized Seismograph Network (WWSSN) was stablished.
-The record of these seismographs considerably improved the seismic catalogs in different part of the world \citep{Shearer2009}.
-Fig.~\ref{fig:completness_scatter} shows the magnitude distribution of events with respect to the time of occurrence of the events.
-%
-%\begin{figure*} [!ht]
-%\centering
-%\includegraphics[scale=0.6]{figures/pdf/completness_scatter.pdf} 
-%\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c)Central, d)Kopeh-Dagh, e)Zagros}
-%\label{fig:completness_scatter}
-%\end{figure*}
-%
-% According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions' catalog.
-We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
-In order to be able to compare the results with \citet{Zare2014} we merge the data of Azerbaijan and Alborz seismic regions.
-Fig.~\ref{fig:completness_compare_zare_2014_Az_Al} shows the completeness of catalog for earthquakes with different magnitude range in Azerbaijan-Alborz region.
-According to this figure, midrange magnitudes ($ 4 < Mw < 6 $) fairly obey the network developments in 1900 and 1961.
-The completeness thresholds for each magnitude range which are reported by \citet{Zare2014} are shown by dashed green line.
-In this study we follow the \citet{Frankel1995} approach to determine the completeness of each region.
-Even though the approach used by \citet{Frankel1995} will lead to the conservative results, we make sure that we don't use a period of time without knowing the complete number of events.
-Determining the completeness of the catalog is very sensitive to the data.
-Converting earthquake magnitudes from different scales to moment magnitude obviously has some error.
-Having broader range of magnitude will help to minimize these sort of error.
-In this study we consider the magnitude intervals for completeness study as $Mw = 1$.
-%
-%\begin{figure*} [!ht]
-%\centering
-%\includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
-%\caption{Cumulative number of earthquakes with respect to the time.
-Magnitude range is represented in a box at the top left corner.
-Solid black lines represent the starting of early instrumental (1900) and instrumental (1961) period.
-Green dashed lines represents the completeness threshold reported by \citet{Zare2014}.
-Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
-%\label{fig:completness_compare_zare_2014_Az_Al}
-%\end{figure*}
-%
-%\noindent
-%Fig.~\ref{fig:comp_test_all_mag} illustrates the completeness of data for each magnitude threshold in five different regions.
-A uniform rise of cumulative number of earthquake in each magnitude range, defines the threshold for catalog completeness.
-We define the completeness of each magnitude range at a time which the cumulative number of earthquake increase linearly with time.
-We assume the catalog for earthquakes with magnitude greater than  7 ($M_w > 7$) is complete from the first historical earthquake report.
-Determining the completeness of the catalog for $ 6 < Mw \leq 7 $ needs precise observation of the catalog.
-In Azerbaijan tectonic seismic region after 1045  $Mw = 6.2$ earthquake the catalog seems complete up to 1318.
-However, between 1318 and 1581 (263 years) only one earthquake with magnitude $Mw > 6$ is reported (1440,  $Mw = 6.2$ ).
-Considering the activity of the Azerbaijan region, in this study we assume that the catalog is complete for earthquake with magnitude $ 6 < Mw \leq 7 $ after 1581.
-Similar situation happened at the period of 1715 - 1833.
-It worth to mention that in this case, the time period is shorter than before (118 years), meanwhile in this period of time two earthquakes with magnitude $Mw>7$ occurred in the Azerbaijan region (1721 $Mw=7.7$, 1780 $Mw=7.6$).
-The catalog may or may not be completed after 1045, however in this study we consider 1581 as a completeness threshold for magnitude  $ 6 < Mw \leq 7 $.
-Considering completeness of the catalog for Azerbaijan region from 1581 will result in conservative PGA for the region in compare with the model with threshold of 1045.
-We picked the completeness threshold for other regions and other magnitude ranges according as a year that the cumulative number of earthquakes increment uniformly.
-Table ~\ref{tab:completeness} shows the summary of values used in this study.
-%
-%
-%
-%\begin{figure*} [!ht]
-%\centering
-%\includegraphics[scale=0.28]{figures/pdf/comp_test_all_mag.pdf} 
-%\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Kopek Dagh, g-h)Kopeh Dagh, i-j)Zagros}
-%\label{fig:comp_test_all_mag}
-%\end{figure*}
-%
-%
-%
-%\begin{table*}[!ht]
-%\centering
-%\caption{Completeness threshold of tectonic seismic regions.}
-%\begin{tabular}{ccccccccc}
-% ~           & Azerbaijan & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
-%3-4         & 1961          & 2005   & 2005             & 2005            & 2005    & 2005          \\ \hline
-%4-5         & 1961          & 1961   & 1950             & 1961            & 1961    & 1961          \\ \hline
-%5-6         & 1900          & 1900   & 1900             & 1854            & 1900    & 1900           \\ \hline
-%6-7         & 1581          & 1664   & 1673             & 1837            & 1853    & 1778           \\ \hline
-%7 $< $    & 1042          & -401    & 9                   & 762              & 1439    & -401            \\ 
-%\end{tabular}
-%\label{tab:completeness}
-%\end{table*}

### 2016-06-13 analysis_parameters.tex
cleaning and making progress with params

@@
-\section{Analysis Parameters}
-
-% \subsection{Attenuation Relationship}
-
-% The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-The epistemic uncertainty in attenuation relationship is being considered through using the logic tree approach.
-Having close mean value and similar logic tree weights, logic tree approach will have a minor effect in considering the epistemic uncertainty.
-In this study instead of using  different GMPEs we use the best model of attenuation relationship for PGA \citep{Zafarani2014} as well $\pm$ standard deviation.
-\\
-
-% \noindent
-% The attenuation relationship is:
-
-% \begin{equation}
-% \begin{split}
-% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
-% b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-% \end{split}
-% \end{equation}
+\section{Old Analysis Parameters Section}
 
@@
 
-For each of the three seismic regions, Gutenberg-Richter parameters and maximum magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.\\
-\noindent
+\textcolor{red}{
+[Legacy text to be discussed with Naeem...]\\
+}
+
+\textcolor{blue}{
 \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
@@
 Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.
-
-% \begin{figure*} [!ht]
-% \centering
-% \includegraphics[scale=0.3]{figures/pdf/figure-04} 
-% \caption{The annual probability of exceeding the specified magnitude in different seismic tectonic region (a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros).
-The margin display the positive and negative standard deviation.}
-% \label{fig:annual_m}
-% \end{figure*}
-
-% \noindent
-
-% \begin{table*}[!ht]
-% \centering
-% \caption{Seismicity parameters for three tectonic seismic regions.}
-%     \begin{tabular}{ccccc}
-%     ~                          &         $b-value$     &   $M_{max} $  Calculated & $M_{max}$ obseved \\ \hline
-%     Azerbaijan           & 1.1   $\pm$ 0.03   &   7.93  $\pm$  0.34           &   7.7      			    \\ \hline
-%     Alborz                  &1.03  $\pm$ 0.03   &   7.85  $\pm$  0.66           &   7.8          	            \\ \hline
-%     Kopeh Dagh        & 0.89 $\pm$ 0.04   &   7.78  $\pm$  0.31           &   7.6          	            \\ \hline
-%     Central Iran         & 0.95 $\pm$ 0.04   &   7.84  $\pm$  0.34           &   7.6                           \\ \hline
-%     Zagros                 & 0.99 $\pm$ 0.02  &   7.47  $\pm$  0.26            &  7.4                            \\ \hline
-%     Uniform Model    & 0.9    $\pm$ 0.02  &   7.87  $\pm$  0.26            &  7.8                            \\ 
-%     \end{tabular}
-%  \label{tab:b_value} 
-% \end{table*}
+}
 
@@
 
-\begin{table*}[!ht]
-\centering
-\caption{Completeness threshold of tectonic seismic regions.}
-\begin{tabular}{ccccccccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
-3-4         & 1961          & 2005   & 2005             & 2005            & 2005    & 2005          \\ \hline
-4-5         & 1961          & 1961   & 1950             & 1961            & 1961    & 1961          \\ \hline
-5-6         & 1900          & 1900   & 1900             & 1854            & 1900    & 1900           \\ \hline
-6-7         & 1581          & 1664   & 1673             & 1837            & 1853    & 1778           \\ \hline
-7 $< $    & 1042          & -401    & 9                   & 762              & 1439    & -401            \\ 
-\end{tabular}
-\label{tab:completeness}
-\end{table*}
+% \begin{table*}[!ht]
+% \centering
+% \caption{Completeness threshold of tectonic seismic regions.}
+% \begin{tabular}{ccccccccc}
+%  ~           & Azerbaijan & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
+% 3-4         & 1961          & 2005   & 2005             & 2005            & 2005    & 2005          \\ \hline
+% 4-5         & 1961          & 1961   & 1950             & 1961            & 1961    & 1961          \\ \hline
+% 5-6         & 1900          & 1900   & 1900             & 1854            & 1900    & 1900           \\ \hline
+% 6-7         & 1581          & 1664   & 1673             & 1837            & 1853    & 1778           \\ \hline
+% 7 $< $    & 1042          & -401    & 9                   & 762              & 1439    & -401            \\ 
+% \end{tabular}
+% \label{tab:completeness}
+% \end{table*}
 

### 2016-06-13 completeness.tex
cleaning and making progress with params

@@
+\begin{table*}[t]
+    \centering
+    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
+    \begin{tabular}{lccccrc}
+    	\cline{2-7}                                              \\[-1.6ex]
+                        & 3--4 & 4--5 & 5--6 & 6--7 & 
+                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
+        \hline                                                   \\[-1.6ex]
+        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
+        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
+        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
+        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
+        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
+        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
+        \hline 
+    \end{tabular}
+    \label{tab:params} 
+\end{table*}
+
 \subsection{Completeness}
 
-\textcolor{red}{We will bring the completeness section here.}
+An important property of a seismic catalog is its completeness, which is measured both in terms of the magnitude above w....
+
+This parameter defines the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period, and is used as input to the seismic analysis.
+
+...which varies according to magnitude, is used as input during the seismic hazard analysis process.
+It basically consists in determining the point at which catalog data show a steady occurrence of events.
+There are multiple approaches to determine the completeness of a catalog.
+A simple approach used by \citet{Frankel1995} and others is to identify the year at which the rate of events becomes constant.
+In other words, if looking at a plot of cumulative number of events of a given magnitude range with respect to time, the catalog is assumed to be complete from the year at which moving forward the plot follows a straight line.
+A similar approach based on the maximum value of the first derivative of the frequency-magnitude curve is implemented in the ZMAP software \citep{Wiemer2001}.
+
+One of the difficulties in determining completeness is the availability of data for a long-enough period of time for all magnitude ranges, especially for large magnitude earthquakes of low recurrence.
+\citet{Zare} provide the years for catalog completeness in their the original catalog for the different regions in their study on the seismicity of the Middle East.
+They used the
+
+4.5, and 4.4 for 
+Central Iran, and Zagros tectonic seismic regions, respectively. For the uniform model we used 4.5 as a completeness magnitude.
+
+% 		& Azerbaijan  & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
+% 3-4         & 1961  & 2005   & 2005       & 2005         & 2005   & 2005          \\ \hline
+% 4-5         & 1961  & 1961   & 1950       & 1961         & 1961   & 1961          \\ \hline
+% 5-6         & 1900  & 1900   & 1900       & 1854         & 1900   & 1900           \\ \hline
+% 6-7         & 1581  & 1664   & 1673       & 1837         & 1853   & 1778           \\ \hline
+% 7 $< $      & 1042  & -401   & 9          & 762          & 1439   & -401            \\
+
+% For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
+\citet{Frankel1995} plotted the cumulative number of events against time for different regions.
+He assumes that from the point that the line become linear, the catalog is complete.
+This approach is similar to the MAXC method of ZMAP software \citep{Wiemer2001}, where the completeness treshold is the maximum value of the first derivative of the frequency-magnitude curve.
+
+% Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP, \citet{Zare2014} reported the catalog completeness for the study regions.
+
+% World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
+Up to 1961 these data formed the early instrumental period.
+In 1961 the Worldwide Standardized Seismograph Network (WWSSN) was stablished.
+The record of these seismographs considerably improved the seismic catalogs in different part of the world \citep{Shearer2009}.
+Fig.~\ref{fig:completness_scatter} shows the magnitude distribution of events with respect to the time of occurrence of the events.
+
+According to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions' catalog.
+
+% We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
+In order to be able to compare the results with \citet{Zare2014} we merge the data of Azerbaijan and Alborz seismic regions.
+Fig.~\ref{fig:completness_compare_zare_2014_Az_Al} shows the completeness of catalog for earthquakes with different magnitude range in Azerbaijan-Alborz region.
+According to this figure, midrange magnitudes ($ 4 < Mw < 6 $) fairly obey the network developments in 1900 and 1961.
+The completeness thresholds for each magnitude range which are reported by \citet{Zare2014} are shown by dashed green line.
+
+% In this study we follow the \citet{Frankel1995} approach to determine the completeness of each region.
+Even though the approach used by \citet{Frankel1995} will lead to the conservative results, we make sure that we don't use a period of time without knowing the complete number of events.
+Determining the completeness of the catalog is very sensitive to the data.
+Converting earthquake magnitudes from different scales to moment magnitude obviously has some error.
+Having broader range of magnitude will help to minimize these sort of error.
+In this study we consider the magnitude intervals for completeness study as $Mw = 1$.

### 2016-06-13 composition.tex
cleaning and making progress with params

@@
 
-A fundamental step in regional seismic hazard analysis is the composition of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
+The first fundamental step in regional seismic hazard analysis is the composition of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
 Nowadays, instrumental datasets are easily accessible through international, regional, and local agencies.

### 2016-06-13 parameters.tex
cleaning and making progress with params

\begin{table*}[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{lccc}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.10 $\pm$ 0.03   & 7.93 $\pm$ 0.34   & 7.7                       \\
        Alborz          & 1.03 $\pm$ 0.03   & 7.85 $\pm$ 0.66   & 7.8                       \\
        Kopeh Dagh      & 0.89 $\pm$ 0.04   & 7.78 $\pm$ 0.31   & 7.6                       \\
        Zagros          & 0.99 $\pm$ 0.02   & 7.47 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.95 $\pm$ 0.04   & 7.84 $\pm$ 0.34   & 7.6                       \\
        Uniform Model   & 0.90 $\pm$ 0.02   & 7.87 $\pm$ 0.26   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-04} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for seismic tectonic regions of (a) Alborz, (b) Azerbaijan, (c) Central Iran, (d) Kopeh Dagh, (e) Uniform (f) Zagros. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

\section{Seismicity Parameters}

Following the general approach described in the previous section and using the infrmation collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3). This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and \citet{Kijko_2004_PAG}. HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{}\textcolor{red}{[references needed]}.

As mentioned before, the $a$-value is estimated based on the smoothed number of events ($M \geq 3$) per grid cell, and thus is variable throughout our region of interest. On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within a given seismic zone. In this study we compute values for two different models. In the first model we obtain these parameters independently for each one of the seismic zones influencing the seismic hazard of northern Iran. That means we obtain distinct values of $b$ and $M_{\max}$ for Azerbaijan, Alborz, and Kopeh Dagh, which are our main seismic zones in northern Iran, as well as for the portions of the Zagros and Central-East seismic zones within our region of interest (see Fig.~\ref{fig:iran} for reference). In the second model we consider the whole region of interest as a uniform seismic zone. Admittedly, the second model is somewhat unrealistic if considered from the point of view that different seismic zones have different seismicity parameters. We thought, however, that computing results for a uniform model was useful for the analysis of results and comparisons with other studies.

Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained using HA3 for the five seismic zones in our region of interest and for the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$. Fig.~\ref{fig:annualp} shows the obtained annual probability of exceedance as a function of earthquake magnitude.

% *********************************************************************************************************************
% OLD
% *********************************************************************************************************************

% For each of the three seismic regions, Gutenberg-Richter parameters and maximum magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}. The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package. For smoothed seismicity areas, $b-value$ is assumed constant. The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.

% \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.  Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively. For the uniform model we used 4.5 as a completeness magnitude. In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters. We also used the seismicity parameters of \citet{Karimiparidari2013} as the priory information in HA3 code. The updated values are displayed in Table \ref{tab:b_value}.  Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.

% *********************************************************************************************************************
% OLDER
% *********************************************************************************************************************

% For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}. The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package. For smoothed seismicity areas, $b-value$ is assumed constant. The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\

% \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog. In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters. We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code. The updated values are displayed in Table 2.

% Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively. The completeness of each region can be seen easily from the scatter plot of completeness test.

### 2016-06-13 region.tex
cleaning and making progress with params

--- 2016-06-02 region-of-interest.tex
@@
 Epicentral locations are indicated with stars.
-The labels next to each star or linked with a line to avoid congestion show the magnitude and year of the earthquake.}
+The labels next to each star or linked with a line to avoid congestion show the magnitude and year of the earthquake.
+The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief.}
 	\label{fig:selected}
@@
 These faults are parallel to the northwest-trending structural gain of the Alborz Mountains belt, and include the south-dipping partially blind faults of Davudieh, Shian, and Bagh-E Feyz.
-According to \citet{Ambraseys2005}, Tehran---or the ancient city of Rey---has been devastated in multiple occasions due to severe earthquakes in this area.
+According to \citet{Ambraseys_1982_Book}, Tehran---or the ancient city of Rey---has been devastated in multiple occasions due to severe earthquakes in this area.
 Historical accounts document the occurrence of multiple $M>7$ earthquakes in 743, 958, 1177, 1665, and 1830.

### 2016-06-13 analysis_parameters.tex
fixing figures

@@
 
-\begin{figure*} [!ht]
-\centering
-\includegraphics[scale=0.5]{figures/pdf/figure-05.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros}
-\label{fig:completness_scatter}
-\end{figure*}
+% \begin{figure*} [!ht]
+% \centering
+% \includegraphics[scale=0.5]{figures/pdf/figure-05.pdf} 
+% \caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros}
+% \label{fig:completness_scatter}
+% \end{figure*}
 
@@
 
-\begin{figure*} [!ht]
-\centering
-\includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
-\caption{Cumulative number of earthquakes with respect to the time.
+% \begin{figure*} [!ht]
+% \centering
+% \includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
+% \caption{Cumulative number of earthquakes with respect to the time.
 Magnitude range is represented in a box at the top left corner.
@@
 Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
-\label{fig:completness_compare_zare_2014_Az_Al}
-\end{figure*}
+% \label{fig:completness_compare_zare_2014_Az_Al}
+% \end{figure*}
 
@@
 
-\begin{figure*} [!ht]
-\centering
-\includegraphics[scale=0.28]{figures/pdf/figure-07.pdf} 
-\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Central, g-h)Kopeh Dagh, i-j)Zagros}
-\label{fig:comp_test_all_mag}
-\end{figure*}
+% \begin{figure*} [!ht]
+% \centering
+% \includegraphics[scale=0.28]{figures/pdf/figure-05.pdf} 
+% \caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Central, g-h)Kopeh Dagh, i-j)Zagros}
+% \label{fig:comp_test_all_mag}
+% \end{figure*}
 

### 2016-06-13 composition.tex
fixing figures

@@
 In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with all $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
-The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.
+The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}, which shows the spatial distribution within the region of interest for both historical and instrumental events.
+In turn, Fig.~\ref{fig:scatter} shows the distribution of events in time and magnitude for each of the seismic zones, as well as for the complete region of interest (here referred to as the uniform model).
+
+\begin{figure*} [t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
+	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
+	\label{fig:scatter}
+\end{figure*}

### 2016-06-13 parameters.tex
fixing figures

@@
-\begin{table*}[t]
+\begin{table}[t]
     \centering
     \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
-    \begin{tabular}{lccc}
+    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
         \cline{2-4}                                                                         \\[-1.6ex]
@@
     \label{tab:params} 
-\end{table*}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-04} 
-    \caption{Annual probability of exceedance as a function of earthquake magnitude for seismic tectonic regions of (a) Alborz, (b) Azerbaijan, (c) Central Iran, (d) Kopeh Dagh, (e) Uniform (f) Zagros.
+    \includegraphics[width=\textwidth]{figures/pdf/figure-06} 
+    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
+The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
+THe last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
 The shaded range indicates the models' $\pm 1$ standard deviation.}

### 2016-06-14 completeness.tex
fixing figures
working on comppleteness figure

@@
-\begin{table*}[t]
-    \centering
-    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
-    \begin{tabular}{lccccrc}
-    	\cline{2-7}                                              \\[-1.6ex]
-                        & 3--4 & 4--5 & 5--6 & 6--7 & 
-                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
-        \hline                                                   \\[-1.6ex]
-        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
-        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
-        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
-        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
-        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
-        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
-        \hline 
-    \end{tabular}
-    \label{tab:params} 
-\end{table*}
-
 \subsection{Completeness}
 
-An important property of a seismic catalog is its completeness, which is measured both in terms of the magnitude above w....
+An important aspect of seismic catalogs is their completeness.
+Completeness is is measured both in terms of the year of completeness and the completeness magnitude.
+Both are used in the seismic analysis process.
+The year of completeness is the point in time at which catalog data exhibits a steady rate of event occurrence.
+This is measured for different magnitude ranges.
+A simple approach used by \citet{Frankel1995} and others is to identify the year at which a plot of the cumulative number of events with respect to time becomes (or at least, resembles) a straight line.
 
-This parameter defines the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period, and is used as input to the seismic analysis.
+The completeness magnitude, on the other hand, is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
+While the year of completeness can be determined by inspection of the data, the completeness magnitude requires a numerical analysis of the catalog.
+A common approach is to identify the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
+This method is widely used as implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
 
-...which varies according to magnitude, is used as input during the seismic hazard analysis process.
-It basically consists in determining the point at which catalog data show a steady occurrence of events.
-There are multiple approaches to determine the completeness of a catalog.
-A simple approach used by \citet{Frankel1995} and others is to identify the year at which the rate of events becomes constant.
-In other words, if looking at a plot of cumulative number of events of a given magnitude range with respect to time, the catalog is assumed to be complete from the year at which moving forward the plot follows a straight line.
-A similar approach based on the maximum value of the first derivative of the frequency-magnitude curve is implemented in the ZMAP software \citep{Wiemer2001}.
+One of the difficulties in determining completeness is the availability of data for a long-enough period of time for all magnitude ranges.
+In this study, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7 by inspection, following the approach used by \citet{Frankel1995}.
+This is illustrated in Fig.~\ref{fig:completeness}, where we show the cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our choice of completeness year thresholds.
+For events $M_w>7$, in which case there are no sufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
 
-One of the difficulties in determining completeness is the availability of data for a long-enough period of time for all magnitude ranges, especially for large magnitude earthquakes of low recurrence.
-\citet{Zare} provide the years for catalog completeness in their the original catalog for the different regions in their study on the seismicity of the Middle East.
-They used the
+The chosen years of completeness are compiled in Table \ref{tab:completeness}.
+Also shown in this table are the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest.
 
-4.5, and 4.4 for 
-Central Iran, and Zagros tectonic seismic regions, respectively. For the uniform model we used 4.5 as a completeness magnitude.
-
-% 		& Azerbaijan  & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
-% 3-4         & 1961  & 2005   & 2005       & 2005         & 2005   & 2005          \\ \hline
-% 4-5         & 1961  & 1961   & 1950       & 1961         & 1961   & 1961          \\ \hline
-% 5-6         & 1900  & 1900   & 1900       & 1854         & 1900   & 1900           \\ \hline
-% 6-7         & 1581  & 1664   & 1673       & 1837         & 1853   & 1778           \\ \hline
-% 7 $< $      & 1042  & -401   & 9          & 762          & 1439   & -401            \\
+... \citet{Zare} provide the years for catalog completeness in their the original catalog for the different regions in their study on the seismicity of the Middle East. They used the
 
@@
 
-According to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions' catalog.
-
 % We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
@@
 In this study we consider the magnitude intervals for completeness study as $Mw = 1$.
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[scale=0.28]{figures/pdf/figure-05.pdf} 
+    \caption{Pending.}
+    \label{fig:completeness}
+\end{figure*}
+
+\begin{table}[t]
+    \centering
+    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
+    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
+        \cline{2-7}                                              \\[-1.6ex]
+                        & 3--4 & 4--5 & 5--6 & 6--7 & 
+                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
+        \hline                                                   \\[-1.6ex]
+        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
+        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
+        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
+        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
+        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
+        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
+        \hline 
+    \end{tabular}
+    \label{tab:completeness} 
+\end{table}

### 2016-06-14 figures/gmt/plot-completeness-1.sh

@@ -1,0 +1,108 @@
+
+clear
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT               = 8
+
+gmt gmtset MAP_FRAME_PEN            = 0.75p,black
+gmt gmtset MAP_FRAME_WIDTH          = 0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
+gmt gmtset MAP_LABEL_OFFSET         = 8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
+
+# Read arguments
+# ------------------------------------------------------------------------------
+
+  MAG=$1
+MINYR=$2
+MAXYR=$3
+ MAXN=$4
+
+# Assign static files data
+# ------------------------------------------------------------------------------
+
+AZER=azerbaijan
+ALBO=alborz
+KOPE=kopeh-dagh
+ZAGR=zagros
+CENT=central-east
+
+OUTPUTNAME=completeness
+OUTPUTFILE=${OUTPUTNAME}.ps
+
+# ==============================================================================================================
+# PREPARING ALL THE DATA
+# ==============================================================================================================
+
+
+# Captures the columns necessary for plotting
+# ------------------------------------------------------------------------------
+
+awk -F' ' '{print $1, $'$1'}' ${AZER}.txt > ${AZER}.tmp
+awk -F' ' '{print $1, $'$1'}' ${ALBO}.txt > ${ALBO}.tmp
+awk -F' ' '{print $1, $'$1'}' ${KOPE}.txt > ${KOPE}.tmp
+awk -F' ' '{print $1, $'$1'}' ${ZAGR}.txt > ${ZAGR}.tmp
[…]

### 2016-06-14 analysis_parameters.tex
completed completeness and parameters sections

@@
 
-\textcolor{blue}{
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
+% \textcolor{blue}{
+% \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
 Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively.
@@
 Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.
-}
+% }
 
-\subsection{Catalog Completness}
+% \subsection{Catalog Completness}
 
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
+% For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
 \citet{Frankel1995} plotted the cumulative number of events against time for different regions.
@@
 
-According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions' catalog.
+% According to   \citet{Frankel1995},  we made plots of the cumulative number of events against time for different regions' catalog.
 We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
@@
 
-\noindent
-Fig.~\ref{fig:comp_test_all_mag} illustrates the completeness of data for each magnitude threshold in five different regions.
+% \noindent
+% Fig.~\ref{fig:comp_test_all_mag} illustrates the completeness of data for each magnitude threshold in five different regions.
 A uniform rise of cumulative number of earthquake in each magnitude range, defines the threshold for catalog completeness.

### 2016-06-14 completeness.tex
completed completeness and parameters sections

@@
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/pdf/figure-05.pdf} 
+    \caption{Normalized cumulative number of events and completeness year thresholds for each of the seismic zones considered within the region of interest, and for magnitude intervals of $\Delta M = 1$ between $M_w$ 3 and 6.
+The year thresholds are indicated by a triangle mark at the top and the vertical dashed lines in the background.
+Normalization values for each curve are indicated on the right margins and distinguished by color as indicated in the legend.}
+    \label{fig:completeness}
+\end{figure*}
+
 \subsection{Completeness}
@@
 An important aspect of seismic catalogs is their completeness.
-Completeness is is measured both in terms of the year of completeness and the completeness magnitude.
-Both are used in the seismic analysis process.
-The year of completeness is the point in time at which catalog data exhibits a steady rate of event occurrence.
-This is measured for different magnitude ranges.
-A simple approach used by \citet{Frankel1995} and others is to identify the year at which a plot of the cumulative number of events with respect to time becomes (or at least, resembles) a straight line.
+This characteristic is measured in terms of the year of completeness and the completeness magnitude, which are used as parameters in the seismic analysis process.
+In simple terms, the year of completeness is the point in time at which catalog data exhibits a steady rate of event occurrence or record accumulation.
+This point is typically identified for different magnitude ranges.
+A simple approach used by \citet{Frankel1995} and others is to select the year at which a plot of the cumulative number of events with respect to time becomes (or starts to resemble) a straight line.
 
-The completeness magnitude, on the other hand, is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
-While the year of completeness can be determined by inspection of the data, the completeness magnitude requires a numerical analysis of the catalog.
-A common approach is to identify the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
-This method is widely used as implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+On the other hand, The completeness magnitude, denoted as $M_c$, is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
+While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the catalog.
+A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
+This method is widely used and has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+\citet{Zare2014}, for instance, used this method to identify $M_c$ values for the different regions of the Middle East.
 
-One of the difficulties in determining completeness is the availability of data for a long-enough period of time for all magnitude ranges.
+One of the difficulties in determining completeness is the availability of data for a period of time long enough for all magnitude ranges, so that selection of completeness parameters is reliable.
 In this study, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7 by inspection, following the approach used by \citet{Frankel1995}.
-This is illustrated in Fig.~\ref{fig:completeness}, where we show the cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our choice of completeness year thresholds.
+This is illustrated in Fig.~\ref{fig:completeness}, where we show the normalized cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our choice of the completeness year thresholds in each case.
 For events $M_w>7$, in which case there are no sufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
 
-The chosen years of completeness are compiled in Table \ref{tab:completeness}.
-Also shown in this table are the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest.
+Admittedly, the choice of the threshold years is highly subjective.
+We should note then, that in the process of choosing the points indicated in the plots shown in Fig.~\ref{fig:completeness}, we considered additional contributing information such as the history of instrumentation.
+It is well known, for instance, that the number of recorded earthquakes increased considerably after the first deployment of seismic instruments in the early 1900s, and later with the establishment of the Worldwide Standardized Seismograph Network in 1961.
+We also compared our choices with the year thresholds reported by \citet{Zare2014}, which we found to be consistently earlier than our preferred years of completeness.
+In the end, we proceeded with our selection, which leads to a more conservative estimation of hazard.
 
-... \citet{Zare} provide the years for catalog completeness in their the original catalog for the different regions in their study on the seismicity of the Middle East. They used the
+For the case of the completeness magnitude $M_c$, we adopted the values reported by \citet{Karimiparidari2013}.
+Our choice the $M_c$ values by \citet{Karimiparidari2013} over those of \citet{Zare2014} is based on the fact that the former distinguishes Azerbaijan and Alborz as individual seismic zones---as we do---as opposed to the approach followed by the latter, in which these two are a single, larger seismic zone.
+Both the chosen years of completeness and the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest are summarized in Table \ref{tab:completeness}.
+
+\begin{table}%[t]
+    \centering
+    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
+    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
+        \cline{2-7}                                              \\[-1.6ex]
+                        & 3--4 & 4--5 & 5--6 & 6--7 & 
+                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
+        \hline                                                   \\[-1.6ex]
+        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
+        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
+        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
+        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
+        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
+        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
+        \hline 
+    \end{tabular}
+    \label{tab:completeness} 
+\end{table}
+
+% *********************************************************************************************************************
+% OLD STUFF
+% *********************************************************************************************************************
 
@@
 In this study we consider the magnitude intervals for completeness study as $Mw = 1$.
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[scale=0.28]{figures/pdf/figure-05.pdf} 
-    \caption{Pending.}
-    \label{fig:completeness}
-\end{figure*}
-
-\begin{table}[t]
-    \centering
-    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
-    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
-        \cline{2-7}                                              \\[-1.6ex]
-                        & 3--4 & 4--5 & 5--6 & 6--7 & 
-                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
-        \hline                                                   \\[-1.6ex]
-        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
-        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
-        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
-        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
-        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
-        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
-        \hline 
-    \end{tabular}
-    \label{tab:completeness} 
-\end{table}

### 2016-06-14 parameters.tex
completed completeness and parameters sections

@@
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-06} 
+    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
+The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
+THe last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
+The shaded range indicates the models' $\pm 1$ standard deviation.}
+    \label{fig:annualp}
+\end{figure*}
+
+\section{Seismicity Parameters}
+
+Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3).
+This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.
+HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{}\textcolor{red}{[references needed]}.
+
+The $a$-value is estimated based on the completeness year, the correlation distance, and the (smoothed) number of events per grid cell.
+We count events with magnitude $M_w > 3$ and smooth the number of events for each cell.
+This means each cell has a different $a$-value and thus the result is variable throughout our region of interest.
+On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
+We compute $b$ and $M_{\max}$ for two different models using the information from the catalog for prehistorical, historical, and instrumental seismicity and the computed values of $M_c$.
+In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
+That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the portions of the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
+
+In the second model we consider the whole study area as a uniform seismic zone.
+Admittedly, this assumption is unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
+Nonetheless, computing results for this uniform model is useful for the analysis of results and comparisons with other studies.
+Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones and the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
+
 \begin{table}[t]
@@
 \end{table}
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-06} 
-    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
-The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
-THe last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
-The shaded range indicates the models' $\pm 1$ standard deviation.}
-    \label{fig:annualp}
-\end{figure*}
-
-\section{Seismicity Parameters}
-
-Following the general approach described in the previous section and using the infrmation collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3).
-This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and \citet{Kijko_2004_PAG}.
-HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{}\textcolor{red}{[references needed]}.
-
-As mentioned before, the $a$-value is estimated based on the smoothed number of events ($M \geq 3$) per grid cell, and thus is variable throughout our region of interest.
-On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within a given seismic zone.
-In this study we compute values for two different models.
-In the first model we obtain these parameters independently for each one of the seismic zones influencing the seismic hazard of northern Iran.
-That means we obtain distinct values of $b$ and $M_{\max}$ for Azerbaijan, Alborz, and Kopeh Dagh, which are our main seismic zones in northern Iran, as well as for the portions of the Zagros and Central-East seismic zones within our region of interest (see Fig.~\ref{fig:iran} for reference).
-In the second model we consider the whole region of interest as a uniform seismic zone.
-Admittedly, the second model is somewhat unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
-We thought, however, that computing results for a uniform model was useful for the analysis of results and comparisons with other studies.
-
-Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained using HA3 for the five seismic zones in our region of interest and for the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.
-Fig.~\ref{fig:annualp} shows the obtained annual probability of exceedance as a function of earthquake magnitude.
 

### 2016-06-14 figures/gmt/plot-completeness-norm.sh

@@ -1,0 +1,121 @@
+
+clear
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT               = 8
+
+gmt gmtset MAP_FRAME_PEN            = 0.75p,black
+gmt gmtset MAP_FRAME_WIDTH          = 0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     = 0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
+gmt gmtset MAP_LABEL_OFFSET         = 8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
+
+MINYR=0
+MAXYR=2016
+ MAXN=100
+
+# Assign static files data
+# ------------------------------------------------------------------------------
+
+AZER=azerbaijan
+ALBO=alborz
+KOPE=kopeh-dagh
+ZAGR=zagros
+CENT=central-east
+
+OUTPUTNAME=completeness
+OUTPUTFILE=${OUTPUTNAME}.ps
+
+# ==============================================================================================================
+# PREPARING ALL THE DATA
+# ==============================================================================================================
+
+awk 'FNR==NR{max=($2+0>max)?$2:max;next} {print $1,$2/max}' ${AZER}.txt ${AZER}.txt > ${AZER}.tmp
+awk 'FNR==NR{max=($2+0>max)?$2:max;next} {print $1,$2/max}' ${ALBO}.txt ${ALBO}.txt > ${ALBO}.tmp
+awk 'FNR==NR{max=($2+0>max)?$2:max;next} {print $1,$2/max}' ${KOPE}.txt ${KOPE}.txt > ${KOPE}.tmp
+awk 'FNR==NR{max=($2+0>max)?$2:max;next} {print $1,$2/max}' ${ZAGR}.txt ${ZAGR}.txt > ${ZAGR}.tmp
[…]

### 2016-06-14 figures/gmt/plot-completeness.sh

@@ -15,13 +15,9 @@ gmt gmtset MAP_TICK_LENGTH_PRIMARY  = 6p/3p
 gmt gmtset MAP_LABEL_OFFSET         = 8p
 gmt gmtset MAP_ANNOT_OFFSET_PRIMARY = 5p
 
-# Read arguments
-# ------------------------------------------------------------------------------
-
-  MAG=$1
-MINYR=$2
-MAXYR=$3
- MAXN=$4
+MINYR=0
+MAXYR=2020
+ MAXN=100
 
 # Assign static files data
 # ------------------------------------------------------------------------------
@@ -39,22 +35,13 @@ OUTPUTFILE=${OUTPUTNAME}.ps
 # PREPARING ALL THE DATA
 # ==============================================================================================================
 
+awk -F' ' '{print $1, $2}' ${AZER}.txt > ${AZER}.tmp
+awk -F' ' '{print $1, $2}' ${ALBO}.txt > ${ALBO}.tmp
+awk -F' ' '{print $1, $2}' ${KOPE}.txt > ${KOPE}.tmp
+awk -F' ' '{print $1, $2}' ${ZAGR}.txt > ${ZAGR}.tmp
+awk -F' ' '{print $1, $2}' ${CENT}.txt > ${CENT}.tmp
 
-# Captures the columns necessary for plotting
-# ------------------------------------------------------------------------------
-
-awk -F' ' '{print $1, $'$1'}' ${AZER}.txt > ${AZER}.tmp
-awk -F' ' '{print $1, $'$1'}' ${ALBO}.txt > ${ALBO}.tmp
-awk -F' ' '{print $1, $'$1'}' ${KOPE}.txt > ${KOPE}.tmp
-awk -F' ' '{print $1, $'$1'}' ${ZAGR}.txt > ${ZAGR}.tmp
-awk -F' ' '{print $1, $'$1'}' ${CENT}.txt > ${CENT}.tmp
-
-
-# ==============================================================================================================
[…]

### 2016-06-15 completeness.tex
touches on completeness

@@
 
-On the other hand, The completeness magnitude, denoted as $M_c$, is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
+On the other hand, the completeness magnitude---denoted as $M_c$---is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
 While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the catalog.
 A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
-This method is widely used and has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
-\citet{Zare2014}, for instance, used this method to identify $M_c$ values for the different regions of the Middle East.
+This method is known as the maximum curvature (MAXC) technique.
+It is widely used and has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+\citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
 

### 2016-06-15 parameters.tex
touches on completeness

@@
 This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.
-HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{}\textcolor{red}{[references needed]}.
+HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{Karimiparidari2013, Khodaverdian_2016_BSSA}.
 

### 2016-06-15 completeness.tex
after discussion about completeness with Naeem, years changed

@@
         Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
-        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
-        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
-        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
-        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
+        Alborz          & 2005 & 1961 & 1900 & 1664 &--401 & 4.4 \\
+        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9 & 4.5 \\
+        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439 & 4.4 \\
+        Central-East    & 2005 & 1961 & 1900 & 1837 &  762 & 4.5 \\
         Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]

### 2016-06-15 Hazard_calculation.tex
started thinking about results section

--- 2015-09-28 Hazard_calculation.tex
@@
 
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
+% The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
+These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.
+
+As discussed before the border of the study region
+
 Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
 In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
+Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.
+
 We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
@@
 In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
+
 Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
@@
 Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
+
 Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
@@
 
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
+% \begin{figure} [H]
+% \centering
+% \includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
+% \caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
+% \label{fig:10percent}
+% \end{figure}
 
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
+% \begin{figure} [H]
+% \centering
+% \includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
+% \caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
+% \label{fig:2percent}
+% \end{figure}

### 2016-06-15 hazard_analysis_results.tex
started thinking about results section

@@
 
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-As mentioned earlier we broader the study region by 0.5\textdegree{}-perimeter to avoid the unexpected effect of outer border seismicity as well as avoiding the artifcial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
+% The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
+These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.
+
+% As mentioned earlier we broader the study region by 0.5\textdegree{}-perimeter to avoid the unexpected effect of outer border seismicity as well as avoiding the artifcial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
 Also it provides more uniform surrounding of the study area\citep{Lapajne1997}.
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
+
+% We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
 We assume magnitude increment as $\Delta_M = 0.1$.
 In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
+
 Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
@@
 Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
+
 Regarding the important parameters in determining the location of earhtquake (e.g.
@@
 \subsection{Hazard Curve}
+
 We calculated the probability of exceedance of the ground motion from different ground motion levels, separately for each of 5 regions.
@@
 \subsection{Peak Ground Acceleration}
+
 We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance.

### 2016-06-15 parameters.tex
after discussion about completeness with Naeem, years changed
started thinking about results section

@@
 
-The $a$-value is estimated based on the completeness year, the correlation distance, and the (smoothed) number of events per grid cell.
-We count events with magnitude $M_w > 3$ and smooth the number of events for each cell.
+The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell.
+We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell.
 This means each cell has a different $a$-value and thus the result is variable throughout our region of interest.
 On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
-We compute $b$ and $M_{\max}$ for two different models using the information from the catalog for prehistorical, historical, and instrumental seismicity and the computed values of $M_c$.
+We compute $b$ and $M_{\max}$ using the information from the catalog, which we divide in three sub-catalogs for the prehistorical (before XXXX), historical (between XXXX and XXXX), and instrumental (after XXXX) seismicity.
+In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
+In a recent hazard analysis for whole Iran, \citet{} used variable values of $M_c$ for individual sub-catalogs.
+This is an additional level of complexity we may consider in the future.
+
+We obtain $b$ and $M_{\max}$ for two different models.
 In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
 That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the portions of the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
-
 In the second model we consider the whole study area as a uniform seismic zone.
 Admittedly, this assumption is unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
-Nonetheless, computing results for this uniform model is useful for the analysis of results and comparisons with other studies.
+Computing results for this uniform model is, nonetheless, useful for the analysis of results and comparisons with other studies.
 Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones and the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.

### 2016-06-15 region.tex
started thinking about results section

@@
 Our calculations, however, included data from a slightly larger region with a 0.5\textdegree{}-perimeter as indicated in the figure.
-This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the region of interest.
+This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the effective region of interest and/or to provide a uniform contribution from the earthquakes surrounding the region \citep[see][]{Lapajne1997}.
 The effective region has an area of 1,703 km $\times$ 667 km.

### 2016-06-15 results.tex
started thinking about results section

--- 2015-09-28 smoothed.tex
@@
-\documentclass{article}
-
-\usepackage{textcomp}
-\usepackage{amsmath}    % need for subequations
-\usepackage{graphicx}   % need for figures
-\usepackage{verbatim}   % useful for program listings
-\usepackage{color}      % use if color is used in text
-\usepackage{subfigure}  % use for side-by-side figures
-\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
-\usepackage{cite}
-\usepackage{float}
-\usepackage{natbib}
-\usepackage[utf8]{inputenc}
-\usepackage{simplemargins}
-\usepackage{setspace}
-\usepackage{multirow}
-\usepackage{url}
-
-\usepackage{etoolbox}
-\usepackage{lipsum}
-
-\setallmargins{1in}
-\onehalfspacing
-
-\linespread{1.8} % line space
-
-\patchcmd{\thebibliography}{\section*}{\section*}{}{}
-
-% don't need the following. simply use defaults
-%\setlength{\baselineskip}{15.0pt}    % 16 pt usual spacing between lines
-%\setlength{\parskip}{3pt plus 2pt}
-%\setlength{\parindent}{20pt}
-%\setlength{\oddsidemargin}{0.5cm}
-%\setlength{\evensidemargin}{0.5cm}
-%\setlength{\marginparsep}{0.75cm}
-%\setlength{\marginparwidth}{2.5cm}
-%\setlength{\marginparpush}{1.0cm}
-%\setlength{\textwidth}{150mm}
-
-\usepackage{xcolor}
-\hypersetup{
-    colorlinks,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}
-}
-
-\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}
-%\author{
-
-%\begin{center}
-%\linespread{1}\Large\bfseries {Naeem Khoshnevis}$^*$\\  Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\    \\ \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007 \\  \\ \textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\  3890 Central Avenue, Memphis, TN 38152   \\ Phone (901) 678-4992 \\
-
-%\end{center}
-
-% }
-
-\begin{document}
-%\thispagestyle{empty}
-\maketitle
-
-\newpage
-
-\begin{center}
-\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave.
-Memphis TN 38152 \\ Phone (901) 678-2007\\
-\vspace{10 mm}
- \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
-\vspace{10 mm}
-\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
-\vspace{10 mm}
-\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\
-
-\end{center}
-
-\newpage
-
-\begin{abstract}
-In this study we conduct a new probabilistic seismic hazard assessment for northern Iran, using recently confirmed ground motion prediction equations and updated seismic catalogs.
-We evaluate seismic hazard over three tectonic seismic zones (Alborz Mountain Range, Azerbaijan and Kopeh-Dagh) using smoothed historical seismicity.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, spatially gridded to cells.
-We decluster historical and instrumental seismicity to compute the rate of earthquakes in each grid, and smooth these rates to account for uncertainty in the spatial distribution of future earthquakes.
-We assume each grid cell has spacing of $0.1^{\circ}$ in latitude and $0.1^{\circ}$ in longitude and count the number of earthquakes in each of them.
-We use Gaussian filter to smooth the fraction of earthquakes in incremental intervals of magnitude.
-For this article, in order to consider the seismicity rate, we consider all historical and instrumental earthquakes with magnitude above 3.
-To calculate the seismic hazard we defined two models based on structural damage threshold magnitude, including Mw 4.5 and Mw 5 with weight of 0.3 and 0.7, respectively.
-Seismicity parameters are calculated for each seismic region, and smoothed seismicity is calculated separately for each.
-We add the probability of exceedance of all regions and present the smoothed seismicity hazard in northern Iran.
-The horizontal peak ground acceleration is selected as the ground motion parameter.
-The results are assessed in terms of the expected peak ground acceleration (PGA) with a 10\% and 2\% probability of exceedance in 50 years for rock site conditions.
-The seismic hazard map for northern Iran is presented.
-The maximum seismic hazard values are 0.44 $g$ and  0.74 $g$ for 10\% and 2\% probability in exceedance in 50 years, which are calculated in both Azerbaijan and Alborz tectonic seismic region.
-The result of 10\% probability of exceedance in 50 years are in close agreement with current Iranian code of practice for seismic design of building.
-\end{abstract}
-
-\smallskip
-\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran
-
-\section{Introduction}
-
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.\\
-\noindent
-In northeastern of Iran, at least four historical earthquakes with $M>7$ struck in less than 200 years (1209, 1405) near the city of Neyshabur.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-\noindent
-In the north western of Iran, a study of the seismic history of Tabriz based on available data shows that this region has been seismically active since 634 A.D.
-The historical earthquake data (pre 1900) illustrate that in earlier times the region was destroyed several times by major earthquakes.
-In 858, Tabriz was completely destroyed by a massive earthquake; the 1040 earthquake caused more than 50,000 causalities, and in 1936 due to the earthquake in Tabriz, most of the buildings fissured and even some collapsed \citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-\noindent
-In north central Iran, in the Alborz region, a historical earthquake sequence occurred over a longer time period of 1100 years.
-At least three damaging historical earthquakes ruptured adjacent segments of the Mosha fault for a continuous distance of nearly 200 km: 958 A.D.
-(western segments), 1665 A.D.
-(eastern segments), and 1830 A.D.
-(central segments) \cite{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-\noindent
-Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-In the last three decades, different seismic hazard analysis studies substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the Hazus method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-In this study we used smoothed seismicity \citep{Frankel1995}.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopek Dagh.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We used \citet{Karimiparidari2013} seismicity parameters in these regions.
-We consider the MW5 earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building we also considered Mw45 as a threshold for structural damage to this building.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-\caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-\label{fig:Iran}
-\end{figure}
-
-\noindent
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog from International Institute of Earthquake Engineering and Seismology \citep{IIEES} and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-\\
-\noindent
-Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-\\
-\noindent
-The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-\section{Seismic regions and seismicity rate}
-With respect to different seismicity rates of the regions \cite{Nemati2015}, as well as the completeness of the seismic catalog, the study region is divided into three zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-A review of Iran's historical earthquakes (pre 1900) is provided by \citet{Ambraseys2005}.
-\citet{Karimiparidari2013} converted all historical earthquakes to a unified magnitude ($M_w$), which we use as a historical catalog.
-The International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES} has reported the instrumental data, which also involves earthquakes from border countries which have considerable affect in the seismicity of Iran's border cities.
-In the present study, historical data are integrated with instrumental data.
-For the purpose of this research, each seismic region is defined as a rectangular area bounded by latitudes of $34^{\circ}-40^{\circ}$ N, and longitudes of $43.5^{\circ}-48^{\circ}$ E, $48^{\circ}-58^{\circ}$ E, and $58^{\circ}-61.5^{\circ}$ E for Azerbaijan, Alborz, and Kopeh-Dagh, respectively.
-
-\subsection{Alborz Mountain Range (Alborz)}
-Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran \citep{Berberian1999}.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz \citep{Berberian1999}.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-
-\subsection{Azerbaijan}
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879 \citep{Berberian1999}.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7).
-However, their meizoseismal zones are not well known and so could not be used to identify which faults were responsible for them.
-Earthquakes in 1273 and 1304 were temporal clusters like the 1721-86 events, but the direction of propagation is not known \citep{Berberian1997, Berberian1999}.
-
-\subsection{Kopeh Dagh}
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455 \citep{Berberian2001}.
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-
-\section{Magnitude Conversion}
-
-In this study we use two sets of data, i.e., historical and instrumental seismic catalogs.
-We use the historical catalog reported by \citep{Karimiparidari2013}, which is converted into $M_w$ magnitude.
-Fig.~\ref{fig:historical} shows the historical earthquakes (pre-1900) in northern Iran.
-The instrumental data has been reported mainly by the International Institute of Earthquake Engineering and Seismology of Iran \citep{IIEES}, and are reported in $M_L$ magnitude type.
-In this study we use the relationship that proposed by \citet{Karimiparidari2013}, to convert local magnitude into moment magnitude.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure2.pdf} 
-\caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-\label{fig:historical}
-\end{figure}
-
-\section{Declustering}
-
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure3.pdf} 
-\caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-\label{fig:instrumental}
-\end{figure}
-
-\section{Completeness tests}
-For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-To access catalog completeness, according to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions.
-Fig.~\ref{fig:comptest} shows the completeness of data for each magnitude threshold in three different regions.
-A uniform rise of cumulative number of earthquake in each magnitude big, defines the threshold for catalog completeness.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.3]{figures/pdf/Figure4.pdf} 
-\caption{Completeness test for earthquakes occurred in the three study regions. Red lines represent $M_w > 7$ }
-\label{fig:comptest}
-\end{figure}
-
-We assume the catalog for earthquakes with magnitude greater than $M_w=7$ is complete from the first historical earthquake report.
-Table 1 presents the completeness of catalog of each region for different moment magnitudes.
-
-\begin{table}[h]
-\centering
-\caption{Completeness threshold of three tectonic seismic regions.}
-\begin{tabular}{cccc}
- ~           & Azerbaijan & Alborz & Kopeh Dagh \\ \hline
-3-4         & 2004       & 2004   & 2005       \\ \hline
-4-5         & 1960       & 1960   & 1960       \\ \hline
-5-6         & 1900       & 1900   & 1900       \\ \hline
-6-7         & 1844       & 1809   & 1810         \\ \hline
-7 $< $    &  85          & -400    & 10         \\ \hline
-\end{tabular}
-\end{table}
-
-\section{ Gutenberg-Richter Parameters}
-For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-\noindent
-\citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-\\
-\noindent
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
-
-\begin{table}[h]
-\centering
-\caption{Seismicity parameters for three tectonic seismic regions.}
-    \begin{tabular}{ccccc}
-    ~                   & $b-value$            & $\lambda$                  & $M_{max}$ Calculated & $M_{max}$ obseved \\ \hline
-    Azerbaijan    & 1.06 $\pm$ 0.03  & (1.827  $\pm$ 0.216) & 7.78  $\pm$ 0.26           & 7.7          \\ \hline
-    Alborz           & 1.1  $\pm$ 0.03   & (2.290  $\pm$ 0.282) & 7.91  $\pm$ 0.27           & 7.7          \\ \hline
-    Kopeh Dagh & 0.97  $\pm$ 0.04 & (1.716  $\pm$ 0.243) & 7.67  $\pm$ 0.26           & 7.6          \\
-    \end{tabular}
-
-\end{table}
-
-\section{Methodology for Hazard calculation}
-
-To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_w5$ .
-Category of 5+ and others (M6+ and M7+) assume that future $M_w4.5$ events will occur near where they have occurred in the past.
-\\
-\noindent
-According to \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake if it occurs very close to the structure.
-In this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w5$ and $M_w4.5$ as a threshold magnitude for seismic hazard calculation with weight of 0.7 and 0.3, respectively.\\
-\noindent
-According to \citet{Frankel1995}, we count the number of earthquake $n_i$ with magnitude above $M{_R{_e{_f}}}$ in each cell of a grid with spacing of $0.1^{\circ}$ in both latitude and longitude (about 11 km).
-This count shows the maximum likelihood estimate of $10^a$ for that mentioned cell \citep{Weichert1980, Bender1983} for earthquakes with magnitude greater than $M{_R{_e{_f}}}$.
-Applying the Herrmann formula \citep{Herrmann1977}, the values of $n_i$ are converted from cumulative values (number of events above $M{_R{_e{_f}}}$) to incremental values (number of events from $M{_R{_e{_f}}}$ to $M{_R{_e{_f}}} +\Delta M$ ).
-The grid of $n_i$ values is spatially smoothed by multiplying by a Gaussian function with correlation distance c.
-For each cell $i$, the smoothed value $\tilde{n}_i$ is obtained from \citet{Frankel1995}
-
-\begin{equation}
-\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-\end{equation}
-
-\noindent
-where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-\noindent
-For a grid of sites and by using $\tilde{n}_i$ from Eq.
-(1), the annual probability of exceeding specified ground motions is calculated.
-For each site, the values of $\tilde{n}_i$ are binned by their distance from that site, in a way that $N_k$ denotes the total of $\tilde{n}_i$ values for cells within a certain distance increment of the site.
-Now the annual rate $\lambda (u> u_0 )$ of exceeding ground motion $u_0$ at a specific site is determined from a sum over distance and magnitude \citet{Frankel1995}:
-
-\begin{equation}
-\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} p(u>u_0 | D_k ,M_l),
-\end{equation}
-
-\noindent
-where $k$ is the index for the distance bin, and $l$ is the index for the magnitude bin; $T$ is the time in years of the earthquake catalog used to determine $N_k$.
-Annual rate of earthquakes in the distance bin $k$ and magnitude bin $l$ is the first factor in the summation.
-The $b-value$ is considered uniform throughout most of the area.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}
-
-\section{Attenuation relationship}
-The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-\noindent
-
-The attenuation relationship is:
-
-\begin{equation}
-ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-\end{equation}
-
-where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
-
-\section{Hazard Calculation}
+\section{Results}
 
 The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.\\
-\noindent
-Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
-Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.\\
-\noindent
-We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
-We assume magnitude increment as $\Delta_M = 0.1$.
-In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-\\
-\noindent
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure5.pdf} 
-\caption{Probabilistic PGA (10\% in 50 years), based on smoothed seismicity for Northern Iran }
-\label{fig:10percent}
-\end{figure}
-
-\begin{figure} [H]
-\centering
-\includegraphics[scale=0.8]{figures/pdf/Figure6.pdf} 
-\caption{Probabilistic PGA (2\% in 50 years), based on smoothed seismicity for Northern Iran}
-\label{fig:2percent}
-\end{figure}
-
-\section{Discussion}
-
-Seismic hazard in northern Iran is computed based on background seismicity and projected on a set of hazard maps.
-The results obtained are represented as maps for the spatial distribution of horizontal peak ground acceleration with 10\% and 2\% probability of exceedance in 50 years, which correspond to the return period of 475 and 2475 years.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-Figure 5 presents the map of PGA for 10\% exceedance in 50 years.
-The highest and the lowest contour values are 0.44g and 0.12g, respectively.
-The highest and lowest values in Fig.~\ref{fig:10percent} are 0.74g and 0.19g, respectively.
-(We disregarded the values in the Caspian Sea and also close to the study region's borders).
-Highest hazards are established in the Alborz tectonic seismic region in the city of Damavand, about 55 km east of Tehran city in Tehran province.
-Lowest hazards are established in the Azerbaijan tectonic seismic province, about 31 km east of Shahin Dezh in West Azerbaijan province.
-Also many other places are in higher hazard zone both in Azerbaijan and and Alborz seismic tectonic regions (See Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent}).
-Many seismic hazard analysis studies have been done in the region based on different methods.
-Table 3 presents the PGA value for some of the major cities in northern Iran from different studies.
-
-\begin{table}[h]
-\centering
-\caption{Comparison of PGA, from different studies for selected cities in Northern Iran.
-(V2009:  \citet{vafaie2011}), G2008: \citet{Ghodrati2008}, G2010: \citet{Ghodrati2010},  Ah2013: \citet{Ahmadi2013}, G2003:  \citet{Ghodrati2003}, G2011: \citet{Ghodrati2011}, Ab2014: \citet{Abdollahzadeh2014} , Ra2012: \citet{Rahgozar2012}) }
-\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c |}
-
-\hline
-
-	\multirow{2}{*}{Cities} & \multirow{2}{*}{Lon} & \multirow{2}{*}{Lat} & \multicolumn{2}{|c|}{This study} & \multirow{2}{*}{2800} & Zare & \multicolumn{3}{|c|}{Other Refrences}    \\ 
-	\cline{4-5}  \cline{8-10}  &  &  & 10\% & 2\% &  &  2012 & 10\% & 2\% & ref \\ \hline
-	Orumyeh & 45.07 & 37.55 & 0.22 & 0.39 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Tabriz      & 46.3     & 38.06 & 0.27& 0.50 & 0.35 & 0.35-0.5 & 0.2- 0.65 & 0.3 to 0.9 & V2009 \\ \hline
-	Ardabil    & 48.28 & 38.25 & 0.36 & 0.63 & 0.3 & 0.35-0.5 &  &  &  \\ \hline
-	Manjil     & 49.40 & 36.74 & 0.39 & 0.71 & 0.35 & 0.65 $<$ & 0.25 & 0.4 & G2008 \\ \hline
-	Rasht     & 49.58 & 37.27 & 0.33 & 0.55 & 0.3 & 0.5-0.65 & 0.1 & 0.2 & G2008 \\ \hline 
-	Arak       & 49.68 & 34.09 & 0.24 & 0.48 & 0.25 & 0.35-0.5 & 0.16-0.36 & 0.25-0.55 & G2010 \\ \hline
-	Qazvin   & 50.00 & 36.26 & 0.27 & 0.50 & 0.35 & 0.35-0.5 & 0.31 & 0.42 & Ah2013 \\ \hline
-	 \multirow{2}{*}{Tehran}  & \multirow{2}{*}{51.42} & \multirow{2}{*}{35.69} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.59} & \multirow{2}{*}{0.35} & \multirow{2}{*}{0.35-0.5} & 0.37-0.415 &  &  G2011 \\
-	 \cline{8-10}	             &  &  &  &  &  &  & 0.27-0.46 & 0.35 & G2003\\ \hline
-	Gorgan & 54.43 & 36.83 & 0.39 & 0.69 & 0.3 & 0.35-0.5 & 0.34 & 0.3$<$ & Ab2014\\ \hline
-	Bojnurd & 57.33 & 37.47 & 0.38 & 0.68 & 0.3 & 0.35-0.5 &0.16-0.2  & 0.32-0.45  & Ra2012  \\ \hline
-	Mashhad & 59.6 & 36.29 & 0.16 & 0.28 & 0.3 & 0.35-0.5 &  &  & Ak2011 \\ \hline
-
-\end{tabular}
-
-\end{table}
-
-According to Table 3, the results of smoothed seismicity  are comparable with many other studies that considered faults and seismogenic zones.
-According to \citet{BHRC2014}, our results show that the smoothed seismicity approach gives reasonable regionalized results for 10\% probability of exceedance even when there is no need to introduce seismogenic zones.
-However, in regions for which the catalog is not complete or the study area is near the fault, probabilistic seismic hazard studies, which are implemented by seismic source, should be conducted.
-
-\section{Conclusion}
-
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
-
-\section{Acknowledgements}
-
- We express our appreciation to Art Frankel, PhD, of the U.S.
-Geological Survey, Washington, DC, who kindly provided the Smoothed Probabilistic Seismic Hazard Analysis (PSHA) package.
-We are also very thankful to Andrzej Kijko, PhD, Director of the University of Pretoria Natural Hazard Centre, Pretoria, Africa, who generously provided the software to compute seismicity parameters.
-We wish to thank Mehdi Zare, PhD, engineering seismologist and Associate Professor of Engineering Seismology at the International Institute of Earthquake Engineering and Seismology, Tehran, Iran, for  kindly providing the uniform historical seismic catalog.
-We also are very grateful to the International Institute of Earthquake Engineering and Seismology of Iran, Tehran, Iran, for providing the uniform instrumental earthquake catalog.
-
-\newpage
-
-%\section*{References}
-
-{
-\renewcommand{\bibname}{}
-\bibliographystyle{ascelike}
-\bibliography{PSHA}
-}
-
-\end{document}
+These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.

### 2016-06-16 attenuation.tex
started thinking about results section
baby steps towards cleaning material for use in resutls section

@@
 	r= \sqrt{ r^2_{\mathit{cl}} + h^2 }
-	\, .
+	\, ,
 \end{equation}
@@
 respectively. The value of $V_S$ is assumed to represent average surface rock sites.
+
+We should not here that even though \citet{Kalkan2004} derived the above attenuation relationship for distances $r$ up to 250 km, \citet{Zafarani2014} only used data up to 200 km in their evaluation of the various GMPEs available.
+Therefore, in consistence with \citet{Zafarani2014}, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.
 

### 2016-06-16 hazard.tex
touches on completeness
baby steps towards cleaning material for use in resutls section

@@
 \begin{equation}
-	\tilde{n_i} = \frac
+	\tilde{n}_i = \frac
 		{ \sum_{j} n_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
@@
 where $\tilde{n}_i$ is the smoothed, normalized number of events in cell $i$, $\Delta_{ij}$ is the distance between the $i$-th and $j$-th cells, and $c$ is the correlation distance.
-We use a correlation distance of 30 km.
-The summations in (\ref{eq:nnorm}) are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
+The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
 It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
 We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having complemented the earthquake catalog for events above this threshold.
+
+It is obvious from Eq.~\ref{eq:nnorm} that an important parameter in smoothing the seismicity is the correlation distance.
+Different values of $c$ have been used in past studies, ranging between 10 and 50 km.
+\citet{Frankel1995} and \citet{Boyd2008} assumed $c=50$~km, \citet{Barani2007} used $c=25$~km, and \citet{Foteva2006} used $c=10$ and 15 km.
+According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records.
+We use an intermediate value of $c=30$~km.
+This selection is consistent with epicentral uncertainty for previous hazard zoning maps for Iran \citep[see][]{Zare2012}.
 
@@
 
-It is clear from (\ref{eq:exceed}) that the hazard calculations depends also on the choice of an attenuation relationship to obtain predict the level of ground motion at a site ($u$) for any given earthquake.
+It is clear from Eq.~\ref{eq:exceed} that the hazard calculations depend also on the choice of an attenuation relationship to obtain predict the level of ground motion at a site ($u$) for any given earthquake.
 In the following two sections we describe how we obtained the $b$-values for the different seismic zones influencing the hazard in northern Iran and our choice of a suitable attenuation relationship (ground motion prediction equation).

### 2016-06-16 hazard_analysis_results.tex
baby steps towards cleaning material for use in resutls section

@@
 
-Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
+% Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
 \citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
@@
 
-Regarding the important parameters in determining the location of earhtquake (e.g.
+% Regarding the important parameters in determining the location of earhtquake (e.g.
 velocity model, station distribution, number and quality of seismic phases),\citet{Mirzaei1997} believes the uncertainties of the most reliable epicenters are probably at least 10 km.
@@
 Even though the uncertainties are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
+
 Regarding the study domain and the 0.1 grid size, the total number of source as grid points is 13561.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
+
+% Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
 

### 2016-06-16 parameters.tex
baby steps towards cleaning material for use in resutls section

@@
 \end{figure*}
-
-\section{Seismicity Parameters}
-
-Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3).
-This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.
-HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{Karimiparidari2013, Khodaverdian_2016_BSSA}.
-
-The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell.
-We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell.
-This means each cell has a different $a$-value and thus the result is variable throughout our region of interest.
-On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
-We compute $b$ and $M_{\max}$ using the information from the catalog, which we divide in three sub-catalogs for the prehistorical (before XXXX), historical (between XXXX and XXXX), and instrumental (after XXXX) seismicity.
-In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
-In a recent hazard analysis for whole Iran, \citet{} used variable values of $M_c$ for individual sub-catalogs.
-This is an additional level of complexity we may consider in the future.
-
-We obtain $b$ and $M_{\max}$ for two different models.
-In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
-That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the portions of the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
-In the second model we consider the whole study area as a uniform seismic zone.
-Admittedly, this assumption is unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
-Computing results for this uniform model is, nonetheless, useful for the analysis of results and comparisons with other studies.
-Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones and the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
 
@@
 \end{table}
+
+\section{Seismicity Parameters}
+
+Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3).
+This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.
+HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{Karimiparidari2013, Khodaverdian_2016_BSSA}.
+
+The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell.
+We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell.
+This means each cell has a different $a$-value and thus the result is variable throughout our region of interest.
+On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
+We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in four sub-catalogs: 2 incomplete catalogs for the prehistorical (before 1000) and historical (between 1000 and 1799) events, and two complete catalogs for pre-instrumental (between 1800 and 1899) and instrumental (between 1900 and 2015) events.
+In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
+In a recent hazard analysis for whole Iran, \citet{} used variable values of $M_c$ for individual sub-catalogs.
+This is an additional level of complexity we may consider in the future.
+
+We obtain $b$ and $M_{\max}$ for two different models.
+In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
+That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the portions of the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
+In the second model we consider the whole study area as a uniform seismic zone.
+Admittedly, this assumption is unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
+Computing results for this uniform model is, nonetheless, useful for the analysis of results and comparisons with other studies.
+Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones and the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
 

### 2016-06-16 completeness.tex
fixing table of completeness

@@
 
-\begin{table}%[t]
+\begin{table*}%[t]
     \centering
-    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
-    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
-        \cline{2-7}                                              \\[-1.6ex]
-                        & 3--4 & 4--5 & 5--6 & 6--7 & 
-                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
+    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.
+Year of completeness is provided for magnitude ranges between 3 and 7, with $\mathrm{\Delta}M = 1$.
+The completeness magnitude is provided for the sub-catalogs for three year intervals.}
+    \begin{tabular}{lccccrcccc}
+        \cline{2-10}                                                                                  \\[-1.6ex]
+                        & \multicolumn{5}{c}{Year for $M_w$ ranges} 
+                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} \\
+        \cline{2-6} \cline{8-10}                                                                      \\[-1.6ex]
+                        & 3--4 & 4--5 & 5--6 & 6--7 & \multicolumn{1}{c}{$>7$} 
+                                                            & & 1800--1899 & 1900--1999 & 2000--2015  \\[0.6ex]
         \hline                                                                                        \\[-1.6ex]
-        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
-        Alborz          & 2005 & 1961 & 1900 & 1664 &--401 & 4.4 \\
-        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9 & 4.5 \\
-        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439 & 4.4 \\
-        Central-East    & 2005 & 1961 & 1900 & 1837 &  762 & 4.5 \\
-        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
+        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042  & &     6.0    &     5.0    &     4.2     \\
+        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3.5     \\
+        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     4.0     \\
+        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     \\
+        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     4.0     \\
+        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.8    &     3.8     \\[0.5ex]
         \hline 
@@
     \label{tab:completeness} 
-\end{table}
+\end{table*}
 

### 2016-06-22 parameters.tex
params

@@
         \hline                                                                              \\[-1.6ex]
-        Azerbaijan      & 1.10 $\pm$ 0.03   & 7.93 $\pm$ 0.34   & 7.7                       \\
-        Alborz          & 1.03 $\pm$ 0.03   & 7.85 $\pm$ 0.66   & 7.8                       \\
-        Kopeh Dagh      & 0.89 $\pm$ 0.04   & 7.78 $\pm$ 0.31   & 7.6                       \\
-        Zagros          & 0.99 $\pm$ 0.02   & 7.47 $\pm$ 0.26   & 7.4                       \\
-        Central-East    & 0.95 $\pm$ 0.04   & 7.84 $\pm$ 0.34   & 7.6                       \\
-        Uniform Model   & 0.90 $\pm$ 0.02   & 7.87 $\pm$ 0.26   & 7.8                       \\[0.5ex]
+        Azerbaijan      & 1.16 $\pm$ 0.03   & 7.80 $\pm$ 0.38   & 7.7                       \\
+        Alborz          & 1.00 $\pm$ 0.03   & 7.80 $\pm$ 0.52   & 7.8                       \\
+        Kopeh Dagh      & 0.92 $\pm$ 0.03   & 7.73 $\pm$ 0.28   & 7.6                       \\
+        Zagros          & 1.02 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
+        Central-East    & 1.01 $\pm$ 0.03   & 7.79 $\pm$ 0.31   & 7.6                       \\
+        Uniform Model   & 0.95 $\pm$ 0.01   & 7.84 $\pm$ 0.27   & 7.8                       \\[0.5ex]
         \hline 

### 2016-06-24 abstract.tex
starting again on new completeness adjustments

@@
 % 
-This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield the best fit with data.
+This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data.
 We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh; and for completeness, we also consider the contribution of parts of other neighboring seismic zones that fall within our region of interest.
@@
 Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region.
-Seismic hazard curves are obtained for two models defined based on the assumption that damage occurs above earthquake magnitude thresholds of $M_w$ greater than 4.5 and 5.0, depending on the type of construction.
-We
-also obtain results for a combined scenario using these two models.
+Seismic hazard curves are obtained for different models defined based on the assumption that damage occurs above certain earthquake magnitude thresholds, depending on the type of construction.
+We also obtain results for a combined scenario using different models.
 The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We compare our results to equivalent estimations available in the literature at selected locations and offer our perspective on the differences observed.
+We analyze our results in light of equivalent estimations available in the literature and offer our perspective on the differences observed.
 In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.

### 2016-06-24 completeness.tex
starting again on new completeness adjustments

@@
 This characteristic is measured in terms of the year of completeness and the completeness magnitude, which are used as parameters in the seismic analysis process.
-In simple terms, the year of completeness is the point in time at which catalog data exhibits a steady rate of event occurrence or record accumulation.
-This point is typically identified for different magnitude ranges.
+In simple terms, the year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation.
+This point is typically identified for different magnitude ranges independently.
 A simple approach used by \citet{Frankel1995} and others is to select the year at which a plot of the cumulative number of events with respect to time becomes (or starts to resemble) a straight line.
 
-On the other hand, the completeness magnitude---denoted as $M_c$---is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
-While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the catalog.
+On the other hand, the completeness magnitude ($M_c$) is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
+While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the given catalog.
 A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
@@
 \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
+
+An alternative approach is the goodness-of-fit test method introduced by \citet{Wiemer2000}.........
 
@@
 The completeness magnitude is provided for the sub-catalogs for three year intervals.}
-    \begin{tabular}{lccccrcccc}
-        \cline{2-10}                                                                                  \\[-1.6ex]
+    \begin{tabular}{lccccrcccccc}
+        \cline{2-12}                                                                                  			\\[-1.6ex]
                         & \multicolumn{5}{c}{Year for $M_w$ ranges} 
-                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} \\
+                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} & &$M_c$\\
         \cline{2-6} \cline{8-10}                                                                      			\\[-1.6ex]
                         & 3--4 & 4--5 & 5--6 & 6--7 & \multicolumn{1}{c}{$>7$} 
-                                                            & & 1800--1899 & 1900--1999 & 2000--2015  \\[0.6ex]
+                                                            & & 1800--1899 & 1900--1999 & 2000--2015  & & Whole	\\[0.6ex]
         \hline                                                                                        			\\[-1.6ex]
-        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042  & &     6.0    &     5.0    &     4.2     \\
-        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3.5     \\
-        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     4.0     \\
-        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     \\
-        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     4.0     \\
-        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.8    &     3.8     \\[0.5ex]
+        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042  & &     6.0    &     5.0    &     4.2     & &  4.2 	\\
+        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3.5     & &  4.3 	\\
+        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     4.0     & &  4.9 	\\
+        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     & &  4.8 	\\
+        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     4.0     & &  4.8 	\\
+        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.8    &     3.8     & &  4.8 	\\[0.5ex]
         \hline 

### 2016-06-24 composition.tex
starting again on new completeness adjustments

--- 2016-06-13 composition.tex
@@
 Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}.
-In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with all $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
-The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.
+In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
+The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}, which includes the spatial distribution within the region of interest for both historical and instrumental events; and in Fig.~\ref{fig:scatter}, which presents the distribution of events in time and magnitude for each of the seismic zones, as well as for the complete region of interest (hereafter referred as the uniform model).
+
+\begin{figure*} [t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
+	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
+	\label{fig:scatter}
+\end{figure*}

### 2016-06-24 introduction.tex
starting again on new completeness adjustments

@@
 
-This article presents a new seismic hazard assessment for the northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to be the most reliable attenuation relationship to predict peak ground response in the region.
+This article presents a new seismic hazard assessment for the northern portion of the Iranian plateau, using a smoothed seismicity approach in combination with an updated seismic catalog and a ground motion prediction equation recently evaluated and found to fit well with observations of peak ground response in the region.
 
@@
 
-According to this tectonic setting and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, and up to twenty to twenty-three seismotectonic provinces in the more elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
+According to this tectonic setting and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, and up to twenty to twenty-three seismotectonic provinces in the most elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
 Contemporary, well-accepted models divide Iran into five major tectonic regions: Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran \citep[e.g.,][]{Mirzaei1998}.
@@
 The most recent of these studies \citep{Khodaverdian_2016_BSSA} focuses in the estimation of spatially-variable seismic parameters for the whole country using a similar approach to the one we used here.
-We, however, focus our attention in the northern three seismic zones of the country assuming regionally-based seismic parameters.
+We, however, focus our attention in the northern three seismic zones of the country assuming regionally-based and smoothed seismic parameters.
 Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
@@
 However, other indicators suggest persistent high levels of seismic risk.
-Therefore, more complete and accurate assessments of seismic hazard---incorporating the latest available data and alternative methods---are still deemed necessary.
+Therefore, more complete and accurate assessments of seismic hazard---incorporating the latest available data and alternative methods---are still necessary.
 
@@
 Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions, considering different magnitude thresholds.
-We compare our results to equivalent estimations (hazard curves) available in the literature for selected locations and conclude with a discussion in light of other previous hazard studies.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions using different magnitude thresholds.
+We analyze our results in light of equivalent estimations available in the literature and summarize relevant conclusions.
 

### 2016-07-01 completeness.tex
refurbished completeness and parameters sections with new figure 6

@@
 An important aspect of seismic catalogs is their completeness.
-This characteristic is measured in terms of the year of completeness and the completeness magnitude, which are used as parameters in the seismic analysis process.
-In simple terms, the year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation.
-This point is typically identified for different magnitude ranges independently.
+This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process.
+The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+
+The start-year of completeness is usually identified by inspection.
 A simple approach used by \citet{Frankel1995} and others is to select the year at which a plot of the cumulative number of events with respect to time becomes (or starts to resemble) a straight line.
-
-On the other hand, the completeness magnitude ($M_c$) is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period.
-While the year of completeness can be determined by inspection of the data, the completeness magnitude often requires a numerical analysis of the given catalog.
-A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
-This method is known as the maximum curvature (MAXC) technique.
-It is widely used and has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
-\citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
-
-An alternative approach is the goodness-of-fit test method introduced by \citet{Wiemer2000}.........
-
-One of the difficulties in determining completeness is the availability of data for a period of time long enough for all magnitude ranges, so that selection of completeness parameters is reliable.
-In this study, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7 by inspection, following the approach used by \citet{Frankel1995}.
-This is illustrated in Fig.~\ref{fig:completeness}, where we show the normalized cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our choice of the completeness year thresholds in each case.
+This is done for different magnitude ranges.
+Following this approach, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7.
+Our choices are illustrated in Fig.~\ref{fig:completeness}, where we show the normalized cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our selection of the year of completeness in each case.
+The values shown in this figure and those corresponding to the uniform model of the entire region of interest are summarized in Table \ref{tab:completeness}.
 For events $M_w>7$, in which case there are no sufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
 
-Admittedly, the choice of the threshold years is highly subjective.
+Determining the completeness magnitude $M_c$, on the other hand, is often determined using simple numerical analysis in combination with data inspection.
+Two common approaches are maximum curvature and the goodness-of-fit test methods.
+The maximum curvature method, or MAXC for simplicity, is widely used because as it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+\citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
+We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
+
+We defined these year intervals based on the data magnitude-time distribution (see Fig.~\ref{fig:scatter}) and the idea of distinguishing between historical, early-instrumental, and modern-instrumental catalogs.
+Having augmented the original catalog with $M>3$ earthquakes beginning in 2000 also influenced our choice of the intervals because at this point the uniformity of the catalog is altered.
+No value of $M_c$ was computed for pre-historical (before 1800) data because of scarcity of data.
+Last, we also computed $M_c$ values for the complete regional catalogs, but in this case, in order to maintain uniformity throughout time, we only considered $M>4$ events.
+Fig.~\ref{fig:mc} illustrates the selection of $M_c$ for the case of the main three northern Iran seismic regions, and Table \ref{tab:completeness} presents the final selection of $M_c$ values for these and the other regions, including the uniform northern Iran model for the complete region of interest.
+
+% A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
+
+% One of the difficulties in determining completeness is the availability of data for a period of time long enough for all magnitude ranges, so that selection of completeness parameters is reliable.
+
+The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), and the $M_c$ values for the whole regional catalogs and the start-years of completeness are used later for computing the hazard.
+Admittedly, the choice of the start-years is highly subjective.
 We should note then, that in the process of choosing the points indicated in the plots shown in Fig.~\ref{fig:completeness}, we considered additional contributing information such as the history of instrumentation.
-It is well known, for instance, that the number of recorded earthquakes increased considerably after the first deployment of seismic instruments in the early 1900s, and later with the establishment of the Worldwide Standardized Seismograph Network in 1961.
-We also compared our choices with the year thresholds reported by \citet{Zare2014}, which we found to be consistently earlier than our preferred years of completeness.
-In the end, we proceeded with our selection, which leads to a more conservative estimation of hazard.
+It is well known that the number of recorded earthquakes increased considerably after the first deployment of seismic instruments in the early 1900s, and later with the establishment of the Worldwide Standardized Seismograph Network in 1961.
+We compared our choices with the year thresholds reported by \citet{Zare2014}, which we found to be consistently earlier than our preferred years of completeness.
+In the end, our selection should lead to a slightly more conservative estimations of hazard.
+For the case of $M_c$, we compared our results with the values reported by \citet{Karimiparidari2013} and \citet{Khodaverdian_2016_BSSA} and found them to be in general good agreement, despite differences in the spatial definition of the seismic zones.
 
-For the case of the completeness magnitude $M_c$, we adopted the values reported by \citet{Karimiparidari2013}.
-Our choice the $M_c$ values by \citet{Karimiparidari2013} over those of \citet{Zare2014} is based on the fact that the former distinguishes Azerbaijan and Alborz as individual seismic zones---as we do---as opposed to the approach followed by the latter, in which these two are a single, larger seismic zone.
-Both the chosen years of completeness and the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest are summarized in Table \ref{tab:completeness}.
+% Our choice the $M_c$ values by \citet{Karimiparidari2013} over those of \citet{Zare2014} is based on the fact that the former distinguishes Azerbaijan and Alborz as individual seismic zones---as we do---as opposed to the approach followed by the latter, in which these two are a single, larger seismic zone.
+Both the chosen years of completeness and the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest are ....
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-06.pdf} 
+    \caption{Pending.}
+    \label{fig:completeness}
+\end{figure*}
 

### 2016-07-01 parameters.tex
refurbished completeness and parameters sections with new figure 6

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-06} 
+    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
     \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
@@
 \section{Seismicity Parameters}
+\label{sec:params}
 
@@
 On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
-We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in four sub-catalogs: 2 incomplete catalogs for the prehistorical (before 1000) and historical (between 1000 and 1799) events, and two complete catalogs for pre-instrumental (between 1800 and 1899) and instrumental (between 1900 and 2015) events.
+We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in four sub-catalogs: 2 incomplete catalogs for the prehistorical (before 1000) and historical (between 1000 and 1799) event periods, and two complete catalogs for  early instrumental (between 1800 and 1899) and instrumental (between 1900 and 2015) event periods.
 In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
-In a recent hazard analysis for whole Iran, \citet{} used variable values of $M_c$ for individual sub-catalogs.
-This is an additional level of complexity we may consider in the future.
 

### 2016-07-01 completeness.tex
updates
Preparing the ground to write the results section

@@
 
-% A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
-
-% One of the difficulties in determining completeness is the availability of data for a period of time long enough for all magnitude ranges, so that selection of completeness parameters is reliable.
-
 The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), and the $M_c$ values for the whole regional catalogs and the start-years of completeness are used later for computing the hazard.
@@
 
-% Our choice the $M_c$ values by \citet{Karimiparidari2013} over those of \citet{Zare2014} is based on the fact that the former distinguishes Azerbaijan and Alborz as individual seismic zones---as we do---as opposed to the approach followed by the latter, in which these two are a single, larger seismic zone.
-Both the chosen years of completeness and the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest are ....
-
 \begin{figure*}[t]
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-06.pdf} 
-    \caption{Pending.}
-    \label{fig:completeness}
+    \caption{Selection of completeness magnitude ($M_c$) values for the three main seismic regions in northern Iran.
+The blue squares indicate the computed goodness-of-fit test values and the green circles indicate the cumulative number of events.
+Both are shown as functions of the earthquake magnitude.
+The former is plotted in linear scale (left axes) and the latter is plotted in logarithmic scale (right axes).
+The horizontal dashed lines indicate desired thresholds for the goodness-of-fit values at 80 and 90 percent.
+The vertical red lines show indicate the chosen $M_c$ values for each zone and catalog year interval.}
+    \label{fig:mc}
 \end{figure*}
@@
 
+% A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
+
+% One of the difficulties in determining completeness is the availability of data for a period of time long enough for all magnitude ranges, so that selection of completeness parameters is reliable.
+
+% Our choice the $M_c$ values by \citet{Karimiparidari2013} over those of \citet{Zare2014} is based on the fact that the former distinguishes Azerbaijan and Alborz as individual seismic zones---as we do---as opposed to the approach followed by the latter, in which these two are a single, larger seismic zone.
+Both the chosen years of completeness and the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest are ....
+
 % For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.

### 2016-07-01 results.tex
Preparing the ground to write the results section

@@
-\section{Results}
+\section{Results and Analysis}
 
@@
 These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-08.pdf} 
+    \caption{Pending.}
+    \label{fig:pga}
+\end{figure*}
+
+\begin{figure}%[t]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/pdf/figure-09.pdf} 
+    \caption{Pending.}
+    \label{fig:std}
+\end{figure}
+
+Regarding the study domain and the 0.1 grid size, the total number of source as grid points is 13561.
+
+% \subsection{Hazard Curve}
+
+We calculated the probability of exceedance of the ground motion from different ground motion levels, separately for each of 5 regions.
+We add the probability of all regions in order to have the effect of seismicity from all tectonic seismic regions.
+The results are presented as annual rate of exceedance.
+Fig.~\ref{fig:hazardcurve} represents the hazard curve of different model for some of important northern cities in Iran.
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.4]{figures/pdf/HazardCurve.pdf} 
+\caption{Seismic Hazard Curve of Northern Cities in Iran}
+\label{fig:hazardcurve}
+\end{figure*}
+
+% \subsection{Peak Ground Acceleration}
+
+We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance.
+Fig.~\ref{fig:pga_10_mean} and Fig.~\ref{fig:pga_2_mean} show the results for 10\% and 2\% probability of exceedance in 50 years, respectively.
+These results are according to the mean value of the attenuation relationship.
+
+Fig.~\ref{fig:pga_10_mean_uniform} and Fig.~\ref{fig:pga_2_mean_uniform} show the results for 10\% and 2\% probability of exceedance in 50 years for the uniform model, respectively.
+
+% -------
+
+As discussed before the border of the study region
+
+Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
+In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}.
+Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.
+
+We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude.
+We assume magnitude increment as $\Delta_M = 0.1$.
+In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
+
+Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
+\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
+\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
+\citet{Foteva2006} used 10 and 15 km in a different model.
+Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
+In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
+Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
+Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
+Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
+
+Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
+The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.

### 2016-07-01 figures/gmt/plot-smoothed-pga.sh

@@ -1,0 +1,41 @@
+
+FILENAME=$1
+CPTFILE=tmp.cpt
+OUTFILE=tmp.ps
+GRDFILE=tmp.grd
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+gmt makecpt -CcbcYlOrRd -Do -T0/1.0/0.05 > ${CPTFILE}
+
+gmt surface ${FILENAME}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE}
+
+gmt grdimage ${GRDFILE} -R -JM5i -C${CPTFILE} -K -P -V > ${OUTFILE}
+gmt grdcontour ${GRDFILE} -J -R -C0.1 -A0.1+f6p -W0.5p -O -K -V >> ${OUTFILE}
+gmt psscale -C${CPTFILE} -D5.3i/1i/1.8i/0.15i -E -B0.1 -O -V >>${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILENAME}.pdf -Tf -Au0.5c 
+
+gmt grdimage ${GRDFILE} -R43.5/61.5/34/40 -JM5i -C${CPTFILE} -P -V > ${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILENAME}.png -Tg -Au
+
+rm tmp.cpt
+rm tmp.grd
+rm ${OUTFILE}
+
+# Opening PDF
+# ------------------------------------------------------------------------------
+
+open -a Adobe\ Acrobat\ Pro.app ${FILENAME}.pdf

### 2016-07-01 figures/gmt/plot-smoothed-pga.sh
request for contours in progress...

@@ -22,7 +22,7 @@ gmt makecpt -CcbcYlOrRd -Do -T0/1.0/0.05 > ${CPTFILE}
 gmt surface ${FILENAME}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE}
 
 gmt grdimage ${GRDFILE} -R -JM5i -C${CPTFILE} -K -P -V > ${OUTFILE}
-gmt grdcontour ${GRDFILE} -J -R -C0.1 -A0.1+f6p -W0.5p -O -K -V >> ${OUTFILE}
+gmt grdcontour ${GRDFILE} -J -R -C0.2 -A0.2+f6p -W0.5p -O -K -V >> ${OUTFILE}
 gmt psscale -C${CPTFILE} -D5.3i/1i/1.8i/0.15i -E -B0.1 -O -V >>${OUTFILE}
 
 gmt ps2raster ${OUTFILE} -F${FILENAME}.pdf -Tf -Au0.5c 

### 2016-07-02 figures/gmt/plot-smoothed-diff.sh
improved figures for results

@@ -1,0 +1,47 @@
+
+FILEONE=$1
+FILETWO=uniform_$1
+CPTFILE=tmp.cpt
+OUTFILE=tmp.ps
+GRDFILE1=tmp1.grd
+GRDFILE2=tmp2.grd
+GRDFILE=tmp.grd
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+gmt makecpt -CcbcPRGn -Do -T-0.6/0.6/0.05 > ${CPTFILE}
+
+gmt surface ${FILEONE}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE1}
+gmt surface ${FILETWO}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE2}
+
+gmt grdmath ${GRDFILE2} ${GRDFILE1} SUB = ${GRDFILE}
+
+gmt grdimage ${GRDFILE} -R -JM5i -C${CPTFILE} -K -P -V > ${OUTFILE}
+gmt grdcontour ${GRDFILE} -J -R -A0.2+f6p -W0.5p -O -K -V >> ${OUTFILE}
+gmt psscale -C${CPTFILE} -D5.3i/1i/1.8i/0.15i -E -B0.1 -O -V >>${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILEONE}-diff.pdf -Tf -Au0.5c 
+
+gmt grdimage ${GRDFILE} -R43.5/61.5/34/40 -JM5i -C${CPTFILE} -P -V > ${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILEONE}-diff.png -Tg -Au
+
[…]

### 2016-07-04 results.tex
improved figures for results
working on results section... three figures done, a few more to go

--- 2016-06-15 results.tex
@@
-\section{Results}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-08.pdf} 
+    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability of exceeding earthquake magnitudes $M_w$ 5.5 and 6.5 for (a) the five seismic regions R model and (b) the uniform seismic region U model.}
+    \label{fig:pga}
+\end{figure*}
 
-The PGA hazard maps have been computed for a 10\% and 2\% exceedance probability in 50 years, corresponding to a return period of 475 and 2475 years, from gridded values of historical and instrumental seismic activity.
-These levels of exceedance are a standard practice in seismic designs \citep{BHRC2014}.
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-09.pdf} 
+    \caption{Difference between the mean PGA values obtained for the uniform U model results and the corresponding R models for 2 (left) and 10 (right) percent probabilities of exceeding magnitudes $M_w$ 5.5 (top) and 6.5 (bottom).}
+    \label{fig:pgadiff}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf} 
+    \caption{plus minus std for M6.5.}
+    \label{fig:pgastd}
+\end{figure*}
+
+\section{Results and Analysis}
+
+Using the data, parameters, and procedures described above, we considered different hazard models based on whether we use the five distinct seismic hazard regions or the whole region of interest as a uniform seismic hazard region.
+We call these the R and U models, respectively.
+We also considered two threshold levels of ground motion for events exceeding magnitudes $M_w$ 5.5 and 6.5.
+We refer to these models with the suffixes 5.5 and 6.5, respectively.
+Each of these are considered under two probabilities of exceedance, at 2 and 10 percent in 50 years, for which we use the prefixes 2 and 10, respectively.
+As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5.5 in 50 years under the five seismic regions model as the 2R5.5 model results.
+
+In the R models, we computed the probability of exceedance of the ground motion separately for each region and then add them together in order to have the contribution of all regions for any given grid point within the region of interest.
+The results are obtained in the form of annual rate of exceedance.
+Expected PGA values are therefore a slice or snapshot of the actual hazard curves of each point for any chosen magnitude.
+
+We extract expected levels of ground motion for the two magnitude models, 5.5 and 6.5, based on the assumption that buildings of different construction systems may be vulnerable to different magnitude earthquakes.
+It is natural to anticipate that modern constructions in urban areas in Iran follow current building regulations and are thus well-designed to withstand moderate magnitude earthquakes $M_w$ 4.5--6.5, and to undergo moderate non-life threatening damage during $M_w > 6.5$ events.
+Unconventional constructions in poor city outskirts, rural housing and historical buildings may, however, be vulnerable to $M_w \leq 5.5$, and thus becomes relevant to entertain lower magnitude exceedance levels.
+In turn, the 2 and 10 percent probability of exceedance in a 50-years span are considered a standard practice in seismic design \citep[e.g.,][]{BHRC2014}.
+
+Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship as a measured of gravity (g) throughout the region of interest for the different model combinations.
+As can be expected, the highest levels of ground motion are associated with the 2R5.5 and 2U5.5 models, and the lowest with the 10R6.5 and 10U6.5 models.
+In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region along the border with Turkmenistan, followed by ground motions in the north-central region west from Tehran and Karaj, and in the vicinity of the Piranshahr fault between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}b for reference).
+The Azerbaijan seismic zone does not present equally high levels of expected ground motion.
+In the U models shown in Fig.~\ref{fig:pga}b, on the other hand, the highest levels of expected ground motion are observed precisely in the area corresponding to the Azerbaijan seismic region, especially in the vicinity of the North Tabriz Fault system (see Fig.~\ref{fig:selected} for reference).
+
+In general, the U models exhibit higher levels of expected ground motions when compared to their corresponding R models.
+This is illustrated in Fig.~\ref{fig:pgadiff}, which shows the differences between both set of models, U--R (U minus R).
+In this figure, positive values indicate that the U models have larger mean PGA values than the R models.
+As it can be seen, this is true practically throughout the whole region at very low levels, and in particular in the north-central region at a moderate level of up to 0.2 g and most predominantly in the north-western region of Azerbaijan at levels of about 0.2 to 0.5 g.
+
+Overall, these results are consistent with the seismicity observed in Fig.~\ref{fig:catalog}.
+The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with concentration of strong earthquakes in the Alborz and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
+This may be the cause of
+
+These, of course, are only mean expected levels of ground motion.
+A more complete picture is captured when considering statistical deviations.
+Fig.~\ref{fig:pgastd} shows again the mean PGA for the models 2R6.5 and 10R6.5, but this time along with the marginal values of plus and minus one standard deviation.
+Here, the standard deviation is carried forward in the calculation from the attenuation relationship and thus affects every grid point differently depending on the added contributions from each region.
+The highest expected PGA values are observed in the 2R6.5+STD model with accelerations of higher than 1 g in the Kopeh Dagh region and west of Tehran, and 0.8 g south of the North Tabriz Fault system and in the Zagros region along.
+
+~\\
+* * *
+\\
+
+% \subsection{Hazard Curve}
+
+% We calculated the probability of exceedance of the ground motion from different ground motion levels, separately for each of 5 regions. 
+% We add the probability of all regions in order to have the effect of seismicity from all tectonic seismic regions. 
+% The results are presented as annual rate of exceedance.
+
+Fig.~\ref{fig:hazardcurve} represents the hazard curve of different model for some of important northern cities in Iran.
+
+\begin{figure*} [!ht]
+\centering
+\includegraphics[scale=0.4]{figures/pdf/HazardCurve.pdf} 
+\caption{Seismic Hazard Curve of Northern Cities in Iran}
+\label{fig:hazardcurve}
+\end{figure*}
+
+% \subsection{Peak Ground Acceleration}
+
+We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance.
+
+% Fig.~\ref{fig:pga_10_mean} and Fig.~\ref{fig:pga_2_mean} show the results for 10\% and 2\% probability of exceedance in 50 years, respectively.
+% These results are according to the mean value of the attenuation relationship.
+% Fig.~\ref{fig:pga_10_mean_uniform} and Fig.~\ref{fig:pga_2_mean_uniform} show the results for 10\% and 2\% probability of exceedance in 50 years for the uniform model, respectively.
+
+% -------
+
+% Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
+% In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}. 
+% Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.
+
+% We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude. 
+% We assume magnitude increment as $\Delta_M = 0.1$.
+
+% In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
+
+% Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
+\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
+\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
+\citet{Foteva2006} used 10 and 15 km in a different model.
+Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
+In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
+Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
+
+% Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
+Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
+
+% Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
+The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
+
+% ==================
+% OLD STUFF NOT USED
+% ==================
+
+% Regarding the study domain and the 0.1 grid size, the total number of source as grid points is 13561.
+
+% corresponding to return periods of 475 and 2475 years.

### 2016-07-05 results.tex
preparing figure 11

@@
 
-Using the data, parameters, and procedures described above, we considered different hazard models based on whether we use the five distinct seismic hazard regions or the whole region of interest as a uniform seismic hazard region.
+Using the data, parameters, and procedures described above, we considered different hazard models based on whether we use the five distinct seismic hazard regions or the whole area of interest as a uniform seismic hazard region.
 We call these the R and U models, respectively.
@@
 Each of these are considered under two probabilities of exceedance, at 2 and 10 percent in 50 years, for which we use the prefixes 2 and 10, respectively.
-As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5.5 in 50 years under the five seismic regions model as the 2R5.5 model results.
+These probabilities correspond to return periods of 475 and 2475 years.
+As an example of the chosen nomenclature, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5.5 in 50 years under the five seismic regions model as the 2R5.5 model results.
 
-In the R models, we computed the probability of exceedance of the ground motion separately for each region and then add them together in order to have the contribution of all regions for any given grid point within the region of interest.
+In the distinct regions R models, we computed the probability of exceedance of the ground motion separately for each region and then add them together in order to have the contribution of all regions for any given grid point within the region of interest.
 The results are obtained in the form of annual rate of exceedance.
-Expected PGA values are therefore a slice or snapshot of the actual hazard curves of each point for any chosen magnitude.
+Expected PGA values are therefore a slice of the actual hazard curves cut across all grid points for a chosen magnitude.
 
-We extract expected levels of ground motion for the two magnitude models, 5.5 and 6.5, based on the assumption that buildings of different construction systems may be vulnerable to different magnitude earthquakes.
+We extract expected levels of ground motion for magnitudes 5.5 and 6.5, based on the assumption that buildings of different construction systems may be vulnerable to different magnitude earthquakes.
 It is natural to anticipate that modern constructions in urban areas in Iran follow current building regulations and are thus well-designed to withstand moderate magnitude earthquakes $M_w$ 4.5--6.5, and to undergo moderate non-life threatening damage during $M_w > 6.5$ events.
@@
 Here, the standard deviation is carried forward in the calculation from the attenuation relationship and thus affects every grid point differently depending on the added contributions from each region.
+
 The highest expected PGA values are observed in the 2R6.5+STD model with accelerations of higher than 1 g in the Kopeh Dagh region and west of Tehran, and 0.8 g south of the North Tabriz Fault system and in the Zagros region along.
+These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects, such as inelastic deformation of near-surface geotechnical layers which may often contribute to mitigate peak accelerations.
+
+An additional consideration to make here is the fact that one cannot claim any of the models to be uniquely correct.
+They all carry a certain level of epistemic uncertainty which make them equally accurate and inaccurate at the same time.
+An means to reduce the overall uncertainty intrinsically associated with each model is to use combinations of different models.
+We consider two types of combinations here to aid our analysis.
+First, we combine results at both magnitude thresholds following the hypothesis that in areas were mixed reinforced and unreinforced buildings are present, the hazard and associated expected ground motions will be an average of both models, i.e.
+$frac{1}{2}(5.5+6.5)$.
+Second, we consider a combination of the five-regions model and the uniform model, i.e.
+$frac{1}{2}(\mathrm{U}+\mathrm{R})$, based on the hypothesis that both models carry forward valid information about the local and regional seismicity.
+
+Fig.~\ref{fig:}a shows
 

### 2016-07-05 figures/gmt/plot-smoothed-avg.sh

@@ -1,0 +1,47 @@
+
+FILEONE=$1
+FILETWO=$2
+CPTFILE=tmp.cpt
+OUTFILE=tmp.ps
+GRDFILE1=tmp1.grd
+GRDFILE2=tmp2.grd
+GRDFILE=tmp.grd
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+gmt makecpt -CcbcRdPu -Do -T0/1/0.05 > ${CPTFILE}
+
+gmt surface ${FILEONE}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE1}
+gmt surface ${FILETWO}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE2}
+
+gmt grdmath ${GRDFILE2} ${GRDFILE1} ADD 0.5 MUL = ${GRDFILE}
+
+gmt grdimage ${GRDFILE} -R -JM5i -C${CPTFILE} -K -P -V > ${OUTFILE}
+gmt grdcontour ${GRDFILE} -J -R -A0.2+f6p -W0.5p -O -K -V >> ${OUTFILE}
+gmt psscale -C${CPTFILE} -D5.3i/1i/1.8i/0.15i -E -B0.1 -O -V >>${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILEONE}-${FILETWO}.pdf -Tf -Au0.5c 
+
+gmt grdimage ${GRDFILE} -R43.5/61.5/34/40 -JM5i -C${CPTFILE} -P -V > ${OUTFILE}
+
[…]

### 2016-07-05 figures/gmt/plot-smoothed-avg-all.sh
figure 11 ready

@@ -1,10 +1,7 @@
 
-FILEONE=$1
-FILETWO=$2
+KEY=$1
 CPTFILE=tmp.cpt
 OUTFILE=tmp.ps
-GRDFILE1=tmp1.grd
-GRDFILE2=tmp2.grd
 GRDFILE=tmp.grd
 
 gmt gmtset FONT                     8
@@ -20,23 +17,24 @@ gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
 gmt gmtset MAP_LABEL_OFFSET         8p
 gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
 
-# gmt makecpt -CcbcRdPu -Do -T0/1/0.05 > ${CPTFILE}
-gmt makecpt -CcbcGreens -Do -T0/1/0.05 > ${CPTFILE}
+gmt makecpt -Ces_skywalker_18 -Do -T0/1/0.05 > ${CPTFILE}
 
-gmt surface ${FILEONE}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE1}
-gmt surface ${FILETWO}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE2}
+gmt surface         pga_${KEY}_50_mean_m_55.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -Gtmp1.grd
+gmt surface         pga_${KEY}_50_mean_m_65.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -Gtmp2.grd
+gmt surface uniform_pga_${KEY}_50_mean_m_55.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -Gtmp3.grd
+gmt surface uniform_pga_${KEY}_50_mean_m_65.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -Gtmp4.grd
 
-gmt grdmath ${GRDFILE2} ${GRDFILE1} ADD 0.5 MUL = ${GRDFILE}
+gmt grdmath tmp1.grd tmp2.grd ADD tmp3.grd ADD tmp4.grd ADD 0.25 MUL = ${GRDFILE}
 
 gmt grdimage ${GRDFILE} -R -JM5i -C${CPTFILE} -K -P -V > ${OUTFILE}
 gmt grdcontour ${GRDFILE} -J -R -A0.2+f6p -W0.5p -O -K -V >> ${OUTFILE}
[…]

### 2016-07-05 results.tex
update to results section

@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf} 
-    \caption{plus minus std for M6.5.}
+    \caption{Expected PGA values throughout the region of interest for 2 and 10 percent probability of exceeding an earthquake magnitude $M_w$ 6.5 using the hazard calculations from the five-region R model and the attenuation relationship plus and minus one standard deviation.}
     \label{fig:pgastd}
+\end{figure*}
+
+\begin{figure*}[th!]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-11.pdf} 
+    \caption{Expected PGA values for different combination models.
+(a) Combination of R models for magnitudes $M_w$ 5.5 and 6.5.
+(b) Combination of U models for magnitudes $M_w$ 5.5 and 6.5.
+(c) Combination of R and U models for separate magnitudes $M_w$ 5.5 and 6.5.
+(d) Combination of R and U models, and magnitudes $M_w$ 5.5 and 6.5.}
+    \label{fig:pgaavgs}
 \end{figure*}
@@
 The results are obtained in the form of annual rate of exceedance.
-Expected PGA values are therefore a slice of the actual hazard curves cut across all grid points for a chosen magnitude.
+Expected PGA values are therefore a ``slice'' of the actual hazard curves cut across all grid points for a chosen magnitude.
 
@@
 
-An additional consideration to make here is the fact that one cannot claim any of the models to be uniquely correct.
-They all carry a certain level of epistemic uncertainty which make them equally accurate and inaccurate at the same time.
-An means to reduce the overall uncertainty intrinsically associated with each model is to use combinations of different models.
-We consider two types of combinations here to aid our analysis.
-First, we combine results at both magnitude thresholds following the hypothesis that in areas were mixed reinforced and unreinforced buildings are present, the hazard and associated expected ground motions will be an average of both models, i.e.
-$frac{1}{2}(5.5+6.5)$.
-Second, we consider a combination of the five-regions model and the uniform model, i.e.
-$frac{1}{2}(\mathrm{U}+\mathrm{R})$, based on the hypothesis that both models carry forward valid information about the local and regional seismicity.
+An additional consideration to make here is the fact that any one model cannot be uniquely correct.
+They all carry a certain level of epistemic uncertainty which makes them equally accurate and inaccurate at the same time.
+A means to address the uncertainty intrinsic to each model is to use combinations of different models.
+We consider different types of combinations to aid our analysis.
+First, we combine results at in the R and U models independently by averaging the two magnitude results.
+These combinations follow the hypothesis that in areas where mixed reinforced and unreinforced buildings are present, the hazard and associated expected ground motions will be an average of both magnitude thresholds.
+Fig.~\ref{fig:pgaavgs}a shows the result of this combination for the R models and Fig.~\ref{fig:pgaavgs}b shows the result for the combined U models.
+Second, we consider the combination of the two underlying hazard models R and U for the separate magnitude levels.
+These results are shown in Fig.~\ref{fig:pgaavgs}c.
+Last, we consider an overall combination of both hazard models and magnitude thresholds, as shown in Fig.~\ref{fig:pgaavgs}d.
+At all times we keep separate the probabilities of exceedance.
 
-Fig.~\ref{fig:}a shows
+These figures show interest results.
+Combining the two magnitude levels in either the R or U models (Figs.~\ref{fig:pgaavgs}a and \ref{fig:pgaavgs}b) does not have a significant impact other than finding a middle point in between the two ``slices'' taken at the corresponding hazard curves of all the individual grid points.
+For that matter, defining a threshold at $M_w$ 6.0 is almost equivalent and becomes only a matter of choice.
+Combining both R and U models, and the two magnitude results (Fig.~\ref{fig:pgaavgs}d), on the other hand, oversmooths the results and eliminates some of the detail desirable in this kind of analysis.
+It is therefore the combination of the R and U models, but at the separate magnitude thresholds (Fig.~\ref{fig:pgaavgs}c) the one that offers the most plausible scenario.
+These combinations are the ones that best match the visual inspection of the seismicity of the region (shown in Fig.~\ref{fig:catalog}) and follow the major faults (shown in Fig.~\ref{fig:selected}a), while also bringing into the picture the regional background seismicity of moderate magnitude earthquakes.
+That is, in the combinations shown in Fig.~\ref{fig:pgaavgs}c one can clearly observe the contribution of the North Tabriz Fault system in the Azerbaijan region, the contribution of the Piranshahr and Morvarid faults in the Zagros region, and that of the different faults in the Alborz and Kopeh Dagh regions.
+
+We also note that the overall distribution of PGA values shown in Fig.~\ref{fig:pgaavgs}c are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}.
+These estimates also agree, on average, with other previous studies.
+For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, and 0.4 g around the city of Urmia, where we find equivalent values to be between 0.4 and 0.6 g, and about 0.35 g, respectively.
+The results from \citet{Vafaie2011} for the city of Tabriz, on the other hand, are slightly higher than the averages shown in Fig.~\ref{fig:pgaavgs}c and are closer to those we present in Fig.~\ref{fig:pga}b, which are in the order of 0.8 g and 0.6 for the models 2U5.5 and 10U5.5.
+In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.3 and 0.45 g.
+Similarly, \citet{Abdi2013} reports expected PGA values in the vicinity of Karaj and Tehran to be on the order of 0.3 g.
+Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also of the same order of those we show in Figs.~\ref{fig:pga} and \ref{fig:pgaavgs}c.
+Finally, in for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the nort-east province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.
 
@@
 \\
-
-% \subsection{Hazard Curve}
-
-% We calculated the probability of exceedance of the ground motion from different ground motion levels, separately for each of 5 regions. 
-% We add the probability of all regions in order to have the effect of seismicity from all tectonic seismic regions. 
-% The results are presented as annual rate of exceedance.
 
@@
 
-% \subsection{Peak Ground Acceleration}
-
-We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance.
-
-% Fig.~\ref{fig:pga_10_mean} and Fig.~\ref{fig:pga_2_mean} show the results for 10\% and 2\% probability of exceedance in 50 years, respectively.
-% These results are according to the mean value of the attenuation relationship.
-% Fig.~\ref{fig:pga_10_mean_uniform} and Fig.~\ref{fig:pga_2_mean_uniform} show the results for 10\% and 2\% probability of exceedance in 50 years for the uniform model, respectively.
-
-% -------
-
-% Even though in this study we are interested in investigating seismic hazard study in the northern Iran, in the smoothed seismicity method we defined the border of the study region broadly enough to ensure that the seismicity outside of the border doesn't affect the study area.
-% In addition, the border of the influenced area should surround the area of interest as uniformly as possible \citep{Lapajne1997}. 
-% Therefore, our study region includes parts of central and eastern Iran and the Zagros tectonic seismic regions.
-
-% We calculated the $a-values$ for each cell and spatially smoothed over a grid of $0.1 \times 0.1$ in latitude and longitude. 
-% We assume magnitude increment as $\Delta_M = 0.1$.
-
-% In this model, events are not assigned to specific faults and are assumed to be potential seismogenic sources, and are spatially gridded to cells.
-
-% Different correlation distances have been used in different studies, which are generally dependent on the accuracy of the location of the recorded earthquakes.
-\citet{Frankel1995} and \citet{Boyd2008} assumed the correlation distance to be 50 $km$.
-\citet{Barani2007} used distance of 25 $km$ based on previous studies that suggested the correlation function of the Alps and Apennines in Italy.
-\citet{Foteva2006} used 10 and 15 km in a different model.
-Correlation distance is a very sensitive parameter in smoothed seismic hazard maps, and it is a factor of uncertainty in earthquake location.
-In the Iranian earthquake catalog, the magnitude uncertainties were assumed to be in the interval of $\pm$ 0.25 magnitude units and epicentral errors of $\pm$ 30 km \citep{Zare2012}.
-Even though these error margins are different for different events in terms of instrumental or historical events, in this study we assumed the correlation distance as 30 km because of the lack of knowledge about other historical events.
-
-% Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-
-% Fig.~\ref{fig:10percent} and Fig.~\ref{fig:2percent} show the seismic hazard map based on background seismicity for 10\% and 2\% probability of exceedance in 50 years, respectively.
-The areas of large probabilistic ground motions clearly coincide with zones with a large number of events with magnitude 3 and larger.
-
 % ==================
@@
 
+% The results are presented as annual rate of exceedance.
+
 % Regarding the study domain and the 0.1 grid size, the total number of source as grid points is 13561.
 
-% corresponding to return periods of 475 and 2475 years.
+% Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
+
+% Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
+
+% We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance.
+
+% \citet{Abdollahzadeh2014a} carried out a probabilistic seismic hazard assessment for part of Northern Iran.
+They used the logic tree approach to capture the epistemic uncertainty of seismic hazard assessment in delineation of seismic sources and selection of attenuation relationship.
+They used three attenuation relationships and 2 seismic source models.
+They collected the earthquake catalog from various references and reported the pga for 475 and 2475 years of return period for northern cities.
+
+% \citet{Golara2014} conducted a probabilistic seismic hazard analysis of interconnected infrastructure of Iranian high pressure gas supply system.
+He used line and area source model in order to estimate the Iranian  high-pressure gas supply system's ability to withstand a sudden large ground movements caused by potential earthquakes and related phenomenon that might be expected.
+he used simplified tectonic map after \citet{Alavi1991}.
+He used four attenuation relationships and presented the results for 2475 years of return period.

### 2016-07-05 results.tex
cleaning

@@
 Finally, in for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the nort-east province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.
+Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of previous studies for different points of interest (cities) in northern Iran.
+
+\begin{table}[t]
+    \centering
+    \caption{Comparison of expected PGA values for selected cities in northern Iran between results obtained in this study and those of others.
+For reference, the following codes are used.
+Va11: \citet{Vafaie2011}, Gh08: \citet{Ghodrati2008}, Bo15: \citet{Boostan2015}, Gh03: \citet{Ghodrati2003}, Ab14: \citet{Abdollahzadeh2014a}, Ra12: \citet{Rahgozar2012}, Ad13 \citet{Abdi2013}.}
+    \begin{tabular}{l}
+        \hline
+        Cities      \\
+        \hline
+        Urumieh     \\
+        Tabriz      \\
+        Ardabil     \\
+        Zanjan      \\
+        Manjil      \\
+        Rasht       \\
+        Qazvin      \\
+        Karaj       \\
+        Tehran      \\
+        Sari        \\
+        Semnan      \\
+        Gorgan      \\
+        Bojnurd     \\
+        Mashhad     \\
+        \hline
+    \end{tabular}
+    \label{tab:pga} 
+\end{table}
 
@@
 He used four attenuation relationships and presented the results for 2475 years of return period.
+
+% The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
+In this study we used two models for seismic hazard calculation, including $M_w>5$ and $M_w>4.5$.
+$M_w$ is the minimum magnitude that can affect the engineering site.
+
+% In the probabilistic seismic hazard analysis increasing minimum magnitude will decrease the mean rate of earthquake occurrence ($\nu=exp(\alpha - \beta M_0)$), and also increase the value for the probability density function in the initial magnitudes.
+In a simple source the difference between different models specially in higher pga levels is negligible.
+However, in this study where we consider each event as a seismic source with different $\alpha$ and $\beta$ value, the results are considerably different.
+According to our results the reduction of the mean rate of earthquake occurrence has considerable effect on the results.

### 2016-07-05 GMT_sctipts/smoothed_pga/pga_data_plots.m
cleaning

@@ -1,175 +1,0 @@
-clc
-clear all
-close all 
-
-
-load ('pga_10_50_mean_m_45.txt');
-load ('pga_10_50_mean_m_45_uniform.txt');
-load ('pga_10_50_mean_m_5.txt');
-load ('pga_10_50_mean_m_5_uniform.txt');
-load ('pga_10_50_minus_m_45.txt');
-load ('pga_10_50_minus_m_45_uniform.txt');
-load ('pga_10_50_minus_m_5.txt');
-load ('pga_10_50_minus_m_5_uniform.txt');
-load ('pga_10_50_plus_m_45.txt');
-load ('pga_10_50_plus_m_45_uniform.txt');
-load ('pga_10_50_plus_m_5.txt');
-load ('pga_10_50_plus_m_5_uniform.txt');
-load ('pga_2_50_mean_m_45.txt');
-load ('pga_2_50_mean_m_45_uniform.txt');
-load ('pga_2_50_mean_m_5.txt');
-load ('pga_2_50_mean_m_5_uniform.txt');
-load ('pga_2_50_minus_m_45.txt');
-load ('pga_2_50_minus_m_45_uniform.txt');
-load ('pga_2_50_minus_m_5.txt');
-load ('pga_2_50_minus_m_5_uniform.txt');
-load ('pga_2_50_plus_m_45.txt');
-load ('pga_2_50_plus_m_45_uniform.txt');
-load ('pga_2_50_plus_m_5.txt');
-load ('pga_2_50_plus_m_5_uniform.txt');
-
-
-% NW differ slightly in 2% & 10% 
-figure;
-scatter3(pga_2_50_mean_m_5_uniform(:,1),pga_2_50_mean_m_5_uniform(:,2),pga_2_50_mean_m_5_uniform(:,3),40,pga_2_50_mean_m_5_uniform(:,3),'filled')
-title ('pga-2-50-mean-m-5-uniform')
-
-
-figure;
-scatter3(pga_10_50_mean_m_5_uniform(:,1),pga_10_50_mean_m_5_uniform(:,2),pga_10_50_mean_m_5_uniform(:,3),40,pga_10_50_mean_m_5_uniform(:,3),'filled')
-title ('pga-10-50-mean-m-5-uniform')
-
-% 
-% %%%%%%%%%%%%%%%%%%%
-
-figure;
[…]

### 2016-07-05 GMT_sctipts/smoothed_pga/smoothed_pga.sh

@@ -1,38 +1,0 @@
-#!/bin/sh
-# Makes smoothed seismicity map from EQ catalog
-
-filename=`echo $1`
-
-gmt4 gmtset HEADER_FONT = 4
-gmt4 gmtset HEADER_FONT_SIZE = 20
-gmt4 gmtset GRID_CROSS_SIZE_PRIMARY = 1
-gmt4 gmtset LABEL_FONT = 4
-gmt4 gmtset LABEL_FONT_SIZE = 20
-
-
-
-gmt4 psxy -R43.5/61.5/34/40 -Jm1.2c -Ba1f0.2/a1f0.2WSNE -W5t5_5:0 -K  -H  -Y5  sqrt.d >pgamap.ps
-gmt4 blockmean $filename.txt -R -I.01>tempmean
-gmt4 surface tempmean -R -I.01 -Gtempmap.grd -T0.3
-gmt4 grdimage tempmap.grd -R -Jm1.2c -Ccont1.cpt -K -O >>pgamap.ps
-gmt4 grdcontour tempmap.grd -Jm1.2c -R -O -K -C0.1 -A0.1 >> pgamap.ps
-gmt4 pscoast -R -Jm1.2c -B2g2/2g2:."Northern Iran seismic zone 10% in 50y PGA Hazard Map": -Dh -W1 -K -O -Na >>pgamap.ps
-gmt4 psscale -Ccont1.cpt -D14.0/3.5/6.0/0.3 -O -B:g: -X9 >>pgamap.ps
-
-#ps2pdf pgamap.ps pgaMapO1.pdf
-
-#ps2raster pgamap.ps -TG -Au -FpgaMapO1-png
-
-ps2pdf pgamap.ps $filename.pdf
-
-
-#gv pgamap.ps &
-
-# uncomment to have png surface
-#psxy -R43.5/61.5/34/40 -Jm1.2c -Ba1f0.2/a1f0.2WSNE -W5t5_5:0 -K  -H  -Y5  sqrt.d >pgamap.ps
-#psbasemap -R -Jm1.2c -Bwesn  -K  -Y5 >pgamap.ps
-#blockmean pga_2_50.txt -R -I.01>tempmean
-#surface tempmean -R -I.01 -Gtempmap.grd -T0.3
-#grdimage tempmap.grd -R -Jm1.2c -Ccont1.cpt -K  -O >>pgamap.ps
[…]

### 2016-07-07 results.tex
table 3

@@
 
+\input{table-pga}
+
 We also note that the overall distribution of PGA values shown in Fig.~\ref{fig:pgaavgs}c are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}.
@@
 Finally, in for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the nort-east province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.
-Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of previous studies for different points of interest (cities) in northern Iran.
-
-\begin{table}[t]
-    \centering
-    \caption{Comparison of expected PGA values for selected cities in northern Iran between results obtained in this study and those of others.
-For reference, the following codes are used.
-Va11: \citet{Vafaie2011}, Gh08: \citet{Ghodrati2008}, Bo15: \citet{Boostan2015}, Gh03: \citet{Ghodrati2003}, Ab14: \citet{Abdollahzadeh2014a}, Ra12: \citet{Rahgozar2012}, Ad13 \citet{Abdi2013}.}
-    \begin{tabular}{l}
-        \hline
-        Cities      \\
-        \hline
-        Urumieh     \\
-        Tabriz      \\
-        Ardabil     \\
-        Zanjan      \\
-        Manjil      \\
-        Rasht       \\
-        Qazvin      \\
-        Karaj       \\
-        Tehran      \\
-        Sari        \\
-        Semnan      \\
-        Gorgan      \\
-        Bojnurd     \\
-        Mashhad     \\
-        \hline
-    \end{tabular}
-    \label{tab:pga} 
-\end{table}
+Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
 

### 2016-07-07 figures/gmt/plot-smoothed-choice.sh

@@ -1,0 +1,43 @@
+
+FILENAME=$1
+CPTFILE=tmp.cpt
+OUTFILE=tmp.ps
+GRDFILE=tmp.grd
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# gmt makecpt -CcbcRdPu -Do -T0/1.0/0.05 > ${CPTFILE}
+# gmt makecpt -CcbcGreens -Do -T0/1.0/0.05 > ${CPTFILE}
+gmt makecpt -Ces_skywalker_18 -Do -T0/1.0/0.05 > ${CPTFILE}
+
+gmt surface ${FILENAME}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE}
+
+gmt grdimage ${GRDFILE} -R -JM5i -C${CPTFILE} -K -P -V > ${OUTFILE}
+gmt grdcontour ${GRDFILE} -J -R -C0.2 -A0.2+f6p -W0.5p -O -K -V >> ${OUTFILE}
+gmt psscale -C${CPTFILE} -D5.3i/1i/1.8i/0.15i -E -B0.1 -O -V >>${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILENAME}.pdf -Tf -Au0.5c 
+
+gmt grdimage ${GRDFILE} -R43.5/61.5/34/40 -JM5i -C${CPTFILE} -P -V > ${OUTFILE}
+
+gmt ps2raster ${OUTFILE} -F${FILENAME}.png -Tg -Au
+
+rm tmp.cpt
+rm tmp.grd
+rm ${OUTFILE}
+
+# Opening PDF
+# ------------------------------------------------------------------------------
+
[…]

### 2016-07-07 attenuation.tex
finalizing results section

--- 2016-06-06 attenuation.tex
@@
 % 
-respectively. The value of $V_S$ is assumed to represent average surface rock sites.
+respectively.
+The standard deviation of the residuals $(\sigma_{\ln y})$ expressing the random variability of the ground motions is 0.612.
+The value of $V_S$ is assumed to represent average surface rock sites.
+
+We should note here that even though \citet{Kalkan2004} derived the above attenuation relationship for distances $r$ up to 250 km, \citet{Zafarani2014} only used data up to 200 km in their evaluation of the various GMPEs available.
+Therefore, in consistence with \citet{Zafarani2014}, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.
 

### 2016-07-07 hazard.tex
finalizing results section

@@
 Different values of $c$ have been used in past studies, ranging between 10 and 50 km.
-\citet{Frankel1995} and \citet{Boyd2008} assumed $c=50$~km, \citet{Barani2007} used $c=25$~km, and \citet{Foteva2006} used $c=10$ and 15 km.
+\citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15 km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40 km.
 According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records.

### 2016-07-07 introduction.tex
finalizing results section

@@
 More recently, in a study aimed to develop a uniform earthquake catalog for Iran, \citet{Karimiparidari2013} further divided the Azerbaijan-Alborz region into two separate seismic zones: Azerbaijan and the Alborz Mountain Range, hereafter referred to simply as Alborz.
-We adopt the latter definition of six seismic seismic zones and focus our attention on those most relevant to the northern part of the country, Azerbaijan, Alborz and Kopeh-Dagh.
+We adopt the latter definition of six seismic zones and focus our attention on those most relevant to the northern part of the country, Azerbaijan, Alborz and Kopeh-Dagh.
 

### 2016-07-07 parameters.tex
finalizing results section

@@
 The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
-THe last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
+The last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
 The shaded range indicates the models' $\pm 1$ standard deviation.}
@@
 On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
-We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in four sub-catalogs: 2 incomplete catalogs for the prehistorical (before 1000) and historical (between 1000 and 1799) event periods, and two complete catalogs for  early instrumental (between 1800 and 1899) and instrumental (between 1900 and 2015) event periods.
+We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
 In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
@@
 In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
-That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the portions of the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
+That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
 In the second model we consider the whole study area as a uniform seismic zone.

### 2016-07-07 results.tex
figures 12 and 13 added
finalizing results section

@@
 As can be expected, the highest levels of ground motion are associated with the 2R5.5 and 2U5.5 models, and the lowest with the 10R6.5 and 10U6.5 models.
-In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region along the border with Turkmenistan, followed by ground motions in the north-central region west from Tehran and Karaj, and in the vicinity of the Piranshahr fault between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}b for reference).
+In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region along the border with Turkmenistan, and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
 The Azerbaijan seismic zone does not present equally high levels of expected ground motion.
@@
 The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with concentration of strong earthquakes in the Alborz and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
-This may be the cause of
+This is because of the higher $b$-value obtained for the Azerbaijan region in the R model as opposed to the lower value for the U model.
 
@@
 Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also of the same order of those we show in Figs.~\ref{fig:pga} and \ref{fig:pgaavgs}c.
-Finally, in for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the nort-east province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.
+Finally, for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the northeast province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.
+
+\begin{figure*}[th!]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-12} 
+    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the four basic models considered in this study, namely R5.5, R6.5, U5.5 and U6.5.}
+    \label{fig:hazardcurve}
+\end{figure*}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/pdf/figure-13} 
+    \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran.
+Here, the two previous studies just mentioned are identified with the codes Gh03 and Bo15, respectively.}
+    \label{fig:tehran}
+\end{figure}
+
 Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
+In addition, we also looked into the more complete picture of the annual probabilities of exceedance as functions of PGA for six cities (all the same as in Table \ref{tab:pga} except Rasht).
+This is shown in Fig.~\ref{fig:hazardcurve} for the four basic models considered before, namely R5.5, R6.5, U5.5 and U6.5, each also including upper and lower ranges of one standard deviation.
+These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance.
+Minor differences are also present in the central cities of Karaj and Tehran, whereas the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones present similar hazard levels between the two models (R and U).
+This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pgadiff} and \ref{fig:pgaavgs}.
+
+Last, we pay additional attention to the capital city of Tehran and compare hazard...
 
@@
 \\
-
-Fig.~\ref{fig:hazardcurve} represents the hazard curve of different model for some of important northern cities in Iran.
-
-\begin{figure*} [!ht]
-\centering
-\includegraphics[scale=0.4]{figures/pdf/HazardCurve.pdf} 
-\caption{Seismic Hazard Curve of Northern Cities in Iran}
-\label{fig:hazardcurve}
-\end{figure*}
 

### 2016-07-08 acknowledge.tex
finished... I think

\section{Acknowledgements}

The authors wish to express their gratitude to Art Frankel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advise on the use of the software. The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information. Access to data provided by IIEES is also greatly appreciated. This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis. CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015--2016).

### 2016-07-08 conclusions.tex
finalizing results section
finished... I think

--- 2015-09-28 Conclusion.tex
@@
-\section{Conclusion}
+\section{Concluding Remarks}
 
-The aim of this study is to conduct a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs.
-Seismic hazard is evaluated over three regions (Azerbaijan, Tehran, Kopeh-Dagh) using the smoothed background seismicity.
-According to our study, in the Alborz  and Azerbaijan regions substantial seismic hazard is observed.
-We studied probabilistic seismic hazard based on smoothed seismicity using historical and instrumental data.
-The results of this paper can be addressed in three main conclusions.
-First, probabilistic seismic hazard analysis using smoothed seismicity is sufficient for 10\% probability of exceedance.
-Second, since this study is based solely on historical and instrumental data, places with very close PGA values to those studies with considering faults as a primary source of seismicity, show normal and predictable seismic activity.
-Third, places with lower hazard values compared to other studies show anomalous seismic activity and suggest the idea of expecting more and bigger events in the future.
-As mentioned before, probabilistic seismic hazard analysis based on smoothed seismicity is very sensitive to input parameters (e.g., correlation distance, $b-value$, catalog completeness, and threshold magnitude for structural damage).
-Studying the sensitivity rate of these parameters could develop a more trustworthy result.
-Maps presented in this paper are for illustrative purposes only, and are not intended to be used in any application.
+We present results from a comprehensive seismic hazard analysis for the region of northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic-zonation models and magnitude thresholds.
+In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model.
+Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard analysis due to the usage of a more complete catalog and inclusion of low-magnitude events.
+In our analysis we found it convenient to combine both the regional and uniform models as a mean to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones.
+Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and the to the location of known seismically active faults.
+While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural ares which are not the subject of specialized hazard studies such as those conducted for major urban areas.
+Future work to improve the results presented here should consider alternative attenuation relationships, especially for estimating other ground motion parameters such as response spectral accelerations for different periods and site effects.
+
+% ---------
+% OLD STUFF
+% ---------
+
+% The result of a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs is provided.
+Seismic hazard is evaluated over entire three regions (Azerbaijan, Alboz, Kopeh-Dagh) as well as part of Central and Zagros tectonic seismic regions using the smoothed background seismicity.
+In order to determine the seismic hazard in North Iran, different studies have been done.
+These studies are based on defining faults as a seismic source model.
+Using faults as a seismic source model could result in accurate values in case the faults are precisely determined.
+There are considerable uncertainties on fault characteristic, specially on fault length.
+Instead of using faults as a seismic source, we consider each earthquake event as a point source in the model.
+We reduce the uncertainty in earthquake location by smoothing the number of earthquake in adjacent cells.
+We defined models based on considering the whole North Iran as a uniform seismic tectonic regions and 5 different seismic tectonic regions.
+The differences in catalog completeness, b value, and maximum magnitude of earthquake in these two models resulted in different results.
+This indicate the idea that dividing regions into subregions is necessary in order to be able to get accurate results.
+The result are also sensitive to the minimum magnitude.
+The structures built according to engineering code are supposed to withstand the earthquake with magnitude 5 at the reasonable distance.
+However, closer $M_w > 4.5$ for those structures and also older masonry structures could cause structural damage.
+A combination of two models $(M_w > 4.5, M_w>5)$ in each city based on number of engineering and old masonry structures will provide more accurate results.
+The results are provided for mean peak horizontal acceleration in bedrock.
+The ground acceleration in soil deposits and inside basin will be bigger than the provided values.
+This model reduce the epistemic uncertainty regarding the recognizing faults and earthquake location.
+Combination of this model with a study based on using faults will increase the values for existing non-active seismic fault regions.

### 2016-07-08 results.tex
finished... I think

@@
 Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
-In addition, we also looked into the more complete picture of the annual probabilities of exceedance as functions of PGA for six cities (all the same as in Table \ref{tab:pga} except Rasht).
-This is shown in Fig.~\ref{fig:hazardcurve} for the four basic models considered before, namely R5.5, R6.5, U5.5 and U6.5, each also including upper and lower ranges of one standard deviation.
+As mentioned before, overall, our results are close or within the ranges from most studies.
+The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad.
+This is likely due to the authors working with mower magnitude thresholds (not clearly reported) than other studies where hazard is usually estimated based on earthquake magnitudes exceeding $M_w > 5$.
+Although not included here for brevity we also computed expected PGA values for a magnitude threshold of $M_w$ 4.5 and 5.0.
+We found the former case to yield results closer to those of \citet{Golara2014}, but not to the other studies.
+Using lower magnitude thresholds may be of relevance if evaluating poorly constructed and unreinforced buildings vulnerable to low-to-moderate magnitude earthquakes.
+
+Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA.
+The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the four basic models R5.5, R6.5, U5.5 and U6.5.
+In each case we also show $\pm 1$ standard deviation (shaded ranges).
 These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance.
-Minor differences are also present in the central cities of Karaj and Tehran, whereas the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones present similar hazard levels between the two models (R and U).
+Minor differences are also present in the results of the central cities of Karaj and Tehran, whereas for the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones, the R and U models yield similar hazard levels.
 This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pgadiff} and \ref{fig:pgaavgs}.
 
-Last, we pay additional attention to the capital city of Tehran and compare hazard...
-
-~\\
-* * *
-\\
+Last, we put additional attention on the results for the capital city of Tehran.
+We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015}.
+Our results are similar to those obtained by \citet{Ghodrati2003} between 0.4 and 0.8 g (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-3}$), but we obtain lower probabilities for the ground motion amplitudes between 0.1 and 0.4 g, and higher probabilities for very low ($<0.1$ g) and much higher PGA ($>0.8$ g) values.
+These differences with \citet{Ghodrati2003}, nonetheless, are still within our levels of uncertainty.
+A similar interpretation can be made for the comparison with \citet{Boostan2015} for low PGA values ($<0.4$ g), but the trajectory of their hazard curve suggests much higher probabilities of exceeding PGA values above 0.6 g, which is contrary to our findings.
 

### 2016-07-08 main.tex
completed first revision of abstract
changed references filename and made modifications to notes about the 2016 paper
looks like done

@@
 \usepackage{marvosym}
+\usepackage{textcomp}
 
@@
 	N.~Khoshnevis \and
+	R.~Taborda \and
 	S.~Azizzadeh-Roodpish \and
-	R.~Taborda \and
 	C.~H.~Cramer
@@
 	\and
-	S.~Azizzadeh-Roodpish \and R.~Taborda (\Letter)\at
+	R.~Taborda (\Letter) \and S.~Azizzadeh-Roodpish \at
 	Department of Civil Engineering, and
@@
 \bibliographystyle{spbasic}
-\bibliography{PSHA}
+\bibliography{references}
 % \nocite{*}

### 2016-07-09 acknowledge.tex
implemented final comments from Naeem

@@
 
-The authors wish to express their gratitude to Art Frankel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advise on the use of the software.
+The authors wish to express their gratitude to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advise on the use of the software.
 The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information.

### 2016-07-09 completeness.tex
finalizing results section
implemented final comments from Naeem

@@
 
-The start-year of completeness is usually identified by inspection.
+The start-year of completeness is commonly identified by inspection.
 A simple approach used by \citet{Frankel1995} and others is to select the year at which a plot of the cumulative number of events with respect to time becomes (or starts to resemble) a straight line.
@@
 Having augmented the original catalog with $M>3$ earthquakes beginning in 2000 also influenced our choice of the intervals because at this point the uniformity of the catalog is altered.
-No value of $M_c$ was computed for pre-historical (before 1800) data because of scarcity of data.
 Last, we also computed $M_c$ values for the complete regional catalogs, but in this case, in order to maintain uniformity throughout time, we only considered $M>4$ events.
@@
 The horizontal dashed lines indicate desired thresholds for the goodness-of-fit values at 80 and 90 percent.
-The vertical red lines show indicate the chosen $M_c$ values for each zone and catalog year interval.}
+The vertical red lines indicate the chosen $M_c$ values for each zone and catalog year interval.}
     \label{fig:mc}

### 2016-07-09 conclusions.tex
implemented final comments from Naeem

@@
 
-We present results from a comprehensive seismic hazard analysis for the region of northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic-zonation models and magnitude thresholds.
+We present results from a comprehensive seismic hazard analysis for the region of northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models and magnitude thresholds.
 In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model.

### 2016-07-09 parameters.tex
implemented final comments from Naeem

@@
 
-Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3 (version 3).
+Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3, version 3 \citep{Kijko_2004_HA3}.
 This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.

### 2016-07-09 results.tex
implemented final comments from Naeem

@@
 Last, we consider an overall combination of both hazard models and magnitude thresholds, as shown in Fig.~\ref{fig:pgaavgs}d.
-At all times we keep separate the probabilities of exceedance.
 
@@
 These estimates also agree, on average, with other previous studies.
-For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, and 0.4 g around the city of Urmia, where we find equivalent values to be between 0.4 and 0.6 g, and about 0.35 g, respectively.
-The results from \citet{Vafaie2011} for the city of Tabriz, on the other hand, are slightly higher than the averages shown in Fig.~\ref{fig:pgaavgs}c and are closer to those we present in Fig.~\ref{fig:pga}b, which are in the order of 0.8 g and 0.6 for the models 2U5.5 and 10U5.5.
-In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.3 and 0.45 g.
-Similarly, \citet{Abdi2013} reports expected PGA values in the vicinity of Karaj and Tehran to be on the order of 0.3 g.
+For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.2 and 0.4 g.
+The results from \citet{Vafaie2011} for the city of Tabriz, on the other hand, are slightly higher than the averages shown in Fig.~\ref{fig:pgaavgs}c and are closer to those we present in Fig.~\ref{fig:pga}b, which are in the order of 0.8 and 0.6 g for the models 2U5.5 and 10U5.5.
+In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.2 and 0.35 g, which are closer to the values reported by \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.3 g.
 Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also of the same order of those we show in Figs.~\ref{fig:pga} and \ref{fig:pgaavgs}c.
@@
 The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad.
-This is likely due to the authors working with mower magnitude thresholds (not clearly reported) than other studies where hazard is usually estimated based on earthquake magnitudes exceeding $M_w > 5$.
-Although not included here for brevity we also computed expected PGA values for a magnitude threshold of $M_w$ 4.5 and 5.0.
+This is likely due to the authors working with lower magnitude thresholds (not clearly reported) than other studies where hazard is usually estimated based on earthquake magnitudes exceeding $M_w > 5$.
+Although not included here for brevity, we also computed expected PGA values for magnitude thresholds $M_w$ 4.5 and 5.0.
 We found the former case to yield results closer to those of \citet{Golara2014}, but not to the other studies.
 Using lower magnitude thresholds may be of relevance if evaluating poorly constructed and unreinforced buildings vulnerable to low-to-moderate magnitude earthquakes.
+We should also note that, in general, the smoothed seismicity method used here tends to lead to lower hazard estimations than those obtained using specific fault definitions (as opposed to point sour\-ces).
 

### 2016-07-14 figures/gmt/plot-smoothed-choice.sh
new figure 8, 9 and 10, and the scripts used

@@ -18,8 +18,8 @@ gmt gmtset MAP_LABEL_OFFSET         8p
 gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
 
 # gmt makecpt -CcbcRdPu -Do -T0/1.0/0.05 > ${CPTFILE}
-# gmt makecpt -CcbcGreens -Do -T0/1.0/0.05 > ${CPTFILE}
-gmt makecpt -Ces_skywalker_18 -Do -T0/1.0/0.05 > ${CPTFILE}
+gmt makecpt -CcbcGreens -Do -T0/1.0/0.05 > ${CPTFILE}
+# gmt makecpt -Ces_skywalker_18 -Do -T0/1.0/0.05 > ${CPTFILE}
 
 gmt surface ${FILENAME}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE}
 

### 2016-07-14 figures/gmt/plot-smoothed-diff.sh

@@ -20,7 +20,7 @@ gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
 gmt gmtset MAP_LABEL_OFFSET         8p
 gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
 
-gmt makecpt -CcbcPRGn -Do -T-0.6/0.6/0.05 > ${CPTFILE}
+gmt makecpt -CcbcPRGn -Do -T-0.5/0.5/0.05 > ${CPTFILE}
 
 gmt surface ${FILEONE}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE1}
 gmt surface ${FILETWO}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE2}

### 2016-07-14 figures/gmt/plot-smoothed-pga.sh

@@ -17,7 +17,7 @@ gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
 gmt gmtset MAP_LABEL_OFFSET         8p
 gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
 
-gmt makecpt -CcbcYlOrRd -Do -T0/1.0/0.05 > ${CPTFILE}
+gmt makecpt -CcbcYlOrRd -Do -T0/1/0.05 > ${CPTFILE}
 
 gmt surface ${FILENAME}.txt -R43.5/61.5/34/40 -I0.01 -T0.3 -G${GRDFILE}
 

### 2016-07-14 composition.tex
finalizing results section
implemented simple editorial changes suggested by Cramer

@@
 \citet{Mirzaei1997} compiled a catalog with historical events dating back to the 4th century B.C.~and instrumental earthquakes through 1994 in which a comprehensive list of studies was considered and magnitudes uniformly converted to surface wave magnitude ($M_s$).
-Most ground motion prediction equations employed today in seismic hazard, however, use moment magnitude ($M_w$) instead.
+Most ground motion prediction equations employed today in seismic hazard studies, however, use moment magnitude ($M_w$) instead.
 
@@
 While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
-By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar for events $M_w \geq 4$ catalog but only included data up until 2011, which excluded the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.
+By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar catalog for events $M_w \geq 4$ but only included data through 2011, excluding the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.
 
@@
 In these cases we used the empirical relationship introduced by \citet{Deniz2010} to convert $M_D$ to $M_w$.
-Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results to adjust well with the general trend.
+Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found that results agree well with the general trend.
 
-Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}.
+Selection and declustering was also done in a manner consistent with the original catalog, using the method of \citet{Gardner1974}.
 In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.

### 2016-07-14 region.tex
implemented simple editorial changes suggested by Cramer

@@
 The locations of these and other notable events, including the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes, are shown in Fig.~\ref{fig:selected}b.
-More recently, the same region was stroke by the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage and took the lives of more than 1500 people.
+More recently, the same region was struck by the $M_w$ 6.1 1997 Ardabil and $M_w$ 6.4 2012 Tabriz earthquakes, which caused extensive damage and took the lives of more than 1500 people.
 
@@
 The Main Kopeh-Dagh Fault is responsible for the $M_w$ 7.3 1948 earthquake (Fig.~\ref{fig:selected}b).
-This event stroke Ashgabat, the capital city of Turkmenistan, and destroyed more than 30 villages in Iran.
+This event struck Ashgabat, the capital city of Turkmenistan, and destroyed more than 30 villages in Iran.
 Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at the boundary between the Neyshabur and Binalud reverse faults (Fig.~\ref{fig:selected}a) between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001}.

### 2016-07-14 results.tex
implemented simple editorial changes suggested by Cramer

@@
 
-In the distinct regions R models, we computed the probability of exceedance of the ground motion separately for each region and then add them together in order to have the contribution of all regions for any given grid point within the region of interest.
+In the distinct regions R models, we computed the probability of exceedance of the ground motion separately for each region and then added their exceedance rates at a given level of ground motion in order to have the contribution of all regions for any given grid point within the region of interest.
 The results are obtained in the form of annual rate of exceedance.
-Expected PGA values are therefore a ``slice'' of the actual hazard curves cut across all grid points for a chosen magnitude.
+Expected PGA values are therefore a ``slice'' of the actual hazard curves cut across all grid points for a chosen exceedance rate.
 

### 2016-07-15 results.tex
fixed table 3 to new values for M5

@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf} 
-    \caption{Expected PGA values throughout the region of interest for 2 and 10 percent probability of exceeding an earthquake magnitude $M_w$ 6.5 using the hazard calculations from the five-region R model and the attenuation relationship plus and minus one standard deviation.}
+    \caption{Pending.}
+    % \caption{Expected PGA values throughout the region of interest for 2 and 10 percent probability of exceeding an earthquake magnitude $M_w$ 6.5 using the hazard calculations from the five-region R model and the attenuation relationship plus and minus one standard deviation.}
     \label{fig:pgastd}
@@
 
-\begin{figure*}[th!]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-11.pdf} 
-    \caption{Expected PGA values for different combination models.
+% \begin{figure*}[th!]
+%     \centering
+%     \includegraphics[width=\textwidth]{figures/pdf/figure-11.pdf} 
+%     \caption{Expected PGA values for different combination models.
 (a) Combination of R models for magnitudes $M_w$ 5.5 and 6.5.
@@
 (d) Combination of R and U models, and magnitudes $M_w$ 5.5 and 6.5.}
-    \label{fig:pgaavgs}
-\end{figure*}
+%     \label{fig:pgaavgs}
+% \end{figure*}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-12} 
+    \includegraphics[width=\textwidth]{figures/pdf/figure-11} 
     \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the four basic models considered in this study, namely R5.5, R6.5, U5.5 and U6.5.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/pdf/figure-13} 
+    \includegraphics[width=\columnwidth]{figures/pdf/figure-12} 
     \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran.

### 2016-07-15 abstract.tex
finished making changes requested by cramer

@@
 After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
-Seismicity parameters are calculated for each seismic zone separately, and for comparison purposes we also consider the combination of all zones into a single seismotectonic region.
-Seismic hazard curves are obtained for different models defined based on the assumption that damage occurs above certain earthquake magnitude thresholds, depending on the type of construction.
-We also obtain results for a combined scenario using different models.
-The results are presented in terms of expected peak ground acceleration curves and hazard maps, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We analyze our results in light of equivalent estimations available in the literature and offer our perspective on the differences observed.
+Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region.
+We also consider the combination ot these two basic models.
+The results are presented in terms of expected peak ground acceleration maps and hazard curves at select locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
 In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.

### 2016-07-15 attenuation.tex
finished making changes requested by cramer

@@
 
-Since our hazard analysis here focuses on PGA values, we concentrated our attention in the last set of GMPEs.
+Since our hazard analysis here focuses on PGA values only, we concentrated our attention in the last set of GMPEs.
 In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other.
@@
 % 
-where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, $V_S$ is the shear wave velocity of the site of interest, and the distance $r$ is given by
+where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, $V_S$ is the shear wave velocity of the site of interest.
+In this equation, the distance $r$ is given by
 % 
@@
 We should note here that even though \citet{Kalkan2004} derived the above attenuation relationship for distances $r$ up to 250 km, \citet{Zafarani2014} only used data up to 200 km in their evaluation of the various GMPEs available.
-Therefore, in consistence with \citet{Zafarani2014}, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.
-
-% *********************************************************************************************************************
-% OLD
-% *********************************************************************************************************************
-
-% The choice of the ground motion attenuation relationship, as a highly influential factor, is of a great importance in seismic hazard analysis.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-The epistemic uncertainty in attenuation relationship is being considered through using the logic tree approach.
-Having close mean value and similar logic tree weights, logic tree approach will have a minor effect in considering the epistemic uncertainty.
-In this study instead of using  different GMPEs we use the best model of attenuation relationship for PGA \citep{Zafarani2014} as well $\pm$ standard deviation.
-\\
-
-% \noindent
-% The attenuation relationship is:
-
-% \begin{equation}
-% \begin{split}
-% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+  \\ 
-% b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-% \end{split}
-% \end{equation}
-
-% *********************************************************************************************************************
-% OLDER
-% *********************************************************************************************************************
-
-% \section{Attenuation relationship}
-
-% The choice of a ground motion attenuation model is of great importance since attenuation has proven to be a highly influential factor of seismic hazard.
-\citet{Zafarani2014} used 163 free-field acceleration time histories recorded at epicentral distance of up to 200 km from 32 earthquakes to investigate the predictive capabilities of the local, regional, and next generation attenuation (NGA) ground-motion prediction equations and determined their applicability for northern Iran.
-After evaluating different Ground Motion Prediction Equations, \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008} represented suitable performance for  PGA  with LLH (Log-Likelihood method) score of 1.54, 1.55, and 1.59.
-Mean of the mentioned attenuation relationships (not shown here), are very close together, especially at higher magnitude.
-Using \citet{Scherbaum2009} approach and \citet{Zafarani2014} coefficients we calculated the logic tree weights as 0.3376, 0.3354, and 0.3270, respectively.
-Getting close mean values and logic tree weights, in order to consider the epistemic uncertainty, instead of using several GMPEs we use the top rank GMPE (i.e.
-\citet{Kalkan2004} ) with  $\pm$ standard deviation with weight of 0.2 (for each of standard deviation branches) and 0.6 for the mean value.
-\\
-
-% \noindent
-
-% The attenuation relationship is:
-
-% \begin{equation}
-% ln\ (Y) = b_1 + b_2(M_w-6) + b_3( M_w-6)^{2}+ b_5ln\ r + b_V \ ln(V_S/V_A) \  with \  r= \sqrt{R{r^2_{cl} + h^2}}  
-% \end{equation}
-
-% where $Y$ is in $g$, $b_1 = 0.393$, $b_2 = 0.576$, $b_3 = -0.107$, $b_5 = -0.899$, $b_V = -0.200$, $V_A = 1112$, $h(km) = 6.91$, $\sigma_{ln\ Y} = 0.612$.
+Therefore, in consistence with the latter, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.

### 2016-07-15 composition.tex
finished making changes requested by cramer

@@
 In these cases we used the empirical relationship introduced by \citet{Deniz2010} to convert $M_D$ to $M_w$.
-Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found that results agree well with the general trend.
+Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results agree well with the general trend.
 

### 2016-07-15 conclusions.tex
finished making changes requested by cramer

@@
 
-We present results from a comprehensive seismic hazard analysis for the region of northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models and magnitude thresholds.
+We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models.
 In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model.
@@
 In our analysis we found it convenient to combine both the regional and uniform models as a mean to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones.
-Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and the to the location of known seismically active faults.
-While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural ares which are not the subject of specialized hazard studies such as those conducted for major urban areas.
+Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and to the location of known seismically active faults.
+While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers.
 Future work to improve the results presented here should consider alternative attenuation relationships, especially for estimating other ground motion parameters such as response spectral accelerations for different periods and site effects.
-
-% ---------
-% OLD STUFF
-% ---------
-
-% The result of a new probabilistic seismic hazard assessment for northern Iran using updated seismic catalogs is provided.
-Seismic hazard is evaluated over entire three regions (Azerbaijan, Alboz, Kopeh-Dagh) as well as part of Central and Zagros tectonic seismic regions using the smoothed background seismicity.
-In order to determine the seismic hazard in North Iran, different studies have been done.
-These studies are based on defining faults as a seismic source model.
-Using faults as a seismic source model could result in accurate values in case the faults are precisely determined.
-There are considerable uncertainties on fault characteristic, specially on fault length.
-Instead of using faults as a seismic source, we consider each earthquake event as a point source in the model.
-We reduce the uncertainty in earthquake location by smoothing the number of earthquake in adjacent cells.
-We defined models based on considering the whole North Iran as a uniform seismic tectonic regions and 5 different seismic tectonic regions.
-The differences in catalog completeness, b value, and maximum magnitude of earthquake in these two models resulted in different results.
-This indicate the idea that dividing regions into subregions is necessary in order to be able to get accurate results.
-The result are also sensitive to the minimum magnitude.
-The structures built according to engineering code are supposed to withstand the earthquake with magnitude 5 at the reasonable distance.
-However, closer $M_w > 4.5$ for those structures and also older masonry structures could cause structural damage.
-A combination of two models $(M_w > 4.5, M_w>5)$ in each city based on number of engineering and old masonry structures will provide more accurate results.
-The results are provided for mean peak horizontal acceleration in bedrock.
-The ground acceleration in soil deposits and inside basin will be bigger than the provided values.
-This model reduce the epistemic uncertainty regarding the recognizing faults and earthquake location.
-Combination of this model with a study based on using faults will increase the values for existing non-active seismic fault regions.

### 2016-07-15 hazard.tex
finished making changes requested by cramer

@@
 where $N$ is the number of earthquakes with magnitude greater than or equal to $M$, $a$ accounts for the number of earthquakes that occur within a given region, and $b$ is a measure of the occurrence of earthquakes relative to magnitude \citep{Gutenberg1944}.
-These parameters can be assumed constant or variable depending on the approach used.
+These parameters can be assumed constant within a region or spatially variable depending on the approach used.
 
@@
 This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.
-In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes.
+In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes within and around the region.
 The spatial variation of $a$ is defined based on dividing the region of interest into regular-size grid cells.
@@
 
-It is clear from Eq.~\ref{eq:exceed} that the hazard calculations depend also on the choice of an attenuation relationship to obtain predict the level of ground motion at a site ($u$) for any given earthquake.
+It is clear from Eq.~\ref{eq:exceed} that the hazard calculations depend also on the choice of an attenuation relationship to predict the level of ground motion at a site ($u$) for any given earthquake.
 In the following two sections we describe how we obtained the $b$-values for the different seismic zones influencing the hazard in northern Iran and our choice of a suitable attenuation relationship (ground motion prediction equation).
-
-% *********************************************************************************************************************
-% PENDING TO USE
-% *********************************************************************************************************************
-
-% We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-
-% Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$.
-
-% Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
-
-% According to Building and Housing Research Center \citep{BHRC2014}, $M_w 5$ is considered as a threshold magnitude for onsetting the structural damage.
-
-% In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it,
-
-% in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
-
-% *********************************************************************************************************************
-% ALREADY USED
-% *********************************************************************************************************************
-
-% Occurrence of devastating historical earthquake and also essential needs for constructing new buildings and infrastructures inspired researchers to study the seismic hazard of northern Iran from different points of view.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years corresponding to 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone have the highest acceleration.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-% In this study we use background seismicity to estimate the seismic hazard in northern Iran.
-Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2003, Kalkan2009, Moschetti2014, Boyd2008}.
-
-% \subsection{Analysis Method}
-
-% \subsubsection{smoothed seismicity method}
-
-% We use spatially smoothed seismic hazard analysis \citep{Frankel1995} to estimate the seismic hazard. 
-% In this model, seismic events are spatially gridded to cells. 
-% We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage. 
-% % According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above. 
-% % Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur. 
-% Since the catalog's completeness for $M_w > 3$ and $M_w > 4$ are different, we use two magnitude completeness range for less than $M_w 5$. 
-% Earthquake greater than magnitude 5, most probably will occur near where they have occurred in the past.
-% According to Building and Housing Research Center \citep{BHRC2014}, $M_w 5$ is considered as a threshold magnitude for onsetting the structural damage. 
-% In the smoothed seismicity method, the model uses each event location as a point source, 
-% hence $M_w 4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, 
-% in this study, in order to consider the probabilistic seismic hazard, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
-% In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
-% We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
-number of events bigger than $M_{ref}$) values to incremental (i.e.
-number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values.
-
-% Using Gaussian function we smooth the number of events in each cell. The smoothed value $\tilde{n}_i$ is obtained from
-
-% \begin{equation}
-% \tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-% \end{equation}
-
-% \noindent
-% where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.
-
-% Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
-
-% Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to
-
-% \begin{equation}
-% \begin{split}
-% \lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} \\
-% p(u>u_0 | D_k ,M_l),
-% \end{split}
-% \end{equation}
-
-% \noindent
-% where $k$ and $l$ are denoted as index of distance and magnitude bin.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}.
-
-% *********************************************************************************************************************
-% OLD STUFF
-% *********************************************************************************************************************
-
-%%% My (Naeem) original text
-
-%\subsection{Background}
-%
-%Regarding historical earthquakes and the need for constructing new buildings and infrastructure, different seismic hazard analyses were conducted in Iran.
-Dividing Iran into 20 tectonic seismic regions, \citet{Tavakoli1999} prepared iso-acceleration contour lines and seismic hazard zonation for return periods of 75 and 475 years or 50\% and 10\% probability of exceedance in 50 years, based on major known lines and area source models.
-According to their study, North Tabriz fault zone and north of Tehran fault zone are in the highest acceleration contour.
-Maximum mean acceleration in the vicinity of these tectonic elements is predicted to be around 0.45 $g$ and 0.3 $g$ for a return period of 475 and 75 years, respectively.
-In the smaller scale, using the logic tree approach to compensate for uncertainties in the attenuation relationship, \citet{Ghodrati2003} presented a probabilistic seismic hazard assessment of metropolitan Tehran, the capital of Iran.
-The results showed that the PGA ranges from 0.27-0.46 $g$ for a return period of 475 years and from 0.33-0.55 $g$ for a return period of 950 years.
-%In this study we use background seismicity to calculate the seismic hazard.Using background seismicity, \citet{Cao1996} conducted a seismic hazard estimation study in southern California.
-They concluded that one could obtain similar results implementing background seismicity to those obtained by introducing zones for areas with well-recorded seismicity patterns.
-\citet{Lapajne1997} used spatially smoothed seismicity modeling to acquire a seismic hazard outlook in Slovenia.
-They defined 4 different models with different correlation distances, including a model based of the total released seismic energy.
-They gained an acceptable PGA in comparison with other seismic hazard approaches.
-\citet{Akinci2004} estimate the seismic hazard in central and northern Italy using smoothed historical seismicity.
-Their results showed that the smoothed seismicity approach gives reasonable regionalized results without introducing seismogenic zones.
-This approach has also been used in many regions with different seismicity patterns \citep{Wesson1999, Klein2001, Hamdache2008, Kalkan2009, Moschetti2014, Boyd2008}.
-%
-%\subsection{Analysis Method}
-%\subsubsection{smoothed seismicity method}
-%To calculate the seismic hazard, we use spatially smoothed seismic hazard analysis \citep{Frankel1995}.
-In this model, seismic events are spatially gridded to cells.
-We are attempting to assess the relative likelihood of moderate earthquakes ($M_w > 4.5$), which cause structural damage.
-According to \citet{Frankel1995}, moderate earthquakes generally occur in areas that there have been significant numbers of events of magnitude 3 and above.
-Therefore, these events provide a reasonable guide to where moderate earthquakes will most likely occur.
-Since the catalog's completeness for $M3+$ and $M4+$ is different, we use two magnitude completeness range for less than $M_ w5$ .
-Category 5+ and others ($M6+$ and $M7+$) assume that future $M_w 4.5$ events will occur near where they have occurred in the past.
-\\
-%\noindent
-%According to Building and Housing Research Center  \citep{BHRC2014}, $M_w5$ is considered as a threshold magnitude to structural damage.
-In the smoothed seismicity method, the model uses each event location as a point source, hence $M_w4.5$ could be damaging earthquake for old masonry buildings or even engineering building if it is very close to it, in this study, in order to consider the probabilistic seismic hazard of both models, we defined two models based on $M_w 5$ and $M_w 4.5$ as a threshold magnitude for seismic hazard calculation.
-\\
-%\noindent
-%\noindent
-%In order to calculate the annual rate ($\lambda$) of exceeding ground motion ($u$) at a specific site, according to \citet{Frankel1995}, first we need to divide the region into cells (0.1*0.1) and count all earthquake events which are bigger than $M_{ref}$ in each cell.
-We use Herrmann formula \citep{Herrmann1977} to convert the cumulative (i.e.
-number of events bigger than $M_{ref}$) values to incremental (i.e.
-number of events from$M_{ref}$ to $M_{ref}+\Delta_m$) values.
-Using Gaussian function we smooth the number of events in each cell.
-The smoothed value $\tilde{n}_i$ is obtained from
-%
-%\begin{equation}
-%\tilde{n_i}=\frac{\sum_{j} n_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}}{\sum_{j} e^{\frac{-\Delta_{ij}^{2}}{c^2}}},
-%\end{equation}
-%
-%\noindent
-%where,  $\tilde{n}_i$  is normalized to preserve the total number of events.
-$\Delta{_i{_j}}$ is the distance between the $i{_t{_h}}$ and $j{_t{_h}}$ cell.
-The sum is calculated over cells $j$ within a distance of $3c$ of cell $i$.\\
-%\noindent
-%Then we discretized the magnitude and distance in uniform bins and get the total number of Normalized, smoothed events ($N_k$) inside the certain distance increment.
-%Having ($N_k$) and $T$ (catalog time duration that we calculated $N_k$ within that duration), we can calculate the annual rate  $\lambda (u> u_0 )$ of exceeding ground motion according to 
-%
-%\begin{equation}
-%\begin{split}
-%\lambda(u>u_{0}) = \sum_{k}\sum_{l}10^{[log(\frac{N_{k}}{T}-b(M_l-M{_r{_e{_f}}}))]} \\
-%p(u>u_0 | D_k ,M_l),
-%\end{split}
-%\end{equation}
-
-%\noindent
-%where $k$ and $l$ are denoted as index of distance and magnitude bin.
-$P(u>u_0 | D_k,M_l )$ is the probability that for an earthquake at distance $D_k$ with magnitude $M_l$, u at the site will exceed  ground motion $u_0$.
-This probability depends on the attenuation relation and the standard deviation (aleatory variability) of the ground motion for any specific distance and magnitude \citep{Frankel1995}

### 2016-07-15 introduction.tex
finished making changes requested by cramer

@@
 While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to reduce the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
-In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh; but for completeness, we also consider the partial contribution of the areas of Zagros and the central-east seismic zones within our domain of interest (see Fig.~\ref{fig:iran}).
-In addition, for comparison purposes, we obtain results for the the combination of all seismic zones as a uniform region.
+In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}).
+In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone.
+We used both these models and the combination of them to interpret seismic hazard in northern Iran.
 
-In the following sections we describe in greater detail our region of interest, review the associated tectonics and seismicity, and provide additional information about the adopted approach.
-Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness, the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions using different magnitude thresholds.
-We analyze our results in light of equivalent estimations available in the literature and summarize relevant conclusions.
-
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
-% Pieces of text in original introduction that could or should be used later
-% --------------------------------------------------------------------------
-
-% \citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the HAZUS method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-
-% Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-
-% An important aspect of seismic hazard is the proper definition of attenuation parameters.
-In a recent effort, \citet{Zafarani2014} reviewed multiple ground motion prediction equations available in the literature and concluded that the most appropriate attenuation relationship to be used in northern Iran was \citet{Kallan2004}
-
-% \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-
-% In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-
-% Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-
-% We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $M_w$ 4.5 as a threshold for structural damage.
-
-% The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
-
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
-% Naeem's original Introduction
-% -----------------------------
-
-% Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-The occurrence of these earthquakes has imposed notable destruction to the buildings and lifelines, and unfortunately, has caused extensive loss of human life.
-These earthquakes are categorized in various tectonic seismic zones.
-Different tectonic seismic regions have been defined for Iran in different studies.
-Some of these studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Regarding the other tectonic seismic regions, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Northern Iran has many highly populated cities (e.g., Tehran, Tabriz, and Mashhad), in which many destructive earthquakes have been reported.
-
-% In the last three decades, different seismic hazard analysis studies \citep[e.g.,][]{Tavakoli1999,Ghodrati2003} substantially improved the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-\citet{Ghodrati2013} conducted a seismic risk assessment for the city of Tehran using the HAZUS method \citep{FEMA2003}.
-They represent that these efforts successfully decrease the total mean damage ratio in Tehran from 0.302739 in 1996 to 0.272859 in 2006.
-Even though the results are satisfactory, the continuous improvement of procedures for defining the seismic hazard at regional (national) and local levels is essential for the optimum design of earthquake-resistant structures.
-In this study we use another model to overcome the aleatory and epistemic uncertainties regarding earthquake location and source mechanism in northern Iran.\\
-
-% In this study we used smoothed seismicity approach \citep{Frankel1995} in order to do seismic hazard analysis.
-We divided northern Iran in three seismotectonic regions including Azerbaijan, Alborz, and Kopeh Dagh.
-We also consider seismicity of part of Central-East Iran and Zagros regions.
-We computed seismic parameters and catalog completeness in these regions.
-Zagros and Central Iran seismotectonic regions have considerable effect on the Northern part.
-We consider the $Mw \  5$ earthquake as a threshold magnitude  for structural damage.
-In order to consider damage to the historical masonry building (which includes most part of big cities and rural areas) we also considered $Mw \  4.5$ as a threshold for structural damage to these kind of building.
-
-% Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one mainshock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
-Recorded events and a partially quiet period suggest that strong earthquakes must be expected in Alborz within the next decade, which may cause significant damage to northern Iran.
-Using newly recorded data, \citet{Zafarani2014} defined the most appropriate attenuation relationship for use in the Azerbaijan, Alborz and Kopeh-Dagh regions.
-In this study we use an updated catalog and the recently confirmed attenuation relationship for northern Iran \citep[i.e.,][]{Kalkan2004} in order to conduct seismic hazard analysis from background seismicity.
-We follow \citet{Frankel1995} approach to calculate hazard from background seismicity for northern Iran.
-This differs from the traditional approach in which area source zones are drawn around seismicity or tectonic provinces for the calculation of seismic hazard \citep{Cornell1968}.
-
-% Having limited knowledge in seismic sources, \citet{Frankel1995} used this approach to map seismic hazards in central and eastern United States.
-The major features of Frankel's approach are to abandon tectonic seismic zones and to use point sources in seismic hazard analysis.
-This method is simpler for hazards calculation and is based solely on recorded seismicity history.
-In the smoothed-seismicity approach we avoid choosing zone boundaries that are sometimes poorly delineated by data and drawn by subjectively merging geological and seismological information.
-Even though probabilistic seismic hazard involving fault sources is more realistic and accurate, recognizing sources could present considerable uncertainty.
-\citet{Masson2006} studied 19 points of the GPS network that have been installed in the framework of French-Iranian cooperation.
-At some stations (e.g., the ATTA station) they expect to record significant movement, based on the region's historical activity.
-Surprisingly, they recorded velocity of $0\  mm/yr$.
-
-% The smoothed-seismicity method simply assumes that patterns of historical earthquakes predict future activity.
-We generate maps of peak ground acceleration with 2\% and 10\% probabilities in exceedance of 50 years in northern tectonic seismic zones, including Azerbaijan, Alborz, and Kopeh-Dagh and in central-eastern Iran and a small portion of the northern Zagros region.
-Since we do not introduce faults into the model, our results show variability due only to the characteristics of seismicity and ground motion.
+In the following sections we describe our region of interest in greater detail, review its associated tectonics and seismicity, and provide additional information about the adopted approach.
+Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness and the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude $M_w /geq 5$.
+We analyze our results in light of similar estimates available in the literature and summarize the most relevant conclusions.

### 2016-07-15 parameters.tex
finished making changes requested by cramer

@@
 In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
-That is, we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
+We call this the \textit{R Model}.
+In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
 In the second model we consider the whole study area as a uniform seismic zone.
-Admittedly, this assumption is unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
-Computing results for this uniform model is, nonetheless, useful for the analysis of results and comparisons with other studies.
-Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones and the uniform regional model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
-
-% *********************************************************************************************************************
-% OLD
-% *********************************************************************************************************************
-
-% For each of the three seismic regions, Gutenberg-Richter parameters and maximum magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in each grid cells.
-
-% \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, 4.5, 4.5, and 4.4 for Azerbaijan, Alborz,  Kopeh-Dagh, Central Iran, and Zagros tectonic seismic regions, respectively.
-For the uniform model we used 4.5 as a completeness magnitude.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of \citet{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table \ref{tab:b_value}.
-Annual occurrence rate of the earthquake for each region is shown in Fig.~\ref{fig:annual_m}.
-
-% *********************************************************************************************************************
-% OLDER
-% *********************************************************************************************************************
-
-% For each of the three seismic regions, Gutenberg-Richter parameters and Max magnitude ($M_{max}$) were calculated using Seismic Hazard Assessment code (HA3) \citep{kijko2004}.
-The regional maximum magnitude for each region is estimated by the \citet{Kijko1989} method, which is implemented in the HA3 package.
-For smoothed seismicity areas, $b-value$ is assumed constant.
-The $a-value$ can vary spatially and is determined by counting earthquakes above $M$ 3.0 in grid cells.\\
-
-% \citet{Karimiparidari2013} applied the Maximum Curvature (MAXC) technique \citep{Wyss1999, Wiemer2000} by ZMap \citep{Wiemer2001} to calculate the level of completeness of instrumental part of the catalog.
-In this study we use those magnitudes of completeness as the magnitude threshold in the calculation of the seismicity parameters.
-We also used the seismicity parameters of this study \citep{Karimiparidari2013} as the priory information in HA3 code.
-The updated values are displayed in Table 2.
-
-% Following the \citet{Karimiparidari2013}, we assume the catalog is complete for earthquakes with magnitude 4.5, 4.4, and 4.5 for Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions, respectively.
-The completeness of each region can be seen easily from the scatter plot of completeness test.
+We call it the \textit{U Model}.
+Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
+However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to reduce epistemic uncertainty.
+Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.

### 2016-07-15 results.tex
finished making changes requested by cramer

@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-08.pdf} 
-    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability of exceeding earthquake magnitudes $M_w$ 5.5 and 6.5 for (a) the five seismic regions R model and (b) the uniform seismic region U model.}
+    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability for earthquake magnitudes exceeding $M_w$ 5 for (a) the five-seismic regions R model and (b) the uniform seismic region U model.}
     \label{fig:pga}
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-09.pdf} 
-    \caption{Difference between the mean PGA values obtained for the uniform U model results and the corresponding R models for 2 (left) and 10 (right) percent probabilities of exceeding magnitudes $M_w$ 5.5 (top) and 6.5 (bottom).}
-    \label{fig:pgadiff}
+    \caption{Difference between the mean PGA values obtained for the uniform U model results and the corresponding R models for 2 (left) and 10 (right) percent probabilities of exceeding magnitudes $M_w$ 5.}
+    \label{fig:pga.diff}
 \end{figure*}
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf} 
-    \caption{Pending.}
-    % \caption{Expected PGA values throughout the region of interest for 2 and 10 percent probability of exceeding an earthquake magnitude $M_w$ 6.5 using the hazard calculations from the five-region R model and the attenuation relationship plus and minus one standard deviation.}
-    \label{fig:pgastd}
+    \caption{Expected PGA values throughout the region of interest for 2 (left) and 10 (right) percent probability of exceeding an earthquake magnitude $M_w$ 5 using the combined model (R,U) hazard calculations.
+Mean expected values are shown in the middle, whereas the top and bottom frames correspond to the results obtained using plus and minus one standard deviation.}
+    \label{fig:pga.ru.std}
 \end{figure*}
 
-% \begin{figure*}[th!]
-%     \centering
-%     \includegraphics[width=\textwidth]{figures/pdf/figure-11.pdf} 
-%     \caption{Expected PGA values for different combination models.
-(a) Combination of R models for magnitudes $M_w$ 5.5 and 6.5.
-(b) Combination of U models for magnitudes $M_w$ 5.5 and 6.5.
-(c) Combination of R and U models for separate magnitudes $M_w$ 5.5 and 6.5.
-(d) Combination of R and U models, and magnitudes $M_w$ 5.5 and 6.5.}
-%     \label{fig:pgaavgs}
-% \end{figure*}
+\input{table-pga}
 
@@
 
-Using the data, parameters, and procedures described above, we considered different hazard models based on whether we use the five distinct seismic hazard regions or the whole area of interest as a uniform seismic hazard region.
+Using the data, parameters, and procedures just described, we considered two different hazard models based on whether we use the five distinct seismic hazard regions or the whole area of interest as a uniform seismic hazard region.
 We call these the R and U models, respectively.
-We also considered two threshold levels of ground motion for events exceeding magnitudes $M_w$ 5.5 and 6.5.
-We refer to these models with the suffixes 5.5 and 6.5, respectively.
-Each of these are considered under two probabilities of exceedance, at 2 and 10 percent in 50 years, for which we use the prefixes 2 and 10, respectively.
+Using these models we obtained hazard curves and expected pGA values for two two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes $M_w \geq 5$.
 These probabilities correspond to return periods of 475 and 2475 years.
-As an example of the chosen nomenclature, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5.5 in 50 years under the five seismic regions model as the 2R5.5 model results.
+For nomenclature purposes, we use the probabilities as a prefix and the magnitude as a suffix on the model type.
+As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5 in 50 years using the five-regions model as the 2R5, whereas for the case of 10 percent probability of exceeding $M_w$ 5 when using the uniform model we would use the tag name 10U5.
 
-In the distinct regions R models, we computed the probability of exceedance of the ground motion separately for each region and then added their exceedance rates at a given level of ground motion in order to have the contribution of all regions for any given grid point within the region of interest.
+Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events $M_w \geq 5$, or conversely, based on the assumption that smaller events at increasing distances will not drive the hazard of a given site.
+In turn, the 2 and 10 percent probability of exceedance in a 50-years span are considered a standard practice in seismic design, and are the probabilities used in the Iranian building code \citep{BHRC2014}.
+
+In the R models, we computed the probability of exceedance of the ground motion separately for each region and then added their exceedance rates at a given level of ground motion in order to have the contribution of all regions for any given grid point within the region of interest.
 The results are obtained in the form of annual rate of exceedance.
@@
 
-We extract expected levels of ground motion for magnitudes 5.5 and 6.5, based on the assumption that buildings of different construction systems may be vulnerable to different magnitude earthquakes.
-It is natural to anticipate that modern constructions in urban areas in Iran follow current building regulations and are thus well-designed to withstand moderate magnitude earthquakes $M_w$ 4.5--6.5, and to undergo moderate non-life threatening damage during $M_w > 6.5$ events.
-Unconventional constructions in poor city outskirts, rural housing and historical buildings may, however, be vulnerable to $M_w \leq 5.5$, and thus becomes relevant to entertain lower magnitude exceedance levels.
-In turn, the 2 and 10 percent probability of exceedance in a 50-years span are considered a standard practice in seismic design \citep[e.g.,][]{BHRC2014}.
-
-Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship as a measured of gravity (g) throughout the region of interest for the different model combinations.
-As can be expected, the highest levels of ground motion are associated with the 2R5.5 and 2U5.5 models, and the lowest with the 10R6.5 and 10U6.5 models.
-In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region along the border with Turkmenistan, and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
+Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship as a measured of gravity (g) throughout the region of interest for the different models, 2R5, 10R5, 2U5 and 10U5.
+As can be expected, the highest PGA values are associated with the 2R5 and 2U5 models, and the lowest with the 10R5 and 10U5 models.
+In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region (near the border with Turkmenistan), and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
 The Azerbaijan seismic zone does not present equally high levels of expected ground motion.
@@
 In general, the U models exhibit higher levels of expected ground motions when compared to their corresponding R models.
-This is illustrated in Fig.~\ref{fig:pgadiff}, which shows the differences between both set of models, U--R (U minus R).
+This is illustrated in Fig.~\ref{fig:pga.diff}, which shows the difference between both models, U--R (U minus R).
 In this figure, positive values indicate that the U models have larger mean PGA values than the R models.
-As it can be seen, this is true practically throughout the whole region at very low levels, and in particular in the north-central region at a moderate level of up to 0.2 g and most predominantly in the north-western region of Azerbaijan at levels of about 0.2 to 0.5 g.
+As it can be seen, this is true practically throughout the whole region at very low levels, and in particular in the north-central region at a moderate level of up to 0.2 g and more predominantly in the north-western region of Azerbaijan at levels of about 0.2 to 0.45 g.
 
@@
 
-These, of course, are only mean expected levels of ground motion.
-A more complete picture is captured when considering statistical deviations.
-Fig.~\ref{fig:pgastd} shows again the mean PGA for the models 2R6.5 and 10R6.5, but this time along with the marginal values of plus and minus one standard deviation.
+With this in mind, we make the following additional consideration.
+No one model (R or U) can be considered uniquely correct.
+Both carry a certain level of epistemic uncertainty.
+A means to address this is to use combinations of different models to incorporate information from all possible models.
+This would also be true, for instance, if in the future we were to consider other attenuation relationships.
+Here we also computed the expected levels of ground motion for a combination of the R and U models (with equal weights).
+We refer to this as the (R,U) model.
+The results of this combined model are shown in Fig.~\ref{fig:pga.ru.std} in the form of expected mean PGA values, along with the marginal values of plus and minus one standard deviation.
 Here, the standard deviation is carried forward in the calculation from the attenuation relationship and thus affects every grid point differently depending on the added contributions from each region.
 
-The highest expected PGA values are observed in the 2R6.5+STD model with accelerations of higher than 1 g in the Kopeh Dagh region and west of Tehran, and 0.8 g south of the North Tabriz Fault system and in the Zagros region along.
-These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects, such as inelastic deformation of near-surface geotechnical layers which may often contribute to mitigate peak accelerations.
-
-An additional consideration to make here is the fact that any one model cannot be uniquely correct.
-They all carry a certain level of epistemic uncertainty which makes them equally accurate and inaccurate at the same time.
-A means to address the uncertainty intrinsic to each model is to use combinations of different models.
-We consider different types of combinations to aid our analysis.
-First, we combine results at in the R and U models independently by averaging the two magnitude results.
-These combinations follow the hypothesis that in areas where mixed reinforced and unreinforced buildings are present, the hazard and associated expected ground motions will be an average of both magnitude thresholds.
-Fig.~\ref{fig:pgaavgs}a shows the result of this combination for the R models and Fig.~\ref{fig:pgaavgs}b shows the result for the combined U models.
-Second, we consider the combination of the two underlying hazard models R and U for the separate magnitude levels.
-These results are shown in Fig.~\ref{fig:pgaavgs}c.
-Last, we consider an overall combination of both hazard models and magnitude thresholds, as shown in Fig.~\ref{fig:pgaavgs}d.
-
-These figures show interest results.
-Combining the two magnitude levels in either the R or U models (Figs.~\ref{fig:pgaavgs}a and \ref{fig:pgaavgs}b) does not have a significant impact other than finding a middle point in between the two ``slices'' taken at the corresponding hazard curves of all the individual grid points.
-For that matter, defining a threshold at $M_w$ 6.0 is almost equivalent and becomes only a matter of choice.
-Combining both R and U models, and the two magnitude results (Fig.~\ref{fig:pgaavgs}d), on the other hand, oversmooths the results and eliminates some of the detail desirable in this kind of analysis.
-It is therefore the combination of the R and U models, but at the separate magnitude thresholds (Fig.~\ref{fig:pgaavgs}c) the one that offers the most plausible scenario.
-These combinations are the ones that best match the visual inspection of the seismicity of the region (shown in Fig.~\ref{fig:catalog}) and follow the major faults (shown in Fig.~\ref{fig:selected}a), while also bringing into the picture the regional background seismicity of moderate magnitude earthquakes.
-That is, in the combinations shown in Fig.~\ref{fig:pgaavgs}c one can clearly observe the contribution of the North Tabriz Fault system in the Azerbaijan region, the contribution of the Piranshahr and Morvarid faults in the Zagros region, and that of the different faults in the Alborz and Kopeh Dagh regions.
-
-\input{table-pga}
-
-We also note that the overall distribution of PGA values shown in Fig.~\ref{fig:pgaavgs}c are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}.
-These estimates also agree, on average, with other previous studies.
-For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.2 and 0.4 g.
-The results from \citet{Vafaie2011} for the city of Tabriz, on the other hand, are slightly higher than the averages shown in Fig.~\ref{fig:pgaavgs}c and are closer to those we present in Fig.~\ref{fig:pga}b, which are in the order of 0.8 and 0.6 g for the models 2U5.5 and 10U5.5.
-In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.2 and 0.35 g, which are closer to the values reported by \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.3 g.
-Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also of the same order of those we show in Figs.~\ref{fig:pga} and \ref{fig:pgaavgs}c.
-Finally, for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the northeast province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.
+As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a, and thus we consider it to be a better assessment of the seismic hazard in the region.
+It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the Piranshahr and Morvarid faults in the Zagros region and that of the different faults in the Alborz and Kopeh Dagh regions.
+In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the 2(R,U)5+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of city of Tabriz.
+These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigate peak accelerations.
 
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-11} 
-    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the four basic models considered in this study, namely R5.5, R6.5, U5.5 and U6.5.}
+    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R5 and U5, and the combined model (R,U)5.}
     \label{fig:hazardcurve}
 \end{figure*}
+
+We also note that the overall distribution of mean PGA values shown in the middle panels in Fig.~\ref{fig:pga.ru.std} are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}.
+These estimates also agree, on average, with other previous studies.
+For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.35 and 0.5 g in the 10(R,U)5 model.
+Similarly, for the particular case of the city of Tabriz, \citet{Vafaie2011} obtained slightly higher expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\%, respectively, where our mean values are about 0.53 and 0.36 g for the same corresponding probabilities.
+In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.50 and 0.30 g, for 2 and 10\% respectively.
+The latter estimate is in good agreement with \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.27--0.31 g for 10\% probability of exceedance.
+Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also on the same order of those shown in Fig.~\ref{fig:pga.ru.std}.
+Finally, for the city of Bojnurd in the northeast province of Khorasan in the Kopeh Dagh seismic region, \citet{Rahgozar2012} reports expected PGA values in the ranges of 0.28--0.49 and 0.15--0.22 g for 2 and 10\%, where we obtain mean values of 0.51 and 0.34 g, respectively.
+
+Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
+As mentioned before, overall, our results are close or within the ranges from most studies.
+The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad, where their results are closer to those of our upper (+STD) range of values.
+Although not included here for brevity, we also computed expected PGA values for a magnitude thresholds $M_w$ 4.5.
+In that case, our results are closer to those of \citet{Golara2014}, but begin to deviate from the rest.
+We should note that, in general, the smoothed seismicity method used here tends to lead to lower hazard estimations than those obtained using specific fault definitions (as opposed to point sour\-ces), and thus is sensitive to the appropriate selection of the magnitude threshold.
+
+Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA.
+The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the two basic models R5 and U5 and the combined model (R,U)5.
+In each case we also show the range $\pm 1$ standard deviation (shaded areas).
+These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance.
+Minor differences are also present in the results of the central cities of Karaj and Tehran, whereas for the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones, the R and U models yield similar if not equivalent hazard estimates.
+This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pga.diff} and \ref{fig:pga.ru.std}.
 
@@
 
-Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
-As mentioned before, overall, our results are close or within the ranges from most studies.
-The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad.
-This is likely due to the authors working with lower magnitude thresholds (not clearly reported) than other studies where hazard is usually estimated based on earthquake magnitudes exceeding $M_w > 5$.
-Although not included here for brevity, we also computed expected PGA values for magnitude thresholds $M_w$ 4.5 and 5.0.
-We found the former case to yield results closer to those of \citet{Golara2014}, but not to the other studies.
-Using lower magnitude thresholds may be of relevance if evaluating poorly constructed and unreinforced buildings vulnerable to low-to-moderate magnitude earthquakes.
-We should also note that, in general, the smoothed seismicity method used here tends to lead to lower hazard estimations than those obtained using specific fault definitions (as opposed to point sour\-ces).
-
-Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA.
-The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the four basic models R5.5, R6.5, U5.5 and U6.5.
-In each case we also show $\pm 1$ standard deviation (shaded ranges).
-These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance.
-Minor differences are also present in the results of the central cities of Karaj and Tehran, whereas for the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones, the R and U models yield similar hazard levels.
-This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pgadiff} and \ref{fig:pgaavgs}.
-
 Last, we put additional attention on the results for the capital city of Tehran.
 We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015}.
-Our results are similar to those obtained by \citet{Ghodrati2003} between 0.4 and 0.8 g (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-3}$), but we obtain lower probabilities for the ground motion amplitudes between 0.1 and 0.4 g, and higher probabilities for very low ($<0.1$ g) and much higher PGA ($>0.8$ g) values.
-These differences with \citet{Ghodrati2003}, nonetheless, are still within our levels of uncertainty.
-A similar interpretation can be made for the comparison with \citet{Boostan2015} for low PGA values ($<0.4$ g), but the trajectory of their hazard curve suggests much higher probabilities of exceeding PGA values above 0.6 g, which is contrary to our findings.
-
-% ==================
-% OLD STUFF NOT USED
-% ==================
-
-% The results are presented as annual rate of exceedance.
-
-% Regarding the study domain and the 0.1 grid size, the total number of source as grid points is 13561.
-
-% Regarding the study domain and the 0.1 grid size, the total number of source is grid sites is 11651.
-
-% Even though \citet{Kalkan2004} derived the attenuation relationship up to 250 km, since \citet{Zafarani2014} used data up to 200 km to evaluate the GMPEs, we set the model to compute the ground motions at distances of less than 200 km.
-
-% We pick the peak ground acceleration for 10\% and 2\% probability of exceedance in 50 years which correspond with 0.002 and 0.0004 annual rate of exceedance.
-
-% \citet{Abdollahzadeh2014a} carried out a probabilistic seismic hazard assessment for part of Northern Iran.
-They used the logic tree approach to capture the epistemic uncertainty of seismic hazard assessment in delineation of seismic sources and selection of attenuation relationship.
-They used three attenuation relationships and 2 seismic source models.
-They collected the earthquake catalog from various references and reported the pga for 475 and 2475 years of return period for northern cities.
-
-% \citet{Golara2014} conducted a probabilistic seismic hazard analysis of interconnected infrastructure of Iranian high pressure gas supply system.
-He used line and area source model in order to estimate the Iranian  high-pressure gas supply system's ability to withstand a sudden large ground movements caused by potential earthquakes and related phenomenon that might be expected.
-he used simplified tectonic map after \citet{Alavi1991}.
-He used four attenuation relationships and presented the results for 2475 years of return period.
-
-% The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger.
-In this study we used two models for seismic hazard calculation, including $M_w>5$ and $M_w>4.5$.
-$M_w$ is the minimum magnitude that can affect the engineering site.
-
-% In the probabilistic seismic hazard analysis increasing minimum magnitude will decrease the mean rate of earthquake occurrence ($\nu=exp(\alpha - \beta M_0)$), and also increase the value for the probability density function in the initial magnitudes.
-In a simple source the difference between different models specially in higher pga levels is negligible.
-However, in this study where we consider each event as a seismic source with different $\alpha$ and $\beta$ value, the results are considerably different.
-According to our results the reduction of the mean rate of earthquake occurrence has considerable effect on the results.
+Our results are similar to those obtained by \citet{Ghodrati2003} in the range between 0.2 and 0.7 (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-2}$), but the trend indicates we would obtain increasingly higher probabilities associated with PGA values above 0.8 g.
+Conversely, the trend in the hazard curve from \citet{Boostan2015} suggest the city is to expect significantly higher levels of ground motion at higher probability rates, which is contrary to our findings and those of \citet{Ghodrati2003}.

### 2016-07-18 abstract.tex
edits suggested by Naeem

@@
 Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region.
-We also consider the combination ot these two basic models.
-The results are presented in terms of expected peak ground acceleration maps and hazard curves at select locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+We also consider the combination of these two basic models.
+The results are presented in terms of expected peak ground acceleration maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
 We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.

### 2016-07-18 introduction.tex
edits suggested by Naeem

@@
 Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness and the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude $M_w /geq 5$.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude $M_w \geq 5$.
 We analyze our results in light of similar estimates available in the literature and summarize the most relevant conclusions.

### 2016-07-18 results.tex
edits suggested by Naeem

@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-08.pdf} 
-    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability for earthquake magnitudes exceeding $M_w$ 5 for (a) the five-seismic regions R model and (b) the uniform seismic region U model.}
+    \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability of exceedance in 50 years for (a) the five-seismic regions R model and (b) the uniform seismic region U model.}
     \label{fig:pga}
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-09.pdf} 
-    \caption{Difference between the mean PGA values obtained for the uniform U model results and the corresponding R models for 2 (left) and 10 (right) percent probabilities of exceeding magnitudes $M_w$ 5.}
+    \caption{Difference between the mean PGA values from models U and R for 2 (left) and 10 (right) percent probabilities of exceedance in 50 years.}
     \label{fig:pga.diff}
@@
 We call these the R and U models, respectively.
-Using these models we obtained hazard curves and expected pGA values for two two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes $M_w \geq 5$.
+Using these models we obtained hazard curves and expected PGA values for two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes $M_w \geq 5$.
 These probabilities correspond to return periods of 475 and 2475 years.
-For nomenclature purposes, we use the probabilities as a prefix and the magnitude as a suffix on the model type.
-As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5 in 50 years using the five-regions model as the 2R5, whereas for the case of 10 percent probability of exceeding $M_w$ 5 when using the uniform model we would use the tag name 10U5.
+For nomenclature purposes, we use the probabilities as a suffix on the model type.
+As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5 in 50 years using the five-regions model as the R2, whereas for the case of 10 percent probability of exceedance when using the uniform model we would use the tag name U10.
 
@@
 
-Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship as a measured of gravity (g) throughout the region of interest for the different models, 2R5, 10R5, 2U5 and 10U5.
-As can be expected, the highest PGA values are associated with the 2R5 and 2U5 models, and the lowest with the 10R5 and 10U5 models.
+Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship as a measured of gravity (g) throughout the region of interest for the different models, R2, R10, U2 and U10.
+As can be expected, the highest PGA values are associated with the R2 and U2 models, and the lowest with the R10 and U10 models.
 In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region (near the border with Turkmenistan), and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
@@
 It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the Piranshahr and Morvarid faults in the Zagros region and that of the different faults in the Alborz and Kopeh Dagh regions.
-In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the 2(R,U)5+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of city of Tabriz.
+In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of city of Tabriz.
 These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigate peak accelerations.
@@
 Similarly, for the particular case of the city of Tabriz, \citet{Vafaie2011} obtained slightly higher expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\%, respectively, where our mean values are about 0.53 and 0.36 g for the same corresponding probabilities.
-In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.50 and 0.30 g, for 2 and 10\% respectively.
+In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 g for Tehran, where we found equivalent results to be about 0.25--0.35 g for a 10\% probability of exceedance.
 The latter estimate is in good agreement with \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.27--0.31 g for 10\% probability of exceedance.
@@
 The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad, where their results are closer to those of our upper (+STD) range of values.
-Although not included here for brevity, we also computed expected PGA values for a magnitude thresholds $M_w$ 4.5.
-In that case, our results are closer to those of \citet{Golara2014}, but begin to deviate from the rest.
-We should note that, in general, the smoothed seismicity method used here tends to lead to lower hazard estimations than those obtained using specific fault definitions (as opposed to point sour\-ces), and thus is sensitive to the appropriate selection of the magnitude threshold.
+
+% ***
+
+% Although not included here, we also computed expected PGA values for a magnitude threshold $M_w$ 4.5.
+In that case, our results are closer to those of \citet{Golara2014}, but deviate from the rest.
+In general, the smoothed seismicity method tends to lead to lower hazard estimations than those obtained using specific fault definitions (as opposed to point sources) where the concept of a threshold becomes unnecessary and the hazard, and thus is sensitive to the appropriate selection of the magnitude threshold.
+
+% ***
 
 Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA.
-The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the two basic models R5 and U5 and the combined model (R,U)5.
+The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the two basic R and U models and the combined (R,U) model.
 In each case we also show the range $\pm 1$ standard deviation (shaded areas).
@@
 We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015}.
-Our results are similar to those obtained by \citet{Ghodrati2003} in the range between 0.2 and 0.7 (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-2}$), but the trend indicates we would obtain increasingly higher probabilities associated with PGA values above 0.8 g.
+Our results are similar to those obtained by \citet{Ghodrati2003} in the range between 0.2 and 0.7 g (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-2}$), but the trend indicates we would obtain increasingly higher probabilities associated with PGA values above 0.8 g.
 Conversely, the trend in the hazard curve from \citet{Boostan2015} suggest the city is to expect significantly higher levels of ground motion at higher probability rates, which is contrary to our findings and those of \citet{Ghodrati2003}.

### 2016-07-19 attenuation.tex
implemented last set of changes by cramer

@@
 We should note here that even though \citet{Kalkan2004} derived the above attenuation relationship for distances $r$ up to 250 km, \citet{Zafarani2014} only used data up to 200 km in their evaluation of the various GMPEs available.
-Therefore, in consistence with the latter, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.
+Therefore, to be consistent with the latter, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.

### 2016-07-19 compilation.tex
implemented last set of changes by cramer

--- 2016-07-15 composition.tex
@@
 
-\subsection{Composition}
+\subsection{Compilation}
 
-The first fundamental step in regional seismic hazard analysis is the composition of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
+The first fundamental step in regional seismic hazard analysis is the compilation of a reliable seismic catalog that includes both historically documented and instrumentally recorded earthquakes.
 Nowadays, instrumental datasets are easily accessible through international, regional, and local agencies.
 Historical data, on the other hand, lends itself to subjective interpretation.
-Notable previous efforts to compose uniform earthquake catalogs for Iran include but are not limited to \citet{Ambraseys_1982_Book}, \citet{moinfar1994}, and \citet{Berberian_1995_Tech}.
+Notable previous efforts to compile uniform earthquake catalogs for Iran include but are not limited to \citet{Ambraseys_1982_Book}, \citet{moinfar1994}, and \citet{Berberian_1995_Tech}.
 These studies, however, differ from each other in their use of magnitude scales or magnitude conversion rules, and the extent to which they accept historical accounts as valid data.
@@
 
-In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and complement it for our particular region of interest.
+In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and augment it for our particular region of interest.
 This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
@@
 For the particular case of our region of interest, the catalog prepared by \citet{Zare2014} included events $M_w \geq 4$ between 550 B.C.~and 2006.
-We took information from the catalog up to December 1999, and complemented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes.
+We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}.
 By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar catalog for events $M_w \geq 4$ but only included data through 2011, excluding the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.
@@
 Selection and declustering was also done in a manner consistent with the original catalog, using the method of \citet{Gardner1974}.
-In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks.
+In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, augmented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new catalog removing foreshocks and aftershocks.
 The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}, which includes the spatial distribution within the region of interest for both historical and instrumental events; and in Fig.~\ref{fig:scatter}, which presents the distribution of events in time and magnitude for each of the seismic zones, as well as for the complete region of interest (hereafter referred as the uniform model).

### 2016-07-19 completeness.tex
finished making changes requested by cramer
implemented last set of changes by cramer

@@
 The values shown in this figure and those corresponding to the uniform model of the entire region of interest are summarized in Table \ref{tab:completeness}.
-For events $M_w>7$, in which case there are no sufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
+For events $M_w>7$, in which case there are insufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
 
@@
 
-The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), and the $M_c$ values for the whole regional catalogs and the start-years of completeness are used later for computing the hazard.
+The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), and the $M_c$ values for the complete regional catalogs and the start-years of completeness are used later for computing the hazard.
 Admittedly, the choice of the start-years is highly subjective.
@@
 \end{table*}
-
-% *********************************************************************************************************************
-% OLD STUFF
-% *********************************************************************************************************************
-
-% A common approach consists on identifying the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve.
-
-% One of the difficulties in determining completeness is the availability of data for a period of time long enough for all magnitude ranges, so that selection of completeness parameters is reliable.
-
-% Our choice the $M_c$ values by \citet{Karimiparidari2013} over those of \citet{Zare2014} is based on the fact that the former distinguishes Azerbaijan and Alborz as individual seismic zones---as we do---as opposed to the approach followed by the latter, in which these two are a single, larger seismic zone.
-Both the chosen years of completeness and the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest are ....
-
-% For the smoothed seismicity method, completeness of each magnitude in the catalog is an important factor.
-\citet{Frankel1995} plotted the cumulative number of events against time for different regions.
-He assumes that from the point that the line become linear, the catalog is complete.
-This approach is similar to the MAXC method of ZMAP software \citep{Wiemer2001}, where the completeness treshold is the maximum value of the first derivative of the frequency-magnitude curve.
-
-% Using the cumulative frequency-magnitude distribution of \citet{Gutenberg1944} and also frequency magnitude distribution approach in software ZMAP, \citet{Zare2014} reported the catalog completeness for the study regions.
-
-% World widely large earthquakes were routinely located after increasing number of seismic stations establishment in the early 1900s \citep{Shearer2009}.
-Up to 1961 these data formed the early instrumental period.
-In 1961 the Worldwide Standardized Seismograph Network (WWSSN) was stablished.
-The record of these seismographs considerably improved the seismic catalogs in different part of the world \citep{Shearer2009}.
-Fig.~\ref{fig:completness_scatter} shows the magnitude distribution of events with respect to the time of occurrence of the events.
-
-% We pick the Mw 0.5 increments in magnitude to be able to compare the results with \citet{Zare2014}.
-In order to be able to compare the results with \citet{Zare2014} we merge the data of Azerbaijan and Alborz seismic regions.
-Fig.~\ref{fig:completness_compare_zare_2014_Az_Al} shows the completeness of catalog for earthquakes with different magnitude range in Azerbaijan-Alborz region.
-According to this figure, midrange magnitudes ($ 4 < Mw < 6 $) fairly obey the network developments in 1900 and 1961.
-The completeness thresholds for each magnitude range which are reported by \citet{Zare2014} are shown by dashed green line.
-
-% In this study we follow the \citet{Frankel1995} approach to determine the completeness of each region.
-Even though the approach used by \citet{Frankel1995} will lead to the conservative results, we make sure that we don't use a period of time without knowing the complete number of events.
-Determining the completeness of the catalog is very sensitive to the data.
-Converting earthquake magnitudes from different scales to moment magnitude obviously has some error.
-Having broader range of magnitude will help to minimize these sort of error.
-In this study we consider the magnitude intervals for completeness study as $Mw = 1$.

### 2016-07-19 hazard.tex
implemented last set of changes by cramer

@@
 It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
-We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having complemented the earthquake catalog for events above this threshold.
+We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.
 
@@
 By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within large grid-cells of size 1\textdegree{} $\times$ 1\textdegree{} based on the average seismicity within a 200-km radius from each cell.
-While gridding $b$-values and considering the influence of neighboring large-size cells allows to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may pollute the computation of $b$-values.
+While gridding $b$-values and considering the influence of neighboring large-size cells allows to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may bias the computation of $b$-values.
 Admittedly, these are subjective decisions and any reasonable choice can be considered valid or within the margins of the associated epistemic uncertainty.

### 2016-07-19 results.tex
implemented last set of changes by cramer

@@
 For nomenclature purposes, we use the probabilities as a suffix on the model type.
-As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5 in 50 years using the five-regions model as the R2, whereas for the case of 10 percent probability of exceedance when using the uniform model we would use the tag name U10.
+As an example, we refer to the results for 2 percent probability of exceedance in 50 years using the five-regions model as the R2, whereas for the case of 10 percent probability of exceedance when using the uniform model we use the tag name U10.
 
@@
 
-Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship as a measured of gravity (g) throughout the region of interest for the different models, R2, R10, U2 and U10.
+Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship in units of gravity (g) throughout the region of interest for the different models, R2, R10, U2 and U10.
 As can be expected, the highest PGA values are associated with the R2 and U2 models, and the lowest with the R10 and U10 models.
-In results for the R models shown Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region (near the border with Turkmenistan), and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
+For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region (near the border with Turkmenistan), and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
 The Azerbaijan seismic zone does not present equally high levels of expected ground motion.
-In the U models shown in Fig.~\ref{fig:pga}b, on the other hand, the highest levels of expected ground motion are observed precisely in the area corresponding to the Azerbaijan seismic region, especially in the vicinity of the North Tabriz Fault system (see Fig.~\ref{fig:selected} for reference).
+For the U model results shown in Fig.~\ref{fig:pga}b, on the other hand, the highest levels of expected ground motion are observed precisely in the area corresponding to the Azerbaijan seismic region, especially in the vicinity of the North Tabriz Fault system (see Fig.~\ref{fig:selected} for reference).
 
@@
 In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of city of Tabriz.
-These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigate peak accelerations.
+These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigating peak accelerations.
 
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-11} 
-    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R5 and U5, and the combined model (R,U)5.}
+    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U).}
     \label{fig:hazardcurve}
@@
 These estimates also agree, on average, with other previous studies.
-For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.35 and 0.5 g in the 10(R,U)5 model.
+For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.35 and 0.50 g in the (R,U)10 model.
 Similarly, for the particular case of the city of Tabriz, \citet{Vafaie2011} obtained slightly higher expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\%, respectively, where our mean values are about 0.53 and 0.36 g for the same corresponding probabilities.
@@
 As mentioned before, overall, our results are close or within the ranges from most studies.
-The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad, where their results are closer to those of our upper (+STD) range of values.
+The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher than the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad, where their results are closer to those of our upper (+STD) range of values.
 

### 2016-07-20 completeness.tex
implemented edits suggested by Shima

@@
     \includegraphics[width=0.8\textwidth]{figures/pdf/figure-05.pdf} 
-    \caption{Normalized cumulative number of events and completeness year thresholds for each of the seismic zones considered within the region of interest, and for magnitude intervals of $\Delta M = 1$ between $M_w$ 3 and 6.
+    \caption{Normalized cumulative number of events and completeness year thresholds for each of the seismic zones considered within the region of interest, and for magnitude intervals of $\Delta M = 1$ between $M_w$ 3 and 7.
 The year thresholds are indicated by a triangle mark at the top and the vertical dashed lines in the background.

### 2016-09-21 response.tex
Response letter template and reviosion format added.

\setlength{\paperwidth}{210mm}
\setlength{\paperheight}{297mm}% fixed.

\documentclass{article}

\usepackage[review]{myreviewpckg}
\usepackage{simplemargins}

\clubpenalty=10000  % Orphan - First of paragraph left behind
\widowpenalty=10000 % Widow  - Last of paragraph sent ahead

\setallmargins{1in}

\begin{document}

\begin{center}
	\bf
	\large
	Authors' Response to Reviewer 1 (Anonymous)
\end{center}

\noindent
We thank the reviewer for his/her comments and suggestions, which helped us improve the manuscript. To help the review process, in the annotated manuscript version of the paper, we have highlighted the changes that resulted from these comments in green colored font when appropriate. In the following, we provide a response to each comment. The original comments are in italic black font, followed by our responses in regular blue font.
\vspace{2ex}
\newline

\introcomment{~}{%
Objective of this paper is quantitative evaluation of the validity of the four different 3D velocity structure model in southern California by means of numerical simulation of ground motions from observed earthquakes. They tested 30 moderate sized earthquakes, and showed the GOF in the various presentations including event average and station average. Finally, they concluded that CVMS4.26 yielded the better results among four tested models. Overall, this paper is quite well written, and materials presented in this paper is informative. The results of this paper will benefit to the community. I have some comments to further improve the significance of their study.
}

\comment{1}{%
The authors showed the spatial distribution of GOF on tha mep in Figures 9, 10, 11, and 15. Actual GOF values were obtained only at stations where observed records were available. The authors spatially interpolated GOF values to draw the map. However, I think it is not a good representation of the results. Because the stations were not uniformly distributed, some isolated stations had stronger impact on these maps. It controls the impression of these figures. I think that color representing GOF should be given only inside the symbol (i.e. circle) representing individual stations, and the area without station should not be colored.
}

\response{%
The reviewer brings an important point to the table. We did consider this option in the past---in two previous publications by the leading author---and rejected it. The major issue with the suggested format is that the symbols (e.g., circles) would have to be large enough in order for the colors to be noticeable. This is fine if the stations are sufficiently scattered throughout the domain at somewhat even distances from each other. Unfortunately, that is not the case. A good number of stations are in (very) close proximity to each other---specially in the basin area---and then the size of the symbols becomes an issue. One is then left with no good option. If the symbols are made small enough to avoid overlapping, the color is not visible; and if they are large enough for the color to be noticeable, then they will often overlap. Both options lead to a more difficult interpretation of the results than the imperfect option of the surface interpolation. In addition, as mentioned in the manuscript, the format chosen to present the results in these figures has already been used in two previous publications (Taborda and Bielak, 2013, 2014). This is an advantage because consistency allows one to look back at previous results and appreciate the differences and improvements achieved over the years. Furthermore, this or other similar formats have been used or adopted by other authors (e.g., Olsen and Mayhew, 2010; Lee et al.~2015). All things considered, we have added a comment when presenting the results of the first figure to make explicit the fact that the interpolation is artificial. Please see page 25.
}

\comment{2}{%
As shown in Figures 8 and 9, GOF values for the same station have large deviation. Thus, the information on the standard deviation among events can be added to Figure 15. I think this point is very important in this kind of study, and possible reasons for obtaining large GOF deviation for the same station using the same 3D velocity model needs to be addressed in deep by the authors. Since, the same 3D velocity model are used in the numerical simulation, the validity of source model might affect this comparison. The calibration and validation of the source models should be adequately given in this paper.
}

\response{%
We thank the reviewer for pointing this out. Indeed, the standard deviation at the individual stations is a matter of importance. We had this information at our disposal but did not realize it was worth including it in the manuscript in the form of a figure. We now present this information in the new Figure 16, which illustrates the variance in the average scores obtained for each station in the form of the unbiased sample standard deviation. A comment on the results presented in this new figure is now included in pages 33 and 34.
}

\newpage

\begin{center}
	\bf
	\large
	Authors' Response to Reviewer 2 (Robert Graves)
\end{center}

\noindent
We thank the reviewer for his comments and suggestions, which helped us improve the manuscript. To help the review process, in the annotated manuscript version of the paper, we have highlighted the changes that resulted from these comments in green colored font when appropriate. In the following, we provide a response to each comment. The original comments are in italic black font, followed by our responses in regular blue font.
\vspace{2ex}
\newline

\introcomment{~}{%
This paper presents an analysis of 3D ground motion simulations for 30 earthquakes in the Los Angeles basin region that were computed using four different 3D seismic velocity models. The goal of the analysis is to compare the results obtained with the different models to see which models, or parts thereof, perform better, and to provide a baseline for comparison of future model iterations.
}

\introcomment{~}{%
This paper is very well written, interesting and informative and my view of this work is quite favorable. I think the paper is worthy of publication after some minor revision.
}

\introcomment{~}{%
My main general comment has to do with the use of the word ``validation'' that appears throughout the manuscript. In a number of these instances, I feel it would be more appropriate if the term ``validation'' were replaced with the term ``assessment'' (or something similar, like ``evaluation''). To me, the ``validation'' of something implies it to be true (e.g., I validated your parking permit), whereas the assessment of something simply means it is being analyzed and its performance possibly ranked with respect to something else. Most of what is done in this paper is an assessment of the simulation results, since in the end, none of the velocities models is truly “validated”. This assessment process is nonetheless very important in that it provides a relative measure of the performance of each of the velocity models. I would suggest the authors consider using a different term as they go through the revision of the paper.
}

\response{
We understand and agree, to some extent, with the points raised here by the reviewer. Our intention was to evaluate the models, or assess the model, through a validation of the simulations. We believe the word validation is well used here when referring to the comparisons of the synthetics with data in the same sense in which the terms ``validation'' and ``verification'' has been defined in other publications such as Bielak et al.~(2010) or Taborda and Bielak (2013). That said, the author stands correct in that we may have been abused the use of the word in several instances when we were not being specific about the validation of the individual simulations themselves, but through them, we were actually evaluating the models. In this spirit we have welcomed and adopted most if not all the suggestions by the reviewer in this regard, including the change in the title, which makes it simpler and more to the point. These changes are documented in the answers to the individual comments below.
}

\introcomment{~}{%
A detailed listing of all my specific comments is included in the accompanying marked-up copy of the manuscript.
}

\comment{1}{%
Page 1, title. The phrasing ``validation of recorded events'' does not sound correct. The events are real and the records are true data, therefore they are not being validated (we assume them to be valid). I think the title would be more appropriate if the words ``and Validation'' were removed.
}

\response{The suggested change to the title was adopted.}

\comment{2}{%
Page 2. General comment on the use of the term ``validation''. In a number of places in this paper, I feel it would be more appropriate if the term ``validation'' were replaced with the term ``assessment'' (or something similar, like ``evaluation''). To me, the ``validation'' of something implies it to be true (e.g., I validated your parking permit), whereas the assessment of something simple means it is being analyzed. Most of what is done in this paper is an assessment of the simulation results, which is nonetheless very important in that it provides a relative measure of the performance of each of the velocity models.
}

\response{We introduced a small change in the abstract and other similar changes in several other places throughout the manuscript to better express the essence of the comparisons done in light of the point raised by the reviewer. Also see our response to other comments below.}

\comment{3}{%
Page 4, line 17. Replace with ``collection of recorded''
}

\response{Fixed.}

\comment{4}{%
Page 5, figure 1. Difficult to see the labels ``A'', ``B'' and ``C'' in Figure 1c.
}

\response{The labels are now framed in a circle with white background. This should make them more visible.}

\comment{5}{%
Page 6, line 20--24. I'm not sure what this means. Can you explain further?
}

\response{We eliminated this sentence. A better explanation is out of the scope of the paper and is not of major relevance. We took this opportunity, instead, to make clarity about the fact that the model CVM-S4.26 as used here is in fact a modification of the raw model that resulted from the inversion done on top of CVM-S4. We did this in consultation with colleagues from SCEC to satisfy recent changes in the nomenclature of the models.}

\comment{6}{%
Page 6, line 41. Delete ``In turn''.
}

\response{Done.}

\comment{7}{%
Page 10, line 12. Should be ``BC''.
}

\response{Fixed.}

\comment{8}{%
Page 10, line 38. The event IDs are a unique and vitally important component of the data archival system used by the Southern California Seismic Network. Please add a citation to the Southern California Earthquake Data Center, i.e., SCEDC (2013): SCEDC (2013). Southern California Earthquake Center, Caltech, Dataset, doi:10.7909/C3WD3xH1
}

\response{Citation to SCEDC is now included.}

\comment{9}{%
Page 10, lines 41--43. Is Lee et al. (2011) the correct reference as several of the events occurred after the publication date of this paper? Also, does this mean that all of the events considered in the current analysis were also used in the 3D tomographic inversion to develop CVM-S4.26? And, how many of these events were also used in the 3D tomographic updates to CVM-H?
}

\response{We modified the text to provide a better explanation. Yes, all the events considered here were used in the inversions that led to CVM-S4.26. In total, 17 of the 30 events were also used in the 3D tomographic updates to CVM-H. In addition to the text, we also modified the table to provide information about which of these events were used in CVM-H.}

\comment{10}{%
Page 11, figure 4. Difficult to see the event labels in Figure 4.
}

\response{We change the labels to bold font, which should make them easier to see.}

\comment{11}{%
Page 12, line 58. On the left hand side of the relation, should this be ``$\tau_s$'' instead of ``$t_s$''?
}

\response{Yes. We fixed it.}

\comment{12}{%
Page 15, line 44--45. Replace ``originated'' with ``originating''.
}

\response{Done.}

\comment{13}{%
Page 17, figure 6. The gray contour lines in Figures 6 and 7 mask some of the details. Maybe redo the figures without the gray lines, or use a thinner line.
}

\response{We removed the contour lines in both figures.}

\comment{14}{%
Page 18, lines 46--50. Wording of this sentence is a bit awkward. Maybe redo with something like, ``These three events were selected because their locations sample different paths into the various basins and they are also large enough to generate significant motions throughout most of the simulation domain''.
}

\response{We adopted the suggested wording. Thank you, it does read better.}

\comment{15}{%
Page 19, line 50. Replace ``faults'' with ``fault''.
}

\response{Done.}

\comment{16}{%
Page 19, line 60. I think replacing ``validation'' with ``comparison'' would be more appropriate in this sentence.
}

\response{Agree. We changed it.}

\comment{17}{%
Page 20, line 22. Missing ``)'' at end of sentence.
}

\response{Fixed.}

\comment{18}{%
Page 20, line 35. Delete ``that free surface''.
}

\response{Done. Thanks!}

\comment{19}{%
Page 21, line 6. Replace ``derivate'' with ``differentiate''.
}

\response{Done.}

\comment{20}{%
Page 21, line 58. Should be ``equal to''.
}

\response{Fixed.}

\comment{21}{%
Page 22, lines 7--9. Why not the beginning of the slip function? Admittedly, this is just a small shift.
}

\response{Well... this was a suggestion of many years ago in a SCEC Annual Meeting in conversation with Carl Tape when we (Taborda and Bielak) first worked on the validation simulations of the Chino Hills earthquake. The rationale, as I (Taborda) remember it was based on the half rise-time being a reasonable compromise with respect to uncertainty about the rupture time as registered in the records' metadata. We do not believe it makes a major difference here, where the rise time is rather small for all events, and thus yes, it is admittedly a very small shift. For simulations of larger events with finite source models, however, this may be significant. In our experience with the previous Chino Hills simulations (Taborda and Bielak, 2013, 2014) where a finite source was used, this assumption yielded good results. But perhaps this may need to be evaluated more carefully.}

\comment{22}{%
Page 22, line 54. Replace ``this type'' with ``these types''.
}

\response{Done.}

\comment{23}{%
Page 26, line 47. Maybe ``MODEL'' instead of ``MODELS''.
}

\response{We actually think is appropriate to use the plural here. We will keep it this way unless the editorial team suggests different.}

\comment{24}{%
Page 29, line 35. Replace ``Fig. 11'' with ``Fig. 13''.
}

\response{Done.}

\comment{25}{%
Page 29, line 40. Replace ``is'' with ``are''.
}

\response{Done.}

\comment{26}{%
Page 29, line 53. Replace ``derived'' with ``derived from''.
}

\response{Done.}

\comment{27}{%
Page 31, line 48. Caption of Fig. 15 states only top 20 events are used for average. Please check and correct.
}

\response{The caption of the figure stands correct. We modified the text (now in page 32) to be in agreement with the figure.}

\comment{28}{%
Page 32, line 35. Replace ``even'' with ``event''.
}

\response{Done.}

\comment{29}{%
Page 32, line 36. Replace ``station'' with ``stations''.
}

\response{Done.}

\comment{30}{%
Page 32, line 39. Replace ``dotes'' with ``dots''.
}

\response{Done.}

\comment{31}{%
Page 32, lines 52--54. Maybe replace ``showed to be independent to'' with ``do not correlate with''.
}

\response{We adopted this suggestion. Thanks.}

\comment{32}{%
Page 33, line 12. Change ``not'' to ``no''.
}

\response{Done.}

\comment{33}{%
Page 33, line 13. Change ``the basin's depth'' to ``basin depth''.
}

\response{Done.}

\comment{34}{%
Page 33, line 28. Maybe change ``model'' to ``GTL model'' just for clarity.
}

\response{Yes, thank you.}

\comment{35}{%
Page 33, line 32. I think CVM-S4, and therefore CVM-S4.26, do, in fact, include a GTL model (see Magistrale et al.~2000). It is just not as comprehensive or sophisticated as the Ely Vs30-based GTL approach. My suggestion is to replace ``GTL model'' with ``more comprehensive GTL model''.
}

\response{While we have differences in our understanding of what constitutes a GTL model in a CVM, we recognize that this clearer wording can help the reader, and thus we adopted the suggestion. Thank you.}

\comment{36}{%
Page 33, line 39. Delete ``the region of''.
}

\response{Done.}

\comment{36}{%
Page 33, line 41. Maybe change ``velocity'' to ``seismic velocity'' just for clarity at the beginning of this section.
}

\response{Done.}

\comment{37}{%
Page 33, line 43. Replace ``of fits'' with ``fit''.
}

\response{Done.}

\comment{38}{%
Page 33, line 45. Delete ``simulation''.
}

\response{Done.}

\comment{39}{%
Page 33, lines 54--56. Related to my point in comment \#2, I think this sentence would be more correct if the word ``validation'' were removed.
}

\response{Agree. We removed the word ``validation''.}

\comment{40}{%
Page 34, figure 15 caption. Text states all events are used in average. Please check.
}

\response{See our response to comment 27.}

\comment{41}{%
Page 34, line 44. As long as the input model to the inversion is reasonably good. Which the results here suggest that CVM-S4 is a reasonably good starting model. I think it would be worthwhile to point this out.
}

\response{Agree. We added a note in the conclusions to reflect this.}

\comment{42}{%
Page 35, figure 16 caption. Change ``SC'' to ``SB''.
}

\response{Done.}

\comment{43}{%
Page 35, line 59. Again, I believe that CVM-S4.26 already has some sort of GTL. I suggest modifying the text here to read ``more
detailed geotechnical''.
}

\response{We modified the sentence to adopt this suggestion.}

\comment{44}{%
Page 35, line 60. Delete ``additional''.
}

\response{Done.}

\comment{45}{%
Page 36, line 7. Maybe change ``considering'' to ``possibly including''.
}

\response{Thank you for this suggestion. We changed the wording.}

\comment{46}{%
Page 36, lines 9--11. Change to ``as sufficient data become available''.
}

\response{Fixed.}

\end{document}

### 2016-09-21 response.tex
comments updated.

@@
 	\large
-	Authors' Response to Reviewer 1 (Anonymous)
+	Authors' Response to Reviewer 1 
 \end{center}
@@
 \introcomment{~}{%
-Objective of this paper is quantitative evaluation of the validity of the four different 3D velocity structure model in southern California by means of numerical simulation of ground motions from observed earthquakes.
-They tested 30 moderate sized earthquakes, and showed the GOF in the various presentations including event average and station average.
-Finally, they concluded that CVMS4.26 yielded the better results among four tested models.
-Overall, this paper is quite well written, and materials presented in this paper is informative.
-The results of this paper will benefit to the community.
-I have some comments to further improve the significance of their study.
+The authors perform a seismic hazard analysis for northern Iran using a newly developed source model from smoothed seismicity.
+The work is an important contribution to seismic hazard analyses in Iran.
+Development of the seismic source model follows a careful analysis of the earthquake catalogs for information about spatially varying earthquake rates, maximum magnitudes and b-values.
+The authors are careful to acknowledge that alternative means for estimating earthquake recurrence - and for other components of the source and ground motion characterization - also exist, and that this work is only one approach for characterizing hazard in the region.
 }
@@
 \comment{1}{%
-The authors showed the spatial distribution of GOF on tha mep in Figures 9, 10, 11, and 15.
-Actual GOF values were obtained only at stations where observed records were available.
-The authors spatially interpolated GOF values to draw the map.
-However, I think it is not a good representation of the results.
-Because the stations were not uniformly distributed, some isolated stations had stronger impact on these maps.
-It controls the impression of these figures.
-I think that color representing GOF should be given only inside the symbol (i.e.
-circle) representing individual stations, and the area without station should not be colored.
+Pp3, Line 71: A short, summary description of previous source models would highlight the contribution of this work.
+In particular, summary details of the work by Khodaverdian et al should be included to indicate how the approach of the authors differs from previous work.
 }
@@
 \response{%
-The reviewer brings an important point to the table.
-We did consider this option in the past---in two previous publications by the leading author---and rejected it.
-The major issue with the suggested format is that the symbols (e.g., circles) would have to be large enough in order for the colors to be noticeable.
-This is fine if the stations are sufficiently scattered throughout the domain at somewhat even distances from each other.
-Unfortunately, that is not the case.
-A good number of stations are in (very) close proximity to each other---specially in the basin area---and then the size of the symbols becomes an issue.
-One is then left with no good option.
-If the symbols are made small enough to avoid overlapping, the color is not visible; and if they are large enough for the color to be noticeable, then they will often overlap.
-Both options lead to a more difficult interpretation of the results than the imperfect option of the surface interpolation.
-In addition, as mentioned in the manuscript, the format chosen to present the results in these figures has already been used in two previous publications (Taborda and Bielak, 2013, 2014).
-This is an advantage because consistency allows one to look back at previous results and appreciate the differences and improvements achieved over the years.
-Furthermore, this or other similar formats have been used or adopted by other authors (e.g., Olsen and Mayhew, 2010; Lee et al.~2015).
-All things considered, we have added a comment when presenting the results of the first figure to make explicit the fact that the interpolation is artificial.
-Please see page 25.
+Response will be here.
 }
@@
 \comment{2}{%
-As shown in Figures 8 and 9, GOF values for the same station have large deviation.
-Thus, the information on the standard deviation among events can be added to Figure 15.
-I think this point is very important in this kind of study, and possible reasons for obtaining large GOF deviation for the same station using the same 3D velocity model needs to be addressed in deep by the authors.
-Since, the same 3D velocity model are used in the numerical simulation, the validity of source model might affect this comparison.
-The calibration and validation of the source models should be adequately given in this paper.
+Pp 3, line 77: Fault-based/geologic-based earthquake recurrence estimates 
 }
@@
 \response{%
-We thank the reviewer for pointing this out.
-Indeed, the standard deviation at the individual stations is a matter of importance.
-We had this information at our disposal but did not realize it was worth including it in the manuscript in the form of a figure.
-We now present this information in the new Figure 16, which illustrates the variance in the average scores obtained for each station in the form of the unbiased sample standard deviation.
-A comment on the results presented in this new figure is now included in pages 33 and 34.
+Response will be here.
+}
+
+\comment{3}{%
+Pp 4, line 106: Should this be northwest?
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{4}{%
+Pp 6, line 168: It would be good to add a reference for the GEM effort.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{5}{%
+Pp7-8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing.
+Typically, one either specifies a minimum magnitude of completeness (Mc) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding Mc.
+In reading the text, it appears that both methods were used.
+Please clarify.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{6}{%
+Pp7-8: The authors should note that some authors use an alternative smoothing kernel $(~exp(-(D/2*sigma)^2)$.
+Comparison of the smoothing length between different studies may require consideration of a $sqrt(2)$ factor.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{7}{%
+Pp7-8: In addition to the Mirzaei et al.
+(1997) reference, some authors employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods (e.g., Werner et al., 2011; Moschetti, 2015).
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{7}{%
+Pp 9: Kagan and Jackson, 1994 should also be included in the reference list.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{8}{%
+Pp 10, line 302: " ...
+subjective decisions and any reasonable choice ...
+" I would disagree that these are subjective decisions.
+My opinion is that you have applied scientific judgment.
+You clearly need to communicate where judgment is applied; however, \\
+- Details about the implementation of the two seismicity rate models (U, R) should be expanded.
+Are sub-catalogs developed for the five separate regions and then used to develop separate a-grids?
+Presumably, the separate rate files are then used to compute hazard curves and are summed at each location.
+\\
+-A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.\\
+-Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{9}{%
+Pp 14, line 391 The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA.
+Recent papers by Atkinson and others have demonstrated this effect.
+You may wish to argue that Mmin was chosen based on the expected smallest magnitude capable of causing damage.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{10}{%
+Figure 7: Is the magnitude-frequency distribution just a truncated (Mmin, Mmax) GR model? Figure 7 suggests that the MFD may be tapered?
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{11}{%
+Pp 12, line 345: "...
+controls the spatial extent to which the local occurrence of earthquakes ..." I would argue that the smoothed seismicity controls the local occurrence and spatial distribution of earthquakes and that the GMPEs control the intensity level at a particular site given earthquake locations and magnitudes from your source model.
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{12}{%
+Pp 13, line 361: Change "approached" to "approach" and "lead" to "led."
+}
+
+\response{%
+Response will be here.
+}
+
+\comment{13}{%
+The approach to generating Figure 10 should be clarified.
+It appears that the probabilistic ground motions from the R and U model are averaged and used to compute a standard deviation.
+The formal method for combining alternative models in PSHA is through the logic tree; this is equivalent to weighting the models in hazard (rate) space, rather than in ground motion (intensity, PGA) space.
+It appears that the authors have done the latter, though I may be incorrect.
+If this is the case, please correct.
+It is very reasonable to combine the R and U models to produce another alternative model.
+This work is not a comprehensive seismic hazard analysis, and presentation of probabilistic ground motions from the R, U and a weighted model would be reasonable goal.
+However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying b- and Mmax-values for the R model greatly complicate the comparison.
+As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references?Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015).
+Applying these methods is beyond the scope of this work, but might be recognized as a future direction.
+}
+
+\response{%
+Response will be here.
 }
@@
 	\large
-	Authors' Response to Reviewer 2 (Robert Graves)
+	Authors' Response to Reviewer 2 
 	\end{center}
@@
 \introcomment{~}{%
-This paper presents an analysis of 3D ground motion simulations for 30 earthquakes in the Los Angeles basin region that were computed using four different 3D seismic velocity models.
-The goal of the analysis is to compare the results obtained with the different models to see which models, or parts thereof, perform better, and to provide a baseline for comparison of future model iterations.
+Review of Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity by Naeem Khoshnevis, Ricardo Taborda, Shima Azizzadeh-Roodpish, and Chris H. Cramer
 }
@@
 \introcomment{~}{%
-This paper is very well written, interesting and informative and my view of this work is quite favorable. I think the paper is worthy of publication after some minor revision.
-}
-
-\introcomment{~}{%
-My main general comment has to do with the use of the word ``validation'' that appears throughout the manuscript.
-In a number of these instances, I feel it would be more appropriate if the term ``validation'' were replaced with the term ``assessment'' (or something similar, like ``evaluation'').
-To me, the ``validation'' of something implies it to be true (e.g., I validated your parking permit), whereas the assessment of something simply means it is being analyzed and its performance possibly ranked with respect to something else.
-Most of what is done in this paper is an assessment of the simulation results, since in the end, none of the velocities models is truly “validated”.
-This assessment process is nonetheless very important in that it provides a relative measure of the performance of each of the velocity models.
-I would suggest the authors consider using a different term as they go through the revision of the paper.
-}
-
-\response{
-We understand and agree, to some extent, with the points raised here by the reviewer.
-Our intention was to evaluate the models, or assess the model, through a validation of the simulations.
-We believe the word validation is well used here when referring to the comparisons of the synthetics with data in the same sense in which the terms ``validation'' and ``verification'' has been defined in other publications such as Bielak et al.~(2010) or Taborda and Bielak (2013).
-That said, the author stands correct in that we may have been abused the use of the word in several instances when we were not being specific about the validation of the individual simulations themselves, but through them, we were actually evaluating the models.
-In this spirit we have welcomed and adopted most if not all the suggestions by the reviewer in this regard, including the change in the title, which makes it simpler and more to the point.
-These changes are documented in the answers to the individual comments below.
-}
-
-\introcomment{~}{%
-A detailed listing of all my specific comments is included in the accompanying marked-up copy of the manuscript.
+In this paper, the researchers present a new seismic hazard analysis of northern Iran.
+The paper makes use of the latest available data and methods, is thorough in its review of previous work, and is very well presented and written.
+I have a few suggestions that I think would improve the impact of their results.
+The annotated version of the manuscript contains additional and more specific suggestions.
 }
@@
 \comment{1}{%
-Page 1, title.
-The phrasing ``validation of recorded events'' does not sound correct.
-The events are real and the records are true data, therefore they are not being validated (we assume them to be valid).
-I think the title would be more appropriate if the words ``and Validation'' were removed.
+The authors present uncertainty in their hazard estimate but do not include a more exhaustive logic tree analysis.
+Effectively, they have two branches: a regional model and uniform model.
+It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis.
+I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in a-value, b-value, and Mmax, for example, are considered.
+Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
 }
 
-\response{The suggested change to the title was adopted.}
+\response{Response will be here.}
 
 \comment{2}{%
-Page 2.
-General comment on the use of the term ``validation''.
-In a number of places in this paper, I feel it would be more appropriate if the term ``validation'' were replaced with the term ``assessment'' (or something similar, like ``evaluation'').
-To me, the ``validation'' of something implies it to be true (e.g., I validated your parking permit), whereas the assessment of something simple means it is being analyzed.
-Most of what is done in this paper is an assessment of the simulation results, which is nonetheless very important in that it provides a relative measure of the performance of each of the velocity models.
+While I think that the regional and uniform models are generally correct within 1.5 degrees of the border, I think that outside of this region, they may be moderately underestimating hazard by not considering sources with 200 km of their region of interest.
+Their buffer zone for sources is presently 50 km.
 }
 
-\response{We introduced a small change in the abstract and other similar changes in several other places throughout the manuscript to better express the essence of the comparisons done in light of the point raised by the reviewer.
-Also see our response to other comments below.}
+\response{Response will be here.}
 
 \comment{3}{%
-Page 4, line 17. Replace with ``collection of recorded''
+It would be good if the abstract is more specific about the results. Where is the hazard greatest? What sources contribute to regions of higher hazard?
 }
-
-\response{Fixed.}
+\response{Response will be here.}
 
 \comment{4}{%
-Page 5, figure 1. Difficult to see the labels ``A'', ``B'' and ``C'' in Figure 1c.
+In the second paragraph of the introduction, I would include a reference to a figure of the region to help readers less familiar with the area.
+This figure should also be referred to in subsequent paragraphs.
+It is probably sufficient to move reference to figure 1 here.
 }
-
-\response{The labels are now framed in a circle with white background. This should make them more visible.}
+\response{Response will be here.}
 
 \comment{5}{%
-Page 6, line 20--24. I'm not sure what this means. Can you explain further?
+line 39:   eighth        -> eight
 }
-
-\response{We eliminated this sentence.
-A better explanation is out of the scope of the paper and is not of major relevance.
-We took this opportunity, instead, to make clarity about the fact that the model CVM-S4.26 as used here is in fact a modification of the raw model that resulted from the inversion done on top of CVM-S4.
-We did this in consultation with colleagues from SCEC to satisfy recent changes in the nomenclature of the models.}
+\response{Response will be here.}
 
 \comment{6}{%
-Page 6, line 41. Delete ``In turn''.
+line 55   focuses in -> focuses on
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{7}{%
-Page 10, line 12. Should be ``BC''.
+line 56 -> Please be more specific about how your analysis differs from previous analyses.
 }
-
-\response{Fixed.}
+\response{Response will be here.}
 
 \comment{8}{%
-Page 10, line 38.
-The event IDs are a unique and vitally important component of the data archival system used by the Southern California Seismic Network.
-Please add a citation to the Southern California Earthquake Data Center, i.e., SCEDC (2013): SCEDC (2013).
-Southern California Earthquake Center, Caltech, Dataset, doi:10.7909/C3WD3xH1
+line 60 -> Can you be more specific? What are the other indicators?
 }
-
-\response{Citation to SCEDC is now included.}
+\response{Response will be here.}
 
 \comment{9}{%
-Page 10, lines 41--43.
-Is Lee et al.
-(2011) the correct reference as several of the events occurred after the publication date of this paper?
-Also, does this mean that all of the events considered in the current analysis were also used in the 3D tomographic inversion to develop CVM-S4.26?
-And, how many of these events were also used in the 3D tomographic updates to CVM-H?
+line 71 -> Include reference? Include reference.
 }
-
-\response{We modified the text to provide a better explanation.
-Yes, all the events considered here were used in the inversions that led to CVM-S4.26.
-In total, 17 of the 30 events were also used in the 3D tomographic updates to CVM-H.
-In addition to the text, we also modified the table to provide information about which of these events were used in CVM-H.}
+\response{Response will be here.}
 
 \comment{10}{%
-Page 11, figure 4. Difficult to see the event labels in Figure 4.
+line 78 -> reduce -> acknowledge
 }
-
-\response{We change the labels to bold font, which should make them easier to see.}
+\response{Response will be here.}
 
 \comment{11}{%
-Page 12, line 58. On the left hand side of the relation, should this be ``$\tau_s$'' instead of ``$t_s$''?
+line 99 -> Is 0.5 degrees enough?
+To what distance do you do your ground motion calculations?
+In the western United States, they are done to 200 km.
+In the central and eastern, they are done to 1000 km.
+Depending on this value, you should include sources up to this distance from your region of interest.
 }
-
-\response{Yes. We fixed it.}
+\response{Response will be here.}
 
 \comment{12}{%
-Page 15, line 44--45. Replace ``originated'' with ``originating''.
+line106 -> northeast -> northwest
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{13}{%
-Page 17, figure 6. The gray contour lines in Figures 6 and 7 mask some of the details. Maybe redo the figures without the gray lines, or use a thinner line.
+line 114 -> There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
 }
-
-\response{We removed the contour lines in both figures.}
+\response{Response will be here.}
 
 \comment{14}{%
-Page 18, lines 46--50.
-Wording of this sentence is a bit awkward.
-Maybe redo with something like, ``These three events were selected because their locations sample different paths into the various basins and they are also large enough to generate significant motions throughout most of the simulation domain''.
+line 180 -> The smaller events should also help to inform the G-R relationship.
 }
-
-\response{We adopted the suggested wording. Thank you, it does read better.}
+\response{Response will be here.}
 
 \comment{15}{%
-Page 19, line 50. Replace ``faults'' with ``fault''.
+line 182 -> How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{16}{%
-Page 19, line 60. I think replacing ``validation'' with ``comparison'' would be more appropriate in this sentence.
+line 192 -> What is the total number of events before and after declustering?
 }
-
-\response{Agree. We changed it.}
+\response{Response will be here.}
 
 \comment{17}{%
-Page 20, line 22. Missing ``)'' at end of sentence.
+line 224 -> Why did you use this method? What are the benefits of one or the other?
 }
-
-\response{Fixed.}
+\response{Response will be here.}
 
 \comment{18}{%
-Page 20, line 35. Delete ``that free surface''.
+line 232 -> It is unclear how you chose Mc. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
 }
-
-\response{Done. Thanks!}
+\response{Response will be here.}
 
 \comment{19}{%
-Page 21, line 6. Replace ``derivate'' with ``differentiate''.
+line 267 -> add ?and?
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{20}{%
-Page 21, line 58. Should be ``equal to''.
+line 289 -> You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
 }
-
-\response{Fixed.}
+\response{Response will be here.}
 
 \comment{21}{%
-Page 22, lines 7--9. Why not the beginning of the slip function? Admittedly, this is just a small shift.
+line 297 -> provided below ? provided in the next section
 }
-
-\response{Well...
-this was a suggestion of many years ago in a SCEC Annual Meeting in conversation with Carl Tape when we (Taborda and Bielak) first worked on the validation simulations of the Chino Hills earthquake.
-The rationale, as I (Taborda) remember it was based on the half rise-time being a reasonable compromise with respect to uncertainty about the rupture time as registered in the records' metadata.
-We do not believe it makes a major difference here, where the rise time is rather small for all events, and thus yes, it is admittedly a very small shift.
-For simulations of larger events with finite source models, however, this may be significant.
-In our experience with the previous Chino Hills simulations (Taborda and Bielak, 2013, 2014) where a finite source was used, this assumption yielded good results.
-But perhaps this may need to be evaluated more carefully.}
+\response{Response will be here.}
 
 \comment{22}{%
-Page 22, line 54. Replace ``this type'' with ``these types''.
+line 300 -> allows one to draw information ? allows to draw information 
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{23}{%
-Page 26, line 47. Maybe ``MODEL'' instead of ``MODELS''.
+line 323 -> Be more specific about how HA3 computes b and Mmax. What is its method?
 }
-
-\response{We actually think is appropriate to use the plural here. We will keep it this way unless the editorial team suggests different.}
+\response{Response will be here.}
 
 \comment{24}{%
-Page 29, line 35. Replace ``Fig. 11'' with ``Fig. 13''.
+line 335 -> Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{25}{%
-Page 29, line 40. Replace ``is'' with ``are''.
+line 337 -> a means to reduce epistemic ? a means to account for epistemic 
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{26}{%
-Page 29, line 53. Replace ``derived'' with ``derived from''.
+line 361 -> lead -> leads
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{27}{%
-Page 31, line 48. Caption of Fig. 15 states only top 20 events are used for average. Please check and correct.
+line 364 -> How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
 }
-
-\response{The caption of the figure stands correct. We modified the text (now in page 32) to be in agreement with the figure.}
+\response{Response will be here.}
 
 \comment{28}{%
-Page 32, line 35. Replace ``even'' with ``event''.
+line 365: add ?and?
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{29}{%
-Page 32, line 36. Replace ``station'' with ``stations''.
+line 370 -> Could you consider other depths to help fill out your range of epistemic uncertainty?
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{30}{%
-Page 32, line 39. Replace ``dotes'' with ``dots''.
+line 371 -> How does this value compare with the models you decided not to use?
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{31}{%
-Page 32, lines 52--54. Maybe replace ``showed to be independent to'' with ``do not correlate with''.
+line 376 -> In this case, you should consider all sources with 200 km of your area of interest.
 }
-
-\response{We adopted this suggestion. Thanks.}
+\response{Response will be here.}
 
 \comment{32}{%
-Page 33, line 12. Change ``not'' to ``no''.
+line 394:  50-years -> 50-year
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{33}{%
-Page 33, line 13. Change ``the basin's depth'' to ``basin depth''.
+line 420 -> with concentration ? with a concentration
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{34}{%
-Page 33, line 28. Maybe change ``model'' to ``GTL model'' just for clarity.
+line 422 -> I would have stated this differently.
+It looks like the lower b-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
 }
-
-\response{Yes, thank you.}
+\response{Response will be here.}
 
 \comment{35}{%
-Page 33, line 32.
-I think CVM-S4, and therefore CVM-S4.26, do, in fact, include a GTL model (see Magistrale et al.~2000).
-It is just not as comprehensive or sophisticated as the Ely Vs30-based GTL approach.
-My suggestion is to replace ``GTL model'' with ``more comprehensive GTL model''.
+line 428 -> Why equal weights?
 }
-
-\response{While we have differences in our understanding of what constitutes a GTL model in a CVM, we recognize that this clearer wording can help the reader, and thus we adopted the suggestion.
-Thank you.}
+\response{Response will be here.}
 
 \comment{36}{%
-Page 33, line 39. Delete ``the region of''.
+line 431 -> I'm not sure I quite understand this.
+The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve.
+Adding it as epistemic as well will cause double counting.
+If you want to include figure 10, a proper logic tree analysis to include more forms of epistemic uncertainty should be performed.
+For example, add branches for uncertainty in which GMPE you choose, uncertainty in b-value, uncertainty in Mmax, uncertainty in a-value, uncertainty in smoothing parameter, etc.
 }
-
-\response{Done.}
-
-\comment{36}{%
-Page 33, line 41. Maybe change ``velocity'' to ``seismic velocity'' just for clarity at the beginning of this section.
-}
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{37}{%
-Page 33, line 43. Replace ``of fits'' with ``fit''.
+line 434 -> Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the b-values are truly different between regions and better represented by the regional analysis.
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{38}{%
-Page 33, line 45. Delete ``simulation''.
+line 439: of city of Tabriz -> of the city of Tabriz.
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{39}{%
-Page 33, lines 54--56. Related to my point in comment \#2, I think this sentence would be more correct if the word ``validation'' were removed.
+line 450 ->  for 2 and 10\%, respectively ? for 2 and 10\% in 50 years, respectively.
 }
-
-\response{Agree. We removed the word ``validation''.}
+\response{Response will be here.}
 
 \comment{40}{%
-Page 34, figure 15 caption. Text states all events are used in average. Please check.
+line 453 ->  for a 10\% probability of exceedance ?  for a 10\% probability of exceedance in 50 years.
 }
-
-\response{See our response to comment 27.}
+\response{Response will be here.}
 
 \comment{41}{%
-Page 34, line 44.
-As long as the input model to the inversion is reasonably good.
-Which the results here suggest that CVM-S4 is a reasonably good starting model.
-I think it would be worthwhile to point this out.
+line 455 -> 0.27-0.31 g for 10\% probability of exceedance ->  0.27-0.31 g for the same exceedance probability
 }
-
-\response{Agree. We added a note in the conclusions to reflect this.}
+\response{Response will be here.}
 
 \comment{42}{%
-Page 35, figure 16 caption. Change ``SC'' to ``SB''.
+line 458 ->  for 2 and 10\% ? for 2 and 10\% in 50 years
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{43}{%
-Page 35, line 59. Again, I believe that CVM-S4.26 already has some sort of GTL. I suggest modifying the text here to read ``more
-detailed geotechnical''.
+line 461 -> our results are close or within ? our results are close to or within 
 }
-
-\response{We modified the sentence to adopt this suggestion.}
+\response{Response will be here.}
 
 \comment{44}{%
-Page 35, line 60. Delete ``additional''.
+line 462 -> Can you explain the differences in their analysis relative to yours that lead to higher values?
 }
-
-\response{Done.}
+\response{Response will be here.}
 
 \comment{45}{%
-Page 36, line 7. Maybe change ``considering'' to ``possibly including''.
-}
-
-\response{Thank you for this suggestion. We changed the wording.}
+line 466 -> exceedance as functions of PGA ? exceedance as functions of PGA, also known as hazard curves}
+\response{Response will be here.}
 
 \comment{46}{%
-Page 36, lines 9--11. Change to ``as sufficient data become available''.
+line 475 -> Can you explain the differences in the hazard analysis that led to differences in hazard?}
+\response{Response will be here.}
+
+\comment{47}{%
+line 462 -> Can you explain the differences in their analysis relative to yours that lead to higher values?
 }
+\response{Response will be here.}
 
-\response{Fixed.}
+\comment{48}{%
+lline 488 -> Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
+you only use one GMPE (though you do consider two b-value and Mmax based models).
+}
+\response{Response will be here.}
+
+\comment{49}{%
+line 488 -> hazard analysis ? hazard analyses
+}
+\response{Response will be here.}
+
+\comment{50}{%
+line 490 -> models as a mean ? models as a means}
+\response{Response will be here.}
+
+\comment{51}{%
+line 493 -> Though you suggest the uniform model is unrealistic on line 334.}
+\response{Response will be here.}
+
+\comment{52}{%
+line 502 -> for providing advise ? for providing advice}
+\response{Response will be here.}
+
+\comment{53}{%
+line 509 ->  Should this be Sunset?}
+\response{Response will be here.}
+
+\comment{54}{%
+p 25 ? table2 -> What did you do for the earthquakes occurring outside of these five zones?}
+\response{Response will be here.}
+
+\comment{55}{%
+p 26 ? table3 -> Specify units.}
+\response{Response will be here.}
+
+\comment{56}{%
+p32 ? figure 3 -> You should also show events in the buffer zone used to compute hazard.}
+\response{Response will be here.}
+
+\comment{57}{%
+p34 ?
+figure 5 -> Which seismic zone corresponds to which color?
+It looks like either reporting or rates have changed over time.
+For example, I might argue that the red region was not complete for M3 and above until 2005.
+}
+\response{Response will be here.}
+
+\comment{58}{%
+P37: 10 percent of probability -> 10 percent probability }
+\response{Response will be here.}
+
+\comment{59}{%
+p 39 ? figure 11 -> Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
+\response{Response will be here.}
+
+\comment{60}{%
+p 39 ? figure 11 -> p 41 ? figure 12 -> Can you include curves or points for the other studies in Table 3?}
+\response{Response will be here.}
 

### 2016-09-23 response.tex
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
 \response{%
-Response will be here.
+Fixed, Thanks.
 }
@@
 \response{%
-Response will be here.
+Thanks for the comment. We computed hazard for events $M_w > 4.5$ and modified the text. 
 }
@@
 \response{%
-Response will be here.
+Yes it is truncated GR model. (Figure caption is not fixed yet.)
 }
@@
 \response{%
-Response will be here.
+Done.
 }
@@
 
-\response{Response will be here.}
+\response{That right. We increased the buffer zone up to 2 degrees. (Haven't modified the text)}
 
@@
 \comment{5}{%
-line 39:   eighth        -> eight
+line 39:   eight        -> eighth
 }
-\response{Response will be here.}
+\response{Fixed.}
 
@@
 }
-\response{Response will be here.}
+\response{Done. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{Fixed.}
 
@@
 }
-\response{Response will be here.}
+\response{We reanalyze the hazard with 2 degrees buffer zone. (Not modified in the text.)}
 
@@
 }
-\response{Response will be here.}
+\response{Done. Thanks}
 
@@
 }
-\response{Response will be here.}
+\response{Thanks for the comment. Added to the text.}
 
@@
 \comment{19}{%
-line 267 -> add ?and?
+line 267 -> add 'and'
 }
-\response{Response will be here.}
+\response{Added. Thanks.}
 
@@
 \comment{21}{%
-line 297 -> provided below ? provided in the next section
+line 297 -> provided below -> provided in the next section
 }
-\response{Response will be here.}
+\response{Fixed.}
 
 \comment{22}{%
-line 300 -> allows one to draw information ? allows to draw information 
+line 300 :  allows to draw information -> allows one to draw information 
 }
-\response{Response will be here.}
+\response{Done.}
 
@@
 \comment{25}{%
-line 337 -> a means to reduce epistemic ? a means to account for epistemic 
+line 337 -> a means to reduce epistemic -> a means to account for epistemic 
 }
-\response{Response will be here.}
+\response{Done.}
 
@@
 }
-\response{Response will be here.}
+\response{Two reviewer suggested two different word. Both of them are correct. Please see.}
 
@@
 }
-\response{Response will be here.}
+\response{As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs.
+We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or ?central?
+GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE.
+In the previeous study (Khodaverdian 2016), they used Akkar and Bommer (2010) and Ghasemi et al (2009) along side other equations.
+Akkar and Bommer (2010) derived the equation up to 100 Km, which they used for 200 km.
+Also Ghasemi et al (2009) is presented the coefficients for spectral acceleration not PGA.
+Of course this alternative method has been a hotly-debated topic, and there is no clear consensus about that, however, the plots of attenuation relationships in different magnitude illustrate the fact that with this approach we can address the epistemic uncertainty in an acceptable range.
+We totally agree with the reviewer?s comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers.
+In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig X.}
 
 \comment{28}{%
-line 365: add ?and?
+line 365: add 'and'
 }
-\response{Response will be here.}
+\response{Added. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{The Kalkan and Gulkan (2004) attenuation relationship is originally generated for Turkey.
+However, in the recent test by Zafarani and Mousavi (2014), it gives acceptable results for PGA.
+Since the high accuracy achieved by the current depth, and we have no idea how different depth will change the results, we prefer to not to use a parameter without knowing the effects.
+}
 
@@
 }
-\response{Response will be here.}
+\response{We modified the buffer zone. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{33}{%
-line 420 -> with concentration ? with a concentration
+line 420 -> with concentration -> with a concentration
 }
-\response{Response will be here.}
+\response{Added. Thanks.}
 
@@
 \comment{39}{%
-line 450 ->  for 2 and 10\%, respectively ? for 2 and 10\% in 50 years, respectively.
+line 450 ->  for 2 and 10\%, respectively -> for 2 and 10\% in 50 years, respectively.
 }
@@
 \comment{58}{%
-P37: 10 percent of probability -> 10 percent probability }
+P37: 10 percent of probability $\to$ 10 percent probability }
 \response{Response will be here.}
@@
 \comment{59}{%
-p 39 ? figure 11 -> Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
-\response{Response will be here.}
+p 39,figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
+\response{Included.}
 
 \comment{60}{%
-p 39 ? figure 11 -> p 41 ? figure 12 -> Can you include curves or points for the other studies in Table 3?}
+p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
 \response{Response will be here.}

### 2016-09-23 attenuation.tex
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
 In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other.
-Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the approached of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis lead to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
+Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{led} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
 These results meant that neither of them had a substantial advantage over the others.
@@
 % 
-where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, $V_S$ is the shear wave velocity of the site of interest.
+where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, \myrevision{and} $V_S$ is the shear wave velocity of the site of interest.
 In this equation, the distance $r$ is given by

### 2016-09-23 compilation.tex
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
 We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, \myrevision{also the smaller events help to inform G-R relationship} .
 By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar catalog for events $M_w \geq 4$ but only included data through 2011, excluding the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.

### 2016-09-23 hazard.tex
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
 In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.
+This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, \myrevision{and} Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.
 In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes within and around the region.
@@
 In turn, we consider the $b$-values to be constant within each seismic zone as delimited in Fig.~\ref{fig:iran}.
-Details about the calculation of the $b$-value for each zone are provided below.
+Details about the calculation of the $b$-value for each zone are provided \myrevision{in the next section}.
 By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within large grid-cells of size 1\textdegree{} $\times$ 1\textdegree{} based on the average seismicity within a 200-km radius from each cell.
-While gridding $b$-values and considering the influence of neighboring large-size cells allows to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may bias the computation of $b$-values.
+While gridding $b$-values and considering the influence of neighboring large-size cells allows \myrevision{one} to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may bias the computation of $b$-values.
 Admittedly, these are subjective decisions and any reasonable choice can be considered valid or within the margins of the associated epistemic uncertainty.

### 2016-09-23 introduction.tex
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
 This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges.
-It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eight century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
+It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the \myrevision{eighth} century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
 
@@
 Over the last three decades there have been multiple efforts to better estimate the seismic parameters and hazard, and improve the assessment of seismic risk in Iran \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE, Khodaverdian_2016_BSSA}.
-The most recent of these studies \citep{Khodaverdian_2016_BSSA} focuses in the estimation of spatially-variable seismic parameters for the whole country using a similar approach to the one we used here.
+The most recent of these studies \citep{Khodaverdian_2016_BSSA} focuses \myrevision{on} the estimation of spatially-variable seismic parameters for the whole country using a similar approach to the one we used here.
 We, however, focus our attention in the northern three seismic zones of the country assuming regionally-based and smoothed seismic parameters.
@@
 Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
-While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to reduce the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
+While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
 In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}).

### 2016-09-23 parameters.tex
edits suggested by Naeem
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
-    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
-The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
-The last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
-The shaded range indicates the models' $\pm 1$ standard deviation.}
-    \label{fig:annualp}
-\end{figure*}
-
-\begin{table}[t]
-    \centering
-    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
-    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
-        \cline{2-4}                                                                         \\[-1.6ex]
-                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
-        \hline                                                                              \\[-1.6ex]
-        Azerbaijan      & 1.16 $\pm$ 0.03   & 7.80 $\pm$ 0.38   & 7.7                       \\
-        Alborz          & 1.00 $\pm$ 0.03   & 7.80 $\pm$ 0.52   & 7.8                       \\
-        Kopeh Dagh      & 0.92 $\pm$ 0.03   & 7.73 $\pm$ 0.28   & 7.6                       \\
-        Zagros          & 1.02 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
-        Central-East    & 1.01 $\pm$ 0.03   & 7.79 $\pm$ 0.31   & 7.6                       \\
-        Uniform Model   & 0.95 $\pm$ 0.01   & 7.84 $\pm$ 0.27   & 7.8                       \\[0.5ex]
-        \hline 
-    \end{tabular}
-    \label{tab:params} 
-\end{table}
-
 \section{Seismicity Parameters}
@@
 Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
-However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to reduce epistemic uncertainty.
+However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty.
 Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
+
+\begin{table}%[t]
+    \centering
+    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
+    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
+        \cline{2-4}                                                                         \\[-1.6ex]
+                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
+        \hline                                                                              \\[-1.6ex]
+        Azerbaijan      & 1.16 $\pm$ 0.03   & 7.80 $\pm$ 0.38   & 7.7                       \\
+        Alborz          & 1.00 $\pm$ 0.03   & 7.80 $\pm$ 0.52   & 7.8                       \\
+        Kopeh Dagh      & 0.92 $\pm$ 0.03   & 7.73 $\pm$ 0.28   & 7.6                       \\
+        Zagros          & 1.02 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
+        Central-East    & 1.01 $\pm$ 0.03   & 7.79 $\pm$ 0.31   & 7.6                       \\
+        Uniform Model   & 0.95 $\pm$ 0.01   & 7.84 $\pm$ 0.27   & 7.8                       \\[0.5ex]
+        \hline 
+    \end{tabular}
+    \label{tab:params} 
+\end{table}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-07} 
+    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
+The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
+The last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
+The shaded range indicates the models' $\pm 1$ standard deviation.}
+    \label{fig:annualp}
+\end{figure*}

### 2016-09-23 results.tex
fixed size of fig 12
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt

@@
 We call these the R and U models, respectively.
-Using these models we obtained hazard curves and expected PGA values for two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes $M_w \geq 5$.
+Using these models we obtained hazard curves and expected PGA values for two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes \myrevision{$M_w \geq 4.5$}.
 These probabilities correspond to return periods of 475 and 2475 years.
@@
 
-Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events $M_w \geq 5$, or conversely, based on the assumption that smaller events at increasing distances will not drive the hazard of a given site.
-In turn, the 2 and 10 percent probability of exceedance in a 50-years span are considered a standard practice in seismic design, and are the probabilities used in the Iranian building code \citep{BHRC2014}.
+Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events \myrevision{$M_w \geq 4.5$}, or conversely, \myrevision{$M_{min}$ was chosen based on the expected smallest magnitude capable of causing damage}.
+In turn, the 2 and 10 percent probability of exceedance in a \myrevision{50-year} span are considered a standard practice in seismic design, and are the probabilities used in the Iranian building code \citep{BHRC2014}.
 
@@
 Overall, these results are consistent with the seismicity observed in Fig.~\ref{fig:catalog}.
-The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with concentration of strong earthquakes in the Alborz and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
+The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with \myrevision{a} concentration of strong earthquakes in the Alborz and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
 This is because of the higher $b$-value obtained for the Azerbaijan region in the R model as opposed to the lower value for the U model.
@@
 It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the Piranshahr and Morvarid faults in the Zagros region and that of the different faults in the Alborz and Kopeh Dagh regions.
-In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of city of Tabriz.
+In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of \myrevision{the} city of Tabriz.
 These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigating peak accelerations.
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/pdf/figure-12} 
+    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-12} 
     \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran.

### 2016-09-23 figures/gmt/seismicity.sh

@@ -35,7 +35,7 @@ gmt grdmath mytopo.hist 3 DIV = mytopo.norm
 # Top Map - Historical
 # ------------------------------------------------------------------------------
 
-gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWnes -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+gmt psbasemap -R41.5/63.5/32/42 -JM5i -BWnes -Ba2f1 -Y8i -V -P -K > ${PSNAME}
 
 # gmt psbasemap -R -J -BWnes -Ba2f1 -Y-3.5i -V -P -O -K >> ${PSNAME}
 gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
@@ -49,7 +49,7 @@ gmt psxy data.txt -R -J -Sc -W0.5 -Chistorical.cpt -V -K -O >> ${PSNAME}
 # Bottom Map - Instrumental
 # ------------------------------------------------------------------------------
 
-gmt psbasemap -R -J -BWneS -Ba2f1 -Y-2.5i -V -P -O -K >> ${PSNAME}
+gmt psbasemap -R -J -BWneS -Ba2f1 -Y-3.2i -V -P -O -K >> ${PSNAME}
 gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
 gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
 gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
@@ -63,24 +63,24 @@ gmt psxy data.txt -R -J -Sc -W0.5 -G0/220/140 -V -K -O >> ${PSNAME}
 cat << END | \
 awk '{print $2,$3,$1,($4^3.2)/1000}' | \
 gmt psxy -R -J -N -Sc -W0.5 -Chistorical.cpt -V -K -O >> ${PSNAME}
-1900   63	37.5	5.0
-1900   63	36.7	6.0
-1900   63	35.7	7.0
-1900   63	34.5	8.0
+1900   65	37.5	5.0
+1900   65	36.7	6.0
+1900   65	35.7	7.0
+1900   65	34.5	8.0
 END
 
[…]

### 2016-09-26 response.tex
Updated figures added to the figure 6 illustrator file. Needs more polishing.

@@
 
+\introcomment{~}{%
+Summary of modifications (Remove before submitting)\\
+- Buffer zone updated.\\
+- Data updated.\\
+- b-values updated.\\
+- Completeness parameters updated.\\
+- Figure 1: Buffer Zone Updated.\\
+- Figure 3: Seismicity.sh modified. Historical.txt and Instrumental.txt updated to new data. \\
+- Figure 4: Updated.\\
+- Figure 5: The excel file is updated. The figure needs to be updated.\\
+- Figure 6: Updated data completeness plots added to the figure. Figure needs final polishing. \\
+
+}
+
 \end{document}

### 2016-09-27 response.tex
Figure 7(Annual Probability of exceedance.)  updated.
Couple of comments were addressed.

@@
 \response{%
-Response will be here.
+You are right.
+We used both methods in the study.
+First we compute the $b-value$ and $M_{max}$ for each region, or the uniform model using the HA3 package written by Dr.
+Kijko.
+$M_c$ is used as an input in the software to get accurate results.
+We computed the smoothed seismic hazard using the Seiskit package, written by Dr.
+Frankel.
+In estimating the seismic hazard, specifically $a-value$, we need to define a start year of completeness for each magnitude range.
+We modified the text to clarify the statement.
 }
@@
 \response{%
-Response will be here.
+Added. Thanks.
 }
@@
 \response{%
-Response will be here.
+Added to the text. Thanks.
 }
@@
 
-\response{Response will be here.}
+\response{Thanks for the comment.
+Based on explanation of GMPEs section (please see comment no.?) we decided to define a suite of GMPE and also provide the uncertainty.
+We consider the epistemic uncertainty, based on defining two different model (which considers the uncertainty in $b-value$ and $M_max$).
+In order to make it clear we added two GMPE suites (plus and minus one standard deviation) also we defined the uncertainty in $M_{max}$.
+This approach will cover the most of uncertainty in the study.}.
 
@@
 \comment{5}{%
-line 39:   eight        -> eighth
+line 39:   eight  $\to$ eighth
 }
@@
 \comment{6}{%
-line 55   focuses in -> focuses on
+line 55   focuses in $\to$ focuses on
 }
@@
 \comment{7}{%
-line 56 -> Please be more specific about how your analysis differs from previous analyses.
+line 56 $\to$ Please be more specific about how your analysis differs from previous analyses.
 }
@@
 \comment{8}{%
-line 60 -> Can you be more specific? What are the other indicators?
+line 60 $\to$ Can you be more specific? What are the other indicators?
 }
@@
 \comment{9}{%
-line 71 -> Include reference? Include reference.
+line 71 $\to$ Include reference? Include reference.
 }
-\response{Response will be here.}
+\response{Done. Thanks.}
 
 \comment{10}{%
-line 78 -> reduce -> acknowledge
+line 78 $\to$ reduce $\to$ acknowledge
 }
@@
 \comment{11}{%
-line 99 -> Is 0.5 degrees enough?
+line 99 $\to$ Is 0.5 degrees enough?
 To what distance do you do your ground motion calculations?
@@
 \comment{12}{%
-line106 -> northeast -> northwest
+line106 $\to$ northeast $\to$ northwest
 }
@@
 \comment{13}{%
-line 114 -> There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
+line 114 $\to$ There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
 }
-\response{Response will be here.}
+\response{Thanks for the comment. It is 26 April 1721,$M_s ~ 7.3$ earthquake}
 
 \comment{14}{%
-line 180 -> The smaller events should also help to inform the G-R relationship.
+line 180 $\to$ The smaller events should also help to inform the G-R relationship.
 }
@@
 \comment{15}{%
-line 182 -> How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
+line 182 $\to$ How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
 }
@@
 \comment{16}{%
-line 192 -> What is the total number of events before and after declustering?
+line 192 $\to$ What is the total number of events before and after declustering?
 }
-\response{Response will be here.}
+\response{Number of events before decluttering: 10441, total foreshock: 971, total aftershock: 4206, declustered data 5254.
+It should be noted that, these numbers are representing the events in the study region (including the bufferzone).
+It partly includes events from Central and Zagros region.
+For completeness study we studied the whole data for each region.}
 
 \comment{17}{%
-line 224 -> Why did you use this method? What are the benefits of one or the other?
+line 224 $\to$ Why did you use this method? What are the benefits of one or the other?
 }
@@
 \comment{18}{%
-line 232 -> It is unclear how you chose Mc. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
+line 232 $\to$ It is unclear how you chose Mc. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
 }
@@
 \comment{19}{%
-line 267 -> add 'and'
+line 267 $\to$ add 'and'
 }
@@
 \comment{20}{%
-line 289 -> You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
+line 289 $\to$ You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
 }
-\response{Response will be here.}
+\response{Added. Thanks.}
 
 \comment{21}{%
-line 297 -> provided below -> provided in the next section
+line 297 $\to$ provided below $\to$ provided in the next section
 }
@@
 \comment{22}{%
-line 300 :  allows to draw information -> allows one to draw information 
+line 300 :  allows to draw information $\to$ allows one to draw information 
 }
@@
 \comment{23}{%
-line 323 -> Be more specific about how HA3 computes b and Mmax. What is its method?
+line 323 $\to$ Be more specific about how HA3 computes b and Mmax. What is its method?
 }
-\response{Response will be here.}
+\response{Method added. Thanks.}
 
 \comment{24}{%
-line 335 -> Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
+line 335 $\to$ Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
 }
@@
 \comment{25}{%
-line 337 -> a means to reduce epistemic -> a means to account for epistemic 
+line 337 $\to$ a means to reduce epistemic $\to$ a means to account for epistemic 
 }
@@
 \comment{26}{%
-line 361 -> lead -> leads
+line 361 $\to$ lead $\to$ leads
 }
@@
 \comment{27}{%
-line 364 -> How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
+line 364 $\to$ How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
 }
@@
 \comment{29}{%
-line 370 -> Could you consider other depths to help fill out your range of epistemic uncertainty?
+line 370 $\to$ Could you consider other depths to help fill out your range of epistemic uncertainty?
 }
@@
 \comment{30}{%
-line 371 -> How does this value compare with the models you decided not to use?
+line 371 $\to$ How does this value compare with the models you decided not to use?
 }
@@
 \comment{31}{%
-line 376 -> In this case, you should consider all sources with 200 km of your area of interest.
+line 376 $\to$ In this case, you should consider all sources with 200 km of your area of interest.
 }
@@
 \comment{32}{%
-line 394:  50-years -> 50-year
+line 394:  50-years $\to$ 50-year
 }
@@
 \comment{33}{%
-line 420 -> with concentration -> with a concentration
+line 420: with concentration $\to$ with a concentration
 }
@@
 \comment{34}{%
-line 422 -> I would have stated this differently.
+line 422 $\to$ I would have stated this differently.
 It looks like the lower b-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
@@
 \comment{35}{%
-line 428 -> Why equal weights?
+line 428 $\to$ Why equal weights?
 }
@@
 \comment{36}{%
-line 431 -> I'm not sure I quite understand this.
+line 431 $\to$ I'm not sure I quite understand this.
 The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve.
@@
 }
-\response{Response will be here.}
+\response{We modified the approach and considered the mentioned uncertainties.}
 
 \comment{37}{%
-line 434 -> Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the b-values are truly different between regions and better represented by the regional analysis.
+line 434 $\to$ Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the b-values are truly different between regions and better represented by the regional analysis.
 }
@@
 \comment{38}{%
-line 439: of city of Tabriz -> of the city of Tabriz.
+line 439: of city of Tabriz $\to$ of the city of Tabriz.
 }
-\response{Response will be here.}
+\response{Fixed. Thanks.}
 
 \comment{39}{%
-line 450 ->  for 2 and 10\%, respectively -> for 2 and 10\% in 50 years, respectively.
+line 450 $\to$  for 2 and 10\%, respectively $\to$ for 2 and 10\% in 50 years, respectively.
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{40}{%
-line 453 ->  for a 10\% probability of exceedance ?  for a 10\% probability of exceedance in 50 years.
+line 453 $\to$  for a 10\% probability of exceedance ?  for a 10\% probability of exceedance in 50 years.
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{41}{%
-line 455 -> 0.27-0.31 g for 10\% probability of exceedance ->  0.27-0.31 g for the same exceedance probability
+line 455 $\to$ 0.27-0.31 g for 10\% probability of exceedance $\to$  0.27-0.31 g for the same exceedance probability
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{42}{%
-line 458 ->  for 2 and 10\% ? for 2 and 10\% in 50 years
+line 458 $\to$  for 2 and 10\% ? for 2 and 10\% in 50 years
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{43}{%
-line 461 -> our results are close or within ? our results are close to or within 
+line 461: our results are close or within $\to$ our results are close to or within 
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{44}{%
-line 462 -> Can you explain the differences in their analysis relative to yours that lead to higher values?
+line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
 }
@@
 \comment{45}{%
-line 466 -> exceedance as functions of PGA ? exceedance as functions of PGA, also known as hazard curves}
-\response{Response will be here.}
+line 466 $\to$ exceedance as functions of PGA ? exceedance as functions of PGA, also known as hazard curves}
+\response{Added. Thanks.}
 
 \comment{46}{%
-line 475 -> Can you explain the differences in the hazard analysis that led to differences in hazard?}
+line 475 $\to$ Can you explain the differences in the hazard analysis that led to differences in hazard?}
 \response{Response will be here.}
@@
 \comment{47}{%
-line 462 -> Can you explain the differences in their analysis relative to yours that lead to higher values?
+line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
 }
@@
 \comment{48}{%
-lline 488 -> Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
+lline 488 $\to$ Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
 you only use one GMPE (though you do consider two b-value and Mmax based models).
@@
 \comment{49}{%
-line 488 -> hazard analysis ? hazard analyses
+line 488:  hazard analysis $\to$ hazard analyses
 }
-\response{Response will be here.}
+\response{Done.}
 
 \comment{50}{%
-line 490 -> models as a mean ? models as a means}
-\response{Response will be here.}
+line 490: models as a mean $\to$ models as a means}
+\response{Done.}
 
 \comment{51}{%
-line 493 -> Though you suggest the uniform model is unrealistic on line 334.}
+line 493 $\to$ Though you suggest the uniform model is unrealistic on line 334.}
 \response{Response will be here.}
@@
 \comment{52}{%
-line 502 -> for providing advise ? for providing advice}
-\response{Response will be here.}
+line 502 $\to$ for providing advise ? for providing advice}
+\response{Done.}
 
 \comment{53}{%
-line 509 ->  Should this be Sunset?}
-\response{Response will be here.}
+line 509 $\to$  Should this be Sunset?}
+\response{Yes. Thanks.}
 
 \comment{54}{%
-p 25 ? table2 -> What did you do for the earthquakes occurring outside of these five zones?}
-\response{Response will be here.}
+p 25 ? table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
+\response{There are earthquakes out of the regions, mainly above the Caspian see. Since those area are not in our region of interest, and are fairly far from our region, we ignored them.}
 
 \comment{55}{%
-p 26 ? table3 -> Specify units.}
+p 26 ? table3 $\to$ Specify units.}
 \response{Response will be here.}
@@
 \comment{56}{%
-p32 ? figure 3 -> You should also show events in the buffer zone used to compute hazard.}
-\response{Response will be here.}
+p32 ? figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
+\response{Done.}
 
@@
 p34 ?
-figure 5 -> Which seismic zone corresponds to which color?
+figure 5 $\to$ Which seismic zone corresponds to which color?
 It looks like either reporting or rates have changed over time.
@@
 - Figure 6: Updated data completeness plots added to the figure. Figure needs final polishing. \\
-
+- Figure 7: Updated. 
 }

### 2016-09-27 acknowledge.tex
Couple of comments were addressed.

--- 2016-07-08 acknowledge.tex
@@
 
-The authors wish to express their gratitude to Art Frankel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advise on the use of the software.
+The authors wish to express their gratitude to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing \myrevision{advice} on the use of the software.
 The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information.
@@
 This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis.
-CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015--2016).
+CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State \myrevision{Sunset} Laws (SB 1510 and HB 1608, 2015--2016).

### 2016-09-27 completeness.tex
Couple of comments were addressed.

@@
 This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process.
-The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range \myrevision{which in this study we use these values in estimating $a-values$ of smoothed seismic hazard, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+\myrevision{ We use $M_c$ for each catalog to compute the $b-value$ and $M_{max}$}
 

### 2016-09-27 conclusions.tex
Couple of comments were addressed.

@@
 In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model.
-Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard analysis due to the usage of a more complete catalog and inclusion of low-magnitude events.
-In our analysis we found it convenient to combine both the regional and uniform models as a mean to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones.
+Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard \myrevision{analyses} due to the usage of a more complete catalog and inclusion of low-magnitude events.
+In our analysis we found it convenient to combine both the regional and uniform models as a \myrevision{means} to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones.
 Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and to the location of known seismically active faults.

### 2016-09-27 hazard.tex
Couple of comments were addressed.

@@
 In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, \myrevision{and} Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014}.
+This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, \myrevision{and} Turkey \myrevision{\citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014,Kagan1994}}.
 In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes within and around the region.
@@
 where $\tilde{n}_i$ is the smoothed, normalized number of events in cell $i$, $\Delta_{ij}$ is the distance between the $i$-th and $j$-th cells, and $c$ is the correlation distance.
-The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
+\myrevision{An alternative smoothing kernel has been used in recent studies \citep[e.g.][]{Moscheti2015}}.The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
 It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
@@
 Different values of $c$ have been used in past studies, ranging between 10 and 50 km.
-\citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15 km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40 km.
+\citet{Frankel1995},\myrevision{\citet{Boyd2007},  \citet{Boyd2008}, and \citet{Petersen2015}}  assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15 km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40 km.
 According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records.
+\myrevision{Also some studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing length for adaptive and fixed smoothed seismicity methods \citep[e.g.][]{Werner2011,Moscheti2015}}.
 We use an intermediate value of $c=30$~km.

### 2016-09-27 introduction.tex
Couple of comments were addressed.

@@
 
-Most previous studies focus on particular locations or are based on specific categorization of seismogenic faults, which are often subjectively interpreted and limited to data availability.
-We use the smoothed seismicity method introduced by \citet{Frankel1995}.
+\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults citep[e.g.][]{Ghodrati2003,Vafai2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}.
 This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.

### 2016-09-27 parameters.tex
Couple of comments were addressed.

@@
 On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
-We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog, which we divide in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
+We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog.
+\myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko1989} method.
+Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.
+We divide the} catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
 In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.

### 2016-09-27 results.tex
Couple of comments were addressed.

@@
 For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.35 and 0.50 g in the (R,U)10 model.
-Similarly, for the particular case of the city of Tabriz, \citet{Vafaie2011} obtained slightly higher expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\%, respectively, where our mean values are about 0.53 and 0.36 g for the same corresponding probabilities.
-In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 g for Tehran, where we found equivalent results to be about 0.25--0.35 g for a 10\% probability of exceedance.
-The latter estimate is in good agreement with \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.27--0.31 g for 10\% probability of exceedance.
+Similarly, for the particular case of the city of Tabriz, \citet{Vafaie2011} obtained slightly higher expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\% \myrevision{in 50 years}, respectively, where our mean values are about 0.53 and 0.36 g for the same corresponding probabilities.
+In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 g for Tehran, where we found equivalent results to be about 0.25--0.35 g for a 10\% probability of exceedance \myrevision{in 50 years}.
+The latter estimate is in good agreement with \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.27--0.31 g for \myrevision{the same exceedance probability}.
 Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also on the same order of those shown in Fig.~\ref{fig:pga.ru.std}.
-Finally, for the city of Bojnurd in the northeast province of Khorasan in the Kopeh Dagh seismic region, \citet{Rahgozar2012} reports expected PGA values in the ranges of 0.28--0.49 and 0.15--0.22 g for 2 and 10\%, where we obtain mean values of 0.51 and 0.34 g, respectively.
+Finally, for the city of Bojnurd in the northeast province of Khorasan in the Kopeh Dagh seismic region, \citet{Rahgozar2012} reports expected PGA values in the ranges of 0.28--0.49 and 0.15--0.22 g for 2 and 10\% \myrevision{in 50 years}, where we obtain mean values of 0.51 and 0.34 g, respectively.
 
 Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
-As mentioned before, overall, our results are close or within the ranges from most studies.
+As mentioned before, overall, our results are close \myrevision{to} or within the ranges from most studies.
 The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher than the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad, where their results are closer to those of our upper (+STD) range of values.
@@
 
-Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA.
+Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA\myrevision{, also known as hazard curve}.
 The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the two basic R and U models and the combined (R,U) model.

### 2016-09-30 response.tex
figure-11.ai is updated.

@@
 \comment{54}{%
-p 25 ? table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
+p 25, table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
 \response{There are earthquakes out of the regions, mainly above the Caspian see. Since those area are not in our region of interest, and are fairly far from our region, we ignored them.}
@@
 \comment{55}{%
-p 26 ? table3 $\to$ Specify units.}
+p 26, table3 $\to$ Specify units.}
 \response{Response will be here.}
@@
 \comment{56}{%
-p32 ? figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
+p32, figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
 \response{Done.}
@@
 \comment{57}{%
-p34 ?
-figure 5 $\to$ Which seismic zone corresponds to which color?
+p34, figure 5 $\to$ Which seismic zone corresponds to which color?
 It looks like either reporting or rates have changed over time.
@@
 - Figure 6: Updated data completeness plots added to the figure. Figure needs final polishing. \\
-- Figure 7: Updated. 
+- Figure 7: Updated.\\
+- Figure 11: Updated.\\ 
 }

### 2016-10-01 response.tex
Updatet, polished, many figures and comments.

@@
 \response{%
-Response will be here.
+We added the logic tree to the study to consider the epistemic uncertainty, instead of giving the range of uncertainty.
+In practice, we define the grids for the whole region, however, estimate the $a-value$ and also the probability of exceedance for each region, separately.
+To do that, in each run we just provide the seismic source data ( in this case location and magnitude) for the specific region.
+Based on the logic tree approach we conducted 162 runs to get the results $(3 M * 3 B * 6 R(5 region+1 uniform)*3 GMPE)$.
 }
@@
 \response{%
-Response will be here.
+Thanks. Modified it. 
 }
@@
 However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying b- and Mmax-values for the R model greatly complicate the comparison.
-As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references?Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015).
+As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references, Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015).
 Applying these methods is beyond the scope of this work, but might be recognized as a future direction.
@@
 \response{%
-Response will be here.
+Thanks for the informative comment.
+In Figure 10, we combined the regional (R) and uniform (U) results (We combine the probability of exceedance, then compute the pga)  with similar weights (i.e., 0.5).
+The positive and negative standard deviation plots comes from GMPE+Uncertainty  and GMPE-Uncertainty.
+We were showing the range of variation for PGA around the median value.
+As we discussed before, in order to consider the epistemic uncertainty, instead of presenting the range of uncertainty, we used the logic tree approach and modified Figure 10.
+The weights are presented in logic tree figure.
 }
@@
 \response{Thanks for the comment.
-Based on explanation of GMPEs section (please see comment no.?) we decided to define a suite of GMPE and also provide the uncertainty.
-We consider the epistemic uncertainty, based on defining two different model (which considers the uncertainty in $b-value$ and $M_max$).
-In order to make it clear we added two GMPE suites (plus and minus one standard deviation) also we defined the uncertainty in $M_{max}$.
-This approach will cover the most of uncertainty in the study.}.
+Based on explanation of GMPEs section (please see comment no.?) we decided to define a suite of GMPE as well as plus and minus one standard deviation.
+We consider the epistemic uncertainty in tectonic seismic regions, $M_{max}$, $b-value$, and attenuation relationship through a standard logic tree analysis.}.
 
@@
 
-\response{That right. We increased the buffer zone up to 2 degrees. (Haven't modified the text)}
+\response{That is right. We increased the buffer zone up to 2 degrees. (Haven't modified the text)}
 
@@
 }
-\response{Response will be here.}
+\response{We  added the reference for figure 1. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{They didn't provide a numerical value, or numbers on the contour lines, however, we read the images with Matlab and locate the values. We added to the table. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{Modified. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{We added a comprehensive logic tree analysis after revision.}
 
@@
 p 26, table3 $\to$ Specify units.}
-\response{Response will be here.}
+\response{Done. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{Thanks for the comment.
+The problem with that region is having less than and equal sign on magnitude 4.
+There are many earthquakes go to that category because of that condition.
+Since, converting earthquake magnitude always has an error margin, we think the comment is relevant.
+Based on the data we assume 2005 as a completeness magnitude.
+We presented the legends at the bottom of the figure.}
 
@@
 p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
-\response{Response will be here.}
+\response{Added.}
 
 \introcomment{~}{%
-Summary of modifications (Remove before submitting)\\
+Summary of modifications (May or may not addressed as comment.)\\
 - Buffer zone updated.\\
@@
 - Figure 11: Updated.\\ 
+- Figure 8: Updated.\\
+- Figure 10: Updated.\\
 }

### 2016-10-01 attenuation.tex
Updatet, polished, many figures and comments.

@@
 The last piece in our hazard analysis process is the choice of an adequate attenuation relationship, or ground motion prediction equation (GMPE).
-This is a highly influential factor because it controls the spatial extent to which the local occurrence of earthquakes can influence regional hazard.
+This is a highly influential factor because it controls \myrevision{the intensity level at a particular site given earthquake locations and magnitude from the source model.}
 

### 2016-10-01 completeness.tex
Updatet, polished, many figures and comments.

--- 2016-07-20 completeness.tex
@@
 This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process.
-The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range \myrevision{which in this study we use these values in estimating $a-values$ of smoothed seismic hazard}, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+\myrevision{ We use $M_c$ for each catalog to compute the $b-value$ and $M_{max}$}
 

### 2016-10-01 parameters.tex
Updatet, polished, many figures and comments.

@@
 We call it the \textit{U Model}.
-Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones have different seismicity parameters.
+Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}.
 However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty.

### 2016-10-01 region.tex
Some comments addressed. Modified Figure1 to 2 degrees buffer zone. Figure2: modified seismicity.sh, updated historical.txt and instrumental.txt
Updatet, polished, many figures and comments.

@@
 
-At the northeast of Iran, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault (NTF) system.
+At the \myrevision{northwest} of Iran, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault (NTF) system.
 This system, shown in Fig.~\ref{fig:selected}a, is a complex northwest-trending structure with a predominant right-lateral, strike-slip faulting mechanism \citep{Berberian1999}.
@@
 In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.7 1721 Tabriz earthquake in the southeastern section, the $M$ 7.6 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
-According to \citet{Jones1834}, the Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively, and the latter presented vertical separations of about 2 to 4 m.
+According to \citet{Jones1834}, the \myrevision{1721} Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively, and the latter presented vertical separations of about 2 to 4 m.
 The locations of these and other notable events, including the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes, are shown in Fig.~\ref{fig:selected}b.

### 2016-10-01 completeness.tex
tables are updated.

@@
                         & \multicolumn{5}{c}{Year for $M_w$ ranges} 
-                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} & &$M_c$\\
+                                                            & & \multicolumn{3}{c}{$M_c$ for sub-catalogs} & & \\
         \cline{2-6} \cline{8-10}                                                                      			\\[-1.6ex]
                         & 3--4 & 4--5 & 5--6 & 6--7 & \multicolumn{1}{c}{$>7$} 
-                                                            & & 1800--1899 & 1900--1999 & 2000--2015  & & Whole	\\[0.6ex]
+                                                            & & 1800--1899 & 1900--1999 & 2000--2015  	\\[0.6ex]
         \hline                                                                                        			\\[-1.6ex]
-        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042  & &     6.0    &     5.0    &     4.2     & &  4.2 	\\
-        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3.5     & &  4.3 	\\
-        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     4.0     & &  4.9 	\\
-        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     & &  4.8 	\\
-        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     4.0     & &  4.8 	\\
-        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.8    &     3.8     & &  4.8 	\\[0.5ex]
+        Azerbaijan      & 2005 & 1961 & 1900 & 1581 & 1042  & &     5.8    &    4.9    &     3.6    \\
+        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3    \\
+        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     3.9    \\
+        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439  & &     5.3    &     4.8    &     3.9     \\
+        Central-East    & 2005 & 1961 & 1900 & 1837 &  762  & &     5.5    &     4.8    &     3.6   \\
+        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401  & &     6.1    &     4.9    &     3.9   \\[0.5ex]
         \hline 

### 2016-10-01 parameters.tex
tables are updated.

@@
 Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
-
+\myrevision{
 \begin{table}%[t]
@@
         \hline                                                                              \\[-1.6ex]
-        Azerbaijan      & 1.16 $\pm$ 0.03   & 7.80 $\pm$ 0.38   & 7.7                       \\
-        Alborz          & 1.00 $\pm$ 0.03   & 7.80 $\pm$ 0.52   & 7.8                       \\
-        Kopeh Dagh      & 0.92 $\pm$ 0.03   & 7.73 $\pm$ 0.28   & 7.6                       \\
-        Zagros          & 1.02 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
-        Central-East    & 1.01 $\pm$ 0.03   & 7.79 $\pm$ 0.31   & 7.6                       \\
-        Uniform Model   & 0.95 $\pm$ 0.01   & 7.84 $\pm$ 0.27   & 7.8                       \\[0.5ex]
+        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
+        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
+        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
+        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
+        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
+        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
         \hline 
@@
 \end{table}
-
+}
 \begin{figure*}[t]

### 2016-10-01 figures/gmt/plot-smoothed-diff.sh
Update and pulished figures.

@@ -1,6 +1,6 @@
 
 FILEONE=$1
-FILETWO=uniform_$1
+FILETWO=$2
 CPTFILE=tmp.cpt
 OUTFILE=tmp.ps
 GRDFILE1=tmp1.grd

### 2016-10-03 response.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.

@@
 }
-\response{Response will be here.}
+\response{According to Wiemer and Wyss (2000), the priority is picking the magnitude which has the peak goodness-of-fit value.
+However at some cases for two or a couple of magnitudes the goodness-of-fit scores are not considerably different.
+In these cases, we pick the minimum magnitude, even though it doesn't have the peak goodness-of-fit value, in order to preserve the valuable earthquake event data.}
 
@@
 }
-\response{We added a comprehensive logic tree analysis after revision.}
+\response{We added a comprehensive logic tree analysis after revision and modified the weights. Please see the text.}
 
@@
 p 25, table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
-\response{There are earthquakes out of the regions, mainly above the Caspian see. Since those area are not in our region of interest, and are fairly far from our region, we ignored them.}
+\response{There are earthquakes out of the regions, mainly above the Caspian see.
+Since those area are not in our region of interest (They mainly are in country of Azerbaijan), and are fairly far from our region, we ignored them.}
 

### 2016-10-03 attenuation.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.

@@
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/attenuation.pdf} 
+    \caption{Variation of horizontal peak ground acceleration (PGA) with distance.
+KG2004: \citet{Kalkan2004}, BA2008: \citet{Boore2008}, AB2010: \citet{Akkar2010}, SO2012: \citet{Soghrat2012}.
+The dashed line are $\pm$uncertainty of KG2004.}
+    \label{fig:att}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/logic.pdf} 
+    \caption{Logic tree for seismic hazard component in the North Iran.}
+    \label{fig:logic}
+\end{figure*}
+
 \section{Attenuation Relationship}
@@
 For the specific case of PGA ($T=0$ s), however, the best results were those obtained with the GMPEs introduced by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}.
+\myrevision{\citet{Soghrat2012} and \citet{Akkar2010} are other attenuation relationships which provide higher scores.}
 
 Since our hazard analysis here focuses on PGA values only, we concentrated our attention in the last set of GMPEs.
-In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other.
-Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{led} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
+In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other.\myrevision{ Fig.~\ref{fig:att} illustrates the variation of horizontal components pga (in g) with distance for four different magnitude.
+Epistemic uncertainty is being considered by using different GMPEs through logic tree approach.
+As \citet{Atkinson2014} suggested, in most cases multiple-GMPEs approach is not necessarily acknowledge the epistemic uncertainty.
+This fact is also obvious from the Fig.~\ref{fig:att} where the alternative approach which is using \citet{Kalkan2004} as a backbone GMPE as well as uncertainties covers a broader range in compare with using the combination of GMPEs.} Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{led} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
 These results meant that neither of them had a substantial advantage over the others.
+\myrevision{Fig.~\ref{fig:logic} represents the total logic tree approach in order to consider the uncertainty in tectonic seismic region, $M_{max}$, $b-value$, and estimated PGA.
+The weights are chosen based on previous studies \citep[e.g.,][]{Pettersen2015}.
+We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}
 

### 2016-10-03 compilation.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.

@@
 In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and augment it for our particular region of interest.
-This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
+This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project \myrevision{\citep{GEM}}.
 It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity.
@@
 Selection and declustering was also done in a manner consistent with the original catalog, using the method of \citet{Gardner1974}.
+\myrevision{Total number of earthquake events in the box before decluttering were 10441, with 971 foreshocks and 4206 aftershocks}.
 In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, augmented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new catalog removing foreshocks and aftershocks.

### 2016-10-03 completeness.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.

@@
 The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range \myrevision{which in this study we use these values in estimating $a-values$ of smoothed seismic hazard}, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
-\myrevision{ We use $M_c$ for each catalog to compute the $b-value$ and $M_{max}$}
+\myrevision{ We use $M_c$ for each catalog to compute the $b-value$ and $M_{max}$.}
 
@@
 
-The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), and the $M_c$ values for the complete regional catalogs and the start-years of completeness are used later for computing the hazard.
+The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), \myrevision{and} the start-years of completeness are used later for computing the hazard.
 Admittedly, the choice of the start-years is highly subjective.

### 2016-10-03 introduction.tex
Updatet, polished, many figures and comments.
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.

--- 2016-09-23 introduction.tex
@@
 It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the \myrevision{eighth} century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
+\myrevision{(see Fig.~\ref{fig:iran})}
 
@@
 
-Most previous studies focus on particular locations or are based on specific categorization of seismogenic faults, which are often subjectively interpreted and limited to data availability.
-We use the smoothed seismicity method introduced by \citet{Frankel1995}.
+\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafai2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}.
 This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
@@
 Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness and the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude $M_w \geq 5$.
+Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude \myrevision{$M_w \geq 4.5$}.
 We analyze our results in light of similar estimates available in the literature and summarize the most relevant conclusions.

### 2016-10-03 results.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.

@@
 
-Fig.~\ref{fig:pga} shows the expected mean PGA values obtained using the selected attenuation relationship in units of gravity (g) throughout the region of interest for the different models, R2, R10, U2 and U10.
+Fig.~\ref{fig:pga} shows the expected mean PGA values obtained \myrevision{as first and second branch of the logic tree approach} for the different models, R2, R10, U2 and U10.
 As can be expected, the highest PGA values are associated with the R2 and U2 models, and the lowest with the R10 and U10 models.
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-11} 
-    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U).}
+    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U).
+\myrevision{Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}}
     \label{fig:hazardcurve}

### 2016-10-04 abstract.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.
Rewrote part of the results.and attributes.

@@
 The results are presented in terms of expected peak ground acceleration maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
+\myrevision{According to this study, maximum hazard happened at the left side of the North Tabriz (1g, 0.62g) , and the right side of the North Alborz faults (0.94 g,0.55 g) for 2 and 10 percent of probability of exceedance in 50 years.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
 In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.

### 2016-10-04 attenuation.tex
Rewrote part of the results.and attributes.

@@
 In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other.\myrevision{ Fig.~\ref{fig:att} illustrates the variation of horizontal components pga (in g) with distance for four different magnitude.
-Epistemic uncertainty is being considered by using different GMPEs through logic tree approach.
+In practice, epistemic uncertainty is being considered by using different GMPEs through logic tree approach.
 As \citet{Atkinson2014} suggested, in most cases multiple-GMPEs approach is not necessarily acknowledge the epistemic uncertainty.
@@
 \myrevision{Fig.~\ref{fig:logic} represents the total logic tree approach in order to consider the uncertainty in tectonic seismic region, $M_{max}$, $b-value$, and estimated PGA.
-The weights are chosen based on previous studies \citep[e.g.,][]{Pettersen2015}.
+The weights are chosen based on previous studies \citep[e.g.,][]{Petersen2015}.
 We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}

### 2016-10-04 conclusions.tex
Rewrote part of the results.and attributes.

@@
 While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers.
-Future work to improve the results presented here should consider alternative attenuation relationships, especially for estimating other ground motion parameters such as response spectral accelerations for different periods and site effects.
+Future work to improve the results presented here should consider \myrevision{other} ground motion parameters such as response spectral accelerations for different periods and site effects.

### 2016-10-04 hazard.tex
Rewrote part of the results.and attributes.

@@
 where $\tilde{n}_i$ is the smoothed, normalized number of events in cell $i$, $\Delta_{ij}$ is the distance between the $i$-th and $j$-th cells, and $c$ is the correlation distance.
-\myrevision{An alternative smoothing kernel has been used in recent studies \citep[e.g.][]{Moscheti2015}}.The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
+\myrevision{An alternative smoothing kernel has been used in recent studies \citep[e.g.][]{Moschetti2015}}.The summations in Eq.~\ref{eq:nnorm} are calculated over the number of $j$ cells within a distance $3c$ from the $i$-th cell.
 It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
@@
 According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records.
-\myrevision{Also some studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing length for adaptive and fixed smoothed seismicity methods \citep[e.g.][]{Werner2011,Moscheti2015}}.
+\myrevision{Also some studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing length for adaptive and fixed smoothed seismicity methods \citep[e.g.][]{Werner2011,Moschetti2015}}.
 We use an intermediate value of $c=30$~km.

### 2016-10-04 introduction.tex
Rewrote part of the results.and attributes.

@@
 
-\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafai2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}.
+\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}.
 This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.

### 2016-10-04 results.tex
Rewrote part of the results.and attributes.

@@
 
-Fig.~\ref{fig:pga} shows the expected mean PGA values obtained \myrevision{as first and second branch of the logic tree approach} for the different models, R2, R10, U2 and U10.
+Fig.~\ref{fig:pga} shows the expected mean PGA values obtained \myrevision{as the first and the second branch of the logic tree approach} for the different models, R2, R10, U2 and U10.
 As can be expected, the highest PGA values are associated with the R2 and U2 models, and the lowest with the R10 and U10 models.
-For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Kopeh Dagh region (near the border with Turkmenistan), and in a small area half-way between the city of Karaj and the Piranshahr fault, where a small concentration of events can be observed in Fig.~\ref{fig:catalog}b, as well as along the Piranshahr and Morvarid fault lines between the Zagros and Azerbaijan seismic regions (see Fig.~\ref{fig:selected}a for reference).
-The Azerbaijan seismic zone does not present equally high levels of expected ground motion.
+For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Azerbaijan region at the left side of the North Tabriz Fault and also in border of Kopeh Dagh and Alborz tectonic seismic regions at the right side of the North Alborz Fault.
+We observe higher hazard in the Alborz region an small area at right side of the Mosha Fault.
 For the U model results shown in Fig.~\ref{fig:pga}b, on the other hand, the highest levels of expected ground motion are observed precisely in the area corresponding to the Azerbaijan seismic region, especially in the vicinity of the North Tabriz Fault system (see Fig.~\ref{fig:selected} for reference).
@@
 In this figure, positive values indicate that the U models have larger mean PGA values than the R models.
-As it can be seen, this is true practically throughout the whole region at very low levels, and in particular in the north-central region at a moderate level of up to 0.2 g and more predominantly in the north-western region of Azerbaijan at levels of about 0.2 to 0.45 g.
+As it can be seen, this is true practically throughout the whole region at very low levels, and in particular in the north-west region at a moderate level of up to 0.2 g and more predominantly in the Zagros at levels of about 0.2 to 0.45 g.
+The higher results in uniform model occurred because of higher $M_{max}$ and lover $b-value$ in comparison with regional model.
 
 Overall, these results are consistent with the seismicity observed in Fig.~\ref{fig:catalog}.
-The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with \myrevision{a} concentration of strong earthquakes in the Alborz and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
+The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with \myrevision{a} concentration of strong earthquakes in the Azerbaijan and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
 This is because of the higher $b$-value obtained for the Azerbaijan region in the R model as opposed to the lower value for the U model.
@@
 A means to address this is to use combinations of different models to incorporate information from all possible models.
-This would also be true, for instance, if in the future we were to consider other attenuation relationships.
-Here we also computed the expected levels of ground motion for a combination of the R and U models (with equal weights).
+Here we also computed the expected levels of ground motion for a combination of the R and U models which is the final result of the logic tree approach as shown at ~\ref{fig:logic}.
 We refer to this as the (R,U) model.
-The results of this combined model are shown in Fig.~\ref{fig:pga.ru.std} in the form of expected mean PGA values, along with the marginal values of plus and minus one standard deviation.
-Here, the standard deviation is carried forward in the calculation from the attenuation relationship and thus affects every grid point differently depending on the added contributions from each region.
+The results of this combined model are shown in Fig.~\ref{fig:pga.ru.std} in the form of expected mean PGA values.
 
 As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a, and thus we consider it to be a better assessment of the seismic hazard in the region.
-It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the Piranshahr and Morvarid faults in the Zagros region and that of the different faults in the Alborz and Kopeh Dagh regions.
-In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2+STD model results, where the expected accelerations are of the order of 1.4 g to the northwest of \myrevision{the} city of Tabriz.
+It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the North Alborz fault in the Alborz region and that of the different faults in the Kopeh Dagh region.
+In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2 model results, where the expected accelerations are of the order of 1.0 g to the northwest of \myrevision{the} city of Tabriz.
 These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigating peak accelerations.
@@
 
-We also note that the overall distribution of mean PGA values shown in the middle panels in Fig.~\ref{fig:pga.ru.std} are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}.
-These estimates also agree, on average, with other previous studies.
+\myrevision{
+We also note that the overall distribution of mean PGA pattern agrees with the recent study by \citet{Khodaverdian_2016_BSSA}.
+However, in general, their results are slightly lower than this study.
+They provided a rough estimate of the PGA, and the seismicity parameters, like completeness magnitude, the catalog, $M_{max}$, and $b-value$ are different in these two studies.
+Consequently, we don't expect to match the results.
+For example  in case of $b-value$, in the same study region, \citet{Khodaverdian_2016_BSSA} reported very high variation of $b-value$ (0.56 - 1.27).
+56\% of grid points have $b-value > 1$ and 53 \% of them are greater than 1.1.
+Where in this study the $b-value$ has a narrow range of variation (0.93-1.15).
+These estimates also agree, on average, with other studies.
+For the Azerbaijan tectonic seismic region for the city of Uremia, we found 0.24 g which is slightly lower than \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for 10 \% probability of exceedance in 50 years.
+For a 2\% probability of exceedance in 50 years, \citet{Golara2014} expected acceleration on the order of 0.3 - 0.5 g, where or mean value is 0.38 g.
+For the city of Tabriz, the results match with \citet{BHRC2014} and are in the range of \citet{Zare2012} for 10 \% probability of exceedance in 50 years.
+\citet{Vafaie2011} expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\% probability of exceedance in 50 years, respectively, where our mean values are about 0.61 and 0.35 g for the same corresponding probabilities.
+For the city of Ardabil, we found 0.73 g and 0.43 g for 2 and 10\% probability of exceedance in 50 years.
+Our results are slightly higher than \citet{BHRC2014}, however, for 10\% probability of exceedance in 50 years, the results are in the range reported by \citet{Zare2012}.
+For 2\% probability of exceedance in 50 years, our results are very close to \citet{Golara2014} and \citet{Khodaverdian_2016_BSSA}.
+In the Alborz tectonic seismic region for the city of Rasht, our results are in a well agreement with the recent study of \citet{Abdollahzadeh2014}.
+For the city of Tehran, the results are in agreement with \citet{Abdi2013}, and slightly lower than  \citet{BHRC2014}, \citet{Za2012}, and \citet{Golara2014} for 10\% probability of exceedance in 50 years.
+For 2\% 10\% probability of exceedance in 50 years, our results are lower than \citet{Golara2014} and higher than \citet{Khodaverdian2015}.
+For the Kopeh Dagh tectonic seismic region for the city of Mashhad, results are lower than \citet{BHRC2014} and higher than \citet{Khodaverdian_2016_BSSA}.}
+
+%We also note that the overall distribution of mean PGA  agree, on average, with other previous studies.
 For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.35 and 0.50 g in the (R,U)10 model.
@@
 As mentioned before, overall, our results are close \myrevision{to} or within the ranges from most studies.
-The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher than the rest, especially in the cities of Tabriz, Karaj, Tehran and Mashhad, where their results are closer to those of our upper (+STD) range of values.
+The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher than the rest.
+\myrevision{One reason for higher value in \citet{Golara2014} is using the maximum credible earthquake as $M_max$.
+The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{max}$.}
 
@@
 The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the two basic R and U models and the combined (R,U) model.
-In each case we also show the range $\pm 1$ standard deviation (shaded areas).
 These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance.
@@
     \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran.
-Here, the two previous studies just mentioned are identified with the codes Gh03 and Bo15, respectively.}
+Here, the two previous studies just mentioned are identified with the codes Gh03 and Bo15, respectively.
+Also the PGA ranges of the \ref{tab:pga} are represented.
+The shaded area represents the upper and lower value of uncertainty at the GMPEs.}
     \label{fig:tehran}
 \end{figure}
-
+\myrevision{
 Last, we put additional attention on the results for the capital city of Tehran.
-We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015}.
-Our results are similar to those obtained by \citet{Ghodrati2003} in the range between 0.2 and 0.7 g (corresponding to annual probabilities of exceedance between $10^{-5}$ and $10^{-2}$), but the trend indicates we would obtain increasingly higher probabilities associated with PGA values above 0.8 g.
+We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015} as well as ranges from other studies for 2 and 10\% probability of exceedance in 50 years.
+Our results are similar to those obtained by \citet{Boostan2015} in the range between 0.1 and 0.3 g (corresponding to annual probabilities of exceedance between $10^{-3}$ and $10^{-1}$), and then it is in the mean range of the mentioned studies.
 Conversely, the trend in the hazard curve from \citet{Boostan2015} suggest the city is to expect significantly higher levels of ground motion at higher probability rates, which is contrary to our findings and those of \citet{Ghodrati2003}.
+Expected PGA range of other studies mentioned at the \ref{tab:pga}, represents, on average, our study presents trustable results.
+The shaded area, represents the upper and lower value of uncertainty at the GMPEs.
+In other word the upper part edge is calculated by just considering GMPEs+Unc  and the lower edge is calculated by just considering GMPEs-Unc.
+It perfectly represents that almost all studies are in the range of uncertainty of the GMPEs, and using one appropriate backbone GMPE as well as the uncertainties could have better role in considering the epistemic uncertainty than using multiple GMPEs as \citet{Atkinson2014} concluded.}

### 2016-10-14 results.tex
improved figure 7 and renamed 12 to 14
rename to new figures 12 and 13
rename to new figures 10 and 11

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf} 
+    \includegraphics[width=\textwidth]{figures/pdf/figure-12.pdf}
     \caption{Expected PGA values throughout the region of interest for 2 (left) and 10 (right) percent probability of exceeding an earthquake magnitude $M_w$ 5 using the combined model (R,U) hazard calculations.
@@
 \input{table-pga}
+
+\begin{figure*}%[h!]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-13}
+    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U).
+\myrevision{Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}}
+    \label{fig:hazardcurve}
+\end{figure*}
 
@@
 
-\begin{figure*}[th!]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-11} 
-    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U).
-\myrevision{Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}}
-    \label{fig:hazardcurve}
-\end{figure*}
-
-\myrevision{
+\myrevision{%
 We also note that the overall distribution of mean PGA pattern agrees with the recent study by \citet{Khodaverdian_2016_BSSA}.
@@
     \centering
-    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-12} 
+    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-14}
     \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran.
@@
 \end{figure}
-\myrevision{
+
+\myrevision{%
 Last, we put additional attention on the results for the capital city of Tehran.

### 2016-10-17 response.tex
Rewrote part of the results.and attributes.
two comments added to the response file.

@@
 \response{%
-Response will be here.
+In Khodaverdian et al (2016), seismicity parameters like $b-value$ and $M_{max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
+Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point.
+Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.
 }
@@
 \response{%
-Response will be here.
+Ricardo, I couldn't find any paper or report as a reference in their website. Please see. 
 }
@@
 \response{%
-Added. Thanks.
+Added. Thanks. (No need to add more explanation. Please see the email.)
 }

### 2016-10-18 abstract.tex
working on figure 14 and abstract

--- 2016-07-15 abstract.tex
@@
 We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh; and for completeness, we also consider the contribution of parts of other neighboring seismic zones that fall within our region of interest.
-In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude.
+\myrevision{In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources distributed within regular grid cells.
 After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
 Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region.
-We also consider the combination ot these two basic models.
-The results are presented in terms of expected peak ground acceleration maps and hazard curves at select locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
-In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.
+In the analysis we consider uncertainties in the ground motion prediction equation, the seismic parameters and combine these basic two models using a logic tree.} The results are presented in terms of expected peak ground acceleration maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+\myrevision{According to our results, the highest levels of hazard are observed in areas west of the North Tabriz and east of the North Alborz faults, where expected peak ground accelerations between about 0.5 g and 1 g have a 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
+We find our results to be helpful in understanding seismic hazard for northern Iran, but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest.

### 2016-10-18 response.tex
Addressed remaining comments, except three of them.

@@
 \response{Thanks for the comment.
-Based on explanation of GMPEs section (please see comment no.?) we decided to define a suite of GMPE as well as plus and minus one standard deviation.
+Based on explanation of GMPEs section (please see comment no.27) we decided to define a suite of GMPE as well as plus and minus one standard deviation.
 We consider the epistemic uncertainty in tectonic seismic regions, $M_{max}$, $b-value$, and attenuation relationship through a standard logic tree analysis.}.
@@
 
-\response{That is right. We increased the buffer zone up to 2 degrees. (Haven't modified the text)}
+\response{That is right. We increased the buffer zone up to 2 degrees.}
 
@@
 }
-\response{Response will be here.}
+\response{Added to the abstract.}
 
@@
 }
-\response{Response will be here.}
+\response{We discussed this before. We need to remove the sentence and rewrite that part.}
 
@@
 }
-\response{We reanalyze the hazard with 2 degrees buffer zone. (Not modified in the text.)}
+\response{We reanalyze the hazard with 2 degrees buffer zone. }
 
@@
 }
-\response{Response will be here.}
+\response{Both methods have been used extensively in previous studies. We just picked one. Text was implying that this method has beneficial to the ZMAP method, we fixed it. Thanks.}
 
@@
 \response{As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs.
-We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or ?central?
-GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE.
+We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or central GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE.
 In the previeous study (Khodaverdian 2016), they used Akkar and Bommer (2010) and Ghasemi et al (2009) along side other equations.
@@
 Of course this alternative method has been a hotly-debated topic, and there is no clear consensus about that, however, the plots of attenuation relationships in different magnitude illustrate the fact that with this approach we can address the epistemic uncertainty in an acceptable range.
-We totally agree with the reviewer?s comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers.
-In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig X.}
+We totally agree with the reviewer's comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers.
+In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig 9.}
 
@@
 }
-\response{Response will be here.}
+\response{In revised version. We used backbone and plus and minus one standard deviation as three GMPEs. }
 
@@
 }
-\response{Response will be here.}
+\response{Based on the modification in GMPEs and uncertainties at the revised version, we rewrite the description part.}
 
@@
 }
-\response{We added a comprehensive logic tree analysis after revision and modified the weights. Please see the text.}
+\response{We added a comprehensive logic tree analysis after revision and modified the weights. Please see figure 9.}
 
@@
 }
-\response{Response will be here.}
+\response{That's right. Removed that part. Thanks.}
 
@@
 }
-\response{Response will be here.}
+\response{They used Maximum Credible Earthquake as $M_{max}$.
+The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{max}$.
+}
 
 \comment{45}{%
-line 466 $\to$ exceedance as functions of PGA ? exceedance as functions of PGA, also known as hazard curves}
+line 466: exceedance as functions of PGA  $\to$ exceedance as functions of PGA, also known as hazard curves}
 \response{Added. Thanks.}
@@
 \comment{47}{%
-line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
-}
-\response{Response will be here.}
-
-\comment{48}{%
 lline 488 $\to$ Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
@@
 
-\comment{49}{%
+\comment{48}{%
 line 488:  hazard analysis $\to$ hazard analyses
@@
 
-\comment{50}{%
+\comment{49}{%
 line 490: models as a mean $\to$ models as a means}
@@
 
+\comment{50}{%
+line 493 $\to$ Though you suggest the uniform model is unrealistic on line 334.}
+\response{That's right. We meant to say less realistic. We fixed the text.}
+
 \comment{51}{%
-line 493 $\to$ Though you suggest the uniform model is unrealistic on line 334.}
-\response{Response will be here.}
-
-\comment{52}{%
 line 502 $\to$ for providing advise ? for providing advice}
@@
 
-\comment{53}{%
+\comment{52}{%
 line 509 $\to$  Should this be Sunset?}
@@
 
-\comment{54}{%
+\comment{53}{%
 p 25, table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
@@
 
-\comment{55}{%
+\comment{54}{%
 p 26, table3 $\to$ Specify units.}
@@
 
-\comment{56}{%
+\comment{55}{%
 p32, figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
@@
 
-\comment{57}{%
+\comment{56}{%
 p34, figure 5 $\to$ Which seismic zone corresponds to which color?
@@
 
+\comment{57}{%
+P37: 10 percent of probability $\to$ 10 percent probability }
+\response{Done.}
+
 \comment{58}{%
-P37: 10 percent of probability $\to$ 10 percent probability }
-\response{Response will be here.}
-
-\comment{59}{%
 p 39,figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
@@
 
-\comment{60}{%
+\comment{59}{%
 p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
@@
 
-\introcomment{~}{%
-Summary of modifications (May or may not addressed as comment.)\\
-- Buffer zone updated.\\
-- Data updated.\\
-- b-values updated.\\
-- Completeness parameters updated.\\
-- Figure 1: Buffer Zone Updated.\\
-- Figure 3: Seismicity.sh modified. Historical.txt and Instrumental.txt updated to new data. \\
-- Figure 4: Updated.\\
-- Figure 5: The excel file is updated. The figure needs to be updated.\\
-- Figure 6: Updated data completeness plots added to the figure. Figure needs final polishing. \\
-- Figure 7: Updated.\\
-- Figure 11: Updated.\\ 
-- Figure 8: Updated.\\
-- Figure 10: Updated.\\
-}
-
 \end{document}

### 2016-10-18 completeness.tex
Addressed remaining comments, except three of them.

@@
 Two common approaches are maximum curvature and the goodness-of-fit test methods.
-The maximum curvature method, or MAXC for simplicity, is widely used because as it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+\myrevision{Both methods have been used extensively at previous studies}.The maximum curvature method, or MAXC for simplicity, is widely used because as it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
 \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
-We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
+\myrevison{\citet{Moscheti2015} applied a combination of methods to study the  long-term earthquake rate model for the Central and Eastern United States.} We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
 

### 2016-10-18 introduction.tex
Addressed remaining comments, except three of them.

@@
 This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
-Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
-While we recognize that probabilistic seismic hazard analysis based on fault systems can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
+\myrevision{In \citep{Khodaverdian_2016_BSSA}, seismicity parameters like $b-value$ and $M_{max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
+Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point.
+Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.} Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
+While we recognize that \myrevision{fault-based/geologic-based earthquake recurrence estimates } can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
 In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}).

### 2016-10-18 parameters.tex
Rewrote part of the results.and attributes.
Addressed remaining comments, except three of them.

@@
 We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog.
-\myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko1989} method.
+\myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko_1989_BSSA} method.
 Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.
@@
 We call it the \textit{U Model}.
-Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}.
+Admittedly, this assumption is somewhat \myrevision{less-realistfic} if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}.
 However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty.

### 2016-10-18 results.tex
updated to match figure files
Addressed remaining comments, except three of them.

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-08.pdf}
+    \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf}
     \caption{Expected mean peak ground acceleration (PGA) for 2 and 10 percent of probability of exceedance in 50 years for (a) the five-seismic regions R model and (b) the uniform seismic region U model.}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-09.pdf}
+    \includegraphics[width=\textwidth]{figures/pdf/figure-11.pdf}
     \caption{Difference between the mean PGA values from models U and R for 2 (left) and 10 (right) percent probabilities of exceedance in 50 years.}
@@
 
-As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a, and thus we consider it to be a better assessment of the seismic hazard in the region.
+As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a.
 It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the North Alborz fault in the Alborz region and that of the different faults in the Kopeh Dagh region.

### 2016-10-19 response.tex
References fixed. Response document polished. Summary of other studies added.

@@
 \response{%
-Response will be here.
+Added thanks.
 }
@@
 \response{%
-Ricardo, I couldn't find any paper or report as a reference in their website. Please see. 
+Added. Thanks.
 }
@@
 \response{%
-Added. Thanks. (No need to add more explanation. Please see the email.)
+Added. Thanks. 
 }
@@
 \response{%
-Yes it is truncated GR model. (Figure caption is not fixed yet.)
+Yes it is truncated GR model. 
 }
@@
 }
-\response{Response will be here.}
-
+\response{In the introduction we explain the method and parameters here and there, however, we added a couple of sentences to briefly explain the method. Thanks}
 \comment{8}{%
@@
 }
-\response{Two reviewer suggested two different word. Both of them are correct. Please see.}
+\response{Fixed. Thanks.}
 
@@
 }
-\response{In revised version. We used backbone and plus and minus one standard deviation as three GMPEs. }
+\response{In the revised version we used backbone and plus and minus one standard deviation as three GMPEs. }
 
@@
 The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{max}$.
+We added the explanation to the text.
 }
@@
 line 475 $\to$ Can you explain the differences in the hazard analysis that led to differences in hazard?}
-\response{Response will be here.}
+\response{Added to the text.}
 
@@
 }
-\response{Response will be here.}
+\response{That is right. We restate the sentence. Thanks.}
 

### 2016-10-19 attenuation.tex
rename figures to new 8 and 9
References fixed. Response document polished. Summary of other studies added.

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/attenuation.pdf} 
+    \includegraphics[width=\textwidth]{figures/pdf/figure-08} 
     \caption{Variation of horizontal peak ground acceleration (PGA) with distance.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/logic.pdf} 
+    \includegraphics[width=\textwidth]{figures/pdf/figure-09}
     \caption{Logic tree for seismic hazard component in the North Iran.}
@@
 As \citet{Atkinson2014} suggested, in most cases multiple-GMPEs approach is not necessarily acknowledge the epistemic uncertainty.
-This fact is also obvious from the Fig.~\ref{fig:att} where the alternative approach which is using \citet{Kalkan2004} as a backbone GMPE as well as uncertainties covers a broader range in compare with using the combination of GMPEs.} Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{led} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
+This fact is also obvious from the Fig.~\ref{fig:att} where the alternative approach which is using \citet{Kalkan2004} as a backbone GMPE as well as uncertainties covers a broader range in compare with using the combination of GMPEs.} Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{leads} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
 These results meant that neither of them had a substantial advantage over the others.

### 2016-10-19 compilation.tex
References fixed. Response document polished. Summary of other studies added.

@@
 In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and augment it for our particular region of interest.
-This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project \myrevision{\citep{GEM}}.
+This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project \myrevision{cited{Zare2014}}.
 It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity.

### 2016-10-19 completeness.tex
References fixed. Response document polished. Summary of other studies added.

@@
 \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
-\myrevison{\citet{Moscheti2015} applied a combination of methods to study the  long-term earthquake rate model for the Central and Eastern United States.} We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
+\myrevision{\citet{Moschetti2015} applied a combination of methods to study the  long-term earthquake rate model for the Central and Eastern United States.} We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
 

### 2016-10-19 conclusions.tex
References fixed. Response document polished. Summary of other studies added.

@@
 In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model.
-Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard \myrevision{analyses} due to the usage of a more complete catalog and inclusion of low-magnitude events.
+Our calculations yield results similar to those of other studies, \myrevision{however, provide different perspective of seismic hazard than previous hazard \myrevision{analyses} due to the usage of a more complete catalog and inclusion of low-magnitude events}.
 In our analysis we found it convenient to combine both the regional and uniform models as a \myrevision{means} to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones.

### 2016-10-19 introduction.tex
References fixed. Response document polished. Summary of other studies added.

@@
 We, however, focus our attention in the northern three seismic zones of the country assuming regionally-based and smoothed seismic parameters.
-Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
+\myrevision{We used two regional and uniform model based on considering of uncertainty in ground motion level, $b-value$, and $M_{max}$, using the most updated seismic catalog of the region.
+For the regional model we assumed uniform $b-value$ for each region.} Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
 Such improvements are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran.
@@
 Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.} Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
-While we recognize that \myrevision{fault-based/geologic-based earthquake recurrence estimates } can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
+While we recognize that \myrevision{fault-based/geologic-based earthquake recurrence estimates} can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
 In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}).

### 2016-10-19 results.tex
References fixed. Response document polished. Summary of other studies added.

@@
 Where in this study the $b-value$ has a narrow range of variation (0.93-1.15).
+They computed the seismicity parameters for each grid point inside a circle with radius of 200 around the grid point, whereas in this study we considered a uniform seismicity parameters for each region.
 These estimates also agree, on average, with other studies.
 For the Azerbaijan tectonic seismic region for the city of Uremia, we found 0.24 g which is slightly lower than \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for 10 \% probability of exceedance in 50 years.
+\citet{Zare2012} expected to see higher values because of using parametric method.
 For a 2\% probability of exceedance in 50 years, \citet{Golara2014} expected acceleration on the order of 0.3 - 0.5 g, where or mean value is 0.38 g.
@@
 In the Alborz tectonic seismic region for the city of Rasht, our results are in a well agreement with the recent study of \citet{Abdollahzadeh2014}.
-For the city of Tehran, the results are in agreement with \citet{Abdi2013}, and slightly lower than  \citet{BHRC2014}, \citet{Za2012}, and \citet{Golara2014} for 10\% probability of exceedance in 50 years.
-For 2\% 10\% probability of exceedance in 50 years, our results are lower than \citet{Golara2014} and higher than \citet{Khodaverdian2015}.
+For the city of Tehran, the results are in agreement with \citet{Abdi2013}, and slightly lower than  \citet{BHRC2014}, \citet{Zare2012}, and \citet{Golara2014} for 10\% probability of exceedance in 50 years.
+For 2\% 10\% probability of exceedance in 50 years, our results are lower than \citet{Golara2014} and higher than \citet{Khodaverdian_2016_BSSA}.
 For the Kopeh Dagh tectonic seismic region for the city of Mashhad, results are lower than \citet{BHRC2014} and higher than \citet{Khodaverdian_2016_BSSA}.}
@@
 We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015} as well as ranges from other studies for 2 and 10\% probability of exceedance in 50 years.
+By applying different combination of magnitude (M) and distance (R), \citet{Boostan2015} presented a new model for probabilistic seismic hazard assessment based on fuzzy sets theory for Tehran, Iran.
+They expected to achieve higher seismic hazard values because of considering a vast uncertainty range for R and M.
+They concluded, non-fuzzy approaches due to not considering all uncertainties leads to non-conservative results.
+\citet{Ghodrati2003} conducted a probabilistic seismic hazard analysis for the same region based on considering the uncertainty in seismicity value and ground motion level through logic tree approach.
+They consider the uncertainty in seismicity parameters by involving the results of \citet{Tavakoli1999}.
+\citet{Tavakoli1999} reported the $b-value$ and $M_{max}$ as $0.52\pm0.02$ and $7.9\pm0.3$, respectively, which is fairly different from the result of this study.
+Even though   \citet{Ghodrati2003} used three GMPEs model,  \citet{Boostan2015} used only one model as attenuation relationship.
+As we discussed earlier, our model fairly well consider the ground motion level uncertainty.
 Our results are similar to those obtained by \citet{Boostan2015} in the range between 0.1 and 0.3 g (corresponding to annual probabilities of exceedance between $10^{-3}$ and $10^{-1}$), and then it is in the mean range of the mentioned studies.

### 2016-10-20 response.tex
working on introduction

@@
 \response{%
-In Khodaverdian et al (2016), seismicity parameters like $b-value$ and $M_{max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
+In Khodaverdian et al (2016), seismicity parameters like $b$-value and $M_{\max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
 Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point.

### 2016-10-20 abstract.tex
working on introduction

--- 2016-07-18 abstract.tex
@@
 This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data.
-We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh; and for completeness, we also consider the contribution of parts of other neighboring seismic zones that fall within our region of interest.
-In the chosen approach, seismic events are not assigned to specific faults but are instead assumed to be potential seismogenic sources, and are spatially distributed within regular grid cells of size equal to 0.1\textdegree{} in both latitude and longitude.
+We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, \myrevision{and parts of other neighboring seismic zones that fall within our region of interest.
+In the chosen approach, seismic events are not assigned to specific faults but assumed to be potential seismogenic sources distributed within regular grid cells.
 After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes.
 Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region.
-We also consider the combination of these two basic models.
-The results are presented in terms of expected peak ground acceleration maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
-In conclusion, we find our results to be helpful in understanding seismic hazard for northern Iran from a regional perspective, but highlight the fact that different methods may need to be combined to obtain more robust estimates at specific areas of interest.
+In the analysis we consider uncertainties in the ground motion prediction equation, the seismic parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+\myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
+We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions}.

### 2016-10-20 introduction.tex
working on introduction

@@
 It is confined between the convergent movements of the Arabian and Eurasian plates, and laterally trapped between the Arabian and eastern Asia-Minor to the west, and the Indian and Eurasian plates to the east \citep{Berberian_1981_Chap}.
-This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges.
+This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges \myrevision{(see Fig.~\ref{fig:iran})}.
 It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the \myrevision{eighth} century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
-\myrevision{(see Fig.~\ref{fig:iran})}
 
@@
 
-Over the last three decades there have been multiple efforts to better estimate the seismic parameters and hazard, and improve the assessment of seismic risk in Iran \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE, Khodaverdian_2016_BSSA}.
-The most recent of these studies \citep{Khodaverdian_2016_BSSA} focuses \myrevision{on} the estimation of spatially-variable seismic parameters for the whole country using a similar approach to the one we used here.
-We, however, focus our attention in the northern three seismic zones of the country assuming regionally-based and smoothed seismic parameters.
-\myrevision{We used two regional and uniform model based on considering of uncertainty in ground motion level, $b-value$, and $M_{max}$, using the most updated seismic catalog of the region.
-For the regional model we assumed uniform $b-value$ for each region.} Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
-Such improvements are reflected in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran.
-However, other indicators suggest persistent high levels of seismic risk.
-Therefore, more complete and accurate assessments of seismic hazard---incorporating the latest available data and alternative methods---are still necessary.
+\myrevision{Over the last three decades there have been multiple efforts to estimate the seismic parameters and seismic hazard of Iran, and improve the assessment of seismic risk in the country \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE, Khodaverdian_2016_BSSA}.
+Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
+Such improvements are reflected, for instance, in lower overall expected damage ratios, as reported by \citet{Ghodrati2013} for the city of Tehran.
+There is, however, room for improvement.
+The most recent of these studies, \citet{Khodaverdian_2016_BSSA}, presents an estimation of spatially-variable seismic parameters for Iran using an approach similar to the one we use here, but does not necessarily focus on hazard.
+Other previous efforts have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.}
 
-Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil.
-This region has suffered devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.
-Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
-Among other things, these studies have highlighted the prevailing differences between studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.
+\myrevision{In the present study, we focus our attention on northern Iran.
+This region houses about 41 percent (32 million) of the total population of the country, with most living in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil.
+This region has suffered multiple devastating earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}, and has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
+Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.}
 
-\myrevision{Most previous studies focus on particular locations  based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.} We use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
-\myrevision{In \citep{Khodaverdian_2016_BSSA}, seismicity parameters like $b-value$ and $M_{max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
+\myrevision{Most previous studies for northern Iran focus on particular locations based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.
+By contrast, we use an approach based on the smoothed seismicity method introduced by \citet{Frankel1995}.
+We use regionally-based and smoothed seismic parameters derived from an up-to-date seismic catalog, use an appropriate attenuation relationship, and consider various levels of uncertainty.} The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
+\myrevision{In \citep{Khodaverdian_2016_BSSA}, the seismic parameters $b$ and $M_{\max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
 Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point.

### 2016-10-20 introduction.tex
done with introduction for now.

@@
 This region has suffered multiple devastating earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}, and has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
-Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.}
+Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults---even if believed inactive---by adopting new methodos and the latest available data.}
 
-\myrevision{Most previous studies for northern Iran focus on particular locations based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.
+\myrevision{Most previous studies for northern Iran focus on particular locations based on specific seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.
 By contrast, we use an approach based on the smoothed seismicity method introduced by \citet{Frankel1995}.
-We use regionally-based and smoothed seismic parameters derived from an up-to-date seismic catalog, use an appropriate attenuation relationship, and consider various levels of uncertainty.} The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
-\myrevision{In \citep{Khodaverdian_2016_BSSA}, the seismic parameters $b$ and $M_{\max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
-Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point.
-Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.} Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
-While we recognize that \myrevision{fault-based/geologic-based earthquake recurrence estimates} can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
+We use regionally-based, smoothed seismic parameters derived from an up-to-date seismic catalog, and an appropriate attenuation relationship.} The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
+Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
+While we recognize that \myrevision{fault-based or geology-based earthquake recurrence estimates} can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
 In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}).
 In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone.
-We used both these models and the combination of them to interpret seismic hazard in northern Iran.
+We used both these models, \myrevision{and different levels of uncertainty in the seismic parameters and ground motion prediction equation, to combine the results using a logic tree} to interpret seismic hazard in northern Iran.
 
 In the following sections we describe our region of interest in greater detail, review its associated tectonics and seismicity, and provide additional information about the adopted approach.
-Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness and the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters.
-Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude \myrevision{$M_w \geq 4.5$}.
-We analyze our results in light of similar estimates available in the literature and summarize the most relevant conclusions.
+\myrevision{Our results are summarized in terms of seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude \myrevision{$M_w \geq 4.5$}, which we analyze in light of similar estimates available in the literature.}

### 2016-10-20 compilation.tex
region and compilation

--- 2016-09-23 compilation.tex
@@
 	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
-	\caption{Location of events considered in the compiled seismic catalog.
+	\caption{Location of events considered in the compiled seismic catalog \myrevision{for the complete region of interest}.
 (a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}.
@@
 In the case of the historical seismicity catalog, the color fill indicates the year of the event.
-The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief.}
+The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief \myrevision{in the background.
+The dashed box indicates the effective region of interest}.}
 	\label{fig:catalog}
@@
 In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and augment it for our particular region of interest.
-This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project.
+This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project \myrevision{\citep[as mentioned in][]{Zare2014}}.
 It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity.
@@
 We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, \myrevision{also the smaller events help to inform G-R relationship} .
-By contrast, a recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA} used a similar catalog for events $M_w \geq 4$ but only included data through 2011, excluding the 2012 $M_w$ 6.4 Tabriz earthquake that severely damaged the northeast part of the country.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, \myrevision{and to help inform the Gutenberg-Richter relationship}.
+By contrast, in the recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA}, the authors used a similar catalog for events $M_w \geq 4$, but only included data through 2011, thus excluding the 2012 $M_w$ 6.4 Tabriz earthquake, which severely damaged the northeast part of the country.
 
@@
 In these cases we used the empirical relationship introduced by \citet{Deniz2010} to convert $M_D$ to $M_w$.
-Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results agree well with the general trend.
+Although this relationship was derived based on a dataset for $M_w \geq 4.5$ events, we extrapolated the equation for lower magnitudes and found the results to agree well with the general trend.
 
 Selection and declustering was also done in a manner consistent with the original catalog, using the method of \citet{Gardner1974}.
+\myrevision{The total number of earthquakes in the complete region of interest before decluttering are 10,441, with 971 foreshocks and 4,206 aftershocks}.
 In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, augmented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new catalog removing foreshocks and aftershocks.

### 2016-10-20 completeness.tex
region and compilation

@@
         Azerbaijan      & 2005 & 1961 & 1900 & 1581 & 1042  & &     5.8    &     4.9    &     3.6    \\
-        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3    \\
+        Alborz          & 2005 & 1961 & 1900 & 1664 &--401  & &     6.2    &     5.0    &     3.0    \\
         Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9  & &     6.1    &     5.0    &     3.9    \\

### 2016-10-20 region.tex
GMPEs, and logic tree figures added. Text modified up to Results and Analysis section.
region and compilation

@@
 The effective region of interest is shown in greater detail at the bottom.
-Details include the location of the major urban centers and seismic faults in northern Iran.}
+It includes the location of the major urban centers and seismic faults in northern Iran.}
 	\label{fig:iran}
@@
 	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-02}
-	\caption{(a) Main fault line and fault systems, and (b) notable earthquakes in the region of interest.
+	\caption{(a) Main fault line and fault systems, and (b) notable earthquakes in the effective region of interest.
 White lines delimit the three major seismic zones in northern Iran.
@@
 
-We define our region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}.
-These limits correspond to the effective region of interest for which we will present results in subsequent sections.
-Our calculations, however, included data from a slightly larger region with a 0.5\textdegree{}-perimeter as indicated in the figure.
+We define our effective region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:iran}.
+These limits correspond to the area for which we will present results in subsequent sections.
+Our calculations, however, included data from a larger region with a \myrevision{2\textdegree{}-perimeter} as indicated in the figure.
 This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the effective region of interest and/or to provide a uniform contribution from the earthquakes surrounding the region \citep[see][]{Lapajne1997}.
@@
 In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.7 1721 Tabriz earthquake in the southeastern section, the $M$ 7.6 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
-According to \citet{Jones1834}, the \myrevision{1721} Shebli and Tabriz earthquakes had surface ruptures of more than 35 and 42 km, respectively, and the latter presented vertical separations of about 2 to 4 m.
+According to \citet{Jones1834}, the \myrevision{1721 Tabriz earthquake had a surface rupture of more than 42 km and presented vertical separations of about 2 to 4 m}.
 The locations of these and other notable events, including the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes, are shown in Fig.~\ref{fig:selected}b.
@@
 Historically, the Kopeh-Dagh seismic zone is also responsible for multiple earthquakes at the boundary between the Neyshabur and Binalud reverse faults (Fig.~\ref{fig:selected}a) between 1209 and 1405 \citep{Berberian1999}, and an estimated $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001}.
-
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
-% Seismic activity in the Iranian plateau is dominated by the tectonic contacts between the Arabian, Eurasian, and Indian plates, which confine the region laterally between the Indian and Eurasian plates, and the Arabian and eastern Asia-Minor plates to the east and west, respectively.
-This setting gives rise to the Zagros, Alborz, and east Iranian mountain ranges, and defines the geology of the region.
-Based on these conditions, Iranian seismicity is typically divided into various seismic zones, varying from as few as four to as many as twenty-three \citep[e.g.,][]{Stocklin1968, Berberian1976, Tavakoli1999}.
-Here, we adopt the model proposed by \citet{Karimiparidari2013}, which consists of six seismic zones: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East, and Makram (Fig.~\ref{fig:iran}).
-
-% Within this context, w
-
-% *********************************************************************************************************************
-% *********************************************************************************************************************
-
-% Naeem's original Text
-% ---------------------
-
-% With respect to different seismicity rates of the regions \citep{Nemati2015}, as well as the completeness of the seismic catalog \citep{Zare2014} , the study region is divided into three tectonic seismic zones.
-Each of these zones is characterized by its respective seismicity parameters values, including b-value and maximum magnitude ($M{_{max}}$).
-Part of Central Iran and Zagros regions are inside of the study region.
-We also calculated the seismicity parameters in these regions.
-Fig.~\ref{fig:Iran} shows the study region and different seismotectonic classification.
-
-% \begin{figure*}[!ht] 
-% \centering
-% \includegraphics[scale=0.7]{figures/pdf/Figure1.pdf} 
-% \caption{ a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}.
-}
-
-% \label{fig:Iran}
-% \end{figure*}
-
-% \subsection{Tectonic Regions and Seismic Faults}
-
-% \subsubsection{Alborz Mountain Range (Alborz)}
-% Tehran region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-Four earthquakes with magnitude more than 7 devastated the Tehran region in four centuries period, from 743 to 1177, but in the last 800 years, only one earthquake at 1830 has struck this region.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
-% The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-% The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
-Recently, the 1990 $M_w$ 7.4 Manjil-Rudbar earthquake caused extensive loss of life and significant damage \citep{USGS_manjil}.
-Based on existing documents, Tehran city and ancient Rey city have been destroyed completely several times by severe earthquakes with magnitudes greater than 7 \citep{Ambraseys2005}.
-\\
-
-% \subsubsection{Azerbaijan}
-% There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-% The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 $m$; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.
-Most recently, earthquakes with $M_w$ 6.1 in 1997 and $M_w$ 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-These earthquakes caused around 1500 casualties and extensive damage \citep{USGS_ardabil,USGS_tabriz}.\\
-
-% \subsubsection{Kopeh Dagh}
-% The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of Ms 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455.
-% The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about $E - W$ \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-% Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-% The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-% Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.\\
-
-% \subsection{Historical  and Instrumental Seismicity}
-% Uniform earthquake catalog is the most important factor in seismic hazard analysis of a region.
-Different studies have been conducted in order to prepare a uniform catalog for Iranian Earthquake.
-Historical event interpretation and different magnitude conversion relationships are some of the factors which make all these catalogs different.
-Among different sources \citet{Ambraseys2005}, \citet{Berberian1994}, and \citet{moinfar1994} are some of the main sources for Iranian earthquake catalog.
-These catalogs contain historical and instrumental earthquakes that have been reported in literature and national and international networks.
-According to \citet{Ambraseys2005}, there are some scattered indication of earthquake effects  back to third millinuim BC.
-However, adequate documentary coverage of individual events begins from seventh century A.D.
-\citet{Mirzaei1997} provided a comprehensive list of studies that have been done in compilation a uniform catalog for Iranian earthquakes in order to prepare a uniform catalog of earthquake (all earthquakes are converted to surface wave magnitude Ms) for seismic hazard assessment in Iran.
-The catalog is covering the period of 4th century B.C.
-through 1994.
-The instrumental data is achievable from three national agencies including IIEES, International Institute of Earthquake Engineering and Seismology; IRSC, The Iranian seismological center, University of Tehran; and BHRC, Building and Housing Research Center (Iran Strong Motion Network) (For more information about these networks see \citet{Karimiparidari2013}).
-% Many most of attenuation relationship use  moment magnitude $M_w$ as an input for the equation \citep{Douglas2011}.
-Moment magnitude is not suffering from saturation and has physical meaning \citep{Kanamori1977}.
-Due to mentioned reasons Mw has become a most appropriate magnitude scale in recent studies.
-%  \citet{Karimiparidari2013}compiled a uniform earthquake catalog for Iran and adjacent areas, using international and national databanks until April 2010.
-They developed relationships between moment magnitude and other magnitude based on orthogonal regression.
-They removed the dependent events (aftershocks and foreshocks) using the procedure by \citet{Gardner1974}.
-The catalog of events with magnitude equal and above Mw 5.5 is provided.
-% \citet{Shahvar2013} presented a unified and homogeneous catalog for the Iranian plateau $(M_w >= 4)$, created by merging data from two local catalogs and seven international agencies for 1900-2011 period.
-They used orthogonal regression method \citep{Castellaro2006} to derive magnitude conversion relation.
-By removing foreshocks and aftershocks according to the procedure detailed in Uhrhammer(1986), they also provided declustered version of the catalog.
-
-% The recent unified catalog for Middle East region is published as a part of Global Earth Model (GEM) and the Earthquake Model of the Middle East (EMME) project by \citet{Zare2014}.
-They used all historical (pre-1900), early and modern instrumental events up to 2006.
-The catalog contains data from Alborz-Azerbaijan, Afghanistan-Pakistan, Saudi Arabia, Caucasus, Central Iran, Kopeh-Dagh, Makran, Zagros, and part of Turkey.
-The magnitude of all events are converted to Mw through relationships which is derived at previous studies or newly derived at the study relationships.
-They declustered data through different methods including \citet{Gardner1974}, Uhrhammer(1986), \citet{Reasenberg1985}, and Gruenthal.
-\citet{Zare2014} provided the catalog completeness for different magnitude range using  the cumulative frequency-magnitude distribution of  \citet{Gutenberg1944} and \citet{richter1958}, and frequency magnitude distributaion of ZMAP \citep{Wiemer2001} software.
-The methods confirms the results of each other.
-
-% In this study we consider earthquakes with Mw equal and greater than 3.
-Earthquakes with magnitude 3 are not considered as a structural threat, however, the epicenter of earthquakes with magnitude $M_w 3$ are a  susceptible location for future bigger earthquakes.
-According to our preliminary data processing based on IIEES data, Iranian catalog for earthquake with magnitude greater and equal 3, is complete from 2005.
-In order to make sure about the completeness of the catalog, we use IIEES data from 2000.
-We used the EMME project data provided by \citet{Zare2014} up to 2000.
-Fig.~\ref{fig:historical} represents the historical data (pre 1900) in the study region.
-
-% \subsubsection{Magnitude Conversion}
-
-% The catalog of recorded earthquake from 2000-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale.
-We converted the $M_L$, $M_s$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}.
-There also some of data which is recorded in $M_D$ (Duration magnitude).
-These data are reported by International Seismological Centre (ISC).
-\citet{Deniz2010}, developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_s$ scales to the $M_w$ scales using orthogonal regression procedure.
-They used data of earthquake that occurred in Turkey from different data centers including ISC.
-In this study we use the conversion equation of \citet{Deniz2010} to convert the Md to Mw.
-Although they defined the equation based on $M_w>=4.5$, we extrapolate the equation for lower magnitude.
-We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate "a" value  in Gutenberge-Richter equation.
-
-% \begin{figure*}[!ht]
-
-% \centering
-% \includegraphics[scale=0.4]{figures/pdf/Figure2.pdf} 
-% \caption{Historical earthquakes of Iran (pre 1900). Different colors represent different year of occurrences and size of circles are proportional to the earthquake magnitude. }
-% \label{fig:historical}
-% \end{figure*}
-
-% \subsubsection{Declustering}
-
-% It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citep{Gardner1974}.
-For north Iran (lon: 42-62.5, lat: 33-41), from 7478 earthquake event we removed 605 Foreshocks and 2917 aftershocks.
-% Whole data that we used for seismicity parameters of Zagros and Central Iran tectonic seismic regions are not included in these numbers.
-Fig.~\ref{fig:instrumental} shows the epicenter of declustered instrumental  earthquakes.
-
-% \begin{figure*}[!ht]
-
-% \centering
-% \includegraphics[scale=0.25]{figures/pdf/Figure3.pdf} 
-% \caption{Declustered instrumental seismicity map (after 1900) of Northern Iran. The study areas are separated at longitude of 48$^{\circ}$ and 55$^{\circ}$ . } 
-% \label{fig:instrumental}
-% \end{figure*}
-
-% \subsection{Divisions}
-
-% As we discussed earlier (see the Introduction section), classifying the tectonic seismic regions has been a controversial debate.
-In this study we consider two seismic tectonic models.
-First model is according to \citet{Mirzaei1998} and \citet{Karimiparidari2013} classification, which includes Azerbaijan, Alborz, Kopek Dagh, and part of Central Iran, and Zagros, the second model is a uniform model for the whole north Iran.

### 2016-10-20 compilation.tex
done with completeness

@@
 We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, \myrevision{and to help inform the Gutenberg-Richter relationship}.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, \myrevision{and to help inform the Guten\-berg-Richter relationship}.
 By contrast, in the recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA}, the authors used a similar catalog for events $M_w \geq 4$, but only included data through 2011, thus excluding the 2012 $M_w$ 6.4 Tabriz earthquake, which severely damaged the northeast part of the country.
@@
 
-Selection and declustering was also done in a manner consistent with the original catalog, using the method of \citet{Gardner1974}.
+Selection and declustering was also done in a manner consistent with the original catalog, using the me\-thod of \citet{Gardner1974}.
 \myrevision{The total number of earthquakes in the complete region of interest before decluttering are 10,441, with 971 foreshocks and 4,206 aftershocks}.

### 2016-10-20 completeness.tex
done with completeness

@@
 This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process.
-The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range \myrevision{which in this study we use these values in estimating $a-values$ of smoothed seismic hazard}, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
-\myrevision{ We use $M_c$ for each catalog to compute the $b-value$ and $M_{max}$.}
+The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+\myrevision{In this study, we use the start-year of completeness as a parameter in the estimation of the $a$-values in the smoothed seismic hazard analysis; and we use the completeness magnitude $M_c$ determined for each sub-catalog to compute the $b$-values and $M_{\max}$.}
 
@@
 
-Determining the completeness magnitude $M_c$, on the other hand, is often determined using simple numerical analysis in combination with data inspection.
-Two common approaches are maximum curvature and the goodness-of-fit test methods.
-\myrevision{Both methods have been used extensively at previous studies}.The maximum curvature method, or MAXC for simplicity, is widely used because as it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+% \myrevision{Both methods have been used extensively in previous studies}.
+% \myrevision{\citet{Moschetti2015} applied a combination of methods to study the long-term earthquake rate model for the Central and Eastern United States.}
+
+Determining the completeness magnitude $M_c$, on the other hand, is often done using simple numerical analysis in combination with data inspection.
+Two common approaches are the maximum curvature method and the goodness-of-fit test method.
+The maximum curvature method, or MAXC for simplicity, is widely used thanks to the fact that it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
 \citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
-\myrevision{\citet{Moschetti2015} applied a combination of methods to study the  long-term earthquake rate model for the Central and Eastern United States.} We use the goodness-of-fit test method introduced by \citet{Wiemer2000}, and compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
+\myrevision{In this study, we use the goodness-of-fit test method introduced by \citet{Wiemer2000} to compute $M_c$.
+We choose this method over the MAXC method because of ease of implementation and to have first-hand control over the final selection of $M_c$, rather than relying on the inner details of the ZMAP software.
+We compute} $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
 
@@
 Having augmented the original catalog with $M>3$ earthquakes beginning in 2000 also influenced our choice of the intervals because at this point the uniformity of the catalog is altered.
-Last, we also computed $M_c$ values for the complete regional catalogs, but in this case, in order to maintain uniformity throughout time, we only considered $M>4$ events.
-Fig.~\ref{fig:mc} illustrates the selection of $M_c$ for the case of the main three northern Iran seismic regions, and Table \ref{tab:completeness} presents the final selection of $M_c$ values for these and the other regions, including the uniform northern Iran model for the complete region of interest.
+Last, we determined the $M_c$ values for the complete regional catalogs, but in this case, in order to maintain uniformity throughout time, we only considered $M>4$ events.
+\myrevision{According to \citet{Wiemer2000}, it is recommended to set $M_c$ at the point where the goodness-of-fit reaches 90 percent.
+However, not all goodness-of-fit plots satisfy this threshold and other considerations must be taken into account.} Fig.~\ref{fig:mc} illustrates the selection of $M_c$ for the case of the main three northern Iran seismic regions, and Table \ref{tab:completeness} presents the final selection of $M_c$ values for these and the other regions, including the uniform northern Iran model for the complete region of interest.
 
-The values of $M_c$ for different time intervals and seismic regions are used to determine the seismicity Gutenberg-Richter parameters $b$ and $M_{\max}$ (see Section \ref{sec:params}), \myrevision{and} the start-years of completeness are used later for computing the hazard.
-Admittedly, the choice of the start-years is highly subjective.
-We should note then, that in the process of choosing the points indicated in the plots shown in Fig.~\ref{fig:completeness}, we considered additional contributing information such as the history of instrumentation.
+\myrevision{We should note that both the choice of the start-years and that of the $M_c$ values are highly subjective.
+In the case of the start-years,} when choosing the points indicated in the plots shown in Fig.~\ref{fig:completeness}, we considered additional contributing information such as the history of instrumentation.
 It is well known that the number of recorded earthquakes increased considerably after the first deployment of seismic instruments in the early 1900s, and later with the establishment of the Worldwide Standardized Seismograph Network in 1961.
 We compared our choices with the year thresholds reported by \citet{Zare2014}, which we found to be consistently earlier than our preferred years of completeness.
-In the end, our selection should lead to a slightly more conservative estimations of hazard.
-For the case of $M_c$, we compared our results with the values reported by \citet{Karimiparidari2013} and \citet{Khodaverdian_2016_BSSA} and found them to be in general good agreement, despite differences in the spatial definition of the seismic zones.
+In this regard, our selection should lead to a slightly more conservative estimations of hazard.
+\myrevision{In the case of the $M_c$ values, on the other hand, we also considered the amount of data available above the chosen $M_c$ and the shapes of the cumulative number of events and goodness-of-fit plots.
+We tried to identify a consistent peak in the goodness-of-fit that coincided with the decay in cumulative number of events, while maintaining a large enough dataset size.
+For this case, we compared our choice of $M_c$ values with those} reported by \citet{Karimiparidari2013} and \citet{Khodaverdian_2016_BSSA} and found our choices to be in general good agreement, despite differences in the spatial definition of the seismic zones.
 

### 2016-10-20 hazard.tex
done for now with hazard section

--- 2016-09-23 hazard.tex
@@
 
-Once a seismic catalog has been defined, the second most important step is precisely the definition of the seismicity parameters $a$ and $b$ used in the Gutenberg-Richter recurrence relation 
+Once a seismic catalog has been defined, the second most important step is the definition of the seismicity parameters $a$ and $b$ used in the Gutenberg-Richter recurrence relation
 %
@@
 	\tilde{n}_i = \frac
-		{ \sum_{j} n_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
-		{ \sum_{j} \exp ( \frac{ -\Delta_{ij}^{2} }{ c^2 } ) }
+		{ \sum_{j} n_{j} \exp \left( \frac{ -\Delta_{ij}^{2} }{ c^2 } \right) }
+		{ \sum_{j} \exp \left( \frac{ -\Delta_{ij}^{2} }{ c^2 } \right) }
 	\, ,
@@
 It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
-We also note that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.
+We also note that \myrevision{other authors have used alternative smoothing kernels \citep[e.g.,][]{Moschetti2015} and that a comparison of the smoothing length between different methods may require additional considerations about the function decay.
+Last, we highlight that} according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.
 
@@
 Different values of $c$ have been used in past studies, ranging between 10 and 50 km.
-\citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15 km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40 km.
+\citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15~km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40~km, \myrevision{while \citet{Boyd2007} and \citet{Petersen2015} include spatial variability in the smoothing parameter}.
 According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records.
-We use an intermediate value of $c=30$~km.
+\myrevision{Other studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods \citep[e.g.,][]{Werner2011, Moschetti2015}}.
+We use an intermediate value of $c = 30$~km.
 This selection is consistent with epicentral uncertainty for previous hazard zoning maps for Iran \citep[see][]{Zare2012}.
@@
 %
-Here, the values of $\tilde{n}_i$ have been previously binned by their distance from the site of interest, $N_k$ is the total of $\tilde{n}_i$ values for cells within a certain bin distance, $T$ is the time in years used to determine $N_k$, and $k$ and $l$ are the indexes of the distance and magnitude bins, respectively.
-$P ( u > u_o | D_k , M_l )$ is the probability of $u$ exceeding $u_o$ given an earthquake of magnitude $M_l$ at a distance $D_k$ \citep{Frankel1995}.
+Here, $N_k$ is the total of $\tilde{n}_i$ values for cells within a certain bin distance, where the values of $\tilde{n}_i$ have been previously binned by their distance from the site of interest; $T$ is the time in years used to determine $N_k$; $k$ and $l$ are the indexes of the distance and magnitude bins, respectively; and $P ( u > u_o | D_k , M_l )$ is the probability of $u$ exceeding $u_o$ given an earthquake of magnitude $M_l$ at a distance $D_k$ \citep{Frankel1995}.
 

### 2016-10-21 parameters.tex
done with section 5

--- 2016-10-01 parameters.tex
@@
 We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog.
-\myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko1989} method.
-Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.
-We divide the} catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
+\myrevision{In HA3, the regional maximum magnitude is estimated according to \citet{Kijko_1989_BSSA} method.
+Magnitude errors are distributed normally and $b$ and $\lambda$ are calculated simultaneously.} We divide the catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
 In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
@@
 We call it the \textit{U Model}.
-Admittedly, this assumption is somewhat unrealistic if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}.
-However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty.
+\myrevision{While the U model may seem less realistic than the R model, if considering that different seismic zones may have different values of $b$ and $M_{max}$, computing hazard for both models allowed us to take into account the epistemic uncertainty associated to the seismic zonation of the region.
+We also consider uncertainty in the seismic parameters $b$ and $M_{max}$ via a logic tree, as explained ahead, and combined the results into separate R and U model branches and a final hazard model combining both R and U results.}
+
 Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
+
 \myrevision{
@@
 }
+
 \begin{figure*}[t]

### 2016-10-21 attenuation.tex
up to logic tree

@@
 
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-09}
-    \caption{Logic tree for seismic hazard component in the North Iran.}
-    \label{fig:logic}
-\end{figure*}
-
 \section{Attenuation Relationship}
@@
 The last piece in our hazard analysis process is the choice of an adequate attenuation relationship, or ground motion prediction equation (GMPE).
-This is a highly influential factor because it controls \myrevision{the intensity level at a particular site given earthquake locations and magnitude from the source model.}
+This is a highly influential factor because it controls \myrevision{the intensity level at a particular site given an earthquake of a certain magnitude and source characteristics and at a particular distance from the location of interest.}
 
@@
 The combined evaluation for PGA, and SA for seven periods (T) between 0.1 and 2.0 s, yielded that the best overall predictions were those of the GMPEs introduced by \citet{Ghasemi_2009_JS}, \citet{Abrahamson_2008_ES}, and \citet{Chiou2008}.
-For the specific case of PGA ($T=0$ s), however, the best results were those obtained with the GMPEs introduced by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}.
-\myrevision{\citet{Soghrat2012} and \citet{Akkar2010} are other attenuation relationships which provide higher scores.}
+For the specific case of PGA ($T = 0$ s), however, the best results were those obtained with the GMPEs introduced by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}.
+\myrevision{Other GMPEs with good prediction results for the region were those of \citet{Soghrat2012} and \citet{Akkar2010}}.
 
-Since our hazard analysis here focuses on PGA values only, we concentrated our attention in the last set of GMPEs.
-In comparisons not shown here for brevity, we found that these GMPEs yielded mean predictions that were very close to each other.\myrevision{ Fig.~\ref{fig:att} illustrates the variation of horizontal components pga (in g) with distance for four different magnitude.
-In practice, epistemic uncertainty is being considered by using different GMPEs through logic tree approach.
-As \citet{Atkinson2014} suggested, in most cases multiple-GMPEs approach is not necessarily acknowledge the epistemic uncertainty.
-This fact is also obvious from the Fig.~\ref{fig:att} where the alternative approach which is using \citet{Kalkan2004} as a backbone GMPE as well as uncertainties covers a broader range in compare with using the combination of GMPEs.} Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{leads} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
-These results meant that neither of them had a substantial advantage over the others.
-\myrevision{Fig.~\ref{fig:logic} represents the total logic tree approach in order to consider the uncertainty in tectonic seismic region, $M_{max}$, $b-value$, and estimated PGA.
-The weights are chosen based on previous studies \citep[e.g.,][]{Petersen2015}.
-We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}
+\myrevision{A common approach used in seismic hazard analysis given the availability of multiple GMPEs is to address the associated epistemic uncertainty through a combination of the various GMPEs.
+However, in comparisons not shown here for brevity, we found that some of these GMPEs yielded mean predictions that were very close to each other.
+In an analysis based on the LLH coefficients reported by \citet{Zafarani2014}, and using the approach of \citet{Scherbaum_2009_BSSA} we found, for instance, that a logic-tree partition for the GMPEs proposed by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, leads to weights of 0.3376, 0.3354, and 0.3270, respectively.
+These results meant that neither of these GMPEs had a substantial advantage over the others.
+This, however, would go against the desired to account for the associated uncertainty.
+Recently, \citet{Atkinson2014} argued that in such cases where multiple GMPEs do not offer sufficient variability, their combination does not necessarily and properly address uncertainty and suggests that, instead, one can better consider a high and low alternative based on a central backbone model.
+Fig.~\ref{fig:att} illustrates the variation of horizontal PGA components (in g) with distance obtained using four of the GMPEs mentioned before for two different earthquake magnitudes.
+In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered prediction and we chose this particular GMPE as our central backbone and define an upper and lower bound as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range of defined by these bounds.}
 
-Based on this, we selected the GMPE proposed by \citet{Kalkan2004} for our analysis. This equation is of the form
+The selected the GMPE proposed by \citet{Kalkan2004} for our analysis is of the form
 %
@@
 We should note here that even though \citet{Kalkan2004} derived the above attenuation relationship for distances $r$ up to 250 km, \citet{Zafarani2014} only used data up to 200 km in their evaluation of the various GMPEs available.
-Therefore, to be consistent with the latter, we set the models in the hazard analysis to compute ground motions (i.e., PGAs) at distances no greater than 200 km.
+Therefore, to be consistent with the latter, we set the models in the hazard analysis to compute ground motion intensities (i.e., PGAs) at distances no greater than 200 km.
+
+% STUFF...
+
+% \myrevision{While other GMPEs were included in the analysis by \citet{Zafarani2014} which also proved to be adequate for the region for other intensity parameters, given our focus on PGA, we concentrated our attention in the above mentioned equations, with particular attention to \citet{Kalkan2004}, \citet{Boore2008}, \citet{Soghrat2012} and \citet{Akkar2010}.}
+
+% In practice, epistemic uncertainty is considered by using different GMPEs through logic tree approach.
+As \citet{Atkinson2014} suggested, in most cases multiple-GMPEs approach is not necessarily acknowledge the epistemic uncertainty.
+This fact is also obvious from the Fig.~\ref{fig:att} where the alternative approach which is using \citet{Kalkan2004} as a backbone GMPE as well as uncertainties covers a broader range in compare with using the combination of GMPEs.} Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{leads} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
+
+% \myrevision{Fig.~\ref{fig:logic} represents the total logic tree approach in order to consider the uncertainty in tectonic seismic region, $M_{max}$, $b-value$, and estimated PGA.
+The weights are chosen based on previous studies \citep[e.g.,][]{Petersen2015}.
+We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}

### 2016-10-21 logictree.tex
up to logic tree

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-09}
    \caption{Logic tree nodes and associated weights used in the seismic hazard analysis for northern Iran.}
    \label{fig:logic}
\end{figure*}

\section{\myrevision{Logic Tree}}

\myrevision{As mentioned in previous sections, we address the uncertainties in our models, seismic parameters and selected ground motion prediction equation via a logic tree. Fig.~\ref{fig:logic} shows the complete set of branches at each of the tree nodes. In particular, we consider uncertainty in the seismic zonation via the combination of the R and U models, the maximum magnitude $M_{\max}$, the seismic $b$-value, and the prediction of PGA intensities in the GMPE by \citet{Kalkan2004}. We assigned the weights to the R and U model arbitrarily, giving more weight to the regional model R based on the expectation that a regionalized model would likely lead to a better seismic hazard analysis. Other weights in the logic tree are based on previous studies \citep[e.g.,][]{Petersen2015}.}

\myrevision{Among other possible parameters for which we could have consider additional sources of uncertainty, we note that we did not consider the variability of the reference depth and seismic velocities in the selected GMPE because these were values fixed to satisfy the fit of the equation with data from northern Iran. Thus introducing uncertainty in these parameters would have been to the detriment of the prediction of PGA values.}

 % We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}

### 2016-10-21 attenuation.tex
done up to logic tree session

@@
 Fig.~\ref{fig:att} illustrates the variation of horizontal PGA components (in g) with distance obtained using four of the GMPEs mentioned before for two different earthquake magnitudes.
-In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered prediction and we chose this particular GMPE as our central backbone and define an upper and lower bound as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range of defined by these bounds.}
+In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered prediction and we chose this particular GMPE as our central backbone and defined an upper and lower bound (plus and minus one standard deviation) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range of defined by these bounds.}
 

### 2016-10-21 attenuation.tex
updates to sections 6 and 7

--- 2016-10-21 attenuation.tex
@@
 In an analysis based on the LLH coefficients reported by \citet{Zafarani2014}, and using the approach of \citet{Scherbaum_2009_BSSA} we found, for instance, that a logic-tree partition for the GMPEs proposed by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, leads to weights of 0.3376, 0.3354, and 0.3270, respectively.
-These results meant that neither of these GMPEs had a substantial advantage over the others.
-This, however, would go against the desired to account for the associated uncertainty.
-Recently, \citet{Atkinson2014} argued that in such cases where multiple GMPEs do not offer sufficient variability, their combination does not necessarily and properly address uncertainty and suggests that, instead, one can better consider a high and low alternative based on a central backbone model.
-Fig.~\ref{fig:att} illustrates the variation of horizontal PGA components (in g) with distance obtained using four of the GMPEs mentioned before for two different earthquake magnitudes.
-In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered prediction and we chose this particular GMPE as our central backbone and define an upper and lower bound as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range of defined by these bounds.}
+These results meant that neither of these GMPEs has a substantial advantage over the others.
+This, however, would go against the need for accounting for uncertainty.
+Recently, \citet{Atkinson2014} argued that in such cases where multiple GMPEs do not offer sufficient variability, their combination does not necessarily and properly addresses uncertainty and suggested that, instead, one considers a set of high and low alternatives based on a central backbone model.
+Fig.~\ref{fig:att} illustrates the variation of horizontal PGA components with distance obtained using four of the GMPEs mentioned before for two different earthquake magnitudes.
+In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered predictions and we chose this particular GMPE as our central backbone.
+Based on it, we defined an upper and lower bound (plus and minus one standard deviation, $\sigma = $????) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range defined by these bounds.}
 
-The selected the GMPE proposed by \citet{Kalkan2004} for our analysis is of the form
+The selected backbone GMPE for our analysis, as proposed by \citet{Kalkan2004}, is of the form
 %
@@
 Therefore, to be consistent with the latter, we set the models in the hazard analysis to compute ground motion intensities (i.e., PGAs) at distances no greater than 200 km.
-
-% STUFF...
-
-% \myrevision{While other GMPEs were included in the analysis by \citet{Zafarani2014} which also proved to be adequate for the region for other intensity parameters, given our focus on PGA, we concentrated our attention in the above mentioned equations, with particular attention to \citet{Kalkan2004}, \citet{Boore2008}, \citet{Soghrat2012} and \citet{Akkar2010}.}
-
-% In practice, epistemic uncertainty is considered by using different GMPEs through logic tree approach.
-As \citet{Atkinson2014} suggested, in most cases multiple-GMPEs approach is not necessarily acknowledge the epistemic uncertainty.
-This fact is also obvious from the Fig.~\ref{fig:att} where the alternative approach which is using \citet{Kalkan2004} as a backbone GMPE as well as uncertainties covers a broader range in compare with using the combination of GMPEs.} Furthermore, based on the LLH coefficients reported by \citet{Zafarani2014}, and using the \myrevision{approach} of \citet{Scherbaum_2009_BSSA}, we found that a logic-tree analysis \myrevision{leads} to weights of 0.3376, 0.3354, and 0.3270 for \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}, respectively.
-
-% \myrevision{Fig.~\ref{fig:logic} represents the total logic tree approach in order to consider the uncertainty in tectonic seismic region, $M_{max}$, $b-value$, and estimated PGA.
-The weights are chosen based on previous studies \citep[e.g.,][]{Petersen2015}.
-We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}

### 2016-10-21 logictree.tex
updates to sections 6 and 7

@@
 We assigned the weights to the R and U model arbitrarily, giving more weight to the regional model R based on the expectation that a regionalized model would likely lead to a better seismic hazard analysis.
-Other weights in the logic tree are based on previous studies \citep[e.g.,][]{Petersen2015}.}
+The uncertainty in $M_{\max}$ and the $b$ value were set equal to ????
+and ????, respectively.
+These values were determined based on the ranges identified in the seismicity analysis as presented before in Table \ref{tab:params}.
+Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude on one standard deviation, $\sigma = $????.
+The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2015}.}
 
@@
 Thus introducing uncertainty in these parameters would have been to the detriment of the prediction of PGA values.}
-
- % We considered the uncertainty in tectonic seismic region through adding the uniform model with lower weight than the most recent accepted classification.}

### 2016-10-21 attenuation.tex
almost done with section 8

@@
 In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered predictions and we chose this particular GMPE as our central backbone.
-Based on it, we defined an upper and lower bound (plus and minus one standard deviation, $\sigma = $????) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range defined by these bounds.}
+Based on it, we defined an upper and lower bound (plus and minus one standard deviation, $\sigma_{\ln y}$) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range defined by these bounds.}
 
@@
 
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-09}
+    \caption{Logic tree nodes and associated weights used in the seismic hazard analysis for northern Iran.
+The uncertainties in each branch are defined based on $\sigma_{\ln y}$ for the GMPE, and on the ranges shown in Table \ref{tab:params} for $b$ and $M_{\max}$.}
+    \label{fig:logic}
+\end{figure*}
+
 We should note here that even though \citet{Kalkan2004} derived the above attenuation relationship for distances $r$ up to 250 km, \citet{Zafarani2014} only used data up to 200 km in their evaluation of the various GMPEs available.

### 2016-10-21 logictree.tex
almost done with section 8

@@
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-09}
-    \caption{Logic tree nodes and associated weights used in the seismic hazard analysis for northern Iran.}
-    \label{fig:logic}
-\end{figure*}
-
 \section{\myrevision{Logic Tree}}
@@
 We assigned the weights to the R and U model arbitrarily, giving more weight to the regional model R based on the expectation that a regionalized model would likely lead to a better seismic hazard analysis.
-The uncertainty in $M_{\max}$ and the $b$ value were set equal to ????
-and ????, respectively.
-These values were determined based on the ranges identified in the seismicity analysis as presented before in Table \ref{tab:params}.
-Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude on one standard deviation, $\sigma = $????.
+The uncertainty in $M_{\max}$ and the $b$ values were set equal to the plus and minus ranges shown in Table \ref{tab:params}.
+Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude of one standard deviation, $\sigma_{\ln y} = 0.612$.
 The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2015}.}

### 2016-10-21 results.tex
almost done with section 8

@@
 Using these models we obtained hazard curves and expected PGA values for two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes \myrevision{$M_w \geq 4.5$}.
-These probabilities correspond to return periods of 475 and 2475 years.
+These probabilities correspond to return periods of 475 and 2,475 years.
 For nomenclature purposes, we use the probabilities as a suffix on the model type.
-As an example, we refer to the results for 2 percent probability of exceedance in 50 years using the five-regions model as the R2, whereas for the case of 10 percent probability of exceedance when using the uniform model we use the tag name U10.
+As an example, we refer to the results for 2 percent probability of exceedance in 50 years using the five-regions model as R2, whereas for the case of 10 percent probability of exceedance when using the uniform model we use the tag name U10.
 
-Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events \myrevision{$M_w \geq 4.5$}, or conversely, \myrevision{$M_{min}$ was chosen based on the expected smallest magnitude capable of causing damage}.
+Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events \myrevision{$M_w \geq 4.5$}, or conversely, \myrevision{$M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage}.
 In turn, the 2 and 10 percent probability of exceedance in a \myrevision{50-year} span are considered a standard practice in seismic design, and are the probabilities used in the Iranian building code \citep{BHRC2014}.
@@
 
-Fig.~\ref{fig:pga} shows the expected mean PGA values obtained \myrevision{as the first and the second branch of the logic tree approach} for the different models, R2, R10, U2 and U10.
+Figure~\ref{fig:pga} shows the expected mean PGA values obtained for the R and U models, \myrevision{included the associated uncertainties in $b$, $M_{\max}$ and the GMPE.
+That is, the results in Fig.~\ref{fig:pga} correspond to the complete regional and uniform model branches in the logic tree for the different sub-models R2, R10, U2 and U10}.
 As can be expected, the highest PGA values are associated with the R2 and U2 models, and the lowest with the R10 and U10 models.
-For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Azerbaijan region at the left side of the North Tabriz Fault and also in border of Kopeh Dagh and Alborz tectonic seismic regions at the right side of the North Alborz Fault.
-We observe higher hazard in the Alborz region an small area at right side of the Mosha Fault.
-For the U model results shown in Fig.~\ref{fig:pga}b, on the other hand, the highest levels of expected ground motion are observed precisely in the area corresponding to the Azerbaijan seismic region, especially in the vicinity of the North Tabriz Fault system (see Fig.~\ref{fig:selected} for reference).
+For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Azerbaijan region \myrevision{on the west side of the North Tabriz Fault and also on and around the border of the Kopeh Dagh and Alborz tectonic seismic regions on the east side of the North Alborz Fault.
+We also observe higher hazard in the Alborz region in a small area east from the Mosha Fault.
+On the other hand, the results shown in Fig.~\ref{fig:pga}b for the U model indicate that in addition to these areas, there are also large expected ground motions in the Zagros seismic zone and increased PGA results in various areas within the Central East seismic region}.
 
@@
 In this figure, positive values indicate that the U models have larger mean PGA values than the R models.
-As it can be seen, this is true practically throughout the whole region at very low levels, and in particular in the north-west region at a moderate level of up to 0.2 g and more predominantly in the Zagros at levels of about 0.2 to 0.45 g.
-The higher results in uniform model occurred because of higher $M_{max}$ and lover $b-value$ in comparison with regional model.
+\myrevision{As it can be seen, this is true practically throughout the whole region at very low levels, but more predominantly in the north-west region at a moderate level of up to 0.2 g and increasingly so in the Zagros region, where the differences between about 0.2 and 0.45 g.
+The higher results in the U model occurred because of higher $M_{max}$ and lower $b$ values in comparison with the R model}.
 
 Overall, these results are consistent with the seismicity observed in Fig.~\ref{fig:catalog}.
-The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with \myrevision{a} concentration of strong earthquakes in the Azerbaijan and Kopeh Dagh regions; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Azerbaijan region.
-This is because of the higher $b$-value obtained for the Azerbaijan region in the R model as opposed to the lower value for the U model.
+The R model results, however, seem to be more sensitive to the influence of large magnitude events observed in both the historical and modern seismicity maps, with a concentration of strong earthquakes in the Azerbaijan and Kopeh Dagh regios; whereas the U model results seem to be more sensitive to the influence of low-to-moderate magnitude events, especially in the Zagros and Central East regions.
 
-With this in mind, we make the following additional consideration.
-No one model (R or U) can be considered uniquely correct.
-Both carry a certain level of epistemic uncertainty.
-A means to address this is to use combinations of different models to incorporate information from all possible models.
-Here we also computed the expected levels of ground motion for a combination of the R and U models which is the final result of the logic tree approach as shown at ~\ref{fig:logic}.
-We refer to this as the (R,U) model.
-The results of this combined model are shown in Fig.~\ref{fig:pga.ru.std} in the form of expected mean PGA values.
+\myrevision{With this in mind, and knowing that no one model (R or U) can be considered uniquely correct, we consider now the combination of both models as presented for the complete logic tree in Fig.~\ref{fig:logic}.
+We refer to this as the (R,U) model and the results are shown in Fig.~\ref{fig:pga.ru.std}, again in the form of expected mean PGA values for 2 and 10 percent in 50 years.}
 
-As it can be seen in Fig.~\ref{fig:pga.ru.std}, the combined (R,U) model follows more closely the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as the major faults shown in Fig.~\ref{fig:selected}a.
+\myrevision{The combined (R,U) model reflects the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as that of the major faults shown in Fig.~\ref{fig:selected}a, but it also reflects the influence that small earthquakes have on the seismicity hazard of the region}.
 It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the North Alborz fault in the Alborz region and that of the different faults in the Kopeh Dagh region.
@@
 
-\myrevision{%
-We also note that the overall distribution of mean PGA pattern agrees with the recent study by \citet{Khodaverdian_2016_BSSA}.
-However, in general, their results are slightly lower than this study.
-They provided a rough estimate of the PGA, and the seismicity parameters, like completeness magnitude, the catalog, $M_{max}$, and $b-value$ are different in these two studies.
-Consequently, we don't expect to match the results.
-For example  in case of $b-value$, in the same study region, \citet{Khodaverdian_2016_BSSA} reported very high variation of $b-value$ (0.56 - 1.27).
-56\% of grid points have $b-value > 1$ and 53 \% of them are greater than 1.1.
-Where in this study the $b-value$ has a narrow range of variation (0.93-1.15).
-They computed the seismicity parameters for each grid point inside a circle with radius of 200 around the grid point, whereas in this study we considered a uniform seismicity parameters for each region.
-These estimates also agree, on average, with other studies.
-For the Azerbaijan tectonic seismic region for the city of Uremia, we found 0.24 g which is slightly lower than \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for 10 \% probability of exceedance in 50 years.
-\citet{Zare2012} expected to see higher values because of using parametric method.
-For a 2\% probability of exceedance in 50 years, \citet{Golara2014} expected acceleration on the order of 0.3 - 0.5 g, where or mean value is 0.38 g.
-For the city of Tabriz, the results match with \citet{BHRC2014} and are in the range of \citet{Zare2012} for 10 \% probability of exceedance in 50 years.
-\citet{Vafaie2011} expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\% probability of exceedance in 50 years, respectively, where our mean values are about 0.61 and 0.35 g for the same corresponding probabilities.
-For the city of Ardabil, we found 0.73 g and 0.43 g for 2 and 10\% probability of exceedance in 50 years.
-Our results are slightly higher than \citet{BHRC2014}, however, for 10\% probability of exceedance in 50 years, the results are in the range reported by \citet{Zare2012}.
-For 2\% probability of exceedance in 50 years, our results are very close to \citet{Golara2014} and \citet{Khodaverdian_2016_BSSA}.
-In the Alborz tectonic seismic region for the city of Rasht, our results are in a well agreement with the recent study of \citet{Abdollahzadeh2014}.
-For the city of Tehran, the results are in agreement with \citet{Abdi2013}, and slightly lower than  \citet{BHRC2014}, \citet{Zare2012}, and \citet{Golara2014} for 10\% probability of exceedance in 50 years.
-For 2\% 10\% probability of exceedance in 50 years, our results are lower than \citet{Golara2014} and higher than \citet{Khodaverdian_2016_BSSA}.
-For the Kopeh Dagh tectonic seismic region for the city of Mashhad, results are lower than \citet{BHRC2014} and higher than \citet{Khodaverdian_2016_BSSA}.}
+\myrevision{We also note that the overall distribution of mean PGA agrees with the recent study by \citet{Khodaverdian_2016_BSSA}.
+However, their results are in general slightly lower than ours.
+Obviously, given the differences in the catalogs, completeness magnitude, and in the seismicity parameters $M_{\max}$ and $b$, we cannot expect PGA values to match.
+For example, in the case of the $b$ values, \citet{Khodaverdian_2016_BSSA} reported large variations netween 0.56 and 1.27, where over 50 percent of the grid points had $b$ values greater than 1; whereas in our study the $b$ values observe a narrow range of variation between 0.93 and 1.15.
+In this regard we should note that \citet{Khodaverdian_2016_BSSA} computed the seismicity parameters for each grid point considering the contributions within a circular area of radius 200 m, whereas we considered a uniform seismicity parameters for each region and account for the uncertainty in the difference between regions via the combination of the R and U models.}
 
-%We also note that the overall distribution of mean PGA  agree, on average, with other previous studies.
-For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA (10\% in 50 years) values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, where we find equivalent values to be between 0.35 and 0.50 g in the (R,U)10 model.
-Similarly, for the particular case of the city of Tabriz, \citet{Vafaie2011} obtained slightly higher expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\% \myrevision{in 50 years}, respectively, where our mean values are about 0.53 and 0.36 g for the same corresponding probabilities.
-In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 g for Tehran, where we found equivalent results to be about 0.25--0.35 g for a 10\% probability of exceedance \myrevision{in 50 years}.
-The latter estimate is in good agreement with \citet{Abdi2013}, who predicts PGA values in the vicinity of Karaj and Tehran to be on the order of 0.27--0.31 g for \myrevision{the same exceedance probability}.
-Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also on the same order of those shown in Fig.~\ref{fig:pga.ru.std}.
-Finally, for the city of Bojnurd in the northeast province of Khorasan in the Kopeh Dagh seismic region, \citet{Rahgozar2012} reports expected PGA values in the ranges of 0.28--0.49 and 0.15--0.22 g for 2 and 10\% \myrevision{in 50 years}, where we obtain mean values of 0.51 and 0.34 g, respectively.
+\myrevision{Altogether, on average, we found our results to be in good agreement with other previous results.
+For the city of Uremia, for instance, we obtained a expected PGA of 0.24 g, which is slightly lower than values obtained by \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for a 10 percent probability of exceedance in 50 years.
+We believe \citet{Zare2012} obtained higher values because their of use of a parametric method.
+For a 2 percent probability of exceedance in 50 years, \citet{Golara2014} obtained expected PGAs on the order of 0.3--0.5 g, where our mean value is 0.38 g.
+For the city of Tabriz, our results match with those obtained by \citet{BHRC2014} and are within the range of values computed by \citet{Zare2012}, for a 10 percent probability.
+These and other similar comparisons are summarized in Table \ref{tab:pga}, where we show our results and those of other previous studies for selected cities in northern Iran.}
 
-Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of other previous studies for selected cities in northern Iran.
-As mentioned before, overall, our results are close \myrevision{to} or within the ranges from most studies.
+\myrevision{As mentioned before, overall, our results are close to or within the ranges provided by most previous studies}.
 The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher than the rest.
-\myrevision{One reason for higher value in \citet{Golara2014} is using the maximum credible earthquake as $M_max$.
-The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{max}$.}
+\myrevision{One possible explanation for the higher values in \citet{Golara2014} is their use of the maximum credible earthquake as the value for $M_{\max}$.
+The maximum credible earthquake is the largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, based on geologic and seismic data.
+Therefore, it is often higher than historical documented observations or instrumental data-driven estimations of $M_{\max}$}.
 
-% ***
-
-% Although not included here, we also computed expected PGA values for a magnitude threshold $M_w$ 4.5.
-In that case, our results are closer to those of \citet{Golara2014}, but deviate from the rest.
-In general, the smoothed seismicity method tends to lead to lower hazard estimations than those obtained using specific fault definitions (as opposed to point sources) where the concept of a threshold becomes unnecessary and the hazard, and thus is sensitive to the appropriate selection of the magnitude threshold.
-
-% ***
-
-Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA\myrevision{, also known as hazard curve}.
-The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran considering the two basic R and U models and the combined (R,U) model.
-These hazard curves exemplify again the differences between the R and U models, which are more prominent in the northwest cities of Tabriz and Ardabil, where the U models yield higher expected values of PGA for any given annual probability of exceedance.
-Minor differences are also present in the results of the central cities of Karaj and Tehran, whereas for the cities of Urmia and Mashhad in the Zagros and Kopeh Dagh seismic zones, the R and U models yield similar if not equivalent hazard estimates.
-This is consistent with our previous observations regarding Figs.~\ref{fig:pga}, \ref{fig:pga.diff} and \ref{fig:pga.ru.std}.
+Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA\myrevision{, also known as hazard curves.
+The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran including the R, U, and the combined (R,U) models.
+Although for these particular cities, the differences are minor in general, they exemplify the results one can obtain at particular locations.
+Here, the more clear differences are observed for the city of Urmia, where the (R,U) model approaches the R model for low values of PGA and then evolves closer to the U model for higher values of PGA}.
 
@@
 
-\myrevision{%
-Last, we put additional attention on the results for the capital city of Tehran.
+*** DONE UP TO HERE ***
+
+\myrevision{Last, we concentrate our attention on the results for the capital city of Tehran.
 We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015} as well as ranges from other studies for 2 and 10\% probability of exceedance in 50 years.

### 2016-10-21 results.tex
done with results section

@@
     \includegraphics[width=0.48\textwidth]{figures/pdf/figure-14}
-    \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran.
-Here, the two previous studies just mentioned are identified with the codes Gh03 and Bo15, respectively.
-Also the PGA ranges of the \ref{tab:pga} are represented.
-The shaded area represents the upper and lower value of uncertainty at the GMPEs.}
+    \caption{Hazard curve comparison between the models considered in this study and the results of \citet{Ghodrati2003} and \citet{Boostan2015}, along with the value-ranges of other studies included in Table \ref{tab:pga} for the city of Tehran, for 2 and 10 percent probability of exceedance in 50 years, as indicated by the circles over the fixed annual probability lines.
+As done before, the following codes are used for the references of two mentioned hazard curves and the values of other studies.
+        Gh03: \citet{Ghodrati2003},
+        Za12: \citet{Zare2012},
+        Ab13: \citet{Abdi2013},
+        BC14: \citet{BHRC2014},
+        Go14: \citet{Golara2014},
+        Bo15: \citet{Boostan2015}, and
+        Kh16: \citet{Khodaverdian_2016_BSSA}.
+    The shaded area represents the upper and lower results obtained when considering the uncertainty in the backbone GMPE.}
     \label{fig:tehran}
@@
 
-*** DONE UP TO HERE ***
+\myrevision{Last, we concentrate our attention on the results for the capital city of Tehran.
+We compare the hazard curve we obtained for Tehran with those computed by \citet{Ghodrati2003} and \citet{Boostan2015}.
+The hazard curve from \citet{Boostan2015} is the result of applying fuzzy sets theory to account for variations in the distance and magnitude of earthquakes.
+\citet{Ghodrati2003}, on the other hand, conducted a probabilistic seismic hazard analysis considering the uncertainty in the seismicity values and the ground motion levels of intensity through a logic tree approach.
+In particular, \citet{Ghodrati2003} used variations in $b$ and $M_{\max}$ based on the previous results of  \citet{Tavakoli1999}, where $b = 0.52 \pm0.02$ and $M_{\max} = 7.9 \pm 0.3$.
+This value of $M_{\max}$ is similar to ours for the region of Alborz, but the $b$ value is rather low.
+While \citet{Ghodrati2003} used three different attenuation relationships in their analysis, \citet{Boostan2015} used only one.
+The results of the comparison are shown in Fig.~\ref{fig:tehran}.
+This figure also includes comparisons with the value-ranges of other studies included in Table \ref{tab:pga} for 2 and 10 percent probability of exceedance in 50 years.}
 
-\myrevision{Last, we concentrate our attention on the results for the capital city of Tehran.
-We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015} as well as ranges from other studies for 2 and 10\% probability of exceedance in 50 years.
-By applying different combination of magnitude (M) and distance (R), \citet{Boostan2015} presented a new model for probabilistic seismic hazard assessment based on fuzzy sets theory for Tehran, Iran.
-They expected to achieve higher seismic hazard values because of considering a vast uncertainty range for R and M.
-They concluded, non-fuzzy approaches due to not considering all uncertainties leads to non-conservative results.
-\citet{Ghodrati2003} conducted a probabilistic seismic hazard analysis for the same region based on considering the uncertainty in seismicity value and ground motion level through logic tree approach.
-They consider the uncertainty in seismicity parameters by involving the results of \citet{Tavakoli1999}.
-\citet{Tavakoli1999} reported the $b-value$ and $M_{max}$ as $0.52\pm0.02$ and $7.9\pm0.3$, respectively, which is fairly different from the result of this study.
-Even though   \citet{Ghodrati2003} used three GMPEs model,  \citet{Boostan2015} used only one model as attenuation relationship.
-As we discussed earlier, our model fairly well consider the ground motion level uncertainty.
-Our results are similar to those obtained by \citet{Boostan2015} in the range between 0.1 and 0.3 g (corresponding to annual probabilities of exceedance between $10^{-3}$ and $10^{-1}$), and then it is in the mean range of the mentioned studies.
-Conversely, the trend in the hazard curve from \citet{Boostan2015} suggest the city is to expect significantly higher levels of ground motion at higher probability rates, which is contrary to our findings and those of \citet{Ghodrati2003}.
-Expected PGA range of other studies mentioned at the \ref{tab:pga}, represents, on average, our study presents trustable results.
-The shaded area, represents the upper and lower value of uncertainty at the GMPEs.
-In other word the upper part edge is calculated by just considering GMPEs+Unc  and the lower edge is calculated by just considering GMPEs-Unc.
-It perfectly represents that almost all studies are in the range of uncertainty of the GMPEs, and using one appropriate backbone GMPE as well as the uncertainties could have better role in considering the epistemic uncertainty than using multiple GMPEs as \citet{Atkinson2014} concluded.}
+\myrevision{As we discussed earlier, and as it can be seen based on the associated uncertainty carried by the GMPE (shaded area), our model accounts fairly well the expected ground motion level of variability.
+In general, for the city of Tehran, the mean results of our R, U and (R,U) models are very similar for all values.
+With respect to \citet{Ghodrati2003} and \citet{Boostan2015}, for PGA values lower than 0.25 g, which correspond to annual probabilities higher than $3 \times 10^{-3}$, our results are fairly close to those of \citet{Boostan2015}.
+However, at PGA values higher than 0.35 g and annual probabilities lower than $1 \times 10^{-3}$, our results fall halfway between the hazard curves of \citet{Ghodrati2003} and \citet{Boostan2015}.
+We also note that on average, our hazard curves are fairly centered with respect to the different discrete value-ranges of the other studies (reported in Table \ref{tab:pga} and indicated with empty-circle ranges in Fig.~\ref{fig:tehran}).
+We also note that all other results fall within the shaded area, which represents the upper and lower bounds of uncertainty in the GMPEs.
+In other words, results from all other studies are below and above our results for the GMPE+Unc.~and GMPE--Unc.~models in our logic tree analysis.
+This provides confidence in the approach followed here based on a centered backbone GMPE and the ideas put forward by \citet{Atkinson2014}.}

### 2016-10-21 conclusions.tex
done with conclusions

--- 2016-10-04 conclusions.tex
@@
 We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models.
-In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model.
-Our calculations yield results similar to those of other studies but offer a more complete picture than previous hazard \myrevision{analyses} due to the usage of a more complete catalog and inclusion of low-magnitude events.
-In our analysis we found it convenient to combine both the regional and uniform models as a \myrevision{means} to consider the epistemic uncertainty intrinsic to the subjective choice of models and seismic zones.
-Such a combination yielded hazard maps that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, and to the location of known seismically active faults.
+In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, \myrevision{including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach.
+In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it.
+We, however, provide a more complete perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
+In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}.
 While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers.
-Future work to improve the results presented here should consider \myrevision{other} ground motion parameters such as response spectral accelerations for different periods and site effects.
+Future work to improve the results presented here should consider \myrevision{other ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.

### 2016-10-21 acknowledge.tex
acknowledgements done

@@
 
-The authors wish to express their gratitude to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing \myrevision{advice} on the use of the software.
+\myrevision{The authors wish to express their thanks to two anonymous reviewers whose comments and suggestions greatly help to improve the original manuscript.
+A message of} gratitude is also extended to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing \myrevision{advice} on the use of the software.
 The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information.

### 2016-10-21 response.tex
some final changes

--- 2016-10-19 response.tex
@@
 \usepackage[review]{myreviewpckg}
+
+\usepackage{textcomp}
 \usepackage{simplemargins}
@@
 
+% ******************************************************************
+% *************************** REVIEWER 1 ***************************
+% ******************************************************************
+
 \begin{center}
@@
 We thank the reviewer for his/her comments and suggestions, which helped us improve the manuscript.
-To help the review process, in the annotated manuscript version of the paper, we have highlighted the changes that resulted from these comments in green colored font when appropriate.
+To help the review process, in the annotated manuscript version of the paper, we have highlighted the most relevant changes that resulted from these comments in green font.
 In the following, we provide a response to each comment.
@@
 \comment{1}{%
-Pp3, Line 71: A short, summary description of previous source models would highlight the contribution of this work.
+Page 3, Line 71: A short, summary description of previous source models would highlight the contribution of this work.
 In particular, summary details of the work by Khodaverdian et al should be included to indicate how the approach of the authors differs from previous work.
@@
 \response{%
-In Khodaverdian et al (2016), seismicity parameters like $b-value$ and $M_{max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree.
-Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point.
-Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.
+We modified parts of the introduction as well as other sections to highlight in a more explicit manner the differences in our study with respect to other previous efforts.
+In the case of Khodaverdian et al (2016), the major difference is in the way the seismicity parameters $b$ and $M_{\max}$ are calculated.
+This is mentioned in the Introduction, and addressed with more clarity in Section 4 (page 11, line 312) and in Section (page 17, line 495).
+As mentioned there, the difference resides in the fact that Khodaverdian et al (2016) compute seismic parameters for grid cells of size 1\textdegree{} $\times$ 1\textdegree{}.
+This means the they compile earthquake catalogs for each grid point considering events within 200 km radius from the grid point, whereas we assume the seismic parameters to be uniform for each tectonic seismic region.
 }
@@
 \comment{2}{%
-Pp 3, line 77: Fault-based/geologic-based earthquake recurrence estimates 
+Page 3, line 77: Fault-based/geologic-based earthquake recurrence estimates
 }
@@
 \response{%
-Added thanks.
+Added, thanks.
 }
@@
 \comment{3}{%
-Pp 4, line 106: Should this be northwest?
+Page 4, line 106: Should this be northwest?
 }
@@
 \response{%
-Fixed, Thanks.
+Yes. Fixed.
 }
@@
 \comment{4}{%
-Pp 6, line 168: It would be good to add a reference for the GEM effort.
+Page 6, line 168: It would be good to add a reference for the GEM effort.
 }
@@
 \response{%
-Added. Thanks.
+We do not have a direct reference to GEM but added a citation to Zare et al (2014), where the connection to GEM is mentioned explicitly.
 }
@@
 \comment{5}{%
-Pp7-8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing.
-Typically, one either specifies a minimum magnitude of completeness (Mc) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding Mc.
+Pages 7--8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing.
+Typically, one either specifies a minimum magnitude of completeness ($M_c$) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding $M_c$.
 In reading the text, it appears that both methods were used.
@@
 \response{%
-You are right.
-We used both methods in the study.
-First we compute the $b-value$ and $M_{max}$ for each region, or the uniform model using the HA3 package written by Dr.
-Kijko.
-$M_c$ is used as an input in the software to get accurate results.
-We computed the smoothed seismic hazard using the Seiskit package, written by Dr.
-Frankel.
-In estimating the seismic hazard, specifically $a-value$, we need to define a start year of completeness for each magnitude range.
-We modified the text to clarify the statement.
+The new version of the Completeness sub-section now clarifies this point.
+The reviewer is right in that we used both methods, but we originally did not clearly explain the procedure.
+We first compute the $b$ and $M_{\max}$ values for each region, or the uniform model, using the HA3 package written by Dr.~Kijko.
+At this point, $M_c$ is used as an input to the HA3 software.
+We then used the Seiskit package written by Dr.~Frankel to compute the smoothed seismicity $a$-values.
+At this point, SeisKit uses the start year of completeness for each magnitude range.
+Please see changes in page 8, lines 211 and 229.
 }
@@
 \comment{6}{%
-Pp7-8: The authors should note that some authors use an alternative smoothing kernel $(~exp(-(D/2*sigma)^2)$.
+Pages 7--8: The authors should note that some authors use an alternative smoothing kernel $(~exp(-(D/2*sigma)^2)$.
 Comparison of the smoothing length between different studies may require consideration of a $sqrt(2)$ factor.
@@
 \response{%
-Added. Thanks. 
+We added a note to this effect in Section 4, and cite the work of Moschetti (2015) as an example.
+A complete analysis of the smoothing length and its influence on the hazard analysis, however, is out of the scope of the present study.
+The modifications done can be found in page 10, line 295.
 }
@@
 \comment{7}{%
-Pp7-8: In addition to the Mirzaei et al.
-(1997) reference, some authors employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods (e.g., Werner et al., 2011; Moschetti, 2015).
+Page 7--8: In addition to the Mirzaei et al (1997) reference, some authors employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods (e.g., Werner et al., 2011; Moschetti, 2015).
 }
@@
 \response{%
-Added to the text. Thanks.
+We included a note to reflect this and added the references suggested by the reviewer. The changes can be seen in page 11, line 304.
 }
@@
 \comment{7}{%
-Pp 9: Kagan and Jackson, 1994 should also be included in the reference list.
+Page 9: Kagan and Jackson (1994) should also be included in the reference list.
 }
@@
 \response{%
-Added. Thanks.
+We added the suggested reference to the list provided in page 10, line 278.
 }
@@
 \comment{8}{%
-Pp 10, line 302: " ...
-subjective decisions and any reasonable choice ...
-" I would disagree that these are subjective decisions.
+Page 10, line 302: ``...subjective decisions and any reasonable choice...'' I would disagree that these are subjective decisions.
 My opinion is that you have applied scientific judgment.
-You clearly need to communicate where judgment is applied; however, \\
-- Details about the implementation of the two seismicity rate models (U, R) should be expanded.
+You clearly need to communicate where judgment is applied; however:
+\\[5pt]
+Details about the implementation of the two seismicity rate models (U, R) should be expanded.
 Are sub-catalogs developed for the five separate regions and then used to develop separate a-grids?
 Presumably, the separate rate files are then used to compute hazard curves and are summed at each location.
-\\
--A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.\\
--Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
+\\[5pt]
+A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.
+\\[5pt]
+Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
 }
@@
 \response{%
-We added the logic tree to the study to consider the epistemic uncertainty, instead of giving the range of uncertainty.
-In practice, we define the grids for the whole region, however, estimate the $a-value$ and also the probability of exceedance for each region, separately.
-To do that, in each run we just provide the seismic source data ( in this case location and magnitude) for the specific region.
-Based on the logic tree approach we conducted 162 runs to get the results $(3 M * 3 B * 6 R(5 region+1 uniform)*3 GMPE)$.
+The reviewer was right to suggest that our original approach to present a combination of the R and U models was not the best.
+In the revised manuscript we have addressed this in two basic manners.
+First, we now provide a better explanation of the rationale behind both models and the reasons to provide a combined result.
+Second, we adopted the suggestion of implementing a logic tree approach in our analysis.
+The adopted logic tree allows us to consider the epistemic uncertainty in the defintion of the seismic zones and also allowed us to include uncertainties in the seismic parameters $b$ and $M_{\max}$.
+For each branch of the logic tree we assigned weights following literature recommendations and our own judgement.
+In total, traversing and combining the different branches meant to conduct 162 runs ( $3 M_{\max} \times 3 b \times (5 \mbox{regions} + 1 \mbox{uniform}) \times 3 \mbox{GMPE}$) to get the combined results of the 2 basic models (R and U), three values of $b$ and $M_{\max}$ and three GMPE alternatives.
+The associated changes can be seen in various sections of the revised manuscript, and in particular in the new Section 7 and the Results Section 8.
 }
@@
 \comment{9}{%
-Pp 14, line 391 The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA.
+Page 14, line 391: The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA.
 Recent papers by Atkinson and others have demonstrated this effect.
-You may wish to argue that Mmin was chosen based on the expected smallest magnitude capable of causing damage.
+You may wish to argue that $M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage.
 }
@@
 \response{%
-Thanks for the comment. We computed hazard for events $M_w > 4.5$ and modified the text. 
+We revised the computations and now present results for events with $M_w > 4.5$. The text was modified accordingly (see page 4, line 94).
 }
@@
 \comment{10}{%
-Figure 7: Is the magnitude-frequency distribution just a truncated (Mmin, Mmax) GR model? Figure 7 suggests that the MFD may be tapered?
+Figure 7: Is the magnitude-frequency distribution just a truncated ($M_{\min}$, $M_{\max}$) Gutenberg-Richter model? Figure 7 suggests that the MFD may be tapered?
 }
@@
 \response{%
-Yes it is truncated GR model. 
+Yes, it is truncated Gutenberg-Richter model. We now make this explicit in the caption of the figure.
 }
@@
 \comment{11}{%
-Pp 12, line 345: "...
-controls the spatial extent to which the local occurrence of earthquakes ..." I would argue that the smoothed seismicity controls the local occurrence and spatial distribution of earthquakes and that the GMPEs control the intensity level at a particular site given earthquake locations and magnitudes from your source model.
+Page 12, line 345: ``...controls the spatial extent to which the local occurrence of earthquakes...'' I would argue that the smoothed seismicity controls the local occurrence and spatial distribution of earthquakes and that the GMPEs control the intensity level at a particular site given earthquake locations and magnitudes from your source model.
 }
@@
 \response{%
-Thanks. Modified it. 
+That is correct. We have modified this sentence accordingly. Please se changes in page 13, line 365.
 }
@@
 \comment{12}{%
-Pp 13, line 361: Change "approached" to "approach" and "lead" to "led."
+Page 13, line 361: Change ``approached'' to ``approach'' and ``lead'' to ``led.''
 }
@@
 \response{%
-Done.
+This part of the text was modified and the requested change may no longer apply, at least in regard to the first suggestion.
+Regarding the second suggestion, we do not quite agree.
+Although there was a typo, the way the sentence was structured, the corrected version uses ``leads'' instead.
 }
@@
 This work is not a comprehensive seismic hazard analysis, and presentation of probabilistic ground motions from the R, U and a weighted model would be reasonable goal.
-However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying b- and Mmax-values for the R model greatly complicate the comparison.
+However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying $b$- and $M_{\max}$-values for the R model greatly complicate the comparison.
 As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references, Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015).
@@
 Thanks for the informative comment.
-In Figure 10, we combined the regional (R) and uniform (U) results (We combine the probability of exceedance, then compute the pga)  with similar weights (i.e., 0.5).
-The positive and negative standard deviation plots comes from GMPE+Uncertainty  and GMPE-Uncertainty.
-We were showing the range of variation for PGA around the median value.
-As we discussed before, in order to consider the epistemic uncertainty, instead of presenting the range of uncertainty, we used the logic tree approach and modified Figure 10.
-The weights are presented in logic tree figure.
+In the original figure 10 we combined the regional (R) and uniform (U) results (i.e., we combined the probabilities of exceedance, and then computed the PGA) with similar weights (i.e., 0.5).
+The positive and negative standard deviation plots came from GMPE + Uncertainty and GMPE -- Uncertainty.
+Our original intention was to show the range of variation for PGA around the median value.
+However, in the revised version of the manuscript this is no longer done.
+The new figure corresponding to the (R,U) combined model (Fig.~12) is now the result of the complete logic tree analysis, which is a more appropriate approach to presenting the results of our analysis.
 }
+
+% ******************************************************************
+% *************************** REVIEWER 2 ***************************
+% ******************************************************************
 
@@
 \noindent
-We thank the reviewer for his comments and suggestions, which helped us improve the manuscript.
-To help the review process, in the annotated manuscript version of the paper, we have highlighted the changes that resulted from these comments in green colored font when appropriate.
+We thank the reviewer for his/her comments and suggestions, which helped us improve the manuscript.
+To help the review process, in the annotated manuscript version of the paper, we have highlighted the most relevant changes that resulted from these comments in green font.
 In the following, we provide a response to each comment.

### 2016-10-21 abstract.tex
some final changes

@@
 Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region.
-In the analysis we consider uncertainties in the ground motion prediction equation, the seismic parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+In the analysis we consider uncertainties in the ground motion prediction equation, the seismicity parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
 \myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.

### 2016-10-21 compilation.tex
almost done with section 8
some final changes

@@
 In the case of the historical seismicity catalog, the color fill indicates the year of the event.
-The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief \myrevision{in the background.
+The borders of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in thin white lines, along with the light-gray shaded relief \myrevision{in the background.
 The dashed box indicates the effective region of interest}.}
 	\label{fig:catalog}
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
+	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
+	\label{fig:scatter}
 \end{figure*}
@@
 The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}, which includes the spatial distribution within the region of interest for both historical and instrumental events; and in Fig.~\ref{fig:scatter}, which presents the distribution of events in time and magnitude for each of the seismic zones, as well as for the complete region of interest (hereafter referred as the uniform model).
-
-\begin{figure*} [t]
-	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
-	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
-	\label{fig:scatter}
-\end{figure*}

### 2016-10-21 conclusions.tex
some final changes

@@
 In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it.
-We, however, provide a more complete perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
+We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
 In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}.

### 2016-10-21 logictree.tex
some final changes

@@
 Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude of one standard deviation, $\sigma_{\ln y} = 0.612$.
-The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2015}.}
+The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2008}.}
 

### 2016-10-21 parameters.tex
up to logic tree
almost done with section 8
some final changes

@@
+\begin{table}%[t]
+    \centering
+    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
+    \myrevision{
+    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
+        \cline{2-4}                                                                         \\[-1.6ex]
+                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
+        \hline                                                                              \\[-1.6ex]
+        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
+        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
+        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
+        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
+        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
+        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
+        \hline
+    \end{tabular}
+    }
+    \label{tab:params}
+\end{table}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{figures/pdf/figure-07}
+    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest \myrevision{following a truncated Gutenberg-Richter model}.
+The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
+The last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
+The shaded range indicates the models' $\pm 1$ standard deviation.}
+    \label{fig:annualp}
+\end{figure*}
+
 \section{Seismicity Parameters}
@@
 Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
-
-\myrevision{
-\begin{table}%[t]
-    \centering
-    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
-    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
-        \cline{2-4}                                                                         \\[-1.6ex]
-                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
-        \hline                                                                              \\[-1.6ex]
-        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
-        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
-        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
-        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
-        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
-        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
-        \hline
-    \end{tabular}
-    \label{tab:params}
-\end{table}
-}
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-07}
-    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
-The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
-The last curve in green corresponds to the complete region of interest, here referred to as the uniform model.
-The shaded range indicates the models' $\pm 1$ standard deviation.}
-    \label{fig:annualp}
-\end{figure*}

### 2016-10-21 results.tex
some final changes

@@
 Obviously, given the differences in the catalogs, completeness magnitude, and in the seismicity parameters $M_{\max}$ and $b$, we cannot expect PGA values to match.
-For example, in the case of the $b$ values, \citet{Khodaverdian_2016_BSSA} reported large variations netween 0.56 and 1.27, where over 50 percent of the grid points had $b$ values greater than 1; whereas in our study the $b$ values observe a narrow range of variation between 0.93 and 1.15.
+For example, in the case of the $b$ values, \citet{Khodaverdian_2016_BSSA} reported large variations between 0.56 and 1.27, where over 50 percent of the grid points had $b$ values greater than 1; whereas in our study the $b$ values observe a narrow range of variation between 0.93 and 1.15.
 In this regard we should note that \citet{Khodaverdian_2016_BSSA} computed the seismicity parameters for each grid point considering the contributions within a circular area of radius 200 m, whereas we considered a uniform seismicity parameters for each region and account for the uncertainty in the difference between regions via the combination of the R and U models.}
@@
 \myrevision{Altogether, on average, we found our results to be in good agreement with other previous results.
-For the city of Uremia, for instance, we obtained a expected PGA of 0.24 g, which is slightly lower than values obtained by \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for a 10 percent probability of exceedance in 50 years.
+For the city of Urmia, for instance, we obtained a expected PGA of 0.24 g, which is slightly lower than values obtained by \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for a 10 percent probability of exceedance in 50 years.
 We believe \citet{Zare2012} obtained higher values because their of use of a parametric method.

### 2016-10-22 response.tex
change modes

@@
 It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis.
-I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in a-value, b-value, and Mmax, for example, are considered.
+I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in $a$-value, $b$-value, and $M_{\max}$, for example, are considered.
 Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
@@
 \response{Thanks for the comment.
-Based on explanation of GMPEs section (please see comment no.27) we decided to define a suite of GMPE as well as plus and minus one standard deviation.
-We consider the epistemic uncertainty in tectonic seismic regions, $M_{max}$, $b-value$, and attenuation relationship through a standard logic tree analysis.}.
+Based on explanation of GMPEs section (please also see comment No.~27) we decided to address uncertainty with a backbone GMPE plus and minus one standard deviation.
+We also consider uncertainty in tectonic seismic regions through variations in the seismicity parameters $M_{\max}$, $b$, and combine the results using a standard logic tree analysis, as suggested.
+These changes are reflected at various points throughout the revised manuscript.}
 
@@
 
-\response{That is right. We increased the buffer zone up to 2 degrees.}
+\response{That is right. We increased the buffer zone up to 2 degrees. See page 4, line 100.}
 
@@
 }
-\response{Added to the abstract.}
+
+\response{We modified the abstract accordingly, but do not provide too much detail as that would significantly increase the length of the abstract, which is not desirable. See new lines 23--25.}
 
@@
 }
-\response{We  added the reference for figure 1. Thanks.}
+
+\response{We added a reference to figure 1 in page 2, line 40.}
 
 \comment{5}{%
-line 39:   eight  $\to$ eighth
+Line 39: eight $\to$ eighth
 }
+
 \response{Fixed.}
@@
 \comment{6}{%
-line 55   focuses in $\to$ focuses on
+Line 55: focuses in $\to$ focuses on
 }
+
 \response{Done. Thanks.}
@@
 \comment{7}{%
-line 56 $\to$ Please be more specific about how your analysis differs from previous analyses.
+Line 56: Please be more specific about how your analysis differs from previous analyses.
 }
-\response{In the introduction we explain the method and parameters here and there, however, we added a couple of sentences to briefly explain the method. Thanks}
+
+\response{We modified the introduction to better explain the method and parameters.
+However, there are some details we still believe go better within the subsequent sections.
+Changes correspond to lines 54 to 76.}
+
 \comment{8}{%
-line 60 $\to$ Can you be more specific? What are the other indicators?
+Line 60: Can you be more specific? What are the other indicators?
 }
-\response{We discussed this before. We need to remove the sentence and rewrite that part.}
+
+\response{In hindsight that was not the best choice of words. Since we modified this part of the introduction, the new text does no longer includes this sentence.}
 
 \comment{9}{%
-line 71 $\to$ Include reference? Include reference.
+Line 71: Include reference.
 }
+
 \response{Done. Thanks.}
@@
 \comment{10}{%
-line 78 $\to$ reduce $\to$ acknowledge
+Line 78: reduce $\to$ acknowledge
 }
+
 \response{Fixed.}
@@
 \comment{11}{%
-line 99 $\to$ Is 0.5 degrees enough?
+Line 99: Is 0.5 degrees enough?
 To what distance do you do your ground motion calculations?
@@
 }
-\response{We reanalyze the hazard with 2 degrees buffer zone. }
+
+\response{We reanalyze the hazard with 2 degrees buffer zone. This is reflected in the new Figures 1 and 3, and in the text (line 100) as well as, of course, in the results.}
 
 \comment{12}{%
-line106 $\to$ northeast $\to$ northwest
+Line106: northeast $\to$ northwest
 }
+
 \response{Done. Thanks}
@@
 \comment{13}{%
-line 114 $\to$ There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
+Line 114: There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
 }
-\response{Thanks for the comment. It is 26 April 1721,$M_s ~ 7.3$ earthquake}
+\response{Thanks for the comment. It is the 26 April 1721 $M_s$ 7.7 earthquake. The change is now in page 4, line 114.}
 
 \comment{14}{%
-line 180 $\to$ The smaller events should also help to inform the G-R relationship.
+Line 180: The smaller events should also help to inform the G-R relationship.
 }
-\response{Thanks for the comment. Added to the text.}
+
+\response{Thanks for the comment. Added to the text in line 182.}
 
 \comment{15}{%
-line 182 $\to$ How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
+Line 182: How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
 }
-\response{They didn't provide a numerical value, or numbers on the contour lines, however, we read the images with Matlab and locate the values. We added to the table. Thanks.}
+
+\response{They did not provide a numerical value, or numbers on the contour lines. However, we read the images with Matlab and located the values and now include them in the new version of Table 3.}
 
 \comment{16}{%
-line 192 $\to$ What is the total number of events before and after declustering?
+Line 192: What is the total number of events before and after declustering?
 }
-\response{Number of events before decluttering: 10441, total foreshock: 971, total aftershock: 4206, declustered data 5254.
-It should be noted that, these numbers are representing the events in the study region (including the bufferzone).
+
+\response{Number of events before decluttering: 10,441; total foreshocks: 971; total aftershocks: 4,206; declustered data: 5,254.
+It should be noted that these numbers are representing the events in the complete study region (including the buffer zone).
 It partly includes events from Central and Zagros region.
-For completeness study we studied the whole data for each region.}
+For the completeness, we studied the whole data for each region.
+This is now explained in page 7, line 195.}
 
 \comment{17}{%
-line 224 $\to$ Why did you use this method? What are the benefits of one or the other?
+Line 224: Why did you use this method? What are the benefits of one or the other?
 }
-\response{Both methods have been used extensively in previous studies. We just picked one. Text was implying that this method has beneficial to the ZMAP method, we fixed it. Thanks.}
+
+\response{Both methods have been used extensively in previous studies.
+We just picked one, mainly so due to ease of implementation, which also allowed us to have complete control over the final selection.
+The text was incorrectly implying that the goodness-of-fit rest method had benefits over the MAXC method.
+We fixed this and now state our reasons in a more transparent way.
+See page 8, line 229.}
 
 \comment{18}{%
-line 232 $\to$ It is unclear how you chose Mc. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
+Line 232: It is unclear how you chose $M_c$. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
 }
+
 \response{According to Wiemer and Wyss (2000), the priority is picking the magnitude which has the peak goodness-of-fit value.
-However at some cases for two or a couple of magnitudes the goodness-of-fit scores are not considerably different.
-In these cases, we pick the minimum magnitude, even though it doesn't have the peak goodness-of-fit value, in order to preserve the valuable earthquake event data.}
+However, in some cases for two or a couple of magnitudes the goodness-of-fit scores are not considerably different.
+In these cases, we pick the minimum magnitude, even though it does not have the peak goodness-of-fit value, in order to preserve more data.
+We also consider the decay of the cumulative number of events.
+This is now explained in the revised manuscript in pages 8 and 9.}
 
 \comment{19}{%
-line 267 $\to$ add 'and'
+Line 267: add 'and'
 }
@@
 \comment{20}{%
-line 289 $\to$ You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
+Line 289: You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
 }
-\response{Added. Thanks.}
+
+\response{We included the suggested reference, though the actual publication year is 2015.}
 
 \comment{21}{%
-line 297 $\to$ provided below $\to$ provided in the next section
+Line 297: provided below $\to$ provided in the next section.
 }
+
 \response{Fixed.}
@@
 \comment{22}{%
-line 300 :  allows to draw information $\to$ allows one to draw information
+Line 300: allows to draw information $\to$ allows one to draw information
 }
+
 \response{Done.}
@@
 \comment{23}{%
-line 323 $\to$ Be more specific about how HA3 computes b and Mmax. What is its method?
+Line 323: Be more specific about how HA3 computes $b$ and $M_{\max}$. What is its method?
 }
-\response{Method added. Thanks.}
+
+\response{This code uses the procedure described in Kijko and Sellevoll (1989). We added a sentence making this explicit in page 12, line 341.}
 
 \comment{24}{%
-line 335 $\to$ Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
+Line 335: Different seismic zone will not necessarily have difference values of $b$ and $M_{\max}$. Change to this: Different seismic zone may have different values of $b$ and $M_{\max}$.
 }
-\response{Modified. Thanks.}
+
+\response{Modified. Thanks. See line 354.}
 
 \comment{25}{%
-line 337 $\to$ a means to reduce epistemic $\to$ a means to account for epistemic
+Line 337: a means to reduce epistemic $\to$ a means to account for epistemic
 }
+
 \response{Done.}
@@
 \comment{26}{%
-line 361 $\to$ lead $\to$ leads
+Line 361: lead $\to$ leads
 }
+
 \response{Fixed. Thanks.}
@@
 \comment{27}{%
-line 364 $\to$ How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
+Line 364: How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
 }
-\response{As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs.
-We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or central GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE.
-In the previeous study (Khodaverdian 2016), they used Akkar and Bommer (2010) and Ghasemi et al (2009) along side other equations.
-Akkar and Bommer (2010) derived the equation up to 100 Km, which they used for 200 km.
-Also Ghasemi et al (2009) is presented the coefficients for spectral acceleration not PGA.
-Of course this alternative method has been a hotly-debated topic, and there is no clear consensus about that, however, the plots of attenuation relationships in different magnitude illustrate the fact that with this approach we can address the epistemic uncertainty in an acceptable range.
-We totally agree with the reviewer's comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers.
-In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig 9.}
+
+\response{This is a point that was also raised by Reviewer 1.
+As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs.
+Especially when the mean of various GMPEs are too close to each other.
+We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or central GMPE, and to define representative upper and lower GMPEs using the standard deviation of the chosen relationship.
+In order to address these concerns we now use the logic tree scheme shown in Fig.~9 and make comments with respect to this in various points throughout the revised version of the manuscript, but in particular in pages 13 and 14, lines 380--397.}
 
 \comment{28}{%
-line 365: add 'and'
+Line 365: add 'and'
 }
+
 \response{Added. Thanks.}
@@
 \comment{29}{%
-line 370 $\to$ Could you consider other depths to help fill out your range of epistemic uncertainty?
-}
-\response{The Kalkan and Gulkan (2004) attenuation relationship is originally generated for Turkey.
-However, in the recent test by Zafarani and Mousavi (2014), it gives acceptable results for PGA.
-Since the high accuracy achieved by the current depth, and we have no idea how different depth will change the results, we prefer to not to use a parameter without knowing the effects.
+Line 370: Could you consider other depths to help fill out your range of epistemic uncertainty?
 }
 
+\response{Not really.
+At least we think it would not be appropriate to do so.
+The Kalkan and Gulkan (2004) attenuation relationship was originally generated for Turkey.
+Later, Zafarani and Mousavi (2014) found that this GMPE yielded acceptable results for PGA for northern Iran if calibrated with the values we report in the manuscript.
+Since the high accuracy achieved by using this GMPE depends on the the current choice of depth, we ignore what would be the effect of considering the variability of $h$, and suspect it will likely be to the detriment of the analysis.
+We make tangential mention to this in the new Section 7.
+See page 15, line 424.}
+
 \comment{30}{%
-line 371 $\to$ How does this value compare with the models you decided not to use?
+Line 371: How does this value compare with the models you decided not to use?
 }
-\response{In the revised version we used backbone and plus and minus one standard deviation as three GMPEs. }
+
+\response{In the revised version we use a backbone GMPE, in addition to GMPEs derived using plus and minus one standard deviation. Therefore, this comment does no longer apply.}
 
 \comment{31}{%
-line 376 $\to$ In this case, you should consider all sources with 200 km of your area of interest.
+Line 376: In this case, you should consider all sources with 200 km of your area of interest.
 }
-\response{We modified the buffer zone. Thanks.}
+\response{We modified the buffer zone and now do this. Thanks.}
 
 \comment{32}{%
-line 394:  50-years $\to$ 50-year
+Line 394: 50-years $\to$ 50-year
 }
@@
 \comment{33}{%
-line 420: with concentration $\to$ with a concentration
+Line 420: with concentration $\to$ with a concentration
 }
+
 \response{Added. Thanks.}
@@
 \comment{34}{%
-line 422 $\to$ I would have stated this differently.
-It looks like the lower b-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
+Line 422: I would have stated this differently.
+It looks like the lower $b$-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
 }
-\response{Based on the modification in GMPEs and uncertainties at the revised version, we rewrite the description part.}
+
+\response{Based on the modification in GMPEs and uncertainties, we rewrote this description.}
 
 \comment{35}{%
-line 428 $\to$ Why equal weights?
+Line 428: Why equal weights?
 }
-\response{We added a comprehensive logic tree analysis after revision and modified the weights. Please see figure 9.}
+
+\response{We added a comprehensive logic tree analysis and modified the weights. Please see figure 9, and the description given in the new Section 7.}
 
 \comment{36}{%
-line 431 $\to$ I'm not sure I quite understand this.
+Line 431: I'm not sure I quite understand this.
 The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve.
@@
 If you want to include figure 10, a proper logic tree analysis to include more forms of epistemic uncertainty should be performed.
-For example, add branches for uncertainty in which GMPE you choose, uncertainty in b-value, uncertainty in Mmax, uncertainty in a-value, uncertainty in smoothing parameter, etc.
+For example, add branches for uncertainty in which GMPE you choose, uncertainty in $b$-value, uncertainty in $M_{\max}$, uncertainty in $a$-value, uncertainty in smoothing parameter, etc.
 }
-\response{We modified the approach and considered the mentioned uncertainties.}
+
+\response{We modified the approach and now consider the uncertainties explicitly via a logic tree analysis. Therefore, we believe this no longer applies as the new approach is more appropriate.}
 
 \comment{37}{%
-line 434 $\to$ Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the b-values are truly different between regions and better represented by the regional analysis.
+Line 434: Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the $b$-values are truly different between regions and better represented by the regional analysis.
 }
-\response{That's right. Removed that part. Thanks.}
+
+\response{Agree. We believe, however, that this can be interpreted as a good indication of how the data is being captured by the analysis. We modified this.}
 
 \comment{38}{%
-line 439: of city of Tabriz $\to$ of the city of Tabriz.
+Line 439: of city of Tabriz $\to$ of the city of Tabriz.
 }
+
 \response{Fixed. Thanks.}
@@
 \comment{39}{%
-line 450 $\to$  for 2 and 10\%, respectively $\to$ for 2 and 10\% in 50 years, respectively.
+Line 450: for 2 and 10\%, respectively $\to$ for 2 and 10\% in 50 years, respectively.
 }
+
 \response{Done.}
@@
 \comment{40}{%
-line 453 $\to$  for a 10\% probability of exceedance ?  for a 10\% probability of exceedance in 50 years.
+Line 453: for a 10\% probability of exceedance $\to$ for a 10\% probability of exceedance in 50 years.
 }
+
 \response{Done.}
@@
 \comment{41}{%
-line 455 $\to$ 0.27-0.31 g for 10\% probability of exceedance $\to$  0.27-0.31 g for the same exceedance probability
+Line 455: 0.27--0.31 g for 10\% probability of exceedance $\to$ 0.27-0.31 g for the same exceedance probability
 }
+
 \response{Done.}
@@
 \comment{42}{%
-line 458 $\to$  for 2 and 10\% ? for 2 and 10\% in 50 years
+Line 458: for 2 and 10\% $\to$ for 2 and 10\% in 50 years
 }
+
 \response{Done.}
@@
 \comment{43}{%
-line 461: our results are close or within $\to$ our results are close to or within
+Line 461: our results are close or within $\to$ our results are close to or within
 }
+
 \response{Done.}
@@
 \comment{44}{%
-line 462 $\to$ Can you explain the differences in their analysis relative to yours that lead to higher values?
-}
-\response{They used Maximum Credible Earthquake as $M_{max}$.
-The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{max}$.
-We added the explanation to the text.
+Line 462: Can you explain the differences in their analysis relative to yours that lead to higher values?
 }
 
+\response{They used Maximum Credible Earthquake as $M_{\max}$.
+The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{\max}$.
+We added the explanation to the text (see page 18, line 511).}
+
 \comment{45}{%
-line 466: exceedance as functions of PGA  $\to$ exceedance as functions of PGA, also known as hazard curves}
-\response{Added. Thanks.}
+Line 466: exceedance as functions of PGA $\to$ exceedance as functions of PGA, also known as hazard curves}
+
+\response{Done.}
 
 \comment{46}{%
-line 475 $\to$ Can you explain the differences in the hazard analysis that led to differences in hazard?}
-\response{Added to the text.}
+Line 475: Can you explain the differences in the hazard analysis that led to differences in hazard?}
+
+\response{We modified this paragraph and included a better description of the differences and results. See pages 18 and 19, lines 524--549.}
 
 \comment{47}{%
-lline 488 $\to$ Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
-you only use one GMPE (though you do consider two b-value and Mmax based models).
+Line 488: Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
+you only use one GMPE (though you do consider two $b$-value and $M_{\max}$ based models).
 }
-\response{That is right. We restate the sentence. Thanks.}
+
+\response{That is right. We restate the sentence and modified the conclusions accordingly.}
 
 \comment{48}{%
-line 488:  hazard analysis $\to$ hazard analyses
+Line 488: hazard analysis $\to$ hazard analyses
 }
+
 \response{Done.}
@@
 \comment{49}{%
-line 490: models as a mean $\to$ models as a means}
+Line 490: models as a mean $\to$ models as a means}
+
 \response{Done.}
@@
 \comment{50}{%
-line 493 $\to$ Though you suggest the uniform model is unrealistic on line 334.}
-\response{That's right. We meant to say less realistic. We fixed the text.}
+Line 493: Though you suggest the uniform model is unrealistic on line 334.
+}
+
+\response{Our choice of words was not the best. We meant to say less realistic. We fixed the text accordingly.}
 
 \comment{51}{%
-line 502 $\to$ for providing advise ? for providing advice}
+Line 502: for providing advise $\to$ for providing advice}
 \response{Done.}
@@
 \comment{52}{%
-line 509 $\to$  Should this be Sunset?}
-\response{Yes. Thanks.}
+Line 509: Should this be Sunset?
+}
+
+\response{Yes. Thank you.}
 
 \comment{53}{%
-p 25, table2 $\to$ What did you do for the earthquakes occurring outside of these five zones?}
-\response{There are earthquakes out of the regions, mainly above the Caspian see.
-Since those area are not in our region of interest (They mainly are in country of Azerbaijan), and are fairly far from our region, we ignored them.}
+Page 25, Table 2: What did you do for the earthquakes occurring outside of these five zones?
+}
+
+\response{
+As it can be seen in Figure 1, earthquakes outside the regions would be too far to be included.
+There are earthquakes above the Caspian see, for instance, and others in the country of Azerbaijan which were ignored because they were beyond the buffer zone (which as it was mentioned before, was expanded).}
 
 \comment{54}{%
-p 26, table3 $\to$ Specify units.}
+Page 26, Table 3: Specify units.}
+
 \response{Done. Thanks.}
@@
 \comment{55}{%
-p32, figure 3 $\to$ You should also show events in the buffer zone used to compute hazard.}
+Page 32, Figure 3: You should also show events in the buffer zone used to compute hazard.}
+
 \response{Done.}
@@
 \comment{56}{%
-p34, figure 5 $\to$ Which seismic zone corresponds to which color?
+Page 34, Figure 5: Which seismic zone corresponds to which color?
 It looks like either reporting or rates have changed over time.
@@
 }
-\response{Thanks for the comment.
+
+\response{%
+Thanks for the comment.
 The problem with that region is having less than and equal sign on magnitude 4.
 There are many earthquakes go to that category because of that condition.
-Since, converting earthquake magnitude always has an error margin, we think the comment is relevant.
+Since converting earthquake magnitude always has an error margin, we think the comment is relevant.
 Based on the data we assume 2005 as a completeness magnitude.
-We presented the legends at the bottom of the figure.}
+We presented the legends at the bottom of the figure.
+}
 
 \comment{57}{%
-P37: 10 percent of probability $\to$ 10 percent probability }
+Page 37: 10 percent of probability $\to$ 10 percent probability
+}
+
 \response{Done.}
@@
 \comment{58}{%
-p 39,figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
+Page 39, Figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.
+}
+
 \response{Included.}
@@
 \comment{59}{%
-p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
-\response{Added.}
+Page 41, Figure 12: Can you include curves or points for the other studies in Table 3?
+}
+
+\response{We did and made comments about this in the Results section.}
 

### 2016-10-22 results.tex
final form for resubmission

@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-12.pdf}
-    \caption{Expected PGA values throughout the region of interest for 2 (left) and 10 (right) percent probability of exceeding an earthquake magnitude $M_w$ 5 using the combined model (R,U) hazard calculations.
+    \caption{Expected PGA values throughout the region of interest for 2 (left) and 10 (right) percent probability of exceeding an earthquake magnitude $M_w$ 4.5 using the combined model (R,U) hazard calculations.
 Mean expected values are shown in the middle, whereas the top and bottom frames correspond to the results obtained using plus and minus one standard deviation.}

### 2017-01-25 abstract.tex
Revision added.

@@
 \myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
-We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions}.
+We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions.
+\color{red}{A comprehensive study of seismic hazard also needs to include a geological and tectonic features (e.g., faults) of the study area.
+Although this study results are in a good agreement with studies based on different assumptions, and mostly gives average values due to the smoothing approach, they should not be considered as a final value in seismic design or seismic risk mitigation decisions}}.

### 2017-01-25 conclusions.tex
Revision added.

@@
 While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers.
-Future work to improve the results presented here should consider \myrevision{other ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.
+Future work to improve the results presented here should consider \myrevision{  \color{red}{generating random fault based on earthquake magnitude as well as considering actual faults}, most recent developed ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.

### 2017-01-26 new-response.tex
response letter to final review

\setlength{\paperwidth}{210mm}
\setlength{\paperheight}{297mm}% fixed.

\documentclass{article}

\usepackage[review]{myreviewpckg}

\usepackage{textcomp}
\usepackage{simplemargins}

\clubpenalty=10000  % Orphan - First of paragraph left behind
\widowpenalty=10000 % Widow  - Last of paragraph sent ahead

\setallmargins{1in}

\begin{document}

\setlength{\parindent}{0ex}

January 26, 2017
\vspace{12ex}

Dr.~Mariano Garc\'{i}a Fern\'{a}ndez\\
Editor in Chief, Journal of Seismology\\
MNCN-CSIC, Madrid, Spain
\vspace{8ex}

\setlength{\parskip}{2ex}

Dear Dr.~Garc\'{i}a Fern\'{a}ndez,

We write in reference to your communication of 12 December 2016 regarding our manuscript submission to the Journal of Seismology, No.~JOSE-D-16-00092R1. We want to thank you for your positive reaction to the revised manuscript and your decision to move forward with the publication of our article, upon the suggested minor changes of language, which we are now pleased to inform we have completed. Enclosed you will find the new version of our submission, which we would appreciate if you could approve at your earliest convenience, so we can proceed with the publication process.

This being said, we did not want to let this opportunity pass by without also addressing the points raised by the third reviewer. We were a little intrigued by the strict criticism of this third reviewer, but at the same time understood the motivation behind his/her comments. While we appreciated very much your candid reaction this this review---given our response to the initial evaluation---, we thought that in addition to following your advise about how to handle it (through minor modifications of form and language), it was still appropriate for us to share with you our views about some of these criticisms. You will also find enclosed our responses, which we hope you will appreciate.

We thank you again for your help during the review process, and look forward to working with the editorial team in the final production and publication of the article.

\vspace{5ex}
Sincerely yours,
\vspace{10ex}

Ricardo Taborda\\
Department of Civil Engineering, and\\
Center for Earthquake Research and Information\\
3890 Central Ave., Memphis, TN 38152\\
phone: 901-678-1527; fax: 901-678-4734\\
University of Memphis

% ******************************************************************
% *************************** REVIEWER 3 ***************************
% ******************************************************************

\newpage

\setlength{\parskip}{0ex}
% \setlength{\parindent}{0ex}

\begin{center}
	\bf
	\large
	Authors' Response to Reviewer 3 Comments
\end{center}

\comment{1}{%
As shown in Figure 2 of this manuscript, the major faults and its characteristicparameter uncertainties should be incorporated into the seismic hazard study of the this region. As the authors stated in Section 4, this type of work has been performed in Tavakoli and Ghafory-Ashtiany (1999) and many others. In order to improve the previous studies, therefore, the seismic hazard maps presented in this manuscript should be modified based on the known major fault sources and areal seismic sources, which are considered as background seismic sources. The smoothed seismicity approach could be used for the background seismic source zones. Otherwise, only using the smoothed seismicity approach could lead to misleading of seismic hazard values and hazard maps in this region, especially when the time span of earthquake catalog is not enough to give us the true seismicity pattern of the region. Lack of consideration for major faults, will have significant and far-reaching consequences for Iran and major metropolitan areas such as Tehran. Accepting the publication in a reputable journal such as Journal of Seismology without consideration for major faults will be a mistake. The reviewer is puzzled why the fourth author of this article who is a reputable researcher has agreed on the publication of this article. The authors write: ``We find our results to be helpful in understanding seismic hazard for northern Iran, but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions.''
}

\response{%
We acknowledge the fact that it would be preferable for any final comprehensive study of the seismic hazard of a region to consider all forms of seismic sources. We also understand that ideally, these sources are to be characterized in terms of the geologic, tectonic, and seismic knowledge of the region. We, however, are also aware that even when these factors are believed to be known, that might still not be sufficient (see Stein, 2012). The smoothed seismicity method is an accepted approach proven to be useful for building a more complete picture of the seismic hazard of a region, but we do not claim, nor do other authors, that the method is robust or comprehensive enough to address seismic hazard in a definitive manner. The method carries advantages as well as disadvantages, which we believe are well documented and acknowledged in our manuscript. Moreover, we are careful not to recommend our findings as final. We are also careful to mention that seismic design or seismic risk mitigation decision cannot solely based on our findings but on a sum of different studies, some of which may use other additional methods and data we did not use. That is why we ``recognize that additional efforts are necessary to obtain a more robust'' hazard estimation. We, nonetheless, also point out that our findings are in good agreement with other fault-based models. For the city of Tehran, for instance, our results are in the mean range of other studies. We use this as an indication that our results are credible and thus could be considered by others for the background seismicity portion of a more comprehensive study.
}

\comment{2}{%
The attenuation relationship used in this study is based on the Joyner-Boore distance, while it appears that the epicentral distance has been used in the smoothed seismicity approach. The authors have not considered the distance adjustment factors, and this lack of distance conversion could lead to underestimate the hazard values in the region, in particular, at low probability of exceedance [2\% PE in 50 year].
}

\response{%
In the smoothed seismicity approach each earthquake as assumed as a point source. That being the case, for any given earthquake in the catalog, the dimensions of the rupturing portion of the fault (length and width) are reduced to a single point in space; and the rupture size and rupture direction become irrelevant. This is not our choice but a fundamental premise of the smoothed seismicity method. The Joyner-Boore distance, on the other hand, is defined as the closest horizontal distance to the vertical projection of the rupture. In finite fault models, where both fault length and rupture direction are meaningful aspects of the source representation, appropriate adjustments need to be done to compute the Joyner-Boore distance with respect to epicentral distance, but that is not the case here. In other words, for point sources, as considered in the smoothed seismicity approach followed, the Joyner-Boore distance is the same as the epicentral distance. It is therefore valid to use the chosen attenuation relationship with epicentral distances.
}

\comment{3}{%
In Figure 4 of this manuscript, the authors have only added the earthquake magnitudes of 3 and greater into a catalog with minimum magnitude of 4 and greater since the year of 2000, and have claimed that the magnitude level of 3--4 is complete from the year of 2005 for all area sources. The authors should explain why they haven't completed their catalog for magnitude 3 and greater for all time. This might affect the period of completeness, declustering and number of events for the recurrence rates.
}

\response{%
We did not consider earthquake with magnitude 3 and above before 2000, simply because there is no data available before that date in a formal catalog. Instrumentation and IIEES reports for earthquakes in the magnitude level 3--4 are well documented only after 2000. The recent study by Zare et al.~(2014) reported the construction of a catalog for all time for a minimum magnitude of 4. We took upon the task of augmenting this catalog by adding the more recent earthquakes after 2012 and the weaker events in the magnitude level 3--4 since 2000. Our completeness analysis of the data shows that the earthquake with magnitude 3 and above is complete from 2005, and given the recurrence rate of smaller earthquakes, we believe the data collected between 2005 and 2015 constitutes a reliable sample for the analysis. We should also note that both softwares used in this study (i.e., HA3 developed by Dr. Kijko, and Seiskit developed by Dr.Frankel) can handle this discontinuity in the catalog.
}

\comment{4}{%
There are few ground motion prediction equations (GMPEs) developed for the Iranian plateau such as Nowroozi (2005), Ghasemi et al.~(2009), Saffari et al.~(2012), and Kale et al.~(2015). The authors do not use these models, and use the model by Kalkan and Gulkan (2004), which has been developed for Turkey. The authors provides a lengthy argument why they do not follow the standard procedure of considering credible GMPEs for the study site. It is not clear why the authors use $h = 6.91$~km and $V_A = 1,112$ m/s. There are no discussions on what the authors consider as their reference site for the PSHA analysis. Is this model developed for a reference site of 1,112 m/s? If so, why?
}

\response{%
The reviewer stands correct when saying that there are other GMPEs that have been developed for the Iranian plateau, different to the one used in our study. Most of these GMPEs, however, are adjusted to fit a certain dataset, as opposed to a complete catalog from the whole northern Iran region. As explained in our manuscript, Zafarani and Mousavi (2014) conducted a careful study in which several local, regional, and next generation attenuation (NGA) GMPEs were evaluated with the objective of determining which GMPEs fitted the data of northern Iran best. Out of the nine GMPEs considered by Zafarani and Mousavi (2014), the one developed by Kalkan and Gulkan (2004) showed the best fits for peak ground acceleration at period, $T = 0$~s. Our hazard analysis is based precisely on PGA at $T=0$~s, for rock sites. Although other GMPEs are more appropriate for other intensity measures and/or different periods, we limited our analysis to this particular intensity measure and thus our selection. We should note, for instance, that the GMPE of Ghasemi et al.~(2009) referenced by the reviewer was one of those evaluated by Zafarani and Mousavi (2014), but unfortunately this GMPE does not include an attenuation relationship for PGA. Other authors mistakenly use spectral accelerations at $T = 0.05$~s as estimation for PGA, but we preferred not to do so. It is also true that the GMPE of Kalkan and Gulkan (2004) was originally developed using data from Turkey, but that does not mean its applicability should be limited to Turkey alone. Several studies have shown before that GMPEs from specific regions can be used in other places in the world if shown to fit local GMPEs or data well (e.g., Campbell and Bozorgnia, 2006, 2015), and this is a common practice in hazard and risk analysis for regions with limited data or attenuation relationships. Last, the reason why we do not change the parameters $h$, $V_A$ or $V_S$ is because doing so would alter the fit of the GMPE with the data.
}

\comment{5}{%
The model provided is slightly different than a recently published work by Khodaverdian et al.~(2016) with some slightly different considerations for various models and parameters, which are not really physics-based information. The authors write: ``Admittedly, these are subjective decisions and any reasonable choice can be considered valid or within the margins of the associated epistemic uncertainty.'' The authors need to provide solid evidence why their model advances Khodavaerdian et al.~(2016).
}

\response{%
We started to work on this paper in the summer of 2015 and submitted the first version of the manuscript for review in the summer of 2016. By pure coincidence, and without our knowledge, Khodaverdian et al.~submitted the first version of their work to the Bulletin of the Seismological Society of America in the summer of 2015, and their work was published in the summer of 2016. We had no way of knowing about their work before it was published, but once we learned about their publication we took the time to delay our submission a couple of months to modify our manuscript so it could reflect on the differences between their work and ours. As summarized in the manuscript, the main difference in the application of the smoothed seismicity method is the treatment of the $b$-value and $M_{\mathrm{c}}$, which they computed and smoothed within a larger grid than the one used for $a$ values. We argue in the manuscript that their approach may lead to over-smoothing across seismic regions and this is, in our view, not the best alternative. We, however, as stated in the quote highlighted by the reviewer, admit that this is a subjective decision which can be considered within the margins of the epistemic uncertainty intrinsic to studies of this nature. We also highlight the fact that the study of Khodaverdian et al.~focuses primarily in the determination of the seismic parameters, while we take the analysis to the hazard level, not only for a single model but for a combination of models that account for uncertainty. In addition, we also note that we used a more complete catalog, which includes recent strong earthquakes in the 2012--2015 period not considered by Khodaverdian et al. That said, we do not pretend to claim we intended to advance Khodaverdian et al., we simply happened to be working on a similar subject around the same time, with some differences which warrant, in our view, the publication of alternative results.
}

\end{document}

### 2017-01-26 abstract.tex
cleaned files of revision comments and modified acknowledgments

--- 2016-10-20 abstract.tex
@@
 This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data.
-We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, \myrevision{and parts of other neighboring seismic zones that fall within our region of interest.
+We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, and parts of other neighboring seismic zones that fall within our region of interest.
 In the chosen approach, seismic events are not assigned to specific faults but assumed to be potential seismogenic sources distributed within regular grid cells.
@@
 Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region.
-In the analysis we consider uncertainties in the ground motion prediction equation, the seismic parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
-\myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
-We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions}.
+In the analysis we consider uncertainties in the ground motion prediction equation, the seismicity parameters and combine the resulting models using a logic tree.
+The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions.
+According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.
+We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed.
+We find our results to be helpful in understanding seismic hazard for northern Iran, but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions.
+
+% SUGGESTED CHANGE BY NAEEM, TO BE USED IN A DIFFERENT PLACE.
+%
+% A comprehensive study of seismic hazard also needs to include a geological and tectonic features (e.g., faults) of the study area.
+Although this study results are in a good agreement with studies based on different assumptions, and mostly gives average values due to the smoothing approach, they should not be considered as a final value in seismic design or seismic risk mitigation decisions}.

### 2017-01-26 acknowledge.tex
cleaned files of revision comments and modified acknowledgments

--- 2016-07-09 acknowledge.tex
@@
 
-The authors wish to express their gratitude to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advise on the use of the software.
+The authors wish to express their thanks to \myrevision{three anonymous reviewers and Editor in Chief Mariano Garc\'{i}a Fern\'{a}ndez whose insightful comments and candid suggestions greatly helped improve the original and revised manuscripts}.
+A message of gratitude is also extended to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advice on the use of the software.
 The authors also thank Andrzej Kijko at the University of Pretoria for providing access to the software for computing the seismicity parameters; and Mehdi Zare at the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for kindly providing the original catalog data and for his assistance in interpreting previous catalog information.
@@
 This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis.
-CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015--2016).
+CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunset Laws (SB 1510 and HB 1608, 2015--2016).

### 2017-01-26 attenuation.tex
done with results section
cleaned files of revision comments and modified acknowledgments

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/pdf/figure-08}
+    \includegraphics[width=0.8\textwidth]{figures/pdf/figure-08}
     \caption{Variation of horizontal peak ground acceleration (PGA) with distance.
@@
 The last piece in our hazard analysis process is the choice of an adequate attenuation relationship, or ground motion prediction equation (GMPE).
-This is a highly influential factor because it controls \myrevision{the intensity level at a particular site given an earthquake of a certain magnitude and source characteristics and at a particular distance from the location of interest.}
+This is a highly influential factor because it controls the intensity level at a particular site given an earthquake of a certain magnitude and source characteristics and at a particular distance from the location of interest.
 
@@
 For the specific case of PGA ($T = 0$ s), however, the best results were those obtained with the GMPEs introduced by \citet{Kalkan2004}, \citet{Chiou2008}, and \citet{Boore2008}.
-\myrevision{Other GMPEs with good prediction results for the region were those of \citet{Soghrat2012} and \citet{Akkar2010}}.
+Other GMPEs with good prediction results for the region were those of \citet{Soghrat2012} and \citet{Akkar2010}.
 
-\myrevision{A common approach used in seismic hazard analysis given the availability of multiple GMPEs is to address the associated epistemic uncertainty through a combination of the various GMPEs.
+A common approach used in seismic hazard analysis given the availability of multiple GMPEs is to address the associated epistemic uncertainty through a combination of the various GMPEs.
 However, in comparisons not shown here for brevity, we found that some of these GMPEs yielded mean predictions that were very close to each other.
@@
 In these and other similar comparisons we noticed that the GMPE proposed by \citet{Kalkan2004} led to centered predictions and we chose this particular GMPE as our central backbone.
-Based on it, we defined an upper and lower bound (plus and minus one standard deviation, $\sigma_{\ln y}$) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range defined by these bounds.}
+Based on it, we defined an upper and lower bound (plus and minus one standard deviation, $\sigma_{\ln y}$) as the two alternative GMPEs in our logic tree analysis, such that---for the most part---the amplitudes predicted by the mean values of other GMPEs fell within the range defined by these bounds.
 
@@
 %
-where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, \myrevision{and} $V_S$ is the shear wave velocity of the site of interest.
+where $Y$ is a ground motion parameter (here representing PGA), $V_A$ is a reference velocity in m/s, and $V_S$ is the shear wave velocity of the site of interest.
 In this equation, the distance $r$ is given by

### 2017-01-26 compilation.tex
cleaned files of revision comments and modified acknowledgments

@@
 	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
-	\caption{Location of events considered in the compiled seismic catalog \myrevision{for the complete region of interest}.
+	\caption{Location of events considered in the compiled seismic catalog for the complete region of interest.
 (a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}.
@@
 In the case of the historical seismicity catalog, the color fill indicates the year of the event.
-The borders of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in thin white lines, along with the light-gray shaded relief \myrevision{in the background.
-The dashed box indicates the effective region of interest}.}
+The borders of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in thin white lines, along with the light-gray shaded relief in the background.
+The dashed box indicates the effective region of interest.}
 	\label{fig:catalog}
@@
 In this study we adopt the catalog compiled for the Middle East by \citet{Zare2014} and augment it for our particular region of interest.
-This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project \myrevision{\citep[as mentioned in][]{Zare2014}}.
+This catalog is particularly relevant because it is published as part of the current effort by the Global Earthquake Model (GEM) partnership and the Earthquake Model of the Middle East (EMME) project \citep[as mentioned in][]{Zare2014}.
 It combines over 28 thousand records from 26 datasets with both historical and instrumental seismicity.
@@
 We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
-While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, \myrevision{and to help inform the Guten\-berg-Richter relationship}.
+While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, and to help inform the Guten\-berg-Richter relationship.
 By contrast, in the recent seismic hazard analysis done for Iran by \citet{Khodaverdian_2016_BSSA}, the authors used a similar catalog for events $M_w \geq 4$, but only included data through 2011, thus excluding the 2012 $M_w$ 6.4 Tabriz earthquake, which severely damaged the northeast part of the country.
@@
 Selection and declustering was also done in a manner consistent with the original catalog, using the me\-thod of \citet{Gardner1974}.
-\myrevision{The total number of earthquakes in the complete region of interest before decluttering are 10,441, with 971 foreshocks and 4,206 aftershocks}.
+The total number of earthquakes in the complete region of interest before decluttering are 10,441, with 971 foreshocks and 4,206 aftershocks.
 In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, augmented the catalog with $M>3$ events up to 2015 from IIEES, and finally declustered the new catalog removing foreshocks and aftershocks.

### 2017-01-26 completeness.tex
up to logic tree
almost done with section 8
done with results section
cleaned files of revision comments and modified acknowledgments

@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/pdf/figure-05.pdf}
+    \includegraphics[width=0.85\textwidth]{figures/pdf/figure-05.pdf}
     \caption{Normalized cumulative number of events and completeness year thresholds for each of the seismic zones considered within the region of interest, and for magnitude intervals of $\Delta M = 1$ between $M_w$ 3 and 7.
@@
 \end{figure*}
-
-\subsection{Completeness}
-
-An important aspect of seismic catalogs is their completeness.
-This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process.
-The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
-\myrevision{In this study, we use the start-year of completeness as a parameter in the estimation of the $a$-values in the smoothed seismic hazard analysis; and we use the completeness magnitude $M_c$ determined for each sub-catalog to compute the $b$-values and $M_{\max}$.}
-
-The start-year of completeness is commonly identified by inspection.
-A simple approach used by \citet{Frankel1995} and others is to select the year at which a plot of the cumulative number of events with respect to time becomes (or starts to resemble) a straight line.
-This is done for different magnitude ranges.
-Following this approach, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7.
-Our choices are illustrated in Fig.~\ref{fig:completeness}, where we show the normalized cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our selection of the year of completeness in each case.
-The values shown in this figure and those corresponding to the uniform model of the entire region of interest are summarized in Table \ref{tab:completeness}.
-For events $M_w>7$, in which case there are insufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
-
-% \myrevision{Both methods have been used extensively in previous studies}.
-% \myrevision{\citet{Moschetti2015} applied a combination of methods to study the long-term earthquake rate model for the Central and Eastern United States.}
-
-Determining the completeness magnitude $M_c$, on the other hand, is often done using simple numerical analysis in combination with data inspection.
-Two common approaches are the maximum curvature method and the goodness-of-fit test method.
-The maximum curvature method, or MAXC for simplicity, is widely used thanks to the fact that it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
-\citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
-\myrevision{In this study, we use the goodness-of-fit test method introduced by \citet{Wiemer2000} to compute $M_c$.
-We choose this method over the MAXC method because of ease of implementation and to have first-hand control over the final selection of $M_c$, rather than relying on the inner details of the ZMAP software.
-We compute} $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
-
-We defined these year intervals based on the data magnitude-time distribution (see Fig.~\ref{fig:scatter}) and the idea of distinguishing between historical, early-instrumental, and modern-instrumental catalogs.
-Having augmented the original catalog with $M>3$ earthquakes beginning in 2000 also influenced our choice of the intervals because at this point the uniformity of the catalog is altered.
-Last, we determined the $M_c$ values for the complete regional catalogs, but in this case, in order to maintain uniformity throughout time, we only considered $M>4$ events.
-\myrevision{According to \citet{Wiemer2000}, it is recommended to set $M_c$ at the point where the goodness-of-fit reaches 90 percent.
-However, not all goodness-of-fit plots satisfy this threshold and other considerations must be taken into account.} Fig.~\ref{fig:mc} illustrates the selection of $M_c$ for the case of the main three northern Iran seismic regions, and Table \ref{tab:completeness} presents the final selection of $M_c$ values for these and the other regions, including the uniform northern Iran model for the complete region of interest.
-
-\myrevision{We should note that both the choice of the start-years and that of the $M_c$ values are highly subjective.
-In the case of the start-years,} when choosing the points indicated in the plots shown in Fig.~\ref{fig:completeness}, we considered additional contributing information such as the history of instrumentation.
-It is well known that the number of recorded earthquakes increased considerably after the first deployment of seismic instruments in the early 1900s, and later with the establishment of the Worldwide Standardized Seismograph Network in 1961.
-We compared our choices with the year thresholds reported by \citet{Zare2014}, which we found to be consistently earlier than our preferred years of completeness.
-In this regard, our selection should lead to a slightly more conservative estimations of hazard.
-\myrevision{In the case of the $M_c$ values, on the other hand, we also considered the amount of data available above the chosen $M_c$ and the shapes of the cumulative number of events and goodness-of-fit plots.
-We tried to identify a consistent peak in the goodness-of-fit that coincided with the decay in cumulative number of events, while maintaining a large enough dataset size.
-For this case, we compared our choice of $M_c$ values with those} reported by \citet{Karimiparidari2013} and \citet{Khodaverdian_2016_BSSA} and found our choices to be in general good agreement, despite differences in the spatial definition of the seismic zones.
 
@@
 \end{figure*}
+
+\subsection{Completeness}
+
+An important aspect of seismic catalogs is their completeness.
+This characteristic is measured in terms of the start-year of completeness and the completeness magnitude, which are both parameters that are later used in the seismic analysis process.
+The start-year of completeness is the point in time at which catalog data exhibit a steady rate of event occurrence or record accumulation for a certain magnitude range, and the completeness magnitude ($M_c$) is the magnitude above which the seismic catalog of a region can be considered complete within a certain time period.
+In this study, we use the start-year of completeness as a parameter in the estimation of the $a$-values in the smoothed seismic hazard analysis; and we use the completeness magnitude $M_c$ determined for each sub-catalog to compute the $b$-values and $M_{\max}$.
+
+The start-year of completeness is commonly identified by inspection.
+A simple approach used by \citet{Frankel1995} and others is to select the year at which a plot of the cumulative number of events with respect to time becomes (or starts to resemble) a straight line.
+This is done for different magnitude ranges.
+Following this approach, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7.
+Our choices are illustrated in Fig.~\ref{fig:completeness}, where we show the normalized cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our selection of the year of completeness in each case.
+The values shown in this figure and those corresponding to the uniform model of the entire region of interest are summarized in Table \ref{tab:completeness}.
+For events $M_w>7$, in which case there are insufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.
+
+Determining the completeness magnitude $M_c$, on the other hand, is often done using simple numerical analysis in combination with data inspection.
+Two common approaches are the maximum curvature method and the goodness-of-fit test method.
+The maximum curvature method, or MAXC for simplicity, is widely used thanks to the fact that it has been implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.
+\citet{Zare2014}, for instance, used this software to identify $M_c$ values for the different regions of the Middle East.
+In this study, we use the goodness-of-fit test method introduced by \citet{Wiemer2000} to compute $M_c$.
+We choose this method over the MAXC method because of ease of implementation and to have first-hand control over the final selection of $M_c$, rather than relying on the inner details of the ZMAP software.
+We compute $M_c$ for different catalog-time intervals, namely 1800--1899, 1900--1999, 2000--2015, and for the complete regional catalogs.
+
+We defined these year intervals based on the data magnitude-time distribution (see Fig.~\ref{fig:scatter}) and the idea of distinguishing between historical, early-instrumental, and modern-instrumental catalogs.
+Having augmented the original catalog with $M>3$ earthquakes beginning in 2000 also influenced our choice of the intervals because at this point the uniformity of the catalog is altered.
+Last, we determined the $M_c$ values for the complete regional catalogs, but in this case, in order to maintain uniformity throughout time, we only considered $M>4$ events.
+According to \citet{Wiemer2000}, it is recommended to set $M_c$ at the point where the goodness-of-fit reaches 90 percent.
+However, not all goodness-of-fit plots satisfy this threshold and other considerations must be taken into account.
+Fig.~\ref{fig:mc} illustrates the selection of $M_c$ for the case of the main three northern Iran seismic regions, and Table \ref{tab:completeness} presents the final selection of $M_c$ values for these and the other regions, including the uniform northern Iran model for the complete region of interest.
+
+We should note that both the choice of the start-years and that of the $M_c$ values are highly subjective.
+In the case of the start-years, when choosing the points indicated in the plots shown in Fig.~\ref{fig:completeness}, we considered additional contributing information such as the history of instrumentation.
+It is well known that the number of recorded earthquakes increased considerably after the first deployment of seismic instruments in the early 1900s, and later with the establishment of the Worldwide Standardized Seismograph Network in 1961.
+We compared our choices with the year thresholds reported by \citet{Zare2014}, which we found to be consistently earlier than our preferred years of completeness.
+In this regard, our selection should lead to a slightly more conservative estimations of hazard.
+In the case of the $M_c$ values, on the other hand, we also considered the amount of data available above the chosen $M_c$ and the shapes of the cumulative number of events and goodness-of-fit plots.
+We tried to identify a consistent peak in the goodness-of-fit that coincided with the decay in cumulative number of events, while maintaining a large enough dataset size.
+For this case, we compared our choice of $M_c$ values with those reported by \citet{Karimiparidari2013} and \citet{Khodaverdian_2016_BSSA} and found our choices to be in general good agreement, despite differences in the spatial definition of the seismic zones.
 

### 2017-01-26 conclusions.tex
cleaned files of revision comments and modified acknowledgments

--- 2016-10-21 conclusions.tex
@@
 We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models.
-In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, \myrevision{including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach.
+In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach.
 In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it.
 We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
-In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}.
+In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region.
 While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers.
-Future work to improve the results presented here should consider \myrevision{other ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.
+Future work to improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and site effects.
+
+% NAEEM SUGGESTED CHANGE AT THE END
+
+% ...should consider generating random fault based on earthquake magnitude as well as considering actual faults, most recent developed ground motion measures of intensity such as response spectral accelerations for different periods and site effects.

### 2017-01-26 hazard.tex
cleaned files of revision comments and modified acknowledgments

@@
 In this study we use the smoothed seismicity method introduced by \citet{Frankel1995}.
-This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, \myrevision{and} Turkey \myrevision{\citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014,Kagan1994}}.
+This method has been used successfully in different regions around the world including Alaska, California, Hawaii, Italy, and Turkey \citep[e.g.,][]{Cao1996, Klein2001, Akinci2004, Kalkan2009, Moschetti2014, Kagan1994}.
 In it, the $b$-value is commonly assumed constant within a given seismic zone of ``homogeneous'' seismogenic characteristics, whereas $a$ is varied spatially according to the cataloged occurrence of earthquakes within and around the region.
@@
 It should be noted that in this process we convert the cumulative number of events to incremental values following \citet{Herrmann1977}.
-We also note that \myrevision{other authors have used alternative smoothing kernels \citep[e.g.,][]{Moschetti2015} and that a comparison of the smoothing length between different methods may require additional considerations about the function decay.
-Last, we highlight that} according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.
+We also note that other authors have used alternative smoothing kernels \citep[e.g.,][]{Moschetti2015} and that a comparison of the smoothing length between different methods may require additional considerations about the function decay.
+Last, we highlight that according to \citet{Frankel1995}, moderate earthquakes generally occur in areas where there have been significant numbers of events with magnitudes $M \geq 3$, thus our interest in having augmented the earthquake catalog for events above this threshold.
 
@@
 Different values of $c$ have been used in past studies, ranging between 10 and 50 km.
-\citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15~km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40~km, \myrevision{while \citet{Boyd2007} and \citet{Petersen2015} include spatial variability in the smoothing parameter}.
+\citet{Frankel1995} and \citet{Boyd2008} assumed a correlation distance of 50~km, \citet{Foteva2006} used 10 and 15~km, \citet{Barani2007} used 25~km, and \citet{Khodaverdian_2016_BSSA} used 40~km, while \citet{Boyd2007} and \citet{Petersen2015} include spatial variability in the smoothing parameter.
 According to \citet{Mirzaei1997}, determining an appropriate value of $c$ depends on the crustal structure of the region, the distribution of stations, and the number and quality of records.
-\myrevision{Other studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods \citep[e.g.,][]{Werner2011, Moschetti2015}}.
+Other studies employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods \citep[e.g.,][]{Werner2011, Moschetti2015}.
 We use an intermediate value of $c = 30$~km.
@@
 In turn, we consider the $b$-values to be constant within each seismic zone as delimited in Fig.~\ref{fig:iran}.
-Details about the calculation of the $b$-value for each zone are provided \myrevision{in the next section}.
+Details about the calculation of the $b$-value for each zone are provided in the next section.
 By contrast, in the recent work by \citet{Khodaverdian_2016_BSSA}, the authors computed spatially-variable $b$-values within large grid-cells of size 1\textdegree{} $\times$ 1\textdegree{} based on the average seismicity within a 200-km radius from each cell.
-While gridding $b$-values and considering the influence of neighboring large-size cells allows \myrevision{one} to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may bias the computation of $b$-values.
+While gridding $b$-values and considering the influence of neighboring large-size cells allows one to draw information from the background seismicity, it is unavoidable to have the contributing areas cross over seismic zones of different characteristics, which may bias the computation of $b$-values.
 Admittedly, these are subjective decisions and any reasonable choice can be considered valid or within the margins of the associated epistemic uncertainty.

### 2017-01-26 introduction.tex
cleaned files of revision comments and modified acknowledgments

@@
 It is confined between the convergent movements of the Arabian and Eurasian plates, and laterally trapped between the Arabian and eastern Asia-Minor to the west, and the Indian and Eurasian plates to the east \citep{Berberian_1981_Chap}.
-This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges \myrevision{(see Fig.~\ref{fig:iran})}.
-It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the \myrevision{eighth} century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
+This entrapment lifts the plateau and gives rise to the three major mountain ranges delimiting Iran's land, the Zagros mountain ranges running from the southeast to the northwest, the Alborz ranges to the north, and the east Iranian ranges (see Fig.~\ref{fig:iran}).
+It also defines the seismic activity of the region---one with a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eighth century---which has repeatedly damaged Iran's infrastructure and taken the lives of thousands.
 
@@
 
-\myrevision{Over the last three decades there have been multiple efforts to estimate the seismic parameters and seismic hazard of Iran, and improve the assessment of seismic risk in the country \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE, Khodaverdian_2016_BSSA}.
+Over the last three decades there have been multiple efforts to estimate the seismic parameters and seismic hazard of Iran, and improve the assessment of seismic risk in the country \citep[e.g.,][]{Tavakoli1999, Moinfar_2000_Chap, Ghodrati2003, Moinfar_2012_WCEE, Khodaverdian_2016_BSSA}.
 Altogether, these previous studies have helped improve the Iranian Code of Practice for Seismic Resistant Design of Buildings \citep{BHRC2014}.
@@
 The most recent of these studies, \citet{Khodaverdian_2016_BSSA}, presents an estimation of spatially-variable seismic parameters for Iran using an approach similar to the one we use here, but does not necessarily focus on hazard.
-Other previous efforts have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.}
+Other previous efforts have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.
 
-\myrevision{In the present study, we focus our attention on northern Iran.
+In the present study, we focus our attention on northern Iran.
 This region houses about 41 percent (32 million) of the total population of the country, with most living in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil.
 This region has suffered multiple devastating earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}, and has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}.
-Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults---even if believed inactive---by adopting new methodos and the latest available data.}
+Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults---even if believed inactive---by adopting new methodos and the latest available data.
 
-\myrevision{Most previous studies for northern Iran focus on particular locations based on specific seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.
+Most previous studies for northern Iran focus on particular locations based on specific seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability.
 By contrast, we use an approach based on the smoothed seismicity method introduced by \citet{Frankel1995}.
-We use regionally-based, smoothed seismic parameters derived from an up-to-date seismic catalog, and an appropriate attenuation relationship.} The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
+We use regionally-based, smoothed seismic parameters derived from an up-to-date seismic catalog, and an appropriate attenuation relationship.
+The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}.
 Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting.
-While we recognize that \myrevision{fault-based or geology-based earthquake recurrence estimates} can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
+While we recognize that fault-based or geology-based earthquake recurrence estimates can be more realistic and accurate, by choosing the smoothed seismicity method we seek to acknowledge the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored.
 In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}).
 In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone.
-We used both these models, \myrevision{and different levels of uncertainty in the seismic parameters and ground motion prediction equation, to combine the results using a logic tree} to interpret seismic hazard in northern Iran.
+We used both these models, and different levels of uncertainty in the seismic parameters and ground motion prediction equation, to combine the results using a logic tree to interpret seismic hazard in northern Iran.
 
 In the following sections we describe our region of interest in greater detail, review its associated tectonics and seismicity, and provide additional information about the adopted approach.
-\myrevision{Our results are summarized in terms of seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude \myrevision{$M_w \geq 4.5$}, which we analyze in light of similar estimates available in the literature.}
+Our results are summarized in terms of seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude $M_w \geq 4.5$, which we analyze in light of similar estimates available in the literature.

### 2017-01-26 logictree.tex
cleaned files of revision comments and modified acknowledgments

@@
-\section{\myrevision{Logic Tree}}
+\section{Logic Tree}
 
-\myrevision{As mentioned in previous sections, we address the uncertainties in our models, seismic parameters and selected ground motion prediction equation via a logic tree.
+As mentioned in previous sections, we address the uncertainties in our models, seismic parameters and selected ground motion prediction equation via a logic tree.
 Fig.~\ref{fig:logic} shows the complete set of branches at each of the tree nodes.
@@
 Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude of one standard deviation, $\sigma_{\ln y} = 0.612$.
-The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2008}.}
+The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2008}.
 
-\myrevision{Among other possible parameters for which we could have consider additional sources of uncertainty, we note that we did not consider the variability of the reference depth and seismic velocities in the selected GMPE because these were values fixed to satisfy the fit of the equation with data from northern Iran.
-Thus introducing uncertainty in these parameters would have been to the detriment of the prediction of PGA values.}
+Among other possible parameters for which we could have consider additional sources of uncertainty, we note that we did not consider the variability of the reference depth and seismic velocities in the selected GMPE because these were values fixed to satisfy the fit of the equation with data from northern Iran.
+Thus introducing uncertainty in these parameters would have been to the detriment of the prediction of PGA values.

### 2017-01-26 parameters.tex
cleaned files of revision comments and modified acknowledgments

--- 2016-10-18 parameters.tex
@@
-\section{Seismicity Parameters}
-\label{sec:params}
-
-Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3, version 3 \citep{Kijko_2004_HA3}.
-This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.
-HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{Karimiparidari2013, Khodaverdian_2016_BSSA}.
-
-The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell.
-We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell.
-This means each cell has a different $a$-value and thus the result is variable throughout our region of interest.
-On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
-We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog.
-\myrevision{ Regional maximum magnitude is estimated according to \citet{Kijko_1989_BSSA} method.
-Magnitude errors are distributed normally and $\beta$ and $\lambda$ are calculated simultaneously.
-We divide the} catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
-In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
-
-We obtain $b$ and $M_{\max}$ for two different models.
-In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
-We call this the \textit{R Model}.
-In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
-In the second model we consider the whole study area as a uniform seismic zone.
-We call it the \textit{U Model}.
-Admittedly, this assumption is somewhat \myrevision{less-realistfic} if considered from the point of view that different seismic zones \myrevision{may have different values of $b$ and $M_{max}$}.
-However, as it will be seen in the Results and Analysis section, computing results for this uniform model was useful because it allowed us to find a combination model computation of hazard in the region of interest as a means to \myrevision{account for} epistemic uncertainty.
-Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.
-\myrevision{
 \begin{table}%[t]
@@
 \end{table}
-}
+
 \begin{figure*}[t]
@@
     \includegraphics[width=\textwidth]{figures/pdf/figure-07}
-    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest.
+    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest following a truncated Gutenberg-Richter model.
 The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country.
@@
 \end{figure*}
+
+\section{Seismicity Parameters}
+\label{sec:params}
+
+Following the general approach described in the previous sections and using the information collected about the seismic catalog and its completeness, we computed the seismicity parameters $a$ and $b$, and the maximum magnitude $M_{\max}$ using the seismic hazard assessment software HA3, version 3 \citep{Kijko_2004_HA3}.
+This software implements the procedures developed by \citet{Kijko_1989_BSSA, Kijko_1992_BSSA}, and subsequent updates by \citet{Kijko_2004_PAG}.
+HA3 is widely used for this type of computations and is regarded as a reliable tool in seismic hazard analysis \citep[see, for instance,][]{Karimiparidari2013, Khodaverdian_2016_BSSA}.
+
+The $a$-value is estimated based on the completeness year, the correlation distance, and the number of events per grid cell.
+We assume magnitude increments of $\Delta M = 0.1$, count events with magnitude $M_w > 3$, and smooth the number of events for each cell.
+This means each cell has a different $a$-value and thus the result is variable throughout our region of interest.
+On the other hand, we consider the $b$-value and $M_{\max}$ to be constant within each of the seismic zones in our study area.
+We compute $b$ and $M_{\max}$ using HA3 and the information from the catalog.
+In HA3, the regional maximum magnitude is estimated according to \citet{Kijko_1989_BSSA} method.
+Magnitude errors are distributed normally and $b$ and $\lambda$ are calculated simultaneously.
+We divide the catalog in five sub-catalogs: one incomplete catalog for the prehistorical period before 1000, one incomplete catalog for the historical period between 1000 and 1799, one complete catalog for the early instrumental period between 1800 and 1899, and two complete catalogs for the instrumental periods between 1900 and 1999, and between 2000 and 2015.
+In this process we use the values of $M_c$ shown in Table \ref{tab:completeness}.
+
+We obtain $b$ and $M_{\max}$ for two different models.
+In the first model we obtain these parameters independently for each one of the five seismic zones influencing the hazard in northern Iran.
+We call this the \textit{R Model}.
+In it we obtain distinct values of $b$ and $M_{\max}$ for the main northern seismic zones of Azerbaijan, Alborz, and Kopeh Dagh, as well as for the Zagros and Central-East seismic zones contributing to our region of interest (see Fig.~\ref{fig:iran} for reference).
+In the second model we consider the whole study area as a uniform seismic zone.
+We call it the \textit{U Model}.
+While the U model may seem less realistic than the R model, if considering that different seismic zones may have different values of $b$ and $M_{max}$, computing hazard for both models allowed us to take into account the epistemic uncertainty associated to the seismic zonation of the region.
+We also consider uncertainty in the seismic parameters $b$ and $M_{max}$ via a logic tree, as explained ahead, and combined the results into separate R and U model branches and a final hazard model combining both R and U results.
+
+Table \ref{tab:params} shows the parameters $b$ and $M_{\max}$ obtained with HA3 for the five seismic zones in the R model and the corresponding ones for the U model, along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$; and Fig.~\ref{fig:annualp} shows the annual probability of exceedance as a function of earthquake magnitude.

### 2017-01-26 region.tex
cleaned files of revision comments and modified acknowledgments

@@
 These limits correspond to the area for which we will present results in subsequent sections.
-Our calculations, however, included data from a larger region with a \myrevision{2\textdegree{}-perimeter} as indicated in the figure.
+Our calculations, however, included data from a larger region with a 2\textdegree{}-perimeter as indicated in the figure.
 This is done to avoid the artificial decay effect that results from smoothing the seismicity along and near the edges of the effective region of interest and/or to provide a uniform contribution from the earthquakes surrounding the region \citep[see][]{Lapajne1997}.
@@
 
-At the \myrevision{northwest} of Iran, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault (NTF) system.
+At the northwest of Iran, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault (NTF) system.
 This system, shown in Fig.~\ref{fig:selected}a, is a complex northwest-trending structure with a predominant right-lateral, strike-slip faulting mechanism \citep{Berberian1999}.
@@
 In the 18th century, in particular, the NTF ruptured three times in a span period of 65 years, which included the $M$ 7.7 1721 Tabriz earthquake in the southeastern section, the $M$ 7.6 1780 Tabriz earthquake in the northwestern section, and the $M$ 6.3 1786 Marand-Mishu on the Mishu reverse fault and the Sufian segment of the NTF.
-According to \citet{Jones1834}, the \myrevision{1721 Tabriz earthquake had a surface rupture of more than 42 km and presented vertical separations of about 2 to 4 m}.
+According to \citet{Jones1834}, the 1721 Tabriz earthquake had a surface rupture of more than 42 km and presented vertical separations of about 2 to 4 m.
 The locations of these and other notable events, including the $M$ 5.5 1807 Tasuj and the $M$ 6.7 1879 South Bozqush earthquakes, are shown in Fig.~\ref{fig:selected}b.

### 2017-01-26 results.tex
cleaned files of revision comments and modified acknowledgments

@@
     \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U).
-\myrevision{Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}}
+Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}
     \label{fig:hazardcurve}
@@
 We call these the R and U models, respectively.
-Using these models we obtained hazard curves and expected PGA values for two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes \myrevision{$M_w \geq 4.5$}.
+Using these models we obtained hazard curves and expected PGA values for two probabilities of exceedance, at 2 and 10 percent in 50 years for events exceeding magnitudes $M_w \geq 4.5$.
 These probabilities correspond to return periods of 475 and 2,475 years.
@@
 
-Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events \myrevision{$M_w \geq 4.5$}, or conversely, \myrevision{$M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage}.
-In turn, the 2 and 10 percent probability of exceedance in a \myrevision{50-year} span are considered a standard practice in seismic design, and are the probabilities used in the Iranian building code \citep{BHRC2014}.
+Our choice for the threshold magnitude is based on the assumption that at the local scale (where a point of interest is close to the source), the hazard will be controlled by events $M_w \geq 4.5$, or conversely, $M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage.
+In turn, the 2 and 10 percent probability of exceedance in a 50-year span are considered a standard practice in seismic design, and are the probabilities used in the Iranian building code \citep{BHRC2014}.
 
@@
 
-Figure~\ref{fig:pga} shows the expected mean PGA values obtained for the R and U models, \myrevision{included the associated uncertainties in $b$, $M_{\max}$ and the GMPE.
-That is, the results in Fig.~\ref{fig:pga} correspond to the complete regional and uniform model branches in the logic tree for the different sub-models R2, R10, U2 and U10}.
+Figure~\ref{fig:pga} shows the expected mean PGA values obtained for the R and U models, included the associated uncertainties in $b$, $M_{\max}$ and the GMPE.
+That is, the results in Fig.~\ref{fig:pga} correspond to the complete regional and uniform model branches in the logic tree for the different sub-models R2, R10, U2 and U10.
 As can be expected, the highest PGA values are associated with the R2 and U2 models, and the lowest with the R10 and U10 models.
-For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Azerbaijan region \myrevision{on the west side of the North Tabriz Fault and also on and around the border of the Kopeh Dagh and Alborz tectonic seismic regions on the east side of the North Alborz Fault.
+For the R model results shown in Fig.~\ref{fig:pga}a, the highest levels of expected ground motion occur in the Azerbaijan region on the west side of the North Tabriz Fault and also on and around the border of the Kopeh Dagh and Alborz tectonic seismic regions on the east side of the North Alborz Fault.
 We also observe higher hazard in the Alborz region in a small area east from the Mosha Fault.
-On the other hand, the results shown in Fig.~\ref{fig:pga}b for the U model indicate that in addition to these areas, there are also large expected ground motions in the Zagros seismic zone and increased PGA results in various areas within the Central East seismic region}.
+On the other hand, the results shown in Fig.~\ref{fig:pga}b for the U model indicate that in addition to these areas, there are also large expected ground motions in the Zagros seismic zone and increased PGA results in various areas within the Central East seismic region.
 
@@
 In this figure, positive values indicate that the U models have larger mean PGA values than the R models.
-\myrevision{As it can be seen, this is true practically throughout the whole region at very low levels, but more predominantly in the north-west region at a moderate level of up to 0.2 g and increasingly so in the Zagros region, where the differences between about 0.2 and 0.45 g.
-The higher results in the U model occurred because of higher $M_{max}$ and lower $b$ values in comparison with the R model}.
+As it can be seen, this is true practically throughout the whole region at very low levels, but more predominantly in the north-west region at a moderate level of up to 0.2 g and increasingly so in the Zagros region, where the differences between about 0.2 and 0.45 g.
+The higher results in the U model occurred because of higher $M_{max}$ and lower $b$ values in comparison with the R model.
 
@@
 
-\myrevision{With this in mind, and knowing that no one model (R or U) can be considered uniquely correct, we consider now the combination of both models as presented for the complete logic tree in Fig.~\ref{fig:logic}.
-We refer to this as the (R,U) model and the results are shown in Fig.~\ref{fig:pga.ru.std}, again in the form of expected mean PGA values for 2 and 10 percent in 50 years.}
+With this in mind, and knowing that no one model (R or U) can be considered uniquely correct, we consider now the combination of both models as presented for the complete logic tree in Fig.~\ref{fig:logic}.
+We refer to this as the (R,U) model and the results are shown in Fig.~\ref{fig:pga.ru.std}, again in the form of expected mean PGA values for 2 and 10 percent in 50 years.
 
-\myrevision{The combined (R,U) model reflects the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as that of the major faults shown in Fig.~\ref{fig:selected}a, but it also reflects the influence that small earthquakes have on the seismicity hazard of the region}.
+The combined (R,U) model reflects the distribution of the region's seismicity shown in Fig.~\ref{fig:catalog} as well as that of the major faults shown in Fig.~\ref{fig:selected}a, but it also reflects the influence that small earthquakes have on the seismicity hazard of the region.
 It displays well the contribution of the North Tabriz Fault system in the Azerbaijan region as well as the contribution of the North Alborz fault in the Alborz region and that of the different faults in the Kopeh Dagh region.
-In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2 model results, where the expected accelerations are of the order of 1.0 g to the northwest of \myrevision{the} city of Tabriz.
+In Fig.~\ref{fig:pga.ru.std}, the highest PGAs are observed in the (R,U)2 model results, where the expected accelerations are of the order of 1.0 g to the northwest of the city of Tabriz.
 These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects or other related conditions which may often contribute to mitigating peak accelerations.
 
-\myrevision{We also note that the overall distribution of mean PGA agrees with the recent study by \citet{Khodaverdian_2016_BSSA}.
+We also note that the overall distribution of mean PGA agrees with the recent study by \citet{Khodaverdian_2016_BSSA}.
 However, their results are in general slightly lower than ours.
@@
 For example, in the case of the $b$ values, \citet{Khodaverdian_2016_BSSA} reported large variations between 0.56 and 1.27, where over 50 percent of the grid points had $b$ values greater than 1; whereas in our study the $b$ values observe a narrow range of variation between 0.93 and 1.15.
-In this regard we should note that \citet{Khodaverdian_2016_BSSA} computed the seismicity parameters for each grid point considering the contributions within a circular area of radius 200 m, whereas we considered a uniform seismicity parameters for each region and account for the uncertainty in the difference between regions via the combination of the R and U models.}
+In this regard we should note that \citet{Khodaverdian_2016_BSSA} computed the seismicity parameters for each grid point considering the contributions within a circular area of radius 200 m, whereas we considered a uniform seismicity parameters for each region and account for the uncertainty in the difference between regions via the combination of the R and U models.
 
-\myrevision{Altogether, on average, we found our results to be in good agreement with other previous results.
+Altogether, on average, we found our results to be in good agreement with other previous results.
 For the city of Urmia, for instance, we obtained a expected PGA of 0.24 g, which is slightly lower than values obtained by \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for a 10 percent probability of exceedance in 50 years.
@@
 For the city of Tabriz, our results match with those obtained by \citet{BHRC2014} and are within the range of values computed by \citet{Zare2012}, for a 10 percent probability.
-These and other similar comparisons are summarized in Table \ref{tab:pga}, where we show our results and those of other previous studies for selected cities in northern Iran.}
+These and other similar comparisons are summarized in Table \ref{tab:pga}, where we show our results and those of other previous studies for selected cities in northern Iran.
 
-\myrevision{As mentioned before, overall, our results are close to or within the ranges provided by most previous studies}.
+As mentioned before, overall, our results are close to or within the ranges provided by most previous studies.
 The only noticeable exceptions are the results of \citet{Golara2014}, whose expected PGA values are significantly higher than the rest.
-\myrevision{One possible explanation for the higher values in \citet{Golara2014} is their use of the maximum credible earthquake as the value for $M_{\max}$.
+One possible explanation for the higher values in \citet{Golara2014} is their use of the maximum credible earthquake as the value for $M_{\max}$.
 The maximum credible earthquake is the largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, based on geologic and seismic data.
-Therefore, it is often higher than historical documented observations or instrumental data-driven estimations of $M_{\max}$}.
+Therefore, it is often higher than historical documented observations or instrumental data-driven estimations of $M_{\max}$.
 
-Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA\myrevision{, also known as hazard curves.
+Following the comparisons shown in Table \ref{tab:pga}, we looked into the more complete picture of the annual probabilities of exceedance as functions of PGA, also known as hazard curves.
 The results are shown in Fig.~\ref{fig:hazardcurve} for six of the main cities in northern Iran including the R, U, and the combined (R,U) models.
 Although for these particular cities, the differences are minor in general, they exemplify the results one can obtain at particular locations.
-Here, the more clear differences are observed for the city of Urmia, where the (R,U) model approaches the R model for low values of PGA and then evolves closer to the U model for higher values of PGA}.
+Here, the more clear differences are observed for the city of Urmia, where the (R,U) model approaches the R model for low values of PGA and then evolves closer to the U model for higher values of PGA.
 
@@
 
-\myrevision{Last, we concentrate our attention on the results for the capital city of Tehran.
+Last, we concentrate our attention on the results for the capital city of Tehran.
 We compare the hazard curve we obtained for Tehran with those computed by \citet{Ghodrati2003} and \citet{Boostan2015}.
@@
 The results of the comparison are shown in Fig.~\ref{fig:tehran}.
-This figure also includes comparisons with the value-ranges of other studies included in Table \ref{tab:pga} for 2 and 10 percent probability of exceedance in 50 years.}
+This figure also includes comparisons with the value-ranges of other studies included in Table \ref{tab:pga} for 2 and 10 percent probability of exceedance in 50 years.
 
-\myrevision{As we discussed earlier, and as it can be seen based on the associated uncertainty carried by the GMPE (shaded area), our model accounts fairly well the expected ground motion level of variability.
+As we discussed earlier, and as it can be seen based on the associated uncertainty carried by the GMPE (shaded area), our model accounts fairly well the expected ground motion level of variability.
 In general, for the city of Tehran, the mean results of our R, U and (R,U) models are very similar for all values.
@@
 In other words, results from all other studies are below and above our results for the GMPE+Unc.~and GMPE--Unc.~models in our logic tree analysis.
-This provides confidence in the approach followed here based on a centered backbone GMPE and the ideas put forward by \citet{Atkinson2014}.}
+This provides confidence in the approach followed here based on a centered backbone GMPE and the ideas put forward by \citet{Atkinson2014}.

### 2017-01-26 attenuation.tex
completed changes based on reviewer 3 comments and our response

@@
 where $r_{\mathit{cl}}$ is the horizontal distance to the site of interest and $h$ is a reference fictitious depth, both given in km.
-According to \citet{Kalkan2004}, in the case of $Y$ representing PGA, the coefficients $b_1$, $b_2$, $b_3$, $b_5$ and $b_V$ are
+\myrevision{We should note here that given the fact that the smoothed seismicity method assumes all earthquakes as individual point sources, $r_{\mathit{cl}}$ is the same as the epicentral distance.} According to \citet{Kalkan2004}, in the case of $Y$ representing PGA, the coefficients $b_1$, $b_2$, $b_3$, $b_5$ and $b_V$ are
 %
@@
 Therefore, to be consistent with the latter, we set the models in the hazard analysis to compute ground motion intensities (i.e., PGAs) at distances no greater than 200 km.
+\myrevision{We should also note that the values of $V_A$, $V_S$ and $h$ were kept constant throughout the calculations for this study.
+This was done because these are the values for which the attenuation relationship showed good agreement with PGA data from northern Iran at rock sites.
+While it would be tempting to adjust these values to the specific site conditions of each grid point, or to match the hypocentral depth of each earthquake in the catalog, doing this would effectively modify the goodness-of-fit of the GMPE with the data, and thus make the predictions inaccurate.}

### 2017-01-26 compilation.tex
completed changes based on reviewer 3 comments and our response

@@
 For the particular case of our region of interest, the catalog prepared by \citet{Zare2014} included events $M_w \geq 4$ between 550 B.C.~and 2006.
-We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
+We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015 \myrevision{(no formal catalog exists with earthquakes $M_w \leq 4$ prior to 2000)}.
 While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, and to help inform the Guten\-berg-Richter relationship.

### 2017-01-26 conclusions.tex
completed changes based on reviewer 3 comments and our response

@@
 We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
-In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region.
-While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers.
-Future work to improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and site effects.
+In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it also led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region.
+While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers \myrevision{or specific sites of interest near notable faults with a history of damaging earthquakes}.
+Future work to \myrevision{complement and} improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and site effects\myrevision{, as well as alternative ground motion prediction equations suitable for northern Iran.
+All things considered, we recognize that additional efforts are necessary to obtain a more robust estimate of hazard, especially for specific areas of interest.
+In this regard, future efforts should be directed to the combination of studies like this for the contribution of the background seismicity with more targeted studies considering extended source models for areas near major fault lines.
+It should also be noted that this is not a final assessment of the seismic hazard of the region, and decisions regarding seismic design or risk mitigation plans should consider this as well as other studies.}
 

### 2017-01-26 introduction.tex
completed changes based on reviewer 3 comments and our response

@@
 There is, however, room for improvement.
-The most recent of these studies, \citet{Khodaverdian_2016_BSSA}, presents an estimation of spatially-variable seismic parameters for Iran using an approach similar to the one we use here, but does not necessarily focus on hazard.
-Other previous efforts have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.
+The most recent of these studies, \citet{Khodaverdian_2016_BSSA}, presents an estimation of spatially-variable seismic parameters for Iran using an approach similar to the one we use here, but does not necessarily focus on hazard\myrevision{, and does not include the latest available data for the region}.
+Other previous efforts \myrevision{also} have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.
+\myrevision{By contrast, our analysis presents a regional perspective which is likely to be more useful for rural areas that are usually not the subject of specialized studies on hazardous faults}.
 

### 2017-01-26 new-response.tex
completed changes based on reviewer 3 comments and our response

@@
 We were a little intrigued by the strict criticism of this third reviewer, but at the same time understood the motivation behind his/her comments.
-While we appreciated very much your candid reaction this this review---given our response to the initial evaluation---, we thought that in addition to following your advise about how to handle it (through minor modifications of form and language), it was still appropriate for us to share with you our views about some of these criticisms.
+While we appreciated very much your candid reaction to this third review---given our response to the two initial ones---, we thought that in addition to following your advise about how to handle it (through minor modifications of form and language), it was still appropriate for us to share with you our views about some of these criticisms.
 You will also find enclosed our responses, which we hope you will appreciate.
+The latest changes to the manuscript are highlighted in the annotated version.
 
@@
 
+\vspace{3ex}
 \comment{1}{%
@@
 
+Changes in the manuscript motivated by the points raised by the reviewer are highlighted in the annotated version of the manuscript, which reflect our view towards as expressed in the responses above.
+
 \end{document}

### 2017-01-26 conclusions.tex
final version re-submitted

@@
 While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers \myrevision{or specific sites of interest near notable faults with a history of damaging earthquakes}.
-Future work to \myrevision{complement and} improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and site effects\myrevision{, as well as alternative ground motion prediction equations suitable for northern Iran.
+Future work to \myrevision{complement and} improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and \myrevision{site conditions, as well as alternative ground motion prediction equations suitable for northern Iran.
 All things considered, we recognize that additional efforts are necessary to obtain a more robust estimate of hazard, especially for specific areas of interest.
@@
 It should also be noted that this is not a final assessment of the seismic hazard of the region, and decisions regarding seismic design or risk mitigation plans should consider this as well as other studies.}
-
-% NAEEM SUGGESTED CHANGE AT THE END
-
-% ...should consider generating random fault based on earthquake magnitude as well as considering actual faults, most recent developed ground motion measures of intensity such as response spectral accelerations for different periods and site effects.

### 2017-02-05 acknowledge.tex
final submission for production as accepted

@@
 
-The authors wish to express their thanks to \myrevision{three anonymous reviewers and Editor in Chief Mariano Garc\'{i}a Fern\'{a}ndez whose insightful comments and candid suggestions greatly helped improve the original and revised manuscripts}.
+The authors wish to express their thanks to three anonymous reviewers and Editor in Chief Mariano Garc\'{i}a Fern\'{a}ndez whose insightful comments and candid suggestions greatly helped improve the original and revised manuscripts.
 A message of gratitude is also extended to Art Fran\-kel at the U.S.~Geological Survey (USGS) for providing access to the Smoothed Probabilistic Seismic Hazard Analysis software and to Morgan Moschetti, also at the USGS, for providing advice on the use of the software.

### 2017-02-05 attenuation.tex
final submission for production as accepted

--- 2017-01-26 attenuation.tex
@@
 where $r_{\mathit{cl}}$ is the horizontal distance to the site of interest and $h$ is a reference fictitious depth, both given in km.
+We should note here that given the fact that the smoothed seismicity method assumes all earthquakes as individual point sources, $r_{\mathit{cl}}$ is the same as the epicentral distance.
 According to \citet{Kalkan2004}, in the case of $Y$ representing PGA, the coefficients $b_1$, $b_2$, $b_3$, $b_5$ and $b_V$ are
@@
 Therefore, to be consistent with the latter, we set the models in the hazard analysis to compute ground motion intensities (i.e., PGAs) at distances no greater than 200 km.
+We should also note that the values of $V_A$, $V_S$ and $h$ were kept constant throughout the calculations for this study.
+This was done because these are the values for which the attenuation relationship showed good agreement with PGA data from northern Iran at rock sites.
+While it would be tempting to adjust these values to the specific site conditions of each grid point, or to match the hypocentral depth of each earthquake in the catalog, doing this would effectively modify the goodness-of-fit of the GMPE with the data, and thus make the predictions inaccurate.

### 2017-02-05 compilation.tex
final submission for production as accepted

--- 2017-01-26 compilation.tex
@@
 For the particular case of our region of interest, the catalog prepared by \citet{Zare2014} included events $M_w \geq 4$ between 550 B.C.~and 2006.
-We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015.
+We took information from the catalog up to December 1999, and augmented it by adding newer and more complete data from IIEES for events $M \geq 3$ between January 2000 and December 2015 (no formal catalog exists with earthquakes $M_w \leq 4$ prior to 2000).
 While we recognize that earthquakes in the range $3 \leq M_w \leq 4$ are unlikely to cause structural damage, we include them as a means to feed the model with information about epicentral locations with potential for future larger magnitude earthquakes \citep{Kafka_2000_BSSA}, and to help inform the Guten\-berg-Richter relationship.

### 2017-02-05 conclusions.tex
final submission for production as accepted

@@
 In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it.
-We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
+We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for northern Iran than previous studies because of the coverage area and our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes.
+
 In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it also led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region.
-While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers \myrevision{or specific sites of interest near notable faults with a history of damaging earthquakes}.
-Future work to \myrevision{complement and} improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and \myrevision{site conditions, as well as alternative ground motion prediction equations suitable for northern Iran.
+While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers or specific sites of interest near notable faults with a history of damaging earthquakes.
+
+Future work to complement and improve the results presented here should consider other ground motion measures of intensity such as response spectral accelerations for different periods and site conditions, as well as alternative ground motion prediction equations suitable for northern Iran.
 All things considered, we recognize that additional efforts are necessary to obtain a more robust estimate of hazard, especially for specific areas of interest.
-In this regard, future efforts should be directed to the combination of studies like this for the contribution of the background seismicity with more targeted studies considering extended source models for areas near major fault lines.
-It should also be noted that this is not a final assessment of the seismic hazard of the region, and decisions regarding seismic design or risk mitigation plans should consider this as well as other studies.}
+In this regard, future efforts should combine studies like this (for the contribution of the background seismicity) with more targeted studies considering extended source models (for areas near major fault lines).
+It should also be noted that this is not a final assessment of the seismic hazard of the region, and decisions regarding seismic design or risk mitigation plans should consider this as well as other studies.

### 2017-02-05 introduction.tex
final submission for production as accepted

--- 2017-01-26 introduction.tex
@@
 There is, however, room for improvement.
-The most recent of these studies, \citet{Khodaverdian_2016_BSSA}, presents an estimation of spatially-variable seismic parameters for Iran using an approach similar to the one we use here, but does not necessarily focus on hazard.
-Other previous efforts have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.
+The most recent of these studies, \citet{Khodaverdian_2016_BSSA}, presents an estimation of spatially-variable seismic parameters for Iran using an approach similar to the one we use here, but does not necessarily focus on hazard, and does not include the latest available data for the region.
+Other previous efforts also have outdated catalogs, use fault-centered hazard analyses, or focus on particular locations or cities.
+By contrast, our analysis presents a regional perspective which is likely to be more useful for rural areas that are usually not the subject of specialized studies on hazardous faults.
 
